### 2014-10-19 prepdata/summary/summary.tex
summary source file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\synctex=1
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{bm}

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Data Preparation\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yifan Zhou} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title
\section{Centroid of Primary Star}
4 methods were tested to locate the centroid of the primary objects
for all 78 cosmic ray removed images of ABPIC-B. I compared the
4 sets of results for each method in order to determine the best
method in this situation where the image of the primary star is
slightly saturated.\par

\subsection{Method Introduction}

\begin{enumerate}
\item \textbf{\texttt{CNTRD.PRO}}\\
  IDL routnine \texttt{CNTRO.PRO} locates the position where the X
  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
  can be adjusted with parameter \texttt{EXTENDBOX}.\par
\item 
\end{enumerate}

\end{document}

### 2014-10-19 prepdata/plot_shiftchange.py
cross correlation and WCS results modified, plots changed accordingly

@@ -1,0 +1,25 @@
+#! /usr/bin/env python
+import numpy as np
+import matplotlib.pyplot as plt
+
+if __name__ == "__main__":
+    fn = 'cubic3_shiftchange.dat'
+    fn1 = 'fshift_shiftchange.dat'
+    stepLength, abs_change, flux_change = np.loadtxt(fn, unpack = True, comments = ';')
+    stepLength, abs_change1, flux_change1 = np.loadtxt(fn1, unpack = True)
+    fig, axes = plt.subplots(figsize = (8, 4), ncols = 2)
+    axes[0].plot(stepLength, abs_change, label = 'cubic3')
+    axes[0].plot(stepLength, abs_change1, label = 'fshift')
+    axes[0].set_title('RMS change')
+    axes[1].plot(stepLength, flux_change, label = 'cubic3')
+    axes[1].plot(stepLength, flux_change1, label = 'fshift')
+    axes[1].set_title('Flux change')
+    for ax in axes:
+        ax.legend(loc = 'best')
+        ax.set_xlabel('Shift length (pixels)')
+        ax.set_ylabel('value change per pixel')
+
+    fig.tight_layout()
+    plt.savefig('test_shift.pdf')
+    plt.close(fig)
+    

### 2014-10-21 prepdata/summary/summary.tex
summary tex files

@@
 \usepackage{amsmath,amsfonts,amsthm} % Math packages
+%\usepackage[nolists, nomarkers]{endfloat}
+\usepackage{hyperref}
 \usepackage{bm}
-
+\usepackage{graphicx}
+\usepackage[section]{placeins}
 \usepackage{sectsty} % Allows customizing section commands
@@
 
-\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
+\setlength\parindent{0pt} % Removes all indentation from paragraphs -
+                          % comment this line for an assignment with
+                          % lots of text
+\setlength\parskip{12pt}
 
@@
 \maketitle % Print the title
+\section{Summary}
+\begin{enumerate}
+\item Cross correlation has the best performance for locating the
+  centroids of star images.
+\item Bicubic interpolation generates smaller RMS fluctuation
+  comparing to \texttt{FSHIFT.pro} when shift images, but does not
+  strictly obey flux conservation. \texttt{FSHIFT.pro} strictly keeps
+  the conservation of flux. Bicubic interpolation causes artifacts
+  around the star images.
+\end{enumerate}
+
 \section{Centroid of Primary Star}
-4 methods were tested to locate the centroid of the primary objects
-for all 78 cosmic ray removed images of ABPIC-B. I compared the
-4 sets of results for each method in order to determine the best
-method in this situation where the image of the primary star is
-slightly saturated.\par
+4 methods to locate the centroid of the primary objects were tested
+for all 78 cosmic ray removed images of ABPIC-B. I compared the 4 sets
+of results in order to determine the best method to find star image
+centroid in this situation where the image is slightly saturated.\par
 
@@
 \begin{enumerate}
-\item \textbf{\texttt{CNTRD.PRO}}\\
-  IDL routnine \texttt{CNTRO.PRO} locates the position where the X
+\item \texttt{CNTRD.PRO}\\
+  IDL routine \texttt{CNTRO.PRO} locates the position where the X
   and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
   can be adjusted with parameter \texttt{EXTENDBOX}.\par
-\item 
+\item \texttt{GCNTRD.PRO}\\
+  IDL routine \texttt{GCNTRD.PRO} fits the star image with a 2D-Gaussian
+  function to search for centroid. The search area cannot be defined
+  in this routine. \texttt{GCNTRD.pro} is likely to fail when the
+  initial guess of centroid coordinates are far away from the true
+  values. This is inconvenient for pipeline scenario, where images
+  of different dithering positions are assigned with same initial
+  values for fitting. In practice, I ran \texttt{CNTRD.PRO} before
+  \texttt{GCNTRD.PRO} to provide initial values for Gaussian fitting.\par
+\item Cross Correlation\\
+  Calculate the cross correlation value to align images. The images
+  taken with different rolling angle were treat separately. Images
+  taken in 1st, 3th, and 5th orbits were calculated cross correlation
+  with the first image in 1st orbit and images taken in 2nd, 4th, and
+  6th orbits with first image in 2nd orbit.\par
+ \item World Coordinate System(WCS)\\
+   Use WCS to align every image. The treatment with different rolling
+   angles is the same as cross correlation method. Centroids were
+   calculated with IDL routine \texttt{XYXY.pro}.\par
 \end{enumerate}
 
+\subsection{Result Comparison}
+Figure \ref{fig:x_off} and \ref{fig:y_off} demonstrates the
+distributions of centroid offsets of \texttt{GCNTRD.pro}, cross
+correlation, and WCS relative to the \texttt{CNTRD.pro} method in $x$
+and $y$ direction. \par
+
+According to the two plots, most of results calculated with all four
+methods are constrained within $\pm 0.2$ pixels. Both in $x$ and $y$
+directions, the histograms of \texttt{GCNTRD.pro} offsets have a
+fairly strange shape, while the distributions of cross correlation and
+WCS methods' offsets show a Gaussian like shape. In $x$-direction, the
+distributions of cross correlation and WCS have similar behavior that
+the centers of two histograms both have $\sim -0.1$ pixels offset. In
+$y$ direction, histogram of cross correlation demonstrates that the
+results for cross correlation and \texttt{CNTRD.pro} are well
+agreed. The histogram of WCS is skewed and has a $\sim -0.1$ pixels
+offset.\par
+
+To sum, \texttt{GCNTRD.pro} method has the worst performance. In
+$x$-direction, the results for cross correlation and WCS agrees well
+and in $y$-direction the results for cross correlation and
+\texttt{CNTRD.pro} agrees well. Thus cross correlation method performs
+best.\par
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{x_off}
+  \caption{$x$-direction offset histogram}
+  \label{fig:x_off}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{y_off}
+  \caption{$y$-direction offset histogram}
+  \label{fig:y_off}
+\end{figure}
+
+\section{Image shift and interpolation algorithm}
+
+I tested two image shift methods that uses two different interpolation
+algorithms. The two algorithms are bicubic interpolation and bilinear
+interpolation(used by  IDL routine \texttt{FSHIFT.pro}).\par
+
+To evalueate the two shift methods, the image is shifted in a random direction
+with a specific length and then shifted back. Both the root mean
+square and mean flux change between the original image and the
+modified image  will be calculated as following:
+\begin{align}
+  &\Delta_{\mathrm{rms}} = \frac{\sqrt{(\mathrm{img}_{0} -
+      \mathrm{img_{shifted}})^{2}}}{N_{\mathrm{pixels}}}\\
+  &\bar{\Delta} = \frac{\mathrm{img}_{0} - \mathrm{img_{shifted}}}{N_{\mathrm{pixels}}}
+\end{align}
+
+The results are demonstrated with figure \ref{fig:shifted}.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{test_shift}
+  \caption{Root mean square and mean flux change betwenn the original image and the modified image as a function of shift length.}
+  \label{fig:shifted}
+\end{figure}
+\begin{enumerate}
+\item bicubic interpolation comes up with a smaller RMS change, thus
+  the error generated by image shift will be smaller with a bicubic interpolation.
+\item \texttt{FSHIFT.pro} strictly keeps flux conserved, while bicubic
+  interpolation ends up with a $\sim \pm 0.003$ per pixel change in flux.
+\item bicubic interpolation will generate ringing artifacts(figure \ref{fig:ringing})
+\end{enumerate}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.6\textwidth]{interpolated}
+  \caption{Ringing artifacts generated by bicubic interpolation.}
+  \label{fig:ringing}
+\end{figure}
 \end{document}

### 2014-11-03 summary/AperturePhot1/aperPhotSummary.tex
start writing summary doc on aperture photometry

--- 2014-10-19 prepdata/summary/summary.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Data Preparation\\ % The assignment title
+\huge Cross Correlation Test and Preliminary Aperture Photometry Result\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 \maketitle % Print the title
-\section{Centroid of Primary Star}
-4 methods were tested to locate the centroid of the primary objects
-for all 78 cosmic ray removed images of ABPIC-B. I compared the
-4 sets of results for each method in order to determine the best
-method in this situation where the image of the primary star is
-slightly saturated.\par
+\section{Summary}
+\begin{enumerate}
+\item Cross Correlation method can align images with the saturated
+  primary star centroid as precise as $\sim 0.01$ pixels, which is far
+  better than the precision of IDL \texttt{cntrd.pro} or
+  \texttt{gcntrd.pro} which is more than $\sim 0.2$ pixels. According
+  to the residual image patterns, cross correlation alignment has
+  better performance tan WCS alignment.
+\item Aperture photometry for secondary object in ABPIC system is
+  measured. The light curves are very similar to Glenn's
+  measurement. However, the light curves for two filters, F125W and
+  F160W agree with each other better in my measurement.
+\item Considering only statistical uncertainties (counting errors) and
+  fluctuation in the background, a rough estimate gives a result of
+  0.3\% for relative uncertainty for one
+  photometry measurement.
 
-\subsection{Method Introduction}
+\end{enumerate}
+\section{Image Alignment}
+\subsection{Alignment Precision Test}
+\subsection{The Modification for IDL \texttt{crosscorr} Routine}
+\subsection{PSF subtraction result}
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{cc_example}
+  \includegraphics[width=\textwidth]{wcs_example}
+  \caption{PSF subtraction comparison}\label{fig:subcomp}
+\end{figure}
+\section{Aperture Photometry Result}
+\subsection{Light Curves}
 
-\begin{enumerate}
-\item \textbf{\texttt{CNTRD.PRO}}\\
-  IDL routnine \texttt{CNTRO.PRO} locates the position where the X
-  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
-  can be adjusted with parameter \texttt{EXTENDBOX}.\par
-\item 
-\end{enumerate}
+The light curve measurements for both absolute fluxes and relative
+fluxes are shown in Figure \ref{fig:lightcurve}. Figure
+\ref{fig:glenn} is Glenn's preliminary measurements. The lower plot in
+figure \ref{fig:lightcurve} is very similar to figure
+\ref{fig:glenn}. However, in figure \ref{fig:glenn}, the light curves
+for F125W and F160W show considerable discrepancies in 5th and 6th
+orbits. However in my measurement, the two curves agree better. Apart
+from this, the most prominent features are shown in both light
+curves, e.g. the light curves are lower in 2nd orbit and the
+discrepancy at start of the 3rd orbit.
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{fluxcurve_aper_05}
+  \includegraphics[width=0.8\textwidth]{relativefluxcurve_aper_05}
+  \caption{Filter F125W and F160W light curves. Upper images shows the
+    curve for absolute flux (count per second) changing with time. The
+    mean values for both light curves are plotted with gray dashed
+    lines. In the lower image, two light curves are normalized with
+    the mean value of itself.}
+  \label{fig:lightcurve}
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centering
+    \includegraphics[width=0.8\textwidth]{ABPIC_DELTA_PERCENT_INITIAL}
+    \caption{Glenn's preliminary measurement}
+    \label{fig:glenn}
+  \end{figure}
+
+\subsection{Error Estimation}
+Considering statistical uncertainty and fluctuation of background sky,
+the relative error for one aperture photometry measurement is below
+0.3\% according to my estimation. The error estimation procedure is
+explained as following.\par
+
+Statistical uncertainty:
+\begin{equation}
+  \sigma_{\mathrm{stat}}^{2}=ft_{\mathrm{expo}}
+\end{equation}
+Background fluctuation:
+\begin{equation}
+  \sigma_{\mathrm{sky}}^{2}=N\sigma_{\mathrm{sky,0}}^{2}t_{expo}
+\end{equation}
+Total error are the combination of these two parts:
+\begin{equation}
+  \sigma^{2} = \sigma_{\mathrm{stat}}^{2}+\sigma_{\mathrm{sky}}^{2}=ft_{\mathrm{expo}}+N\sigma_{\mathrm{sky,0}}^{2}t_{expo}
+\end{equation}
+Relative uncertainty:
+\begin{equation}
+  \frac{\sigma}{\mathrm{Flux}} = \frac{\sqrt{ft_{\mathrm{expo}}+N\sigma_{\mathrm{sky,0}}^{2}t_{expo}}}{ft_{\mathrm{expo}}}
+\end{equation}
+The exposure time are 30s for F125W images and 15s for F160W
+images. Here I adopt 15s for a upper limit estimation. The flux
+intensity for the exoplanet is $\sim 8000$ counts per second. The
+standard deviation for background is $\sim 1$ counts per
+second. Plugin those numbers, I estimated a relative uncertainty for 0.3\%.
 \end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2014-11-03 summary/DataPreparation/_region_.tex
start writing summary doc on aperture photometry

--- 2014-10-19 prepdata/summary/summary.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\message{ !name(summary.tex)}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Short Sectioned Assignment
@@
 
-\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
-\synctex=1
+\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
+
 \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
@@
 \usepackage{sectsty} % Allows customizing section commands
-\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps
+\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
 
@@
 
+\message{ !name(summary.tex) !offset(-3) }
+
 \maketitle % Print the title
@@
 \begin{enumerate}
-\item \textbf{\texttt{CNTRD.PRO}}\\
-  IDL routnine \texttt{CNTRO.PRO} locates the position where the X
-  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
-  can be adjusted with parameter \texttt{EXTENDBOX}.\par
-\item 
+\item \texttt{\textbf{CNTRD.PRO}}
 \end{enumerate}
@@
 \end{document}
+\message{ !name(summary.tex) !offset(-89) }

### 2014-11-05 summary/AperturePhot1/aperPhotSummary.tex
Aperture photometry summary finished

@@
 \begin{enumerate}
-\item Cross Correlation method can align images with the saturated
-  primary star centroid as precise as $\sim 0.01$ pixels, which is far
-  better than the precision of IDL \texttt{cntrd.pro} or
-  \texttt{gcntrd.pro} which is more than $\sim 0.2$ pixels. According
-  to the residual image patterns, cross correlation alignment has
-  better performance tan WCS alignment.
+\item Using cross correlation, images can be aligned with precision of
+  $\sim 0.01$ pixels, which is far better than the precision that IDL
+  \texttt{cntrd.pro} and \texttt{gcntrd.pro} routines can
+  provide. According to the patterns on PSF subtracted images, cross
+  correlation has better performance tan WCS alignment.
 \item Aperture photometry for secondary object in ABPIC system is
-  measured. The light curves are very similar to Glenn's
-  measurement. However, the light curves for two filters, F125W and
-  F160W agree with each other better in my measurement.
-\item Considering only statistical uncertainties (counting errors) and
-  fluctuation in the background, a rough estimate gives a result of
-  0.3\% for relative uncertainty for one
-  photometry measurement.
+  carried out with a fixed aperture radius of 5 pixels. The light
+  curves are very similar to Glenn's measurement. The light curves for
+  two filters, F125W and F160W have better agreement in my
+  measurement.
+\item Taking only statistical uncertainty (counting error) and
+  background fluctuations into account, a rough estimation gives an
+  relative uncertainty of 0.3\% for one photometry measurement.
 
 \end{enumerate}
-\section{Image Alignment}
-\subsection{Alignment Precision Test}
-\subsection{The Modification for IDL \texttt{crosscorr} Routine}
-\subsection{PSF subtraction result}
+\section{Image Registration}
+\subsection{Image Registration Precision Test}
+The performance of image registration method is valuated by the accuracy of
+the measurement for shift between two images. In practice, I
+choose one image, shift this image with a specific distance with
+\texttt{fshift.pro}, measure the shift, and calculate the offset of
+the measured shift and real shift. With above procedure, I tested the
+performance of 3 image registration method. Results are plotted in figure \ref{fig:shift1}.\par
+
+The offsets for cntrd and gcntrd methods can be as large as 0.2 - 0.3
+pixels. However cross correlation method can limit the offset within
+0.06 pixels. It is surprising that none of the three distributions of
+offsets has a Gaussian like  profile. For cross correlation, I plotted
+the offset against the real shift distance. It turned out that the
+offset oscillates with shift distance with a period of exact 1 pixel
+and an amplitude of 0.05 pixels. I do not know clearly why they have
+such a relationship.\par
+
+According to the test result, cross correlation has a much better
+performance on registration images.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{cntrd_off2}
+  \includegraphics[width=0.48\textwidth]{gcntrd_off2}\\
+  \includegraphics[width=0.48\textwidth]{crosscorr_off2}
+  \includegraphics[width=0.48\textwidth]{crosscorr_cenTes.pdf}\\
+  \caption{Measured shifts minus real shifts histogram in x direction
+    measured by IDL \texttt{cntrd.pro} IDL \texttt{gcntrd.pro} and
+    cross correlation}
+  \label{fig:shift1}
+\end{figure}
+
+\subsection{Modification of  Cross correlation}
+The general idea of cross correlation method is that it calculate
+cross correlation matrix of one image and one reference image. The
+coordinate of the maximum in cross correlation matrix then can be
+converted to the shifts in x and y direction of the image  relative to
+the reference image. To locate the peak in cross correlation matrix
+is one key factor of the accuracy of this method. The original
+\texttt{crosscorr.pro} routine use \texttt{polyfit2d.pro} to find the
+maximum, which uses a polynomial function (default order is 4) to fit
+the an area around the maximum value (default is a (5 pixel)$^{2}$
+square) and find the peak. I tried to fit either with a higher order
+or larger area, the result turned to be unstable. Especially, when I
+kept on using an order of 4 polynomial function to fit a (10
+pixel)$^{2}$ square around the peak, the program got stuck and
+returned error.\par
+
+Therefore, I tried \texttt{mpfit2dpeak.pro} routine which fits either
+Gaussian, Lorentz or Moffat function to find the peak. It turned out
+that  mpfit could improve the accuracy of cross correlation for
+nearly an order of magnitude. With mpfit, the offset for measured
+shift and real shift can be limited within 0.008 pixels. However, the
+weird oscillation still exists.\par
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\textwidth]{crosscorr_cenTest2}
+  \caption{offset for measured shift and real shift. The shift is measured by cross correlation with mpfit.}
+\end{figure}
+
+\subsection{Test with Noise Adding in}
+Primary star image is subtracted with a PSF image that has a different
+rolling angle. Thus it is important to know the accuracy in the
+scenario  where only the primary star image stays the same, other
+objects rolled to a specific angle. To simulate rolling, I add 5 fake
+star images in random positions to both original image and shifted
+image and then use cross correlation to measure the shift. As shown in
+figure \ref{fig:shift2}, noise star images does not affect the
+accuracy too much.
+
+\begin{figure}[h]
+      \centering
+      \includegraphics[width=0.8\textwidth]{crosscorr_cenWithNoise}
+      \caption{offset for measured shift and real shift. Original
+        image and shifted iamge were both added with 5 fake star in
+        random poistions.}
+      \label{fig:shift2}
+    \end{figure}
+
+ \section{PSF subtraction result}
+Using cross correlation and  World Coordinate System to register
+images, two set of data were compiled. I carried out the PSF
+subtraction with both data set.\par
+
+For one specific image(img$_{0}$), every other image(img$_{i}$) that was taken with the same
+filter and different rolling angle were selected to be
+subtracted. With equation \ref{eqn:fit}:
+\begin{equation}
+  \label{eqn:fit}
+  res = \sum(img_{0} - c\cdot img_{i})^{2}
+\end{equation}
+tunable scale factor $c$ is calculated with minimum least square
+fitting. The PSF is chosen with the criterion of least residual. \par
+
+Figure \ref{fig:subcomp} illustrate the difference of PSF subtraction
+results between cross correlation and WCS registration. It is clearly
+shown that cross correlation gives a better alignment that the
+residual image is much more even. WCS aligned PSF is clearly offset to
+downright direction.\par
+
+The background fluctuation of the region around secondary is $\sim
+1.0$ counts/s.\par
+
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{wcs_example}
-  \caption{PSF subtraction comparison}\label{fig:subcomp}
+  \caption{PSF subtraction comparison. Above: cross
+    correlation. Below: WCS}\label{fig:subcomp}
 \end{figure}

### 2014-11-06 summary/AperturePhot1/aperPhotSummary.tex
aperture photometry summary1 finished

@@
   provide. According to the patterns on PSF subtracted images, cross
-  correlation has better performance tan WCS alignment.
+  correlation has better performance than WCS alignment.
 \item Aperture photometry for secondary object in ABPIC system is
-  carried out with a fixed aperture radius of 5 pixels. The light
+  carried out, with a fixed aperture radius of 5 pixels. The light
   curves are very similar to Glenn's measurement. The light curves for
-  two filters, F125W and F160W have better agreement in my
+  two filters, F125W and F160W seem to have better agreement in my
   measurement.
@@
 \subsection{Image Registration Precision Test}
-The performance of image registration method is valuated by the accuracy of
-the measurement for shift between two images. In practice, I
-choose one image, shift this image with a specific distance with
-\texttt{fshift.pro}, measure the shift, and calculate the offset of
-the measured shift and real shift. With above procedure, I tested the
-performance of 3 image registration method. Results are plotted in figure \ref{fig:shift1}.\par
+The performance of image registration method is valuated by the
+accuracy of the measurement for shift between two images. In practice,
+I choose one image, shift it for a specific distance with
+\texttt{fshift.pro}, measure the shift with various methods, and
+calculate the difference of the measured shift and real shift. With
+above procedure, I tested the performances of 3 image registration
+methods. Results are demonstrated in figure \ref{fig:shift1}.\par
 
-The offsets for cntrd and gcntrd methods can be as large as 0.2 - 0.3
-pixels. However cross correlation method can limit the offset within
+The difference of measured shift and real shift  for cntrd and gcntrd methods can be as large as 0.2 - 0.3
+pixels. In contrast, cross correlation method can limit the offset within
 0.06 pixels. It is surprising that none of the three distributions of
-offsets has a Gaussian like  profile. For cross correlation, I plotted
+offsets has a Gaussian shaped  profile. For cross correlation, I plotted
 the offset against the real shift distance. It turned out that the
 offset oscillates with shift distance with a period of exact 1 pixel
-and an amplitude of 0.05 pixels. I do not know clearly why they have
+and an amplitude of $\sim$0.06 pixels. I do not know clearly why they have
 such a relationship.\par
 
-According to the test result, cross correlation has a much better
-performance on registration images.
+Nevertheless, according to the test result, cross correlation has a better
+performance on registration images.\par
 
@@
 \subsection{Modification of  Cross correlation}
-The general idea of cross correlation method is that it calculate
-cross correlation matrix of one image and one reference image. The
-coordinate of the maximum in cross correlation matrix then can be
-converted to the shifts in x and y direction of the image  relative to
-the reference image. To locate the peak in cross correlation matrix
-is one key factor of the accuracy of this method. The original
-\texttt{crosscorr.pro} routine use \texttt{polyfit2d.pro} to find the
-maximum, which uses a polynomial function (default order is 4) to fit
-the an area around the maximum value (default is a (5 pixel)$^{2}$
-square) and find the peak. I tried to fit either with a higher order
-or larger area, the result turned to be unstable. Especially, when I
-kept on using an order of 4 polynomial function to fit a (10
-pixel)$^{2}$ square around the peak, the program got stuck and
-returned error.\par
+The general idea of cross correlation registration is to use the
+position of peak  in cross correlation matrix calculated with
+two images to determine how they shift from each other.  To locate the
+peak in cross correlation matrix is one key factor of the accuracy of
+this method. The original \texttt{crosscorr.pro} routine uses
+\texttt{polyfit2d.pro} to find the maximum, which fits a polynomial
+function (default order is 4) to an area around the maximum
+value (default is a (5 pixel)$^{2}$ square) and find the peak. I tried
+to fit either with a higher order or larger area, but the result turned to
+be unstable. Especially, when I kept on using an order of 4 polynomial
+function to fit a (10 pixel)$^{2}$ square around the peak, the program
+got stuck and returned error.\par
 
 Therefore, I tried \texttt{mpfit2dpeak.pro} routine which fits either
-Gaussian, Lorentz or Moffat function to find the peak. It turned out
+Gaussian, Lorentz or Moffat profile  to find the peak. It turned out
 that  mpfit could improve the accuracy of cross correlation for
@@
 scenario  where only the primary star image stays the same, other
-objects rolled to a specific angle. To simulate rolling, I add 5 fake
+objects rolled to a specific angle. To simulate rolling, I added 5 fake
 star images in random positions to both original image and shifted
 image and then use cross correlation to measure the shift. As shown in
-figure \ref{fig:shift2}, noise star images does not affect the
+figure \ref{fig:shift2}, fake star images does not affect the
 accuracy too much.
@@
         image and shifted iamge were both added with 5 fake star in
-        random poistions.}
+        random positions.}
       \label{fig:shift2}
@@
 filter and different rolling angle were selected to be
-subtracted. With equation \ref{eqn:fit}:
+subtracted from img$_{0}$. With equation \ref{eqn:fit}:
 \begin{equation}
@@
 
-Figure \ref{fig:subcomp} illustrate the difference of PSF subtraction
-results between cross correlation and WCS registration. It is clearly
-shown that cross correlation gives a better alignment that the
-residual image is much more even. WCS aligned PSF is clearly offset to
+Figure \ref{fig:subcomp} illustrate an example of the difference of
+PSF subtraction results between cross correlation and WCS
+registration. It is clearly shown that cross correlation gives a
+better alignment. The residual image is more even with cross
+correlation registration. WCS aligned PSF is clearly offset to
 downright direction.\par
@@
 \end{figure}
+
 \section{Aperture Photometry Result}
@@
 for F125W and F160W show considerable discrepancies in 5th and 6th
-orbits. However in my measurement, the two curves agree better. Apart
+orbits. In my measurement, the two curves seemed to agree better. Apart
 from this, the most prominent features are shown in both light
-curves, e.g. the light curves are lower in 2nd orbit and the
-discrepancy at start of the 3rd orbit.
+curves, e.g. the light curves are lower in 2nd orbit and there is a 
+discrepancy of two curves at start of the 3rd orbit.
 

### 2014-11-21 summary/dataReduction1.tex
start to write psf fitting journal

--- 2014-10-19 prepdata/summary/summary.tex
@@
 
-\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
+\setlength\parindent{0pt} % Removes all indentation from paragraphs -
+                          % comment this line for an assignment with
+                          % lots of text
+\setlength\parskip{12pt}
 
+%----------------------------------------------------------------------------------------
+%   TITLE SECTION
+%   ----------------------------------------------------------------------------------------
 %----------------------------------------------------------------------------------------
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Data Preparation\\ % The assignment title
+\huge Note for last two weeks\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 \maketitle % Print the title
-\section{Centroid of Primary Star}
-4 methods were tested to locate the centroid of the primary objects
-for all 78 cosmic ray removed images of ABPIC-B. I compared the
-4 sets of results for each method in order to determine the best
-method in this situation where the image of the primary star is
-slightly saturated.\par
+\section{Ramp effect}
+\begin{quote}
+  \begin{itemize}
+\item 2 ways
+\item check the paper
+ \end{itemize}
+\end{quote}
 
-\subsection{Method Introduction}
+\begin{itemize}
+\item  In \textsl{Wilkins et. al. 2013}\\
 
-\begin{enumerate}
-\item \textbf{\texttt{CNTRD.PRO}}\\
-  IDL routnine \texttt{CNTRO.PRO} locates the position where the X
-  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
-  can be adjusted with parameter \texttt{EXTENDBOX}.\par
-\item 
-\end{enumerate}
+    The ramp effect is neglectable when exposure level is below \textbf{30000} electrons per pixel.
 
+\item In \textsl{Deming et. al. 2013}\\
+
+    They expected ramp effect to be weakly detectable in their data
+    when their exposure level is about \textbf{40000} electrons per pixel.
+\end{itemize}
+
+ In our data, the maximum exposure level at the secondary image is $\sim$2000 e$^-$ per pixel, which is far below 30000 e$^-$ per pixel. Therefore the ramp effect in our case should be small enough.
+
+\section{ PSF photometry}
+>plot PSF photometry with aperture photometry
+
+\subsection{ generate PSF}
+1.
+for the same filter and the same rolling angle, the center of the secondary is not exactly at the same position.
+Using mpfit2dpeak to measure the secondary centroid, the maximum difference in both x and y direction could be as large as 0.05 pixel (measured by cross correlation).
+*This effect would enlarge the  fwhm of the synthesis PSF.*
+
+-> align the image again when generating PSF
+- fshift (a linear interpolation) will slightly change the PSF -- enlarge the FWHM, this problem will be alleviate by oversampling with a cubic interpolation, but could not be eliminated
+- without second alignment with secondary object, synthetic PSF FWHM -- 1.93 pixels
+- align again with secondary object, synthetic PSF FWHM -- 2.00 pixels.
+
+2. *how to normalize the PSF?  
+now, I use the flux in 5 pixel to normalize
+
+3. Large chisq  
+- caused by underestimated of error?
+
+>aperture radius vs standard deviation
+>use aper.pro  to measure photometry and uncertainty
+
+Optimum aperture size is related to the estimation of background fluctuation.
+A difference of 1 count/pixel difference in background fluctuation could lead to 0.5 pixel change in optimum aperture radius.
+Aper.pro routine provides 2 ways to define sky fluctuation:
+1. ﻿﻿﻿﻿directly input sky level and fluctuation when calling the program. The sky value and sigma should be calculated before hand.
+2. input annulus radii of the sky region and let the program calculate it. The sky region here must be an annulus around the secondary object in this case.
+
+I choose to calculate the sky fluctuation separately rather than let aper.pro calculate.
+
+1.
+if the annulus is too close to the secondary object, the flux of the secondary image could contaminate the sky and end up with a higher estimation of sky level and an inaccurate estimate of sky fluctuation.
+2.
+The annulus radii cannot be large too.
+Because the slight change of PSF, the image of the primary cannot be removed completely.
+The residual of the primary image fluctuate largest at the center region as well as the diffraction spikes region.
+When the annulus radii get slightly larger, the annulus would include these region.
+If the annulus radii get even larger to avoid these region, it would cause an under-estimate of the sky fluctuation because the area of this annulus is not affected by psf subtraction.
+
+The optimum aperture radius turned out to be very small, it ranges from 2.8 to 3.5 pixels. which is only 1 pixel larger than fwhm of the image, which is 1.8 pixels.
+
+\section{Analyze light curve}
+>1. is the source varying
+>2. what is the amplitude in two colors
+
+According to aperture photometry, the peak to peak variation is about 2%
+>3. is the change periodic
+At least, it is difficult to find a period by eye.
+
+>4. are the changes in the filter correlated
+
+5. color magnitude diagram (Apai 2013) 
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2014-11-21 summary/DataReduction1/dataReduction1.tex
summary for bad psf fitting finished

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\synctex=1
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
%\usepackage[nolists, nomarkers]{endfloat}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[section]{placeins}
\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs -
                          % comment this line for an assignment with
                          % lots of text
\setlength\parskip{12pt}

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%   ----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Note for last two weeks\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yifan Zhou} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title
\section{Ramp effect}
% \begin{quote}
%   \begin{itemize}
% \item 2 ways
% \item check the paper
%  \end{itemize}
% \end{quote}

\begin{itemize}
\item  In \textsl{Wilkins et. al. 2013}\\
    The ramp effect is neglectable when exposure level is below \textbf{30000} electrons per pixel.
\item In \textsl{Deming et. al. 2013}\\
    They expected ramp effect to be weakly detectable in their data
    when their exposure level is about \textbf{40000} electrons per pixel.
\end{itemize}

 In our data, the maximum exposure level at the secondary image is $\sim$2000 e$^-$ per pixel, which is far below 30000 e$^-$ per pixel. Therefore the ramp effect in our case should be small enough.

 \section{ PSF photometry}
 % \begin{quote}
 %   plot PSF photometry with aperture photometry
 % \end{quote}

 \subsection{PSF Generation}
Different PSFs are generated with different filter and rolling
angle. Therefore totally there were 4 PSFs generated (F125W, Angle 1;
F125W, Angle 2; F160W, Angle 1; F160W, Angle 2). Each PSF is the
combination of all secondary object images with primary star
subtracted, that were taken with same
filter and rolling angle. The images were not re-aligned with the
secondary object centroids (reason explained later).\par

 \subsection{Result}
 \begin{figure}
   \centering
   \includegraphics[width = 0.8\textwidth]{PSFPhotometry_Nov20}
   \caption{PSF fitting light curve and aperture photometry ligth
     curve}
   \label{fig:psf}
 \end{figure}

 \begin{figure}
   \centering
   \includegraphics[width = 0.8\textwidth]{PSFFitChisq}
   \caption{PSF fitting reduced $\chi^2$. Yellow shaded patch
     indicates the 2nd orbit.}
   \label{fig:chisq}
 \end{figure}

 Preliminary PSF photometry result is presented with
 Figure \ref{fig:psf}. Colored lines are PSF photometry light curves, with
 aperture photometry light curves plotted in gray lines as
 reference. The PSF photometry results are not well correlated with
 aperture photometry especially in first two orbits. In last three
 orbits, PSF photometry seems to match better with aperture
 photometry.\par

 Figure \ref{fig:chisq} shows the reduced $\chi^{2}$ for PSF
 fitting. All F125W images fit terribly with PSF. However, most of
 F160W images have a good fit, except images taken in second
 orbit. Accordingly, the F160W PSF photometry light curve has the
 largest offset in second orbit (figure \ref{fig:psf}) comparing to
 aperture photometry.\par

\subsection{Possible Reason for Bad Fit and other problem}
% 1. for the same filter and the same rolling angle, the center of the secondary is not exactly at the same position. Using mpfit2dpeak to measure the secondary centroid, the maximum difference in both x and y direction could be as large as 0.05 pixel (measured by cross correlation). *This effect would enlarge the  fwhm of the synthesis PSF.*

% -> align the image again when generating PSF
% - fshift (a linear interpolation) will slightly change the PSF -- enlarge the FWHM, this problem will be alleviate by oversampling with a cubic interpolation, but could not be eliminated
% - without second alignment with secondary object, synthetic PSF FWHM -- 1.93 pixels
% - align again with secondary object, synthetic PSF FWHM -- 2.00 pixels.

\subsubsection{fshift changes PSF}

I checked the F160W second orbit images, and found that for the two
images that have the worst PSF fit, their secondary object images are
clearly from others' -- the FWHMs for these two images are 0.2 pixel
narrower than those for other images. However in the original images
(without registration and primary star subtraction), the PSFs for these
two images are similar to those for others.

In the mean time, I found the PSF's FWHM are enlarged by fshift, which
I guess is due to bilinear interpolation. For the original F160W
PSF, the FHWM is $\sim 1.68$ pixels. After registration and primary
subtraction, it becomes $\sim 1.9$ pixels.

I did some test and confirmed that fshift did change the PSF. I also
found over sampling the image with cubic interpolation
(\texttt{congrid(,cubic=-0.5)})first would alleviate this effect but
could not eliminate it. I guess the degree that fshift enlarge the
FHWM of PSF is related to the fractional part of the shift, but I have
not confirmed it yet.

I think fshift could make the PSF slightly unstable and could be one
of the reason for bad PSF fit. For this reason, I did not align the
image again with the centroids of secondary objects when generating
synthetic PSF because it calls
for fshift again. Actually for the cross correlation aligned images,
the maximum offset for secondary objects' positions is $\sim0.05$ pixel,
which could cause a $\sim0.1$ pixel enlargement in synthetic PSF's FWHM. On the
other hand fshift itself could enlarge the FWHM for $\sim0.1$ pixel.

\subsubsection{How to normalize the PSF? }
To get absolute flux measurement, synthetic PSF has to be
normalized. I am not sure what factor to use for the normalization.

\begin{quote}
aperture radius vs standard deviation
use aper.pro  to measure photometry and uncertainty
\end{quote}

\section{Analyze light curve}
\begin{quote}
 is the source varying
 what is the amplitude in two colors
\end{quote}

According to aperture photometry, the peak to peak variation is about
2%

\begin{quote}
  is the change periodic
\end{quote}

At least, it is difficult to find a period by eye.

\begin{quote}
  are the changes in the filter correlated
\end{quote}
As shown in \ref{fig:corr}, changes in two filters are well correlated.
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Flux_correlation_Nov17}
  \caption{F160W flux vs. F125W flux. Different colors indicate
    different orbits.}
  \label{fig:corr}
\end{figure}

\begin{quote}
  color magnitude diagram (Apai 2013)
\end{quote}
I was confused about magnitude system when converting fluxes to
magnitudes. STSCI provides three magnitude systems, ST magnitude, AB
magnitude, and vega magnitude. I used both AB magnitude and vega
magnitude for conversion and listed the plots in figure \ref{fig:cmd}.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{CMD_ABmag_Nov20}
  \includegraphics[width=0.8\textwidth]{CMD_Vegamag_Nov20}
  \caption{color magnitude diagram, different colors indicate
    different orbits}
  \label{fig:cmd}
\end{figure}

\section{Optimization of Aperture Size}

Optimum aperture size is related to the estimation of background
fluctuation. A difference of 1 count/pixel difference in background
fluctuation could lead to 0.5 pixel change in optimum aperture
radius. Aper.pro routine provides 2 ways to define sky fluctuation:
\begin{enumerate}
\item ﻿﻿﻿﻿directly input sky level and fluctuation when calling the program. The sky value and sigma should be calculated before hand.
\item  input annulus radii of the sky region and let the program calculate it. The sky region here must be an annulus around the secondary object in this case.
\end{enumerate}
I choose to calculate the sky fluctuation separately rather than let aper.pro calculate.

\begin{enumerate}
\item if the annulus is too close to the secondary object, the flux of the secondary image could contaminate the sky and end up with a higher estimation of sky level and an inaccurate estimate of sky fluctuation.    
\item The annulus radii cannot be large too. Because the slight change of
PSF, the image of the primary cannot be removed completely. The
residual of the primary image fluctuate largest at the center region
as well as the diffraction spikes region.  When the annulus radii get
slightly larger, the annulus would include these region. If the
annulus radii get even larger to avoid these region, it would cause an
under-estimate of the sky fluctuation because the area of this annulus
is not affected by psf subtraction.
\end{enumerate}

The optimum aperture radius turned out to be very small, it ranges from 2.8 to 3.5 pixels. which is only 1 pixel larger than fwhm of the image, which is 1.8 pixels.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-02-08 summary/Systematics1/Systematics1.tex
bad pixel marked

--- 2014-11-21 summary/DataReduction1/dataReduction1.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Note for last two weeks\\ % The assignment title
+\huge Systematic Error Correction\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 \maketitle % Print the title
-\section{Ramp effect}
-% \begin{quote}
-%   \begin{itemize}
-% \item 2 ways
-% \item check the paper
-%  \end{itemize}
-% \end{quote}
+\section{Summary}
 
-\begin{itemize}
-\item  In \textsl{Wilkins et. al. 2013}\\
-    The ramp effect is neglectable when exposure level is below \textbf{30000} electrons per pixel.
-\item In \textsl{Deming et. al. 2013}\\
-    They expected ramp effect to be weakly detectable in their data
-    when their exposure level is about \textbf{40000} electrons per pixel.
-\end{itemize}
+According to previous results, there are two kinds of systematic errors
+that downgrade the quality of photometry and need to be corrected.
+\begin{enumerate}
+\item images that are taken with different dithering positions have
+  significant difference in photometry. The most possible cause is 
+  bad flat fielding.
+\item Short timescale variation on the light curves. Red noise needs
+  to be caught and corrected. Following effects can contribute to red
+  noise:
+  ramp effect, jitter of the telescope, telescope temperature
+  fluctuation, intra-pixel  response fluctuation, cosmic rays.
+\end{enumerate}
 
- In our data, the maximum exposure level at the secondary image is $\sim$2000 e$^-$ per pixel, which is far below 30000 e$^-$ per pixel. Therefore the ramp effect in our case should be small enough.
+  \section{Red Noises}
+  \subsection{Ramp Effect and Pointing Problem}
+  According to Deming et al. 2013, Wilkins 2014, ramp effect becomes significant
+  when exposure level is larger than 30000 e$^{-}$ per pixel. For both
+  F125W and F160W images, the largest count rate per pixel at the
+  planetary companions place is 2000 - 2200 e$^{-}$s$^{-}$. For F125W
+  images, the exposure time is 30s for each image while for F160W is
+  15s. Therefore, the pixel that is the peak of the PSF of the
+  companion object in the F125W image may be affected by ramp effect.
 
- \section{ PSF photometry}
- % \begin{quote}
- %   plot PSF photometry with aperture photometry
- % \end{quote}
+  In Figure \ref{fig:peak}, I plotted the count for one pixel that has
+  the largest flux at the PSF region of ABPIC-B for every image. In short time-scale
+  (i.e. in one exposure set, does not demonstrate in the plot), peak
+  fluxes do not have a clear and common ramp effect pattern. For first
+  3 orbits, the counts have large scatterings for different dithering
+  positions. because the peaks of the PSF could locate at the center
+  or edge of the pixel. For the last 3 orbits for which dithering is not
+  applied, the peak pixel count demonstrates clear trend.  In the 4th
+  and 6th orbits, the peak pixel count decreases with time while for
+  5th orbits, it slightly increases with time.
 
- \subsection{PSF Generation}
-Different PSFs are generated with different filter and rolling
-angle. Therefore totally there were 4 PSFs generated (F125W, Angle 1;
-F125W, Angle 2; F160W, Angle 1; F160W, Angle 2). Each PSF is the
-combination of all secondary object images with primary star
-subtracted, that were taken with same
-filter and rolling angle. The images were not re-aligned with the
-secondary object centroids (reason explained later).\par
-
- \subsection{Result}
- \begin{figure}
+    \begin{figure}[th]
     \centering
-   \includegraphics[width = 0.8\textwidth]{PSFPhotometry_Nov20}
-   \caption{PSF fitting light curve and aperture photometry ligth
-     curve}
-   \label{fig:psf}
+    \includegraphics[width=\textwidth]{ramp1Pix}
+    \caption{Count for peak pixel on the image of ABPIC-B. Different
+      color indicate different dithering position. Count rates are measured
+      from the original \texttt{ima} files (no primary subtraction applied)}
+    \label{fig:peak}
   \end{figure}
 
- \begin{figure}
+  First of all, I cannot be certain whether ramp effect plays a
+  significant role in this trend. The exposure levels of peak pixel for
+  F125W images are more than 70000 e$^{-}$, for 5th orbit they are
+  near 90000 e$^{-}$, which are almost reach the fully saturation
+  level of 100000 e$^{-}$. However, short timescale variations are
+  random and no 'hook shaped' (Wilkins et al. 2014) light curves
+  appeared.
+
+  This trends for peak pixel count are correlated with the positions of
+  PSF centroids. I plot the PSF centroids that are measured by Gaussian
+  fitting for 4th, 5th and 6th orbits in Figure \ref{fig:center}. The
+  PSF centroids shifted in a specific direction within one orbit. In
+  4th and 6th orbits, the centroids shift to +y direction and in 5th
+  orbit they shift to (+x, +y) direction. In 4th and 6th orbits, the
+  centroids shift to the edge of the pixel while in 5th orbit, they
+  slightly shift to the pixel center.
+
+  \begin{figure}[th]
     \centering
-   \includegraphics[width = 0.8\textwidth]{PSFFitChisq}
-   \caption{PSF fitting reduced $\chi^2$. Yellow shaded patch
-     indicates the 2nd orbit.}
-   \label{fig:chisq}
+    \includegraphics[width=1.0\textwidth]{Ymove}
+    \caption{PSF centroid shift for ABPIC-B in 4th, 5th, and 6th
+      orbits. Y-axes are the centroid coordinates $(x, y)$ minus the
+      those for the first image in each orbit $(x_0, y_0)$. Red dots
+      are for x-direction and blue + are for y-direction.}
+    \label{fig:center}
   \end{figure}
 
- Preliminary PSF photometry result is presented with
- Figure \ref{fig:psf}. Colored lines are PSF photometry light curves, with
- aperture photometry light curves plotted in gray lines as
- reference. The PSF photometry results are not well correlated with
- aperture photometry especially in first two orbits. In last three
- orbits, PSF photometry seems to match better with aperture
- photometry.\par
-
- Figure \ref{fig:chisq} shows the reduced $\chi^{2}$ for PSF
- fitting. All F125W images fit terribly with PSF. However, most of
- F160W images have a good fit, except images taken in second
- orbit. Accordingly, the F160W PSF photometry light curve has the
- largest offset in second orbit (figure \ref{fig:psf}) comparing to
- aperture photometry.\par
-
-\subsection{Possible Reason for Bad Fit and other problem}
-% 1.
-for the same filter and the same rolling angle, the center of the secondary is not exactly at the same position.
-Using mpfit2dpeak to measure the secondary centroid, the maximum difference in both x and y direction could be as large as 0.05 pixel (measured by cross correlation).
-*This effect would enlarge the  fwhm of the synthesis PSF.*
-
-% -> align the image again when generating PSF
-% - fshift (a linear interpolation) will slightly change the PSF -- enlarge the FWHM, this problem will be alleviate by oversampling with a cubic interpolation, but could not be eliminated
-% - without second alignment with secondary object, synthetic PSF FWHM -- 1.93 pixels
-% - align again with secondary object, synthetic PSF FWHM -- 2.00 pixels.
-
-\subsubsection{fshift changes PSF}
-
-I checked the F160W second orbit images, and found that for the two
-images that have the worst PSF fit, their secondary object images are
-clearly from others' -- the FWHMs for these two images are 0.2 pixel
-narrower than those for other images. However in the original images
-(without registration and primary star subtraction), the PSFs for these
-two images are similar to those for others.
-
-In the mean time, I found the PSF's FWHM are enlarged by fshift, which
-I guess is due to bilinear interpolation. For the original F160W
-PSF, the FHWM is $\sim 1.68$ pixels. After registration and primary
-subtraction, it becomes $\sim 1.9$ pixels.
-
-I did some test and confirmed that fshift did change the PSF. I also
-found over sampling the image with cubic interpolation
-(\texttt{congrid(,cubic=-0.5)})first would alleviate this effect but
-could not eliminate it. I guess the degree that fshift enlarge the
-FHWM of PSF is related to the fractional part of the shift, but I have
-not confirmed it yet.
-
-I think fshift could make the PSF slightly unstable and could be one
-of the reason for bad PSF fit. For this reason, I did not align the
-image again with the centroids of secondary objects when generating
-synthetic PSF because it calls
-for fshift again. Actually for the cross correlation aligned images,
-the maximum offset for secondary objects' positions is $\sim0.05$ pixel,
-which could cause a $\sim0.1$ pixel enlargement in synthetic PSF's FWHM. On the
-other hand fshift itself could enlarge the FWHM for $\sim0.1$ pixel.
-
-\subsubsection{How to normalize the PSF? }
-To get absolute flux measurement, synthetic PSF has to be
-normalized. I am not sure what factor to use for the normalization.
-
-\begin{quote}
-aperture radius vs standard deviation
-use aper.pro  to measure photometry and uncertainty
-\end{quote}
-
-\section{Analyze light curve}
-\begin{quote}
- is the source varying
- what is the amplitude in two colors
-\end{quote}
-
-According to aperture photometry, the peak to peak variation is about
-2%
-
-\begin{quote}
-  is the change periodic
-\end{quote}
-
-At least, it is difficult to find a period by eye.
-
-\begin{quote}
-  are the changes in the filter correlated
-\end{quote}
-As shown in \ref{fig:corr}, changes in two filters are well correlated.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{Flux_correlation_Nov17}
-  \caption{F160W flux vs. F125W flux. Different colors indicate
-    different orbits.}
-  \label{fig:corr}
-\end{figure}
-
-\begin{quote}
-  color magnitude diagram (Apai 2013)
-\end{quote}
-I was confused about magnitude system when converting fluxes to
-magnitudes. STSCI provides three magnitude systems, ST magnitude, AB
-magnitude, and vega magnitude. I used both AB magnitude and vega
-magnitude for conversion and listed the plots in figure \ref{fig:cmd}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{CMD_ABmag_Nov20}
-  \includegraphics[width=0.8\textwidth]{CMD_Vegamag_Nov20}
-  \caption{color magnitude diagram, different colors indicate
-    different orbits}
-  \label{fig:cmd}
-\end{figure}
-
-\section{Optimization of Aperture Size}
-
-Optimum aperture size is related to the estimation of background
-fluctuation. A difference of 1 count/pixel difference in background
-fluctuation could lead to 0.5 pixel change in optimum aperture
-radius. Aper.pro routine provides 2 ways to define sky fluctuation:
+  To sum,
   \begin{enumerate}
-\item ﻿﻿﻿﻿directly input sky level and fluctuation when calling the program. The sky value and sigma should be calculated before hand.
-\item  input annulus radii of the sky region and let the program calculate it. The sky region here must be an annulus around the secondary object in this case.
-\end{enumerate}
-I choose to calculate the sky fluctuation separately rather than let aper.pro calculate.
-
-\begin{enumerate}
-\item if the annulus is too close to the secondary object, the flux of the secondary image could contaminate the sky and end up with a higher estimation of sky level and an inaccurate estimate of sky fluctuation.
-\item The annulus radii cannot be large too. Because the slight change of
-PSF, the image of the primary cannot be removed completely. The
-residual of the primary image fluctuate largest at the center region
-as well as the diffraction spikes region.  When the annulus radii get
-slightly larger, the annulus would include these region. If the
-annulus radii get even larger to avoid these region, it would cause an
-under-estimate of the sky fluctuation because the area of this annulus
-is not affected by psf subtraction.
+  \item Peak pixels have high exposure levels, especially for F125W,
+    ramp effect needs to be considered.
+  \item Telescope has a pointing shift within each orbit, and caused
+    the peak pixel count varies in a specific trend. Since peak pixel
+    contains $\sim 25\%$ of the total flux, if there were a
+    considerable intra-pixel response variation, this pointing shift
+    could be an error source.
   \end{enumerate}
 
-The optimum aperture radius turned out to be very small, it ranges from 2.8 to 3.5 pixels. which is only 1 pixel larger than fwhm of the image, which is 1.8 pixels.
+\subsection{Cosmic Rays in Up-the-Ramp Fitting}
 \end{document}
-
 %%% Local Variables:

### 2015-02-08 ABPIC_Data_Analysis/CentralPixel.py

@@ -1,0 +1,49 @@
+#! /usr/bin/env python
+"""
+check if there is significant ramp effect
+"""
+import pandas as pd
+import sys
+import matplotlib.pyplot as plt
+from brewer2mpl import get_map
+from astropy.io import fits
+import numpy as np
+colors = get_map('Set1', 'Qualitative', 4).mpl_colors
+
+def plotCentralPixel (ax, DF, nPixel = 1):
+    """
+    plot central value, show if it has ramp effect
+    """
+    centralFlux = pd.Series(dtype = float, index = DF.index)
+    dither = DF['DITHER'].values[0]
+    for index, row in DF.iterrows():
+        fitsFile = fits.open('../data/ABPIC-B/' + row['FILENAME'])
+        yc, xc = round(row['XCENTER']), round(row['YCENTER'])
+        centralFlux[index] = np.sort(fitsFile['SCI', 1].data[xc-2: xc + 2, yc - 2: yc + 2].flat)[-1:-1-nPixel:-1].sum()
+    ax.plot(DF.index, centralFlux * DF['EXPOSURE_TIME'], marker = '.', color = colors[dither])
+    
+if __name__ == '__main__':
+    plotFn = sys.argv[1]
+    nPixel = int(sys.argv[2])
+    DF = pd.read_csv('2457042_ima_aper=5_result.csv', parse_dates = {'datetime': ['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    plt.close('all')
+    fig = plt.figure(figsize = (6,8))
+    ax125 = fig.add_subplot(211)
+    ax160 = fig.add_subplot(212)
+    for filt, ax, thres in zip(['F125W', 'F160W'], [ax125, ax160], [800, 1500]):
+        for orbit in range(6, 13):
+            for exposure in range(0, 13):
+                subFrame = DF[(DF['FILTER'] == filt) & (DF['ORBIT'] == orbit)
+                              & (DF['EXPOSURE_SET'] == exposure)]
+                if not subFrame.empty: plotCentralPixel(ax, subFrame, nPixel = nPixel)
+
+    for ax in [ax125, ax160]:
+        ax.set_ylabel('Counts (e$^-$)')
+        ax.set_xlabel('UT')
+
+    ax125.set_title('F125W, maximum {0} pixel(s)'.format(nPixel))
+    ax160.set_title('F160W, maximum {0} pixel(s)'.format(nPixel))
[…]

### 2015-02-08 ABPIC_Data_Analysis/plotCvsX.py

@@ -1,0 +1,33 @@
+#! /usr/bin/env python
+import sys
+import matplotlib.pyplot as plt
+import pandas as pd
+from astropy.io import fits
+import numpy as np
+from brewer2mpl import get_map
+colors = get_map('Set1', 'Qualitative', 4).mpl_colors
+
+
+if __name__ == '__main__':
+    DF = pd.read_csv('2457042_ima_aper=5_result.csv', parse_dates = {'datetime': ['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    plt.close('all')
+    fig = plt.figure(figsize = (6,8))
+    ax125 = fig.add_subplot(211)
+    ax160 = fig.add_subplot(212)
+    for filt, ax, thres in zip(['F125W', 'F160W'], [ax125, ax160], [800, 1500]):
+        for index, orbit in enumerate([10, 11, 12]):
+            subFrame = DF[(DF['FILTER'] == filt) & (DF['ORBIT'] == orbit)]
+            if not subFrame.empty:
+                ax.plot(subFrame.index, subFrame['YCENTER'] - subFrame['YCENTER'].values[0], '.', color = colors[0])
+                ax.plot(subFrame.index, subFrame['XCENTER'] - subFrame['XCENTER'].values[0], '+', color = colors[1])
+
+    for ax in [ax125, ax160]:
+        ax.set_ylabel('Center')
+        ax.set_xlabel('UT')
+
+    ax125.set_title('F125W')
+    ax160.set_title('F160W')
+    fig.autofmt_xdate()
+    fig.savefig('Ymove.pdf')
+    plt.show()
+    

### 2015-02-08 ABPIC_Data_Analysis/showDQ.py

@@ -1,37 +1,79 @@
 import numpy as np
 from astropy.io import fits
 import sys
-import matplotlib.pyplot as plt
+#import matplotlib.pyplot as plt
 import pandas as pd
 
 def dq2Bad(dq, flag):
-    dqbin = ['{0:016b}'.format(i) for i in dq.flat]
-    isBad = np.array([True if dqstr[-flag] == '1' else False for dqstr in dqbin]).reshape(np.shape(dq))
-    return isBad
+    return (dq / flag) % 2
+
+def printCRFlag (fnList, nSamp):
+    """
+    print number of pixels that have CR detection during crcorr
+    """
+    flag = 8192
+    nbad = []
+    for fitsfn in fnList:
+        nbad[:] = []
+        fitsFile = fits.open('../data/ABPIC-B/' + fitsfn)
+        for iSamp in range(1, 1 + nSamp):
+            badPixelMap = dq2Bad(fitsFile['DQ', iSamp].data, flag)
+            nbad.append(np.where(badPixelMap != 0)[0].size)
+
+        fitsFile.close()
+        print fitsfn, nbad
+
+
+def printCREff (DF):
+    """
+    print CR coordinates that is inside the 
+    """
+    flag = 8192
+    nBad = []
+    for index, row in DF.iterrows():
+        dq = fits.open('../data/ABPIC-B/' + row['FILENAME'])['DQ', 1].data
+        bady, badx = np.where(dq2Bad(dq, flag) != 0)
+        inCircle = np.where(np.sqrt((badx - row['XCENTER'])**2 + (bady - row['YCENTER'])**2) < 5)
+        print row['FILENAME'], badx[inCircle], bady[inCircle]
+        nBad.append(len(badx))
+        
+    return nBad
+
+def plotBadPixel (fnList, flags):
+    """
+    plot bad pixel map
+    """
+    pass
+            
 
 if __name__ == '__main__':
-    DF = pd.read_csv('ABPIC-B_fileInfo.csv')
-    fitsFileList = DF['file name']
-    concernedFlag = [3, 5, 6, 7, 13, 14]
+    outFn = sys.argv[1]    
+    DF = pd.read_csv('2015_Jan_16_ima_result.csv')
+    #concernedFlag = [3, 5, 6, 7, 13, 14]
+    concernedFlag = [8192]
     markers = ['x', '+', '.', 's', '3', '4']
-    for fitsfn in fitsFileList:
[…]

### 2015-02-08 data/flatfielding.py

@@ -1,10 +1,14 @@
 import ds9
 import sys
+import os
 
 if __name__ == '__main__':
     fileName = sys.argv[1]
     d = ds9.ds9()
-    d.set('file {0}'.format(fileName))
+    d.set('file {0}'.format(os.path.join(os.getcwd(), fileName)))
+    d.set('scale limits 0.95 1.05')
+    d.set('pan to 500 600 physical')
+    d.set('zoom 4')
     x = [473.78, 483.88, 473.78, 483.88, 508.18, 518.32, 508.18, 518.32]
     y = [587.07, 587.07, 598.30, 598.30, 601.11, 601.11, 612.50, 612.50]
     for xi, yi in zip(x, y):

### 2015-02-09 ABPIC_Data_Analysis/CRvsFlux.py
CR relation not clear, adapt pipeline first

@@ -1,0 +1,18 @@
+#! /usr/bin/env python
+"""
+investigate how CR affect _ima to _flt conversion
+"""
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+
+if __name__ == '__main__':
+    fltDF = pd.read_csv('2015_Jan_07_result.csv', parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    imaDF = pd.read_csv('ima_DataQuality.csv', parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    plt.close('all')
+    fig = plt.figure()
+    Diff = imaDF['FLUX']-fltDF['FLUX']
+    ax = fig.add_subplot(111)
+    ax.plot(imaDF['CR number'], np.abs(Diff), '.')
+    plt.show()
+

### 2015-02-09 ABPIC_Data_Analysis/showDQ.py

@@ -33,9 +33,9 @@ def printCREff (DF):
     for index, row in DF.iterrows():
         dq = fits.open('../data/ABPIC-B/' + row['FILENAME'])['DQ', 1].data
         bady, badx = np.where(dq2Bad(dq, flag) != 0)
-        inCircle = np.where(np.sqrt((badx - row['XCENTER'])**2 + (bady - row['YCENTER'])**2) < 5)
+        inCircle = np.where(np.sqrt((badx - row['XCENTER'])**2 + (bady - row['YCENTER'])**2) < 3)
         print row['FILENAME'], badx[inCircle], bady[inCircle]
-        nBad.append(len(badx))
+        nBad.append(len(badx[inCircle]))
         
     return nBad
 

### 2015-02-11 summary/Systematics1/Systematics1.tex
working result at daniel's office

@@
   \subsection{Cosmic Rays in Up-the-Ramp Fitting}
+  \begin{itemize}
+  \item In majority of \texttt{ima} files, there are several pixels in
+    companion image region that are flagged with 8192 (CR detected by
+    up-the-ramp fitting)
+    \item it is not clear yet number of pixels that have CR flag is
+      correlated with flux scattering
+    \item considering use the same PSF images for PSF subtraction.
+    \end{itemize}
+
+    \subsection{Jitter}
+    \begin{itemize}
+    \item 4 exposures have extremely large jitter value
+     \item RMS jitter values are about 0.001 arcsec (0.1 pixel)in both
+       axes
+     \item jitter values seem not to correlate with flux scattering
+    \end{itemize}
 \end{document}

### 2015-02-11 ABPIC_Data_Analysis/plotCvsX.py

@@ -7,6 +7,17 @@ import numpy as np
 from brewer2mpl import get_map
 colors = get_map('Set1', 'Qualitative', 4).mpl_colors
 
+def plotCvsX (ax, DF, nPixel = 1):
+    """
+    if the value of Central pixel has anything to do with coordinate position
+    """
+    centralFlux = pd.Series(dtype = float, index = DF.index)
+    dither = DF['DITHER'].values[0]
+    for index, row in DF.iterrows():
+        fitsFile = fits.open('../data/ABPIC-B/' + row['FILENAME'])
+        yc, xc = round(row['XCENTER']), round(row['YCENTER'])
+        centralFlux[index] = np.sort(fitsFile['SCI', 1].data[xc-2: xc + 2, yc - 2: yc + 2].flat)[-1:-1-nPixel:-1].sum()
+    ax.plot(DF['YCENTER'], centralFlux * DF['EXPOSURE_TIME'], marker = '.', color = colors[dither])
 
 if __name__ == '__main__':
     DF = pd.read_csv('2457042_ima_aper=5_result.csv', parse_dates = {'datetime': ['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
@@ -15,19 +26,19 @@ if __name__ == '__main__':
     ax125 = fig.add_subplot(211)
     ax160 = fig.add_subplot(212)
     for filt, ax, thres in zip(['F125W', 'F160W'], [ax125, ax160], [800, 1500]):
-        for index, orbit in enumerate([10, 11, 12]):
-            subFrame = DF[(DF['FILTER'] == filt) & (DF['ORBIT'] == orbit)]
-            if not subFrame.empty:
-                ax.plot(subFrame.index, subFrame['YCENTER'] - subFrame['YCENTER'].values[0], '.', color = colors[0])
-                ax.plot(subFrame.index, subFrame['XCENTER'] - subFrame['XCENTER'].values[0], '+', color = colors[1])
+        for orbit in range(10, 13):
+            for exposure in range(0, 13):
+                subFrame = DF[(DF['FILTER'] == filt) & (DF['ORBIT'] == orbit)
+                              & (DF['EXPOSURE_SET'] == exposure)]
+                if not subFrame.empty: plotCvsX(ax, subFrame, 1)
 
     for ax in [ax125, ax160]:
-        ax.set_ylabel('Center')
+        ax.set_ylabel('Counts (e$^-$)')
[…]

### 2015-02-11 ABPIC_Data_Analysis/plotJittervsC.py

@@ -1,0 +1,45 @@
+import glob
+from astropy.io import fits
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+def CentralPixel (DF, nPixel = 1):
+    """
+    plot central value, show if it has ramp effect
+    """
+    centralFlux = []
+    for index, row in DF.iterrows():
+        fitsFile = fits.open('../data/ABPIC-B/' + row['FILENAME'])
+        yc, xc = round(row['XCENTER']), round(row['YCENTER'])
+        centralFlux.append(np.sort(fitsFile['SCI', 1].data[xc-2: xc + 2, yc - 2: yc + 2].flat)[-1:-1-nPixel:-1].sum())
+        fitsFile.close()
+    return np.array(centralFlux)
+
+if __name__ == '__main__':
+    
+    df = pd.read_csv('2015_Jan_07_result.csv', parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    c = CentralPixel(df)
+    AVGjit = []
+    V2jit = []
+    V3jit = []
+    jitList = sorted(glob.glob('../data/ABPIC-B/*jit.fits'))
+    for jitFN in jitList:
+        jit = fits.open(jitFN)
+        for ext in range(1, len(jit)):
+            V2 = jit[ext].data['SI_V2_AVG']
+            V3 = jit[ext].data['SI_V3_AVG']
+            V2 = V2[np.abs(V2) < 1.0]
+            V3 = V3[np.abs(V3) < 1.0]
+            V2jit.append(np.mean(V2))
+            V3jit.append(np.mean(V3))
+
+    df["C"] = c
+    df['V2jit'] = V2jit
+    df['V3jit'] = V3jit
+    # plt.close('all')
+    # #plt.plot(np.sqrt(df[(df['ORBIT'] == 10) & (df['FILTER'] == 'F125W')]['V2jit']**2 + df[(df['ORBIT'] == 10) & (df['FILTER'] == 'F125W')]['V3jit']**2) , df[(df['ORBIT'] == 10) & (df['FILTER'] == 'F125W')]['C'], '.')
+    # subdf = df[(df['ORBIT'] == 10) & (df['FILTER'] == 'F125W')]
+    # dx = subdf['XCENTER'] - subdf['XCENTER'].values[0]
[…]

### 2015-02-11 ABPIC_Data_Analysis/plotLC.py
moving on

@@ -1,0 +1,12 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import sys
+
+if __name__ == '__main__':
+    fn = sys.argv[1]
+    df = pd.read_csv(fn, parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    plt.close('all')
+    plt.plot(df[df['FILTER'] == 'F125W'].index, df[df['FILTER'] == 'F125W']['FLUX'], '+')
+    plt.plot(df[df['FILTER'] == 'F160W'].index, df[df['FILTER'] == 'F160W']['FLUX'], 'x')
+    plt.gcf().autofmt_xdate()
+    plt.show()

### 2015-02-12 ABPIC_Data_Analysis/rampUp.py
are you kidding me HST

@@ -1,0 +1,32 @@
+from astropy.io import fits
+import matplotlib.pyplot as plt
+import sys
+import os
+import numpy as np
+
+if __name__ == '__main__':
+    dataDIR = '../data/ABPIC-B'
+    fn = sys.argv[1]
+    x = int(sys.argv[2]) 
+    y = int(sys.argv[3]) # do not use x or y, they are confusing
+    dim1, dim2 = y, x
+    ima = fits.open(os.path.join(dataDIR, fn))
+    nSamp = ima['primary'].header['nsamp']
+    count = np.zeros(nSamp)
+    sampTime = np.zeros(nSamp)
+    count[0] = ima['sci', nSamp].data[dim1, dim2]
+    sampTime[0] = 0 # zeroth read
+    for i, samp_i in enumerate(range(nSamp - 1, 0, -1)): #last samp is the first readout
+        sampTime[i+1] = ima['sci', samp_i].header['samptime']
+        print ima['sci', samp_i].data[dim1, dim2], ima['dq', samp_i].data[dim1, dim2]
+        count[i+1] = ima['sci', samp_i].data[dim1, dim2] * sampTime[i + 1] + count[0]
+
+    plt.close('all')
+    plt.plot(sampTime, count, marker = '+')
+    print sampTime, count
+    ax = plt.gca()
+    ax.set_xlabel('Time (s)')
+    ax.set_ylabel('Count (e$^-$)')
+    plt.show()
+
+    

### 2015-05-05 2M1207ANALYSIS/stackImages.py
lets start to write paper

@@ -1,0 +1,28 @@
+# /usr/bin/env python
+import pandas as pd
+import matplotlib.pyplot as plt
+from os import path
+from astropy.io import fits
+import numpy as np
+
+if __name__ == '__main__':
+    dataDIR = '../data/2M1207B/'
+    aimDIR = './stackImage'
+    df = pd.read_csv('2M1207B_flt_fileInfo.csv', parse_dates = {'datetime':['obs date', 'obs time']}, index_col = 'datetime')
+    dither = 0
+    subdf = df[df['dither'] == dither]
+    image0 = fits.getdata(path.join(dataDIR, subdf['file name'].values[0]), 'sci')
+    for i in range(len(subdf)):
+        image_i = fits.getdata(path.join(dataDIR,subdf['file name'].values[i]), 'sci') - image0
+        plt.close('all')
+        plt.imshow(np.arcsinh(image_i), vmin = 0, vmax = 5.5, cmap = 'hot')
+        plt.savefig(path.join(aimDIR, subdf['file name'].values[i].rstrip('.fits') + '_dither_{0}'.format(dither) + '.pdf'))
+
+
+
+
+
+
+
+
+

### 2015-05-05 ABPIC_Data_Analysis/compareFlat.py

@@ -1,0 +1,54 @@
+#! /usr/bin/env python
+
+import matplotlib.pyplot as plt
+import pandas as pd
+import sys
+import numpy as np
+
+def plotLightCurve(origDF, newDF, filtername):
+    """
+    plot the light curve
+    """
+    plt.close('all')
+    fig = plt.figure()
+    ax = plt.subplot2grid((3,1), (0,0), rowspan = 2)
+#    origDF['FLUX0'] = origDF['FLUX']
+    origDF['FLUX0'] = origDF['FLUX']/origDF['FLUX'].mean()
+    origDF['ERR0'] = origDF['FLUXERR']/origDF['FLUX']
+    origDF['Time'] = np.float32(origDF.index.values - origDF.index.values[0])/(60 * 60 * 1e9) #time in ns
+
+#    newDF['FLUX0'] = newDF['FLUX']
+    newDF['FLUX0'] = newDF['FLUX']/newDF['FLUX'].mean()
+    newDF['ERR0'] = newDF['FLUXERR']/newDF['FLUX']
+    newDF['Time'] = np.float32(newDF.index.values - newDF.index.values[0])/(60 * 60 * 1e9) #time in ns
+
+
+    t = origDF['Time'] - origDF['Time'].values[0]
+    ax.errorbar(t, origDF['FLUX0'] + 0.04, yerr = origDF['FLUX0'] * origDF['ERR0'], fmt = 's', label = 'Original Flat', mec = '0.2', mew = 0.5)
+    ax.errorbar(t, newDF['FLUX0'], yerr = newDF['FLUX0'] * newDF['ERR0'], fmt = 'o', label = 'Blob Flat', mec = '0.2', mew = 0.5)
+    ax.axhline(y = 1.0, linestyle = '--', color = '0.2', linewidth = 0.8)    
+    ax.axhline(y = 1.04, linestyle = '--', color = '0.2', linewidth = 0.8)
+    ax.legend(loc = 'best')
+    
+    ax.set_ylabel('Normalized Flux', fontsize = 18, fontweight = 'semibold')
+    ax.set_xlabel('Time (h)', fontsize = 18, fontweight = 'semibold')
+
+    ax_diff = plt.subplot2grid((3,1), (2,0), sharex = ax)
+    diff = origDF['FLUX0'].values - newDF['FLUX0'].values
[…]

### 2015-05-05 ABPIC_Data_Analysis/correctCR.py

@@ -13,10 +13,10 @@ if __name__ == '__main__':
             plotDIR = path.join('../data/ABPIC-B_myfits','orbit_{0}_expo_{1}'.format(orbit,nExpo))
             if not path.exists(plotDIR): mkdir(plotDIR)
             subdf = df[(df['orbit'] == orbit) & (df['exposure set'] == nExpo)]
-            exp = ExposureSet(subdf['file ID'].values, dataDIR,[subdf['YCENTER'].values[0], subdf['XCENTER'].values[0]] , orbit, nExpo, subdf['filter'].values[0], useNewFlat = 1)
+            exp = ExposureSet(subdf['file ID'].values, dataDIR,[subdf['YCENTER'].values[0], subdf['XCENTER'].values[0]] , orbit, nExpo, subdf['filter'].values[0], useNewFlat = False)
             #exp.correct(correctAll = True, chisqTh = 2.5)
             exp.noUpTheRamp()
             #exp.testCorrection2(chisqTh = 3, doPlot = True, plotDIR = plotDIR)
-            exp.saveFITS('../data/ABPIC-B_noramp_newflat/', decorator = 'noramp')
-            exp.savePickle('../data/ABPIC-B_noramp_newflat/', decorator = 'noramp')
-            exp.save('../data/ABPIC-B_noramp_newflat/', 'noramp_expSet')
+            exp.saveFITS('../data/ABPIC-B_noramp/', decorator = 'noramp')
+            exp.savePickle('../data/ABPIC-B_noramp/', decorator = 'noramp')
+            exp.save('../data/ABPIC-B_noramp/', 'noramp_expSet')

### 2015-05-05 ABPIC_Data_Analysis/plotLC.py

@@ -27,18 +27,21 @@ if __name__ == '__main__':
     df['ERR0'] = df['FLUXERR']/df['FLUX']
     df['Time'] = np.float32(df.index.values - df.index.values[0])/(60 * 60 * 1e9) #time in ns
 
-    subdf = df[(df['ORBIT'] >= 7)]
+    subdf = df[(df['ORBIT'] >= 7) & (df['CONTAMINATED'] == 0)]
+    #subdf = df[(df['ORBIT'] >= 7)]
     subdf['Time'] = subdf['Time'] - subdf['Time'].values[0]
-    ax.errorbar(subdf[subdf['FILTER'] == 'F125W']['Time'], subdf[subdf['FILTER'] == 'F125W']['FLUX0'], yerr = subdf[subdf['FILTER'] == 'F125W']['FLUX0'] * subdf[subdf['FILTER'] == 'F125W']['ERR0'], fmt = 's', label = 'F125W, Std Dev: {0:.2f}%'.format(subdf[subdf['FILTER'] == 'F125W']['FLUX0'].std() * 100), color = 'b')
-    ax.errorbar(subdf[subdf['FILTER'] == 'F160W']['Time'], subdf[subdf['FILTER'] == 'F160W']['FLUX0'] + 0.03, yerr = subdf[subdf['FILTER'] == 'F160W']['FLUX0'] * subdf[subdf['FILTER'] == 'F160W']['ERR0'], fmt = 's', label = 'F160W, Std Dev: {0:.2f}%'.format(subdf[subdf['FILTER'] == 'F160W']['FLUX0'].std() * 100), color = 'r')
+    ax.errorbar(subdf[subdf['FILTER'] == 'F125W']['Time'], subdf[subdf['FILTER'] == 'F125W']['FLUX0'], yerr = subdf[subdf['FILTER'] == 'F125W']['FLUX0'] * subdf[subdf['FILTER'] == 'F125W']['ERR0'], fmt = 's', label = 'F125W, Std Dev: {0:.2f}%'.format(subdf[subdf['FILTER'] == 'F125W']['FLUX0'].std() * 100), mec = '0.2', mew = 0.5)
[…]

### 2015-05-05 python_src/ExposureSet.py

@@ -16,7 +16,7 @@ class ExposureSet:
     expousre number
     filter
     """
-    def __init__ (self, fnList, dataDIR, peakPos, orbit, nExpo, filterName, size = 5, useNewFlat = 0):
+    def __init__ (self, fnList, dataDIR, peakPos, orbit, nExpo, filterName, size = 5, useNewFlat = False):
         """
         initialize Exopusre set object
         """
@@ -35,7 +35,7 @@ class ExposureSet:
         
         self.HSTFileList = []
         for fn in self.fnList:
-            self.HSTFileList.append(HSTFile(fn, self.dataDIR, self.peakPos, self.size, useNewFlat = useNewFlat))
+            self.HSTFileList.append(HSTFile(fn, self.dataDIR, self.peakPos, self.size, useNewFlat))
 
         self.expTime = self.HSTFileList[0].expTime[-1] # the exposure time for individual file, used for caculating couting uncertainties
         self.isCorrected = np.zeros([2*size + 1, 2*size + 1, self.nFile], dtype = bool)

### 2015-05-05 python_src/HSTFile.py

@@ -14,7 +14,7 @@ class HSTFile:
     fitCountArray
     side
     """
-    def __init__ (self, fileID, dataDIR, peakPos, size, useNewFlat = 0):
+    def __init__ (self, fileID, dataDIR, peakPos, size, useNewFlat):
         """
         initialize ImaFile Object
         """
@@ -55,9 +55,10 @@ class HSTFile:
         for samp_i in range(self.nSamp - 1):
             if useNewFlat:
                 self.countArray[:, :, samp_i] = self.countArray[:, :, samp_i] * pamArray/newFlatArray
+                self.fltCountArray = self.fltCountArray * pamArray/newFlatArray
             else:
                 self.countArray[:, :, samp_i] = self.countArray[:, :, samp_i] * pamArray
-        self.fltCountArray = self.fltCountArray * pamArray
+                self.fltCountArray = self.fltCountArray * pamArray
         self.fitCountArray = self.fltCountArray.copy()
         self.chisqArray = np.ones([2*size + 1, 2*size + 1]) # array to save the chisq result
         self.zeroValue = np.zeros(self.fltCountArray.shape)

### 2015-05-06 summary/ABPIC-PAPER/msv1.tex
finally starting to write paper

\documentclass[iop]{emulateapj}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\shorttitle{Short Title}
\shortauthors{Zhou et al.}

\begin{document}
\title{Cloud structure of planetary mass companion AB Pic-b}
\author{Yifan Zhou, Daniel Apai, ...}
\affil{University of Arizona}

\begin{abstract}
...
\end{abstract}

\keywords{kw1, kw2, ...}
\maketitle
\section{Introcduction}

\section{Observation}
\section{Data Reduction}
\section{Result}
\section{Discussion}
\acknowledgments{
  Acknowledgments. 
}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-05-08 summary/ABPIC-PAPER/msv1.tex
data reduction part finished first version

@@
-\documentclass[iop]{emulateapj}
+\documentclass[apj]{emulateapj}
 
@@
 \usepackage{amsmath}
+\usepackage{natbib}
+\bibliographystyle{apj}
+\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
 \shorttitle{Short Title}
@@
 
+%%% new command %%%
+\newcommand{\ima}{\texttt{ima} file}
+\newcommand{\flt}{\texttt{flt} file}
+\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
 \begin{document}
@@
 \section{Data Reduction}
+
+\subsection{Cosmic Ray Identification}
+The WFC3 \texttt{calwf3} pipeline produces two types of calibrated
+files per exposure, \ima{} and \flt.  The \ima{} contains all
+calibrated non-destructive readouts. The \flt{} is additionally
+processed with an up-the-ramp fit that combines every readout into a
+single image with a linear regression for every pixel. In the
+meanwhile, up-the-ramp fit identifies cosmic ray by searching for
+outliers from the fitting result and makes correction
+coordinately. \citeauthor{Mandell2013} suggested that time series
+extract from {\flt}s have a rms 1.3 times larger than that obtained
+from {\ima}s with their transit spectroscopic observation data using
+WFC3 IR. Similar result was found in our analysis of WFC3 IR
+images. We speculate the larger scattering measured from {\flt}s is
+caused by jitter of the telescope, especially when number of sample
+per exposure is small. \citeauthor{Swain2013} also recommended to use
+non-destructive readouts in data reduction.
+
+We use the last readout in which the peak pixel of AB Pic b's image is
+not saturated for every exposure to carry out photometry
+measurement. For cosmic ray identification, we take a linear fit to
+the sums of pixels in a $7\times7$ box centered on the peak pixel for
+all readouts that do not have unsaturated pixel in that region. We
+identify exposures that have reduced $\chi^{2}$ values greater than
+2.5 as being contaminated by cosmic ray Using this method, there are 9
+out 348 exposures that cosmic ray hits were found in the AB Pic b's
+image region with this criterion. We did not make correction for these
+exposures considering the small number of readouts. Instead we exclude
+these images in further analysis. The scatterings of photometry
+measurements using files processed in this method is reduced by
+factors of 1.65 and 1.41 for F125W data set and F160W data set
+coordinately comparing to those measured with {\flt}s, which is
+consistent with \citet{Mandell2013}.
+
+\subsection{Continuous Bad Pixels Identification}
+Pixels with data quality flags 'bad detector pixels' (DQ = 4),
+'unstable response' (DQ = 32), and 'bad or uncertain flat value' (DQ =
+512) were masked out as suggested by previous exoplanet transit
+spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.
+
+\subsection{Flat Field Correction}
+\subsection{Primary Star PSF Subtraction}
+We removed the point spread function (PSF) of the primary star with
+standard roll subtraction method. For one target image, every other
+image that was taken with the same filter and different roll angle of
+the telescope was selected to form a PSF image cube. The PSF of
+primary star was subtracted by its own PSF in the PSF image.  The
+position offset of the target image and the PSF image was calculated
+with cross correlation. The PSF image was shifted using bilinear
+interpolation to align with the target image. By optimizing with least
+rms residual in the shaded region shown in Figure \ref{fig:image}, the
+amplitude scale of the PSF image was calculated. The PSF image
+provided the smallest subtraction residual among images in the PSF
+cube was selected as final PSF to be subtracted from target image.
+
+Using images with primary star subtracted with above method, an
+average background residual is reached as 2.1 \eps, which is more than
+one order of magnitude smaller than the photon noise. Therefore, our
+photometry is photon noise limited and we did not attempt to use
+more sophisticated PSF subtraction strategy.
+
+\begin{figure}
+  \centering
+  \plotone{original}
+  \plotone{subtracted}
+  \caption{One example of the original(upper panel) and primary star
+    subtracted (lower panel) images of AB Pic system. In the lower
+    panel, white contour defines a region of an annulus with circle
+    excluded. The rms residuals were optimized in this region when
+    calculation the amplitude scales of PSF images when doing primary
+    star image subtraction.}
+  \label{fig:image}
+\end{figure}
+\subsection{Aperture Photometry}
+
+We performed aperture photometry using images processed with above
+procedures.  Centroids of PSF of AB Pic b was located by 2 dimensional
+Gaussian fit with IDL routine \texttt{mpfit2dpeak}
+\citep{Markwardt2009}. Then aperture photometry was calculated using
+\texttt{aper} with aperture radius of 3 pixels. Aperture size is
+determined by taking into account both reducing noise level as well as
+excluding bad pixels.
+
+Photometry uncertainty is the combination of three independent components, readout
+noise, photon noise, and fluctuation in the background. We take the
+square root of the sum of the squares of the three components as the
+uncertainty of one photometry measurement. In fact, the uncertainty is
+denominated by photon noise.
 \section{Result}
 \section{Discussion}
-\acknowledgments{
-  Acknowledgments. 
-}
-
+\bibliography{ref.bib}
 \end{document}

### 2015-05-08 ABPIC_Data_Analysis/TotalRampUp.py
some plot modified coordinately

@@ -5,6 +5,7 @@ import glob
 import sys
 sys.path.append('../python_src')
 from linearFit import linearFit
+import matplotlib.pyplot as plt
 """
 new photometry method, do the up the ramp fit after sum up all pixel values in one read out
 """
@@ -12,10 +13,11 @@ new photometry method, do the up the ramp fit after sum up all pixel values in o
 if __name__ == '__main__':
     pklList = glob.glob('../data/ABPIC-B_myfits/icdg*pkl')
     pklList.sort()
-    size = 9# measure the photometry from a size= box
+    size = 7# measure the photometry from a size= box
     chisqTh = 2.5
     flux = np.zeros(len(pklList))
     fluxerr = np.zeros(len(pklList))
+    chisqList = np.zeros(len(pklList))
     for i, fn in enumerate(pklList):
         hst = pickle.load(open(fn, 'rb'))
         imShape = hst.countArray.shape[:-1] # the last dimension in shape list is the number of samples. First two dimensions are the size of the image for prepared for correction
@@ -35,11 +37,13 @@ if __name__ == '__main__':
         # flux[i] = readoutList[-1]/hst.expTime[nSampEff - 2]
         # fluxerr[i] = errorList[-1]/hst.expTime[nSampEff - 2]
         print fn, chisq, flux[i]
+        chisqList[i] = chisq
 
     df = pd.read_csv('2015_Feb_27_myfits_aper=5_result.csv')
     df['FLUX'] = flux
     df['FLUXERR'] = fluxerr
     df.to_csv('totalRampUp_size_{0}_result.csv'.format(size), index = False)
+
 
 
 

### 2015-05-08 ABPIC_Data_Analysis/calStd.py

@@ -1,0 +1,32 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import sys
+import numpy as np
+
+if __name__ == '__main__':
+    fn = sys.argv[1]
+
+
+    df = pd.read_csv(fn, parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    try:
+        cosmicRayFN = sys.argv[2]
+        cosmicRayDF = pd.read_csv(cosmicRayFN, parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+        df['FLUX'][np.where(np.isnan(cosmicRayDF['FLUX']))[0]] = np.nan
+        print len(np.where(np.isnan(cosmicRayDF['FLUX']))[0]), len(df)
+    except IndexError:
+        pass
+    """
+    normalize not only by filter, but by rolling angle
+    """
+    fig, ax = plt.subplots()
+    df['FLUX0'] = df['FLUX']
+    df.loc[(df['FILTER'] == 'F125W'), 'FLUX0'] = df[(df['FILTER'] == 'F125W')]['FLUX']/df[(df['FILTER'] == 'F125W')]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129), 'FLUX0'] = df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F160W'), 'FLUX0'] = df[(df['FILTER'] == 'F160W')]['FLUX']/df[(df['FILTER'] == 'F160W')]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129), 'FLUX0'] = df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    df['ERR0'] = df['FLUXERR']/df['FLUX']
+    df['Time'] = np.float32(df.index.values - df.index.values[0])/(60 * 60 * 1e9) #time in ns
+
+    subdf = df[(df['ORBIT'] >= 10)]
[…]

### 2015-05-08 ABPIC_Data_Analysis/getPaperImage.py

@@ -1,0 +1,14 @@
+import idlsave
+from astropy.io import fits
+cube =idlsave.read('2015_May_07_prepared.sav')
+cube1 = idlsave.read('2015_May_07_subtracted.sav')
+
+fitsFN = '../data/ABPIC-B/icdg07p3q_flt.fits'
+primaryHD = fits.getheader(fitsFN, 'primary')
+sciHD = fits.getheader(fitsFN, 'sci')
+
+fits1 = fits.HDUList([fits.PrimaryHDU(header = primaryHD), fits.ImageHDU(cube.cube[0, :, :], header = sciHD)])
+fits2 = fits.HDUList([fits.PrimaryHDU(header = primaryHD), fits.ImageHDU(cube1.cube1[0, :, :], header = sciHD)])
+
+fits1.writeto('original.fits', clobber = True)
+fits2.writeto('subtracted.fits', clobber = True)

### 2015-05-08 ABPIC_Data_Analysis/plotPaperImage.py

@@ -1,0 +1,44 @@
+import matplotlib.pyplot as plt
+import aplpy
+import numpy as np
+
+
+
+plt.close('all')
+#fig = plt.figure()
+# gc = aplpy.FITSFigure('original.fits', hdu = 1, figure = fig)
+
+# gc.show_colorscale(cmap = 'hot', interpolation = 'bicubic',vmin=-50, vmax = 2000, stretch = 'arcsinh')
+# ax = plt.gca()
+# ax.set_xlim([44, 184])
+# ax.set_ylim([98, 238])
+# plt.savefig('original.pdf')
+fig1 = plt.figure()
+gc = aplpy.FITSFigure('subtracted.fits', hdu = 1, figure = fig1)
+
+gc.show_colorscale(cmap = 'hot', interpolation = 'bicubic',vmin=-50, vmax = 2000, stretch = 'arcsinh')
+ax = plt.gca()
+
+cen = [114.212, 169.284]
+seccen1 = [94.78, 208.07]
+seccen2 = [114.28, 213.83]
+
+xx, yy = np.meshgrid(range(256), range(256))
+dist = np.sqrt((xx-cen[0])**2 + (yy-cen[1])**2)
+dist1 = np.sqrt((xx-seccen1[0])**2 + (yy-seccen1[1])**2)
+dist2 = np.sqrt((xx-seccen2[0])**2 + (yy-seccen2[1])**2)
+
+mask = np.ones((256, 256))
+mask[(dist>=30) & (dist<=60)] = 0
+mask[dist1<=10] = 1
+mask[dist2<=10] = 1
+
+#ax.contourf(xx, yy, mask, 3, colors = [(0,0,0,0), '0.2', '0.3'], hatches = ['o', None, None], alpha = 0.5, antialiased = True)
+ax.contour(mask, levels = [-0.1,0.9], antialiased = True, lw = 0.8, colors = 'white')
+ax.set_xlim([44, 184])
+ax.set_ylim([99, 239])
+plt.savefig('subtracted.pdf')
+
+
+
+

### 2015-05-09 summary/ABPIC-PAPER/msv1.tex
you have to work on 2m1207

@@
 We performed aperture photometry using images processed with above
-procedures.  Centroids of PSF of AB Pic b was located by 2 dimensional
+procedures.  Centroids of PSFs of AB Pic b were located by 2 dimensional
 Gaussian fit with IDL routine \texttt{mpfit2dpeak}
@@
 \texttt{aper} with aperture radius of 3 pixels. Aperture size is
-determined by taking into account both reducing noise level as well as
+determined by taking into account both minimizing noise level as well as
 excluding bad pixels.

### 2015-05-15 ABPIC_Data_Analysis/pyDS9_blink.py
Just try magit

@@ -16,8 +16,6 @@ import astropy.io.fits as fits
 #     else:
 #         print 'target missing'
 #         return 1
-
-        
 #     d.set(' '.join(['file', fits_name]))
 #     d.set('align yes')
 #     d.set('contour clear')
@@ -28,16 +26,16 @@ import astropy.io.fits as fits
 #     d.set('scale mode 99.5')
 #     d.set('zoom 4')
 #     return center
-    
+
 if __name__ == '__main__':
     d = ds9.ds9()
     d.set('blink no')
-    d.set('frame delete all') # intitialize ds9
+    d.set('frame delete all')  # intitialize ds9
     file_dir = '/home/yzhou/Documents/Exoplanet_Patchy_Project/data/ABPIC-B'
-    
+   
     target = 'ABPIC-B'
     if target == 'ABPIC-B':
-        planet_coord = '06:19:12.94 -58:03:20.9' # RA and Dec of the planet in FK5 coordinate, data obtained from simbed, for pan the iamge to centered on the target
+        planet_coord = '06:19:12.94 -58:03:20.9'   # RA and Dec of the planet in FK5 coordinate, data obtained from simbed, for pan the iamge to centered on the target
     elif target == '2M1207B':
         planet_coord = '12:07:33.467 -39:32:54.00'
     else:
@@ -61,5 +59,3 @@ if __name__ == '__main__':
     d.set('match scale')
     d.set('blink yes')
     d.set('blink interval 1')
-
-    

### 2015-05-15 ABPIC_Data_Analysis/plotHist.py
Mentoring committee meeting finished

@@ -1,0 +1,50 @@
+#/usr/bin/env python
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+plt.style.use('ggplot')
+
+def normalize(df):
+    """
+    normalize the flux by filter and angle
+    """
+    
+    flux0 = np.zeros(len(df))
+    flux0[np.where((df['FILTER'] == 'F125W') & (df['POSANG'] == 129))] = df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    flux0[np.where((df['FILTER'] == 'F125W') & (df['POSANG'] == 101))] = df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 101)]['FLUX']/df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 101)]['FLUX'].mean()
+    flux0[np.where((df['FILTER'] == 'F160W') & (df['POSANG'] == 129))] = df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    flux0[np.where((df['FILTER'] == 'F160W') & (df['POSANG'] == 101))] = df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 101)]['FLUX']/df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 101)]['FLUX'].mean()
+    return flux0
+    
+if __name__ == '__main__':
+    fltFN = '2015_Feb_10_flt_aper=5_result.csv'
+    newFN = '2015_May_02_noramp_aper=5.00_result.csv'
+    fltDF = pd.read_csv(fltFN, parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    newDF = pd.read_csv(newFN, parse_dates = {'datetime':['OBS_DATE', 'OBS_TIME']}, index_col = 'datetime')
+    fltDF = fltDF[fltDF['ORBIT']>=10]
+    newDF = newDF[newDF['ORBIT']>=10]
[…]

### 2015-05-15 ABPIC_Data_Analysis/plotLC.py

@@ -20,16 +20,15 @@ if __name__ == '__main__':
     """
     fig, ax = plt.subplots()
     df['FLUX0'] = df['FLUX']
-    df.loc[(df['FILTER'] == 'F125W'), 'FLUX0'] = df[(df['FILTER'] == 'F125W')]['FLUX']/df[(df['FILTER'] == 'F125W')]['FLUX'].mean()
-    # df.loc[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129), 'FLUX0'] = df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX'].mean()
-    df.loc[(df['FILTER'] == 'F160W'), 'FLUX0'] = df[(df['FILTER'] == 'F160W')]['FLUX']/df[(df['FILTER'] == 'F160W')]['FLUX'].mean()
-    # df.loc[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129), 'FLUX0'] = df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F160W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F125W') & (df['POSANG'] == 101), 'FLUX0'] = df[(df['FILTER'] == 'F125W')& (df['POSANG'] == 101)]['FLUX']/df[(df['FILTER'] == 'F125W')& (df['POSANG'] == 101)]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129), 'FLUX0'] = df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX']/df[(df['FILTER'] == 'F125W') & (df['POSANG'] == 129)]['FLUX'].mean()
+    df.loc[(df['FILTER'] == 'F160W')& (df['POSANG'] == 101), 'FLUX0'] = df[(df['FILTER'] == 'F160W')& (df['POSANG'] == 101)]['FLUX']/df[(df['FILTER'] == 'F160W')& (df['POSANG'] == 101)]['FLUX'].mean()
[…]

### 2015-05-19 2M1207ANALYSIS/PSF_generator.py
expanded PSF parameter space

@@ -1,10 +1,12 @@
 #! /usr/bin/env python
 import subprocess as sp
 import numpy as np
+import os
 """
 Use Tinytim to generate a PSFs
 """
 
+aimDIR = './PSFs/'
 def modifyIn(inFile, jitx, jity, secDis):
     inFile[1] = 'Jitx_{0:0>2d}_Jity_{1:0>2d}_Dis_{2:.2f}_\n'.format(jitx, jity, secDis)
     inFile[9] = '{0:.5f} # Major axis jitter in mas\n'.format(jitx)
@@ -14,15 +16,25 @@ def modifyIn(inFile, jitx, jity, secDis):
 
 if __name__ == '__main__':
     inFile = open('2mass_psf.in', 'r').readlines()
-    jitxList = range(0,50,10)
-    jityList = range(0,50,10)
-    disList = np.arange(2.9, 3.1, 0.05) #fix displacement at 3.0
+    jitxList = range(0,80,10)
+    jityList = range(0,80,10)
+    disList = np.arange(2.6, 2.9, 0.05) #fix displacement at 3.0
     for jitx in jitxList:
         for jity in jityList:
             for dis in disList: 
                 modFile = modifyIn(inFile, jitx, jity, dis)
+                fn = modFile[1].strip()+'00.fits'
+                psf_fn = modFile[1].strip()+'00_psf.fits'
+                tt3_fn = modFile[1].strip()+'.tt3'
                 out = open('temp.in', 'w')
                 out.writelines(modFile)
                 out.close()
                 sp.call(['tiny2', 'temp.in'])
                 sp.call(['tiny3', 'temp.in', 'sub=10'])
+                os.remove(psf_fn)
+                os.remove(tt3_fn)
+                os.rename(fn, os.path.join(aimDIR, fn))
+
+
+
+    

### 2015-05-22 2M1207ANALYSIS/PSF_generator.py
before generate PSFs, commit something

@@ -2,39 +2,45 @@
 import subprocess as sp
 import numpy as np
 import os
+#import sys
 """
 Use Tinytim to generate a PSFs
 """
 
-aimDIR = './PSFs/'
-def modifyIn(inFile, jitx, jity, secDis):
-    inFile[1] = 'Jitx_{0:0>2d}_Jity_{1:0>2d}_Dis_{2:.2f}_\n'.format(jitx, jity, secDis)
+
+xy = [[[135,161], [145,161], [135,173], [145,173]],
+      [[142, 159],[152,159], [142, 171], [152, 171]]]
+
+def modifyIn(inFile, angle, dither, jitx, jity, secDis):
+    xc, yc = xy[angle][dither]
+    inFile[1] = 'Jitx_{0:0>2d}_Jity_{1:0>2d}_Dis_{2:0>2.2f}_angle_{3:d}_dither_{4:d}\n'.format(jitx, jity, secDis,angle, dither)
     inFile[9] = '{0:.5f} # Major axis jitter in mas\n'.format(jitx)
     inFile[10] = '{0:.5f} # Major axis jitter in mas\n'.format(jity)
+    inFile[14] = '{0:d} {1:d}  # Position 1'.format(xc, yc)
     inFile[251] = '{0:.5f} #z4 = Focus\n'.format(secDis/100.)
     return inFile
 
 if __name__ == '__main__':
+
     inFile = open('2mass_psf.in', 'r').readlines()
-    jitxList = range(0,80,10)
-    jityList = range(0,80,10)
-    disList = np.arange(2.6, 2.9, 0.05) #fix displacement at 3.0
-    for jitx in jitxList:
-        for jity in jityList:
-            for dis in disList: 
-                modFile = modifyIn(inFile, jitx, jity, dis)
-                fn = modFile[1].strip()+'00.fits'
-                psf_fn = modFile[1].strip()+'00_psf.fits'
-                tt3_fn = modFile[1].strip()+'.tt3'
-                out = open('temp.in', 'w')
-                out.writelines(modFile)
-                out.close()
-                sp.call(['tiny2', 'temp.in'])
-                sp.call(['tiny3', 'temp.in', 'sub=10'])
-                os.remove(psf_fn)
-                os.remove(tt3_fn)
-                os.rename(fn, os.path.join(aimDIR, fn))
-
-
-
-    
+    jitxList = np.arange(0,50,10)
+    jityList = np.arange(0,50,10)
[…]

### 2015-05-30 summary/TinyTimPSF/TinyTimPSF.tex
do tinytim psf photometry

--- 2015-02-08 summary/Systematics1/Systematics1.tex
@@
 \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
-
+\newcommand{\chisq}{\ensuremath{\chi^2}}
 \title{ 
 \normalfont \normalsize 
-\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
+\textsc{TinyTim PSF} \\ [25pt] % Your university, school and/or department name(s)
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Systematic Error Correction\\ % The assignment title
+\huge Data Preparation\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 \maketitle % Print the title
-\section{Summary}
 
-According to previous results, there are two kinds of systematic errors
-that downgrade the quality of photometry and need to be corrected.
+This document is a summary of using TinyTim PSF to measure the
+photometry of 2M1207 system.
+
+2M1207 system has a very small separation between the primary and
+secondary. The peak of primary and secondary separates about 6
+pixels. A perfect match of primary image and PSF is required at an
+extreme level to ensure a good photometry measurement of
+2M1207b. Image of the same system with different roll angle is an
+option for PSF subtraction. However, considering coarse sample rate of
+WFC3 IR, to shift the image can generate large artifact no matter what
+interpolation method is using. Also, in our data, the angle telescope
+rolled is ~30 degree, which could cause self-subtraction of the
+secondary.
+
+The advantage of TinyTim PSF is that TinyTim can produce 10x super
+sampled PSF so that image shifting and interpolation is no longer a
+problem. The downside of TinyTim is that it has several knobs, such as
+jittering, secondary mirror shift to tune and even using the best
+matched parameter set, TinyTim PSF are not good at modeling
+diffraction spiders and coma due to intrinsic problems.
+
+\section{Generate PSF}
+
 \begin{enumerate}
-\item images that are taken with different dithering positions have
-  significant difference in photometry. The most possible cause is 
-  bad flat fielding.
-\item Short timescale variation on the light curves. Red noise needs
-  to be caught and corrected. Following effects can contribute to red
-  noise:
-  ramp effect, jitter of the telescope, telescope temperature
-  fluctuation, intra-pixel  response fluctuation, cosmic rays.
+  \item specify spectrum for PSF using \texttt{tiny1}, and generate
+    the input script for \texttt{tiny2}
+  \item using python script \texttt{PSF\_generator.py} to modify the
+    input script and run \texttt{tiny2} and \texttt{tiny3} to generate
+    PSF\\
+    Lines in the input script that need to be changed:
+
+    \begin{itemize}
+    \item line 2, the output file name
+    \item line 8, the filter
+    \item line10, major axis jitter in mas
+    \item line 11, minor axis jitter in mas
+    \item line 14, the x and y position on the detector, in integer
+    \item line 260, secondary mirror displacement
+    \end{itemize}
+    \item the way to generate a 10x sampled PSF using \texttt{tiny3}:
+      \texttt{tiny3 input.script sub=10}
 \end{enumerate}
 
-  \section{Red Noises}
-  \subsection{Ramp Effect and Pointing Problem}
-  According to Deming et al. 2013, Wilkins 2014, ramp effect becomes significant
-  when exposure level is larger than 30000 e$^{-}$ per pixel. For both
-  F125W and F160W images, the largest count rate per pixel at the
-  planetary companions place is 2000 - 2200 e$^{-}$s$^{-}$. For F125W
-  images, the exposure time is 30s for each image while for F160W is
-  15s. Therefore, the pixel that is the peak of the PSF of the
-  companion object in the F125W image may be affected by ramp effect.
+\section{Least \chisq Fit}
 
-  In Figure \ref{fig:peak}, I plotted the count for one pixel that has
-  the largest flux at the PSF region of ABPIC-B for every image. In short time-scale
-  (i.e. in one exposure set, does not demonstrate in the plot), peak
-  fluxes do not have a clear and common ramp effect pattern. For first
-  3 orbits, the counts have large scatterings for different dithering
-  positions. because the peaks of the PSF could locate at the center
-  or edge of the pixel. For the last 3 orbits for which dithering is not
-  applied, the peak pixel count demonstrates clear trend.  In the 4th
-  and 6th orbits, the peak pixel count decreases with time while for
-  5th orbits, it slightly increases with time.
+To match the center of PSF and star image, fit the PSF to image in a
+grid of $dx$ and $dy$. The least \chisq fit calculates the amplitude
+of PSF and a sky level. Amplitude and sky level can be solved
+analytically.
+\newcommand{\PSF}{\ensuremath{\mathrm{PSF}}}
+\newcommand{\Img}{\ensuremath{\mathrm{Img}}}
+\begin{equation}
+  \begin{split}
+    \chisq &= \sum_{i} \frac{(\mathrm{Img}_{i} - a\cdot\mathrm{PSF}_{i} -
+      b)^{2}}{\sigma_{i}^{2}}\\
+    &= \sum_{i} \frac{\mathrm{Img}_{i}^{2}+a^{2}\cdot \mathrm{PSF}_{i}^{2}+b^{2}+2ab\cdot \mathrm{PSF}_{i}
+      -2a\cdot \mathrm{Img}_{i}\PSF_{i}-2b \mathrm{Img}_{i}}{\sigma_{i}^{2}}
+  \end{split}
+    \label{eq:chisq}
+\end{equation}
+To obtain least \chisq, $\frac{\partial \chisq}{\partial a} = 0$,
+$\frac{\partial \chisq}{\partial b}=0$. So that
+\begin{equation}
+  \label{eq:calchisq}
+  \begin{bmatrix}
+    &\sum_{i}\frac{\PSF_{i}^{2}}{\sigma_{i}^{2}}
+    &\sum_{i}\frac{\PSF_{i}}{\sigma_{i}^{2}}\\
+    &\sum_{i}\frac{\PSF_{i}}{\sigma_{i}^{2}}
+    &\sum_{i}\frac{b}{\sigma_{i}^{2}}
+  \end{bmatrix}
+  \cdot
+  \begin{bmatrix}
+    &a\\
+    &b
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    &\sum_{i}\frac{\Img_{i}\cdot\PSF_{i}}{\sigma_{i}^{2}}\\
+    &\sum_{i}\frac{\Img_{i}}{\sigma_{i}^{2}}
+  \end{bmatrix}
+\end{equation}
+$a$ and $b$ can be easily solved using simple linear algebra.
 
-    \begin{figure}[th]
-    \centering
-    \includegraphics[width=\textwidth]{ramp1Pix}
-    \caption{Count for peak pixel on the image of ABPIC-B. Different
-      color indicate different dithering position. Count rates are measured
-      from the original \texttt{ima} files (no primary subtraction applied)}
-    \label{fig:peak}
-  \end{figure}
-
-  First of all, I cannot be certain whether ramp effect plays a
-  significant role in this trend. The exposure levels of peak pixel for
-  F125W images are more than 70000 e$^{-}$, for 5th orbit they are
-  near 90000 e$^{-}$, which are almost reach the fully saturation
-  level of 100000 e$^{-}$. However, short timescale variations are
-  random and no 'hook shaped' (Wilkins et al. 2014) light curves
-  appeared.
-
-  This trends for peak pixel count are correlated with the positions of
-  PSF centroids. I plot the PSF centroids that are measured by Gaussian
-  fitting for 4th, 5th and 6th orbits in Figure \ref{fig:center}. The
-  PSF centroids shifted in a specific direction within one orbit. In
-  4th and 6th orbits, the centroids shift to +y direction and in 5th
-  orbit they shift to (+x, +y) direction. In 4th and 6th orbits, the
-  centroids shift to the edge of the pixel while in 5th orbit, they
-  slightly shift to the pixel center.
-
-  \begin{figure}[th]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Ymove}
-    \caption{PSF centroid shift for ABPIC-B in 4th, 5th, and 6th
-      orbits. Y-axes are the centroid coordinates $(x, y)$ minus the
-      those for the first image in each orbit $(x_0, y_0)$. Red dots
-      are for x-direction and blue + are for y-direction.}
-    \label{fig:center}
-  \end{figure}
-
-  To sum,
-  \begin{enumerate}
-  \item Peak pixels have high exposure levels, especially for F125W,
-    ramp effect needs to be considered.
-  \item Telescope has a pointing shift within each orbit, and caused
-    the peak pixel count varies in a specific trend. Since peak pixel
-    contains $\sim 25\%$ of the total flux, if there were a
-    considerable intra-pixel response variation, this pointing shift
-    could be an error source.
-  \end{enumerate}
-
-\subsection{Cosmic Rays in Up-the-Ramp Fitting}
+\section{Fit 2 PSFs together.}
+Simply change equation \ref{eq:calchisq} to
+\newcommand{\PSFI}{\ensuremath{\mathrm{PSF1}}}
+\newcommand{\PSFII}{\ensuremath{\mathrm{PSF2}}}
+\begin{equation}
+  \label{eq:1}  
+  \begin{bmatrix}
+    & \sum_{i} \frac{\PSFI_i^2}{\sigma^2}
+    &\sum_{i}\frac{\PSFI_i\cdot\PSFII_i}{\sigma_i^2}
+    &\sum_{i}\frac{\PSFI_i}{\sigma_i^{2}}\\
+    & \sum_{i} \frac{\PSFI_i\cdot\PSFII_{i}}{\sigma^2}
+    &\sum_{i}\frac{\PSFII_i^{2}}{\sigma_i^2}
+    &\sum_{i}\frac{\PSFII_i}{\sigma_i^{2}} \\
+    &\sum_{i}\frac{\PSFI_{i} }{\sigma_{i}^{2}}
+    &\sum_{i}\frac{\PSFII_{i} }{\sigma_{i}^{2}}
+    &\sum_{i}\frac{b}{\sigma_{i}^{2}}
+  \end{bmatrix}
+  \cdot
+  \begin{bmatrix}
+    &a_1\\
+    &a_2\\
+    & b
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    &\sum_{i}\frac{\Img_i\PSFI_i}{\sigma_i^2}\\
+    &\sum_i \frac{\Img_i\PSFII_i}{\sigma_i^2}\\
+    &\sum_{i}\frac{\Img_{i}}{\sigma_{i}^{2}}
+  \end{bmatrix}
+\end{equation}
 \end{document}

### 2015-05-30 ABPIC_Data_Analysis/PSF_generate_list.py

@@ -1,0 +1,43 @@
+#! /usr/bin/env python
+from __future__ import print_function
+import numpy as np
+import os
+from pyTinyTim import pyTinyTim
+
+#import sys
+"""
+Use Tinytim to generate a PSFs
+"""
+
+
+xy = [[[95,208], [105,208], [95,219], [105,219]],
+      [[129, 222],[139,222], [129, 233], [139, 233]]]
+
+if __name__ == '__main__':
+    inFile = open('abpic.in', 'r').readlines()
+    jitxList = np.arange(0,50,10)
+    jityList = np.arange(0,50,10)
+    disList = np.arange(0, 3.6, 0.2) #fix displacement at 3.0
+    if not os.path.exists('./PSF'):
+        os.mkdir('./PSF')
+
+    
+    for angle in [0, 1]:
+        for dither in range(4):
+            for filter_name in ['F125W', 'F160W']:
+                aimDIR = os.path.join('.','PSF', 'filter_{0}_angle_{1}_dither_{2}'.format(filter_name,angle, dither))
+                if not os.path.exists(aimDIR):
+                    os.mkdir(aimDIR)
+                PSFFNFile = open(os.path.join('.','PSF', 'filter_{0}_angle_{1}_dither_{2}'.format(filter_name, angle, dither), 'fn.dat'), 'w')
+                for jitx in jitxList:
+                    for jity in jityList:
+                        for dis in disList:                        
+                            #aimDIR = os.path.join(os.getcwd(), 'PSFs')
+                            xc, yc = xy[angle][dither]
+                            xc = xc + 380
+                            yc = yc + 380
+                  
+                            psfFN = pyTinyTim(xc, yc, filter_name, jitx, jity, dis, outputDIR = aimDIR)
+                            PSFFNFile.write(psfFN + '\n')
+
+                PSFFNFile.close()

### 2015-05-30 python_src/test.py

@@ -1,0 +1,8 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+
+"""comment
+"""
+
+if __name__ == '__main__':
+    

### 2015-07-03 summary/reply/reply.tex
replied finally

\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\synctex=1
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
%\usepackage[nolists, nomarkers]{endfloat}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[section]{placeins}
\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs -
                          % comment this line for an assignment with
                          % lots of text
\setlength\parskip{12pt}

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Reply to Daniel \& Glenn\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yifan Zhou}
\date{\normalsize\today} % Today's date or a custom date

\usepackage{scalerel}
\usepackage{calc}
\global\newcounter{embedlevel}
\global\newlength\embedspace
\embedspace=2ex
\setcounter{embedlevel}{1}
\newcommand\embed[1]{%
  \stepcounter{embedlevel}%
  \stretchrel{\rule{0.2ex}{1ex}}{\hspace{1.8ex}\parbox{%
    \textwidth-\value{embedlevel}\embedspace}{%
    \rule{0ex}{2ex}\textbf{\textit{#1}}\rule[-1.3ex]{0ex}{1.3ex}%
  }}%
  \vspace{.5ex}%
  \addtocounter{embedlevel}{-1}%
}
\begin{document}

\maketitle % Print the title
\section{Clarifications}
\embed{
1) How do you scale (if you scale) the residuals you subtract?
}

The residuals are not scaled. I simply took the median of the
residuals that have the same dither position and position angle, and
subtracted the median combination from the original images. Since The
chisq distribution of the fitting looks very reasonable for me, I did
not attempt to make further adjustment of the residual models.

\embed{
 2) How do the residuals images look like? What is the relative
 fraction of the light that is not subtracted well?
}

\embed{
 3) When you calculate the brightness of the sources, how do you use
 the information of the residuals and the TinyTim-based PSF?
}

These are very important points. However I did not deal with them very
carefully in the fit. As I showed in our previous discussion,
Tinytim does not provide a precise PSF model so that the residual of
tinytim PSF subtraction has a 2\% - 4\% average relative fraction of
original image(mean(residual/image) $\sim$ 2\%-\%4). For the fitting routine I used this
time,  the fluxes of A and B purely calculated from the
amplitudes of the two components of the PSF. I did not count any flux
from the residual model into the fluxes of A or B.

An average relative fraction of 2-4\% of the residual model could be a
significant source of uncertainty. Especially for the case that I
ignored the flux from the residual totally. However, I have not come up
with any ideas on including the residual flux to the final result. I
think we need further discussion about this point.

\embed{ a) When you say you carried out a "two component tinytim PSF
  fit", it is not clear to me what you mean.  I assume the linear
  superposition of two TinyTim PSFs.  But do you mean one for A and
  one for B that are otherwise identical (or perhaps different in some
  manner other than brightness?).  Or do you mean for B (and perhaps
  also A) you have used a combination of TinyTim PSFs that, in
  combination (perhaps with different defocus of color terms?) better
  represent the observed PSF?  }

I used different PSFs for A and B. My fitting routine firstly
generates a list of PSFs using the position of A and the NIR spectrum
of A (Bonnefoy et. al. 2014) with different telescope jittering. I fit
this PSF to the image of A with an area where the image of B is mostly
excluded ( using a 3-pixel radius mask centered on B) to find the best
matched position and Jittering. Next, I used this jittering to
generate a PSF of B with B's position on detector and B's spectrum
(Patience et al. 2010). In the third step, I fit the two PSFs together
with the position of A fixed , and to find the best matched position
of B and amplitudes of 2 PSFs.

\embed{
b) To me it is interesting (but not really unexpected) that binning
by "same position angle" (i.e., spacecraft roll angle) improves.
Off-rolling does thermally destablise the PSF to some extent - by
changing the angle to the sub-solar point on the Earth as the
telescope orbits and can drive quasi-breathing modes.  I am a bit
surprised that these stabilize out as well as they seem to do (as
exhibited by the factor of 10 improvement in chisq).  It would be
interesting to know how much of that improvement is do to "same
dither position" and how much to "same roll" (as differently binned).
I am sure they both play together to reduce the residuals, but
knowing this could have influence on how future observations might be
constructed.}

The position dependency of the residual pattern comes from at least
three parts.
\begin{enumerate}
\item  Instrumental as Glenn described 
\item The imperfection of flat
  field is not modeled with TinyTim. 
\item  The PSFs are sampled
  differently at different position with a low sample rate.
\end{enumerate}

It is actually difficult to differentiate the improvement in terms of
different instrumental effect, since the there are significant
uncertainty and artifect generated by last two points.

\embed{
Overall, these look good; the question is, of course, how much of the
apparent trend is real.  One note here: It is curious how both A and B
have an increase in the first 3 orbits and then a different behavior
in orbits 4-6.}

\embed{
Could you explain how exactly do you determine the normalization
factors for the different angles/dithering positions?}

I median combined the fluxes calculated with images taking with same
filter, dithering position and roll angles, and devided the median
combination from every photometric result of these exposures.

\section{Discussion and further analysis}
\embed{
Daniel asks: "how much of the apparent trend is real".  This might be
difficult to ascertain.  Clearly the F125W and F160W for A seem well
correlated (1st 3 vs last 3 orbits) , but that correlation possibly
could still be instrumental.  If you took the new light curves as
binned, for B:
}

\embed{
if you average all the points together in each orbit (loosing the
 finer temporal information) is the change in normalized flux for B
 over the six orbits also "consistent" from F125W to F160W **AND** is it
 correlated with A?  It's a little harder to tell (quantitatively) as
 plotted for B simply because it is noisier than A.  In both A and B
 (both bands) the flux (by eye) also seems lower in the last three
 orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
 expect that behavior in A and B to be independent, whereas if
 correalted that may be an instrumental signature.}

I binned the light curve of A and B by orbits using average. According to the result
I obtained, there are no clear correlation/anti-correlation betwee the
fluxes of A and B. Figure \ref{fig:1} presented the orbit-binned light
curves.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{binned_coor_F125W}
  \includegraphics[width=0.45\textwidth]{binned_coor_F160W}
  \caption{Orbit-binned light curves. Binned curve for B showed a sine
  wave shaped curve}
  \label{fig:1}
\end{figure}

\embed{
This looks quite nice and indeed, the 10.9 hours is not a period that
I would obviously associate with an instrumental artifact.  Have you
tried the same for the F160W LC? It would be a nice verification if
you would get a similar periodicity.}

By eye, unbinned light curve of F160W does not show a sine-wave like
shape. However, in the orbit-binned curve, the light curve of B showed
a sine wave shaped curve as shown in Figure \ref{fig:1}. For F160W LC
of B, The least square fit results in a sine curve with a period of
9.3 hr. I also tried to fit the F160W light curve with a sine curve
that has a fixed period of 10.9 hr. I plotted the two best fit sine
curves together with the original observation points as in Figure
\ref{fig:2}. Considering the large scattering of photometric
measurement of B, it is actually hard to tell from Figure \ref{fig:2} whether
the 9.3 hr light curve fits better than the 10.9 hr light curve.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{sineCurveFit}
  \caption{sinusoidal wave fit to the light curve of 2M1207B. For the
    F160W panel, two curves for periods of 9.3 hr and 10.9 hr are
    plotted.}
  \label{fig:2}
\end{figure}

\embed{
Also, to be consistent, can you please use the same fitting procedure
for A (in both filters) and send similar plots?}

I did the fitting for A in both fittings. The rise in first three
orbits is the main feature that defines the sinusoidal wave. However
if it were truly part of a sin wave, the sine function would not be
well constrained by this small segment. For the light curve of F125W,
the fitting routine found a best fitted curve with a period of 6.86
hr. However the points in the 5th orbit are totally off the fitted
curve. For F160W, the fitting routine failed to converge when fitting
a sine curve to the light curve. Figure \ref{fig:3} presented the
fitted sinusoidal wave and the observational points for 2M1207A with
F125W.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{sineCurveFit_primary}
  \caption{sine wave fitting for 2M1207A.}
  \label{fig:3}
\end{figure}

\embed{
(c) I assume the 10.9 hour fit came from a least-squares analysis --
not quite a full observing/sampling period.  "By eye" it certainly
loooks good, but might be interesting to also do a simple periodogram
analysis, just to see if this might be an alias?}

I thought about this idea before. However, 10.9 hour is longer than the
observation baseline and we if that were the case, we did not have a
periodical signal. I was wondering whether the periodogram would work
for data that does not cover a whole period.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-07-03 summary/reply_to_Daniel_Glenn.tex
replied finally

--- 2015-07-03 summary/reply/reply.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Reply to Daniel \& Glenn\\ % The assignment title
+\huge Cross Correlation Test and Preliminary Aperture Photometry Result\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\author{Yifan Zhou}
+\author{Yifan Zhou} % Your name
+
 \date{\normalsize\today} % Today's date or a custom date
 
-\usepackage{scalerel}
-\usepackage{calc}
-\global\newcounter{embedlevel}
-\global\newlength\embedspace
-\embedspace=2ex
-\setcounter{embedlevel}{1}
-\newcommand\embed[1]{%
-  \stepcounter{embedlevel}%
-  \stretchrel{\rule{0.2ex}{1ex}}{\hspace{1.8ex}\parbox{%
-    \textwidth-\value{embedlevel}\embedspace}{%
-    \rule{0ex}{2ex}\textbf{\textit{#1}}\rule[-1.3ex]{0ex}{1.3ex}%
-  }}%
-  \vspace{.5ex}%
-  \addtocounter{embedlevel}{-1}%
-}
 \begin{document}
@@
 \maketitle % Print the title
-\section{Clarifications}
-\embed{
-1) How do you scale (if you scale) the residuals you subtract?
-}
+Clarifications
+>1) How do you scale (if you scale) the residuals you subtract?
 
@@
 
-\embed{
- 2) How do the residuals images look like? What is the relative
- fraction of the light that is not subtracted well?
-}
-
-\embed{
- 3) When you calculate the brightness of the sources, how do you use
- the information of the residuals and the TinyTim-based PSF?
-}
+> 2) How do the residuals images look like? What is the relative fraction of the light that is not subtracted well?     
+> 3) When you calculate the brightness of the sources, how do you use
+> the information of the residuals and the TinyTim-based PSF?
 
 These are very important points. However I did not deal with them very
-carefully in the fit. As I showed in our previous discussion,
+carefully in my previous fit. As I showed in our previous discussion,
 Tinytim does not provide a precise PSF model so that the residual of
-tinytim PSF subtraction has a 2\% - 4\% average relative fraction of
-original image(mean(residual/image) $\sim$ 2\%-\%4). For the fitting routine I used this
+tinytim PSF subtraction has a 2% - 4% average relative fraction of
+original image(mean(residual/image) ~ 2%-%4). For the fitting routine I used this
 time,  the fluxes of A and B purely calculated from the
@@
 
-An average relative fraction of 2-4\% of the residual model could be a
+An average relative fraction of 2-4% of the residual model could be a
 significant source of uncertainty. Especially for the case that I
-ignored the flux from the residual totally. However, I have not come up
+ignored the flux from the residual at all. However, I have not come up
 with any ideas on including the residual flux to the final result. I
@@
 
-\embed{ a) When you say you carried out a "two component tinytim PSF
-  fit", it is not clear to me what you mean.  I assume the linear
-  superposition of two TinyTim PSFs.  But do you mean one for A and
-  one for B that are otherwise identical (or perhaps different in some
-  manner other than brightness?).  Or do you mean for B (and perhaps
-  also A) you have used a combination of TinyTim PSFs that, in
-  combination (perhaps with different defocus of color terms?) better
-  represent the observed PSF?  }
+>a) When you say you carried out a "two component tinytim PSF fit", it is not clear to me what you mean.
+I assume the linear superposition of two TinyTim PSFs.
+But do you mean one for A and one for B that are otherwise identical (or perhaps different in some manner other than brightness?).
+Or do you mean for B (and perhaps also A) you have used a combination  of TinyTim PSFs that, in combination (perhaps with different defocus of color terms?) better represent the observed PSF?
 
@@
 
-\embed{
-b) To me it is interesting (but not really unexpected) that binning
-by "same position angle" (i.e., spacecraft roll angle) improves.
-Off-rolling does thermally destablise the PSF to some extent - by
-changing the angle to the sub-solar point on the Earth as the
-telescope orbits and can drive quasi-breathing modes.  I am a bit
-surprised that these stabilize out as well as they seem to do (as
-exhibited by the factor of 10 improvement in chisq).  It would be
-interesting to know how much of that improvement is do to "same
-dither position" and how much to "same roll" (as differently binned).
-I am sure they both play together to reduce the residuals, but
-knowing this could have influence on how future observations might be
-constructed.}
+>b) To me it is interesting (but not really unexpected) that binning
+>by "same position angle" (i.e., spacecraft roll angle) improves.
+>Off-rolling does thermally destablise the PSF to some extent - by
+>changing the angle to the sub-solar point on the Earth as the
+>telescope orbits and can drive quasi-breathing modes.  I am a bit
+>surprised that these stabilize out as well as they seem to do (as
+>exhibited by the factor of 10 improvement in chisq).  It would be
+>interesting to know how much of that improvement is do to "same
+>dither position" and how much to "same roll" (as differently binned).
+>I am sure they both play together to reduce the residuals, but
+>knowing this could have influence on how future observations might be
+>constructed.
 
-The position dependency of the residual pattern comes from at least
+The position depandency of the residual pattern comes from at least
 three parts.
-\begin{enumerate}
-\item  Instrumental as Glenn described 
-\item The imperfection of flat
-  field is not modeled with TinyTim. 
-\item  The PSFs are sampled
-  differently at different position with a low sample rate.
-\end{enumerate}
+
+1. Instrumental as Glenn described
+2. The imperfection of flat field is not modeled with TinyTim.
+3. The PSFs are sampled differently at different position with a low
+sample rate.
 
@@
 
-\embed{
-Overall, these look good; the question is, of course, how much of the
-apparent trend is real.  One note here: It is curious how both A and B
-have an increase in the first 3 orbits and then a different behavior
-in orbits 4-6.}
+> Overall, these look good; the question is, of course, how much of the
+> apparent trend is real.  One note here: It is curious how both A and B
+> have an increase in the first 3 orbits and then a different behavior
+> in orbits 4-6.
 
-\embed{
-Could you explain how exactly do you determine the normalization
-factors for the different angles/dithering positions?}
+>Could you explain how exactly do you determine the normalization
+>factors for the different angles/dithering positions?
 
@@
 
-\section{Discussion and further analysis}
-\embed{
-Daniel asks: "how much of the apparent trend is real".  This might be
-difficult to ascertain.  Clearly the F125W and F160W for A seem well
-correlated (1st 3 vs last 3 orbits) , but that correlation possibly
-could still be instrumental.  If you took the new light curves as
-binned, for B:
-}
+# Discussion and further analysis
 
-\embed{
-if you average all the points together in each orbit (loosing the
- finer temporal information) is the change in normalized flux for B
- over the six orbits also "consistent" from F125W to F160W **AND** is it
- correlated with A?  It's a little harder to tell (quantitatively) as
- plotted for B simply because it is noisier than A.  In both A and B
- (both bands) the flux (by eye) also seems lower in the last three
- orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
- expect that behavior in A and B to be independent, whereas if
- correalted that may be an instrumental signature.}
+> Daniel asks: "how much of the apparent trend is real".  This might be
+> difficult to ascertain.  Clearly the F125W and F160W for A seem well
+> correlated (1st 3 vs last 3 orbits) , but that correlation possibly
+> could still be instrumental.  If you took the new light curves as
+> binned, for B:
 
-I binned the light curve of A and B by orbits using average. According to the result
+> if you average all the points together in each orbit (loosing the
+>  finer temporal information) is the change in normalized flux for B
+>  over the six orbits also "consistent" from F125W to F160W **AND** is it
+>  correlated with A?  It's a little harder to tell (quantitatively) as
+>  plotted for B simply because it is noisier than A.  In both A and B
+>  (both bands) the flux (by eye) also seems lower in the last three
+>  orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
+>  expect that behavior in A and B to be independent, whereas if
+>  correalted that may be an instrumental signature.
+
+I binned the light curve of A and B by orbits. According to the result
 I obtained, there are no clear correlation/anti-correlation betwee the
-fluxes of A and B. Figure \ref{fig:1} presented the orbit-binned light
-curves.
+fluxes of A and B.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{binned_coor_F125W}
-  \includegraphics[width=0.45\textwidth]{binned_coor_F160W}
-  \caption{Orbit-binned light curves. Binned curve for B showed a sine
-  wave shaped curve}
-  \label{fig:1}
-\end{figure}
+![Orbit-binned light curve, F125W](./binned_coor_F125W.pdf
+"orbit-binned light curve, F125W")
+![Orbit-binned light curve, F160W](./binned_coor_F160W.pdf
+ "orbit-binned light curve, F160W")
 
-\embed{
-This looks quite nice and indeed, the 10.9 hours is not a period that
-I would obviously associate with an instrumental artifact.  Have you
-tried the same for the F160W LC? It would be a nice verification if
-you would get a similar periodicity.}
+> This looks quite nice and indeed, the 10.9 hours is not a period that
+> I would obviously associate with an instrumental artifact.  Have you
+> tried the same for the F160W LC? It would be a nice verification if
+> you would get a similar periodicity.
 
-By eye, unbinned light curve of F160W does not show a sine-wave like
-shape. However, in the orbit-binned curve, the light curve of B showed
-a sine wave shaped curve as shown in Figure \ref{fig:1}. For F160W LC
-of B, The least square fit results in a sine curve with a period of
-9.3 hr. I also tried to fit the F160W light curve with a sine curve
+By eye, light curve of F160W does not show a sine-wave like
+shape. Thus I do not trust the result of a least square fit very
+much. The least square fit results in a sine curve with a period of
+9.26 hr. I also tried to fit the F160W light curve with a sine curve
 that has a fixed period of 10.9 hr. I plotted the two best fit sine
-curves together with the original observation points as in Figure
-\ref{fig:2}. Considering the large scattering of photometric
-measurement of B, it is actually hard to tell from Figure \ref{fig:2} whether
-the 9.3 hr light curve fits better than the 10.9 hr light curve.
+curves together with the original observation.
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{sineCurveFit}
-  \caption{sinusoidal wave fit to the light curve of 2M1207B. For the
-    F160W panel, two curves for periods of 9.3 hr and 10.9 hr are
-    plotted.}
-  \label{fig:2}
-\end{figure}
-
-\embed{
-Also, to be consistent, can you please use the same fitting procedure
-for A (in both filters) and send similar plots?}
+> Also, to be consistent, can you please use the same fitting procedure
+> for A (in both filters) and send similar plots?
 
 I did the fitting for A in both fittings. The rise in first three
-orbits is the main feature that defines the sinusoidal wave. However
-if it were truly part of a sin wave, the sine function would not be
-well constrained by this small segment. For the light curve of F125W,
-the fitting routine found a best fitted curve with a period of 6.86
-hr. However the points in the 5th orbit are totally off the fitted
-curve. For F160W, the fitting routine failed to converge when fitting
-a sine curve to the light curve. Figure \ref{fig:3} presented the
-fitted sinusoidal wave and the observational points for 2M1207A with
-F125W.
+orbits is the main feature that defines the sin wave in the
+fit. However if it were truly part of a sin wave, the sine function is
+not well constrained by this small segment. For the light curve of
+F125W, the fitting routine found a best fitted curve with a period of
+6.86 hr. However the points in the 5th orbit are totally off the
+fitted curve. For F160W, the fitting routine failed to converge when
+fitting a sine curve to the light curve.
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{sineCurveFit_primary}
-  \caption{sine wave fitting for 2M1207A.}
-  \label{fig:3}
-\end{figure}
-
-\embed{
-(c) I assume the 10.9 hour fit came from a least-squares analysis --
-not quite a full observing/sampling period.  "By eye" it certainly
-loooks good, but might be interesting to also do a simple periodogram
-analysis, just to see if this might be an alias?}
+> (c) I assume the 10.9 hour fit came from a least-squares analysis --
+> not quite a full observing/sampling period.  "By eye" it certainly
+> loooks good, but might be interesting to also do a simple periodogram
+> analysis, just to see if this might be an alias?
 
@@
 for data that does not cover a whole period.
-
-\end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2015-07-03 2M1207ANALYSIS/KLIP.py

@@ -3,6 +3,7 @@ from __future__ import print_function, division
 import numpy as np
 from scipy.io import readsav  # read IDL save file
 import matplotlib.pyplot as plt
+from astropy.io import fits
 """KLIP pipe line
    reference:  Sourmer 2012
 adapted from Neil Zimmerman's code
@@ -43,12 +44,12 @@ def KLIP(targetImage, KLBases, effIndex, klip):
     klip -- number of principle component to use
     """
     target_eff = targetImage[effIndex].flatten()
-    KLBases_eff = KLBases[0:klip, effIndex]
+    KLBases_eff = KLBases[0:klip, effIndex[0] * 27 + effIndex[1]]
     # project target image on KL_bases
     coeff = np.dot(KLBases_eff, target_eff)
     image = np.zeros(targetImage.shape)
     for i, c in enumerate(coeff):
-        image += KLBases[i, :].reshape(targetImage.shape)
+        image += KLBases[i, :].reshape(targetImage.shape) * c
     return image
 
 
@@ -73,3 +74,4 @@ if __name__ == '__main__':
     id_eff = getEffIndex(cube0[0].shape, [17, 9], [[6.5, 10]])
     Z = KLtrans(cube0, id_eff)
     im = KLIP(cube1[0], Z, id_eff, 20)
+    fits.writeto('test.fits', im - cube1[0], clobber=True)

### 2015-07-03 2M1207ANALYSIS/correlateBinned.py

@@ -1,0 +1,80 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+"""plot the correlation of binned data
+bin within one orbit
+"""
+
+
+def normFlux(dataFrame, normDither=False):
+    """    Keyword Arguments:
+    dataFrame  -- input data frame
+    normDither -- (default False) if normalize by dither position, default
+    is faulse
+    reurn the normalized flux for primary and secondary
+    """
+    fluxA0 = np.zeros(len(dataFrame))
+    fluxB0 = np.zeros(len(dataFrame))
+    if normDither:
+        for angle in [0, 1]:
+            for dither in range(4):
+                subDF_id = np.where((dataFrame['POSANGLE'] == angle) &
+                                    (dataFrame['DITHER'] == dither))
+                subDF = dataFrame[(dataFrame['POSANGLE'] == angle) &
+                                  (dataFrame['DITHER'] == dither)]
+                fluxA0[subDF_id] = subDF['FLUXA'] / subDF['FLUXA'].mean()
+                fluxB0[subDF_id] = subDF['FLUXB'] / subDF['FLUXB'].mean()
+    if not normDither:
+        fluxA0 = dataFrame['FLUXA'] / dataFrame['FLUXA'].mean()
+        fluxB0 = dataFrame['FLUXB'] / dataFrame['FLUXB'].mean()
+
+    return fluxA0, fluxB0
+
+if __name__ == '__main__':
+    fn125 = '2015_Jun_24TinyTimF125Result.csv'
+    fn160 = '2015_Jun_24TinyTimF160Result.csv'
+    df125 = pd.read_csv(
+        fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df160 = pd.read_csv(
+        fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    f125A0, f125B0 = normFlux(df125, normDither=True)
+    f160A0, f160B0 = normFlux(df160, normDither=True)
+    F125A = []
+    F125B = []
+    for orbit in range(1, 7):
+        F125A.append(f125A0[np.where(df125['ORBIT'] == orbit)].mean())
[…]

### 2015-07-03 2M1207ANALYSIS/examResidual.py

@@ -1,0 +1,25 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+from astropy.io import fits
+import numpy as np
+
+"""examine the residual
+"""
+
+
+def makeAnnulus(center, radius):
+    """obtain annulus index
+"""
+    x, y = center
+    xx, yy = np.meshgrid(np.arange(27), np.arange(27))
+    distance = np.sqrt((xx - x)**2 + (yy - y)**2)
+    idx, idy = np.where(distance < radius)
+    return idx, idy
+
+if __name__ == '__main__':
+    residualFile = './fitsResult/icdg01a1q.fits'
+    im = fits.getdata(residualFile, 0)
+    psf = fits.getdata(residualFile, 1)
+    residual = im - psf
+    id1 = makeAnnulus([13, 13], 5)
+    print(residual[id1].sum())

### 2015-07-03 2M1207ANALYSIS/period_primary.py

@@ -46,33 +46,32 @@ if __name__ == '__main__':
     np.savetxt('F160Result.dat', np.c_[df160['Time'].values, f160A0, f160B0])
     """
     according to calculation made by matlab
-    For F125B amp=0.0139   T=10.9765    dphi=0.5874    baseline=1.0001
+    For F125A amp=0.0139   T=10.9765    dphi=0.5874    baseline=1.0001
     """
     plt.close('all')
     fig = plt.figure()
-    ax125 = fig.add_subplot(211)
-    points125, = ax125.plot(df125['Time'], f125B0, 'o')
+    ax125 = fig.add_subplot(111)
+    points125, = ax125.plot(df125['Time'], f125A0, 'o')
     t = np.linspace(df125['Time'].min(), df125['Time'].max(), 500)
-    modelFlux = 0.0139 * np.sin(2 * np.pi / 10.9765 * t + 0.5874) + 1.0001
+    modelFlux = 0.0041 * np.sin(2 * np.pi / 6.8618 * t - 8.1991) + 1.0008
     line125, = ax125.plot(t, modelFlux)
     ax125.set_title('F125W')
-    """For F160B I used two type fit,
-    1. free parameter fit
-    amp=0.0088    T=9.2692   dphi=-0.1180    baseline=1.0002
-    2. fixed parameter fit
-    amp=0.0080    T=10.9765  dphi=0.2525    baseline=0.9997
-    """
-    ax160 = fig.add_subplot(212)
-    points160, = ax160.plot(df160['Time'], f160B0, 'o')
-    t = np.linspace(df160['Time'].min(), df160['Time'].max(), 500)
-    modelFlux1 = 0.0080 * np.sin(2 * np.pi / 10.9765 * t + 0.2525) + 0.9997
-    modelFlux2 = 0.0088 * np.sin(2 * np.pi / 9.2692 * t - 0.1180) + 1.0002
-    line160_1, = ax160.plot(t, modelFlux1, label='P=10.9')
-    line160_2, = ax160.plot(t, modelFlux2, label='P=9.3')
-    ax160.set_title('F160W')
-    for ax in [ax125, ax160]:
-        ax.set_xlabel('Time (h)')
-        ax.set_ylabel('Nomalized Flux')
-        ax.legend()
-    fig.tight_layout()
-    plt.savefig('sineCurveFit.pdf')
+    plt.savefig('sineCurveFit_primary.pdf')
[…]

### 2015-07-03 2M1207ANALYSIS/plotTinyTimResult.py

@@ -5,11 +5,12 @@ import pandas as pd
 
 plt.style.use('ggplot')
 fn = '2M1207B_flt_F125W_result.csv'
-df = pd.read_csv(fn, parse_dates = {'datetime':['obs date', 'obs time']}, index_col = 'datetime')
-plt.plot(df.index, df['fluxA'], 's', label = '2M1207 A')
-plt.plot(df.index, df['fluxB'], 'o', label = '2M1207 B')
+df = pd.read_csv(
+    fn, parse_dates={'datetime': ['obs date', 'obs time']}, index_col='datetime')
+plt.plot(df.index, df['fluxA'], 's', label='2M1207 A')
+plt.plot(df.index, df['fluxB'], 'o', label='2M1207 B')
 plt.gcf().autofmt_xdate()
-plt.legend(loc = 'best')
+plt.legend(loc='best')
 plt.xlabel('UT')
 plt.ylabel('Normalized flux')
 

### 2015-07-18 summary/reply2/reply.tex
need to add another part of the paper

--- 2015-07-03 summary/reply/reply.tex
@@
 \numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
-\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
+\numberwithin{table}{sectiobn} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
 
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Reply to Daniel \& Glenn\\ % The assignment title
+\huge More Test\\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 \maketitle % Print the title
-\section{Clarifications}
-\embed{
-1) How do you scale (if you scale) the residuals you subtract?
-}
-
-The residuals are not scaled. I simply took the median of the
-residuals that have the same dither position and position angle, and
-subtracted the median combination from the original images. Since The
-chisq distribution of the fitting looks very reasonable for me, I did
-not attempt to make further adjustment of the residual models.
-
-\embed{
- 2) How do the residuals images look like? What is the relative
- fraction of the light that is not subtracted well?
-}
-
-\embed{
- 3) When you calculate the brightness of the sources, how do you use
- the information of the residuals and the TinyTim-based PSF?
-}
-
-These are very important points. However I did not deal with them very
-carefully in the fit. As I showed in our previous discussion,
-Tinytim does not provide a precise PSF model so that the residual of
-tinytim PSF subtraction has a 2\% - 4\% average relative fraction of
-original image(mean(residual/image) $\sim$ 2\%-\%4). For the fitting routine I used this
-time,  the fluxes of A and B purely calculated from the
-amplitudes of the two components of the PSF. I did not count any flux
-from the residual model into the fluxes of A or B.
-
-An average relative fraction of 2-4\% of the residual model could be a
-significant source of uncertainty. Especially for the case that I
-ignored the flux from the residual totally. However, I have not come up
-with any ideas on including the residual flux to the final result. I
-think we need further discussion about this point.
-
-\embed{ a) When you say you carried out a "two component tinytim PSF
-  fit", it is not clear to me what you mean.  I assume the linear
-  superposition of two TinyTim PSFs.  But do you mean one for A and
-  one for B that are otherwise identical (or perhaps different in some
-  manner other than brightness?).  Or do you mean for B (and perhaps
-  also A) you have used a combination of TinyTim PSFs that, in
-  combination (perhaps with different defocus of color terms?) better
-  represent the observed PSF?  }
-
-I used different PSFs for A and B. My fitting routine firstly
-generates a list of PSFs using the position of A and the NIR spectrum
-of A (Bonnefoy et. al. 2014) with different telescope jittering. I fit
-this PSF to the image of A with an area where the image of B is mostly
-excluded ( using a 3-pixel radius mask centered on B) to find the best
-matched position and Jittering. Next, I used this jittering to
-generate a PSF of B with B's position on detector and B's spectrum
-(Patience et al. 2010). In the third step, I fit the two PSFs together
-with the position of A fixed , and to find the best matched position
-of B and amplitudes of 2 PSFs.
-
-\embed{
-b) To me it is interesting (but not really unexpected) that binning
-by "same position angle" (i.e., spacecraft roll angle) improves.
-Off-rolling does thermally destablise the PSF to some extent - by
-changing the angle to the sub-solar point on the Earth as the
-telescope orbits and can drive quasi-breathing modes.  I am a bit
-surprised that these stabilize out as well as they seem to do (as
-exhibited by the factor of 10 improvement in chisq).  It would be
-interesting to know how much of that improvement is do to "same
-dither position" and how much to "same roll" (as differently binned).
-I am sure they both play together to reduce the residuals, but
-knowing this could have influence on how future observations might be
-constructed.}
-
-The position dependency of the residual pattern comes from at least
-three parts.
-\begin{enumerate}
-\item  Instrumental as Glenn described 
-\item The imperfection of flat
-  field is not modeled with TinyTim. 
-\item  The PSFs are sampled
-  differently at different position with a low sample rate.
-\end{enumerate}
-
-It is actually difficult to differentiate the improvement in terms of
-different instrumental effect, since the there are significant
-uncertainty and artifect generated by last two points.
-
-\embed{
-Overall, these look good; the question is, of course, how much of the
-apparent trend is real.  One note here: It is curious how both A and B
-have an increase in the first 3 orbits and then a different behavior
-in orbits 4-6.}
-
-\embed{
-Could you explain how exactly do you determine the normalization
-factors for the different angles/dithering positions?}
-
-I median combined the fluxes calculated with images taking with same
-filter, dithering position and roll angles, and devided the median
-combination from every photometric result of these exposures.
-
-\section{Discussion and further analysis}
-\embed{
-Daniel asks: "how much of the apparent trend is real".  This might be
-difficult to ascertain.  Clearly the F125W and F160W for A seem well
-correlated (1st 3 vs last 3 orbits) , but that correlation possibly
-could still be instrumental.  If you took the new light curves as
-binned, for B:
-}
-
-\embed{
-if you average all the points together in each orbit (loosing the
- finer temporal information) is the change in normalized flux for B
- over the six orbits also "consistent" from F125W to F160W **AND** is it
- correlated with A?  It's a little harder to tell (quantitatively) as
- plotted for B simply because it is noisier than A.  In both A and B
- (both bands) the flux (by eye) also seems lower in the last three
- orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
- expect that behavior in A and B to be independent, whereas if
- correalted that may be an instrumental signature.}
-
-I binned the light curve of A and B by orbits using average. According to the result
-I obtained, there are no clear correlation/anti-correlation betwee the
-fluxes of A and B. Figure \ref{fig:1} presented the orbit-binned light
-curves.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{binned_coor_F125W}
-  \includegraphics[width=0.45\textwidth]{binned_coor_F160W}
-  \caption{Orbit-binned light curves. Binned curve for B showed a sine
-  wave shaped curve}
-  \label{fig:1}
-\end{figure}
-
-\embed{
-This looks quite nice and indeed, the 10.9 hours is not a period that
-I would obviously associate with an instrumental artifact.  Have you
-tried the same for the F160W LC? It would be a nice verification if
-you would get a similar periodicity.}
-
-By eye, unbinned light curve of F160W does not show a sine-wave like
-shape. However, in the orbit-binned curve, the light curve of B showed
-a sine wave shaped curve as shown in Figure \ref{fig:1}. For F160W LC
-of B, The least square fit results in a sine curve with a period of
-9.3 hr. I also tried to fit the F160W light curve with a sine curve
-that has a fixed period of 10.9 hr. I plotted the two best fit sine
-curves together with the original observation points as in Figure
-\ref{fig:2}. Considering the large scattering of photometric
-measurement of B, it is actually hard to tell from Figure \ref{fig:2} whether
-the 9.3 hr light curve fits better than the 10.9 hr light curve.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{sineCurveFit}
-  \caption{sinusoidal wave fit to the light curve of 2M1207B. For the
-    F160W panel, two curves for periods of 9.3 hr and 10.9 hr are
-    plotted.}
-  \label{fig:2}
-\end{figure}
-
-\embed{
-Also, to be consistent, can you please use the same fitting procedure
-for A (in both filters) and send similar plots?}
-
-I did the fitting for A in both fittings. The rise in first three
-orbits is the main feature that defines the sinusoidal wave. However
-if it were truly part of a sin wave, the sine function would not be
-well constrained by this small segment. For the light curve of F125W,
-the fitting routine found a best fitted curve with a period of 6.86
-hr. However the points in the 5th orbit are totally off the fitted
-curve. For F160W, the fitting routine failed to converge when fitting
-a sine curve to the light curve. Figure \ref{fig:3} presented the
-fitted sinusoidal wave and the observational points for 2M1207A with
-F125W.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{sineCurveFit_primary}
-  \caption{sine wave fitting for 2M1207A.}
-  \label{fig:3}
-\end{figure}
-
-\embed{
-(c) I assume the 10.9 hour fit came from a least-squares analysis --
-not quite a full observing/sampling period.  "By eye" it certainly
-loooks good, but might be interesting to also do a simple periodogram
-analysis, just to see if this might be an alias?}
-
-I thought about this idea before. However, 10.9 hour is longer than the
-observation baseline and we if that were the case, we did not have a
-periodical signal. I was wondering whether the periodogram would work
-for data that does not cover a whole period.
 
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2015-07-18 2M1207ANALYSIS/KLIP.py

@@ -21,10 +21,10 @@ def KLtrans(imageCube, effIndex):
     # establish R array
     # for _eff, only non-masked value counts
     # on the other hand, for R, every value conts
-    R_eff = np.zeros((nImages, len(effIndex[0])))
+    R_eff = np.zeros((nImages, len(effIndex)))
     R = np.zeros((nImages, imageCube[0].size))
     for i in range(nImages):
-        R_eff[i, :] = imageCube[i][effIndex].flatten()
+        R_eff[i, :] = imageCube[i].flatten()[effIndex]
         R[i, :] = imageCube[i].flatten()
     eigens, vectors = np.linalg.eig(np.dot(R_eff, R_eff.T))
     # sort by eigen values, get the index from large to small
@@ -43,8 +43,8 @@ def KLIP(targetImage, KLBases, effIndex, klip):
     effIndex -- effective index to discrbie the search area
     klip -- number of principle component to use
     """
-    target_eff = targetImage[effIndex].flatten()
-    KLBases_eff = KLBases[0:klip, effIndex[0] * 27 + effIndex[1]]
+    target_eff = targetImage.flatten()[effIndex]
+    KLBases_eff = KLBases[0:klip, effIndex]
     # project target image on KL_bases
     coeff = np.dot(KLBases_eff, target_eff)
     image = np.zeros(targetImage.shape)
@@ -53,25 +53,52 @@ def KLIP(targetImage, KLBases, effIndex, klip):
     return image
 
 
-def getEffIndex(imShape, center, radiusList):
-    """calculate search region Index
+def getEffCoord(imShape, annulusList):
+    """return index for search region
+    exclude region listed in annulusList
+    annulusList is an n*4 array, including n annulli
+    each annulli centered at annulusList[i][0], annuluslist[i][1]
+    inner radius: annlusList[i][2], out radius: annlusList[i][3]
     """
     xx, yy = np.meshgrid(np.arange(imShape[0]), np.arange(imShape[1]))
-    dist = np.sqrt((xx - center[0])**2 + (yy - center[1])**2)
-    dim1_eff = []
-    dim2_eff = []  # use dimension 1 and 2 instead of x and y
-    for rPair in radiusList:
-        xi, yi = np.where((dist > rPair[0]) & (dist < rPair[1]))
-        dim1_eff.append(xi)
[…]

### 2015-07-18 2M1207ANALYSIS/plotLightCurve.py

@@ -104,8 +104,8 @@ def correlation(df, ifPlot=True):
 
 
 if __name__ == '__main__':
-    fn125 = '2015_Jun_24TinyTimF125Result.csv'
-    fn160 = '2015_Jun_24TinyTimF160Result.csv'
+    fn125 = '2015_Jul_16TinyTimF125Result.csv'
+    fn160 = '2015_Jul_16TinyTimF160Result.csv'
     df125 = pd.read_csv(
         fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
         index_col='datetime')

### 2015-07-18 2M1207ANALYSIS/plotSplitedDataSet.py

@@ -1,0 +1,96 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+from plotLightCurve import normFlux
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+
+"""split the sample by dithering position
+"""
+
+
+def normedSin(t, p):
+    return p[0] * np.sin((2 * np.pi / p[1]) * t + p[2]) + 1
+
+if __name__ == '__main__':
+    fn125 = '2015_Jun_24TinyTimF125Result.csv'
+    fn160 = '2015_Jun_24TinyTimF160Result.csv'
+    ##
+    df125 = pd.read_csv(
+        fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125 = df125.sort_index()
+    # time in ns
+    df125['Time'] = np.float32(
+        df125.index.values - df125.index.values[0]) / (60 * 60 * 1e9)
+
+    df160 = pd.read_csv(
+        fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df160 = df160.sort_index()
+    # time in ns
+    df160['Time'] = np.float32(
+        df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
+    # df160 = df160[df160['ORBIT'] > 1]  # remove the data from the first orbit
+
+    df125_1 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
+    df125_2 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
+    f125A0, f125B0 = normFlux(df125, normDither=True)
+    f125A0_1, f125B0_1 = normFlux(df125_1, normDither=True)
+    f125A0_2, f125B0_2 = normFlux(df125_2, normDither=True)
+
+    # make the plot
+    plt.close('all')
+    fig125 = plt.figure(figsize=(8, 10))
+    t125 = np.linspace(df125['Time'].min(), df125['Time'].max(), 200)
+    # for all data
+    ax1 = fig125.add_subplot(411)
+    ax1.plot(df125['Time'], f125B0, 's', label='whole set')
+    ax1.plot(t125, normedSin(t125, [0.0139, 10.9821, 0.5869]))
[…]

### 2015-07-21 summary/letter/letter_v1.tex
new reply made

\documentclass[apj]{emulateapj}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\shorttitle{Short Title}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\begin{document}
\title{Variability of Planetary Mass Companion 2M1207 B}
\author{Yifan Zhou, Daniel Apai, ...}
\affil{University of Arizona}

\begin{abstract}
...
\end{abstract}

\keywords{kw1, kw2, ...}
\maketitle
%
\section{Introcduction}

\section{Observation}
We carried out high contrast direct imaging observation of  2M1207
system on UT 2014 April 11 using HST.
(\textit{HST} Proposal GO-13418, PI: D. Apai). The data were acquired
with the Wide Field Camera 3 (WFC3, citation needed) in filter F125W
and F160W using the $256\times256$ sub-array mode. We observed
2M1207 system in continuous 6 HST orbits and obtained a data-set that
have a temporal resolution of $\sim1.5$ minutes and baseline of $\sim
8$ hours.

The observation was initially designed to apply standard roll
subtraction to remove the primary star. The telescope roll angles for
data taken in orbit 1, 3, 5 and those taken in orbit 2, 4, 6 have a
difference of $25^{\circ}$, thus the companion would appear at
different position relative to the primary with different roll angle
and the primary in the two data set can be subtracted from each other.
In each orbit we will take a sequence of 13 SPARS25 exposures with
NSAMP=10, alternating between F160W and F125W filters. To improve PSF
sampling and reduce the influence of bad pixels, we applied standard 4
point dithering. In each orbit, exposures were taken with dithering
position 1 -- 4 sequently. To sum, we obtained 70 multi-acuum images
for filter F125W and 64 images for filter F160W with exposure time of
88.4 seconds for both two filters.

\section{Data Reduction}

Through the whole analysis, we used the \flt that were
produced by WFC3's \texttt{calwfc3} pipeline. The \flt were reduced
with calibrations including dark current correction, non-linearity
correction, and flat field correction. A further step of up-the-ramp
fit was applied to combine all non-destructive read and remove cosmic
rays. Although \citeauthor{Mandell2013} stated that WFC3 IR time series
extract from {\flt} have a rms 1.3 times larger than that obtained
from {\ima}, \flt keeps all pixels of the image of 2M1207 A
unsaturated while in most of non-destructive reads the cores of 2M1207
A are saturated, so that with \flt the flux of 2M1207 B can be more
precisely separated from that of 2M1207A.

The small angular separation of 2M1207 A and B (as shown in Figure
\ref{fig:1}) makes precise primary star subtraction and photometry
very difficult. On the under-sampled WFC3 IR detector (plate scale
$\sim 0.13$ arcsec per pixel), the primary and the secondary only
separate by $\sim 6$ pixels, which is about 5 times of the FWHM of the
PSF. In addition, under-sampling of the PSF causes significant
artifacts when shifting the PSF to register images no matter what
interpolation method is used.

\begin{figure}[h]
  \centering
  \plotone{original}
  \plotone{subtracted}
  \caption{WFC3 F160W images of 2M1207A system. Upper: original image,
    lower: residual model and primary PSF subtracted. The image of
    2M1207 B is overshadowed by the halo of the image of 2M1207A and
    can be hardly seen from the original image. With a hybrid PSF
    (residual + Tiny Tim PSF) subtraction, the image of 2M1207 B is
    clearly presented.}
  \label{fig:1}
\end{figure}
\subsection{Tiny Tim PSF Photometry}
To over come the difficulty, we make use of the Tiny Tim PSF simulator
to pursue high precision photometry under this extreme
circumstance. Tiny Tim can produce model PSF based on the filter,
spectrum of target, focus status, and the telescope jitter. One
significant advantage of Tiny Tim PSF over empirical PSF is that Tiny Tim can
produce over-sampled PSF, which makes the shifting and interpolation
rather straight forward. However, Tiny Tim model PSFs have systematic
errors. \citeauthor{Biretta2014} demonstrated that the diffraction
spikes and coma are not well simulated with Tiny Tim for WFC3 IR images.

We start the reduction by making bad pixel masks for every
images. Pixels with data quality flags 'bad detector pixels' (DQ = 4),
'unstable response' (DQ = 32), and 'bad or uncertain flat value' (DQ =
512) were masked out and excluded from further analysis as suggested
by previous transit exoplanet
spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.

We then produced a list of 10x over-sampled PSFs based on the
positions and spectrum \citep{Bonnefoy2014} of 2M1207A with different telescope jitter
ranging from 0 to 50 mini-arcsec per second in both $x$ and $y$
direction. The focus parameter was calculated using the model listed
on the STScI
website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. The
PSFs were registered with the original image by searching on a dynamic
grid and minimizing the residual of a region centered on 2M1207 A with
the image of 2M1207 B mostly excluded. The best fitted primary star
position and telescope jitter were obtained in this step. Then, we
generated the PSF for 2M1207 B based on its position on detector,
spectrum \citep{Patience2010}, and the telescope jitter that had been obtained above. In
the final step, we combined the two PSFs together. We fixed the
position of the primary as it had been fitted in the first step and
fitted for the amplitude of the two PSFs and the precise position of
the secondary. Since the total fluxes of the model PSFs are normalized
to unity as default, the fluxes of 2M1207 A and B are solely
represented by the amplitude of the two PSFs coordinately.

Because of the systematic errors of the Tiny Tim PSF, the quality of the
fitting is not optimistic. The reduced $\chi^{2}$ values are around
$\sim10$. However, we found that the residual patterns were very
stable among the image that have the same dithering position and
telescope rolling. Therefore, we median combined the residual images
that have the same dithering position and telescope rolling angle to
construct 8 residual models (4 dithering position $\times$ 2 telescope
rolling angle) for each filter. We pre-subtract the corresponding
residual from the original image and repeated the procedure that
listed above. Using this extra-step, the systematic error of Tiny Tim
greatly decreased to around unity.

The fluxes for both 2M1207 A and B are clearly correlated with the
dithering position, which is primarily due to imperfection of the flat
field. To reduce the correlation, we normalize each group of exposures
that have the same dithering position and roll angle indivadually --
we took the median of the fluxes that were measured from these
exposures as normalization factors and devided them from every flux
measurement. 
\subsection{Uncertainty Analysis}
\begin{figure*}[h]
  \centering
  \plottwo{F125_corr}{F160_corr}
  \caption{Fluxes of the primary and the secondary is correlated with
    the ditheirng positions. Different symbols represent different
    orbits.}
  \label{fig:fig2}
\end{figure*}
\section{Result}
\begin{figure}[h]
  \centering
  \plotone{sineCurveFit}
  \caption{Normalized light curves for F125W and F160W. Red squares
    are the phtometric measurment for 2M1207 B, and gray dots are for
    2M1207 A.}
  \label{fig:3}
\end{figure}
\section{Discussion }
\begin{itemize}
\item a data-reduction pipeline is developed to obtain high precision
  photometry measurement from high contrast WFC3 IR data. For a
  contrast of $\sim 7$ magnitudes at an angular separation of
  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
  precision of about 2-3\%. 
\item time variability for 2M1207 B was discovered, the light curve of
  2M1207 B for both two colors can be fitted with a T=10.7 hr
  sinusoidal curve.
\item the atmosphere and cloud structure of 2M1207 B. How does it
  compare to the brown dwarf.
\end{itemize}
\bibliography{ref.bib}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-07-21 summary/reply2/reply.tex
new reply made

@@
 
-\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
-\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
-\numberwithin{table}{sectiobn} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
+% \numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
+% \numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
+% \numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
 
@@
 
+\embed{
+  1, repeat analysis excluding Orbit 1? Orbit \#1 is usually less
+    stable than the rest and excluding it would help us verify that
+    those data are not influencing the rest of the data some odd ways
+    via affecting the normalization factors. I suspect that this is
+    not the case, but we should verify.}
+
+  \embed{
+   2, Reduce dither positions 1-3 and 2-4 pairs separately: By reducing
+    and fitting data from groups of only two of the dithering
+    positions (about half the total data) we can verify that the
+    signal we are seeing is present in both halves of the data, which
+    is very convincing.}
+
+  I made several least square fittings with respect to above two
+  points and I plotted the photometric points with the fitted light
+  curve in Figure \ref{fig:fit}
+
+  Excluding the first orbit does not change the result too much. For
+  the light curve of F125W, the fitted sine curve to the data set
+  without the first orbit has almost the same amplitude as that of the
+  whole data-set and a period 1 hr longer. For F160W, the two fit only
+  have very slight difference in phase.
+
+  However, when splitting the data set into two halves, the fitting
+  results have more significant difference, especially for F125W. Two
+  halves of the F125W data set generally have similar trend -- ascend
+  in first two orbits and descend in 2-5 orbits. However, one significant
+  difference is that in the first half, the light curve goes up in the
+  last orbit while in the second half it continues descending. This
+  difference leads to large deviation in the result of sine
+  curve fitting. The periods of best fitted sine curves to the two halves of data
+  are very different. It is 8.8 hr for the first half and 16.9 hr for
+  the second half. Although considering the large scattering, I would
+  guess there would be a local minimum for the fit to the second half
+  at a smaller period. For F160W, the fitting result for the two
+  halves are more similar. The biggest difference is the amplitude, it
+  is 0.006 for the first half and 0.01 for the second half.
+
+  The difference for the fitting result for two halves would at least
+  cast some doubt on the amplitude and period measurement. Also I
+  think it may provide some idea on the uncertainty of the
+  measurement.
+
+  \begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.48\textwidth]{F125W_SplitDataSet}
+    \includegraphics[width=0.48\textwidth]{F160W_SplitDataSet}
+    \caption{phototmetry and fitted sine curves for different data
+      set. The left panel is for F125W and the right is for F160W. The
+    first row is the whole data set, the second is the fit with Orbit \# 1
+  removed, the third is the fit for the first half and the forth is
+  for the second half.}
+    \label{fig:fit}
+  \end{figure}
+
+\embed{
+3, My biggest (but not major) concern is the effect of flat fielding errors.
+I am not quite sure how to exclude their effect completely, perhaps Glenn has a good suggestion.
+Given that we don't really control the flat field errors, one test we should do is to introduce a flat field error and see what changes, if any, this introduces.
+I am thinking here on the following:
+create an artificial flat error mask (AFEM) with uniformly distributed
+noise with a mean value of 1.00 and a sigma of $\sim1\%$. Then
+multiply all your frames with this AFEM right before you start the
+actual reduction; and then compare the light curve emerging from your
+AFEM reduction and the original one, including fitting a sine wave.}
+
+\embed{
+ I would think that a PSF model in which the residuals and the
+ diffraction-limited (TinyTim) components are scaled together is more
+ realistic than keeping the residuals fixed. Would you try scaling
+ these together and see if the results are still the same?}
+
+Actually by adding an artificial flat error mask or scaling the residual
+together with the TinyTim PSFs together does not change the
+photometric measurement too much. The F125W light curve measured as
+original, with an AFEM, and with residual part scaling together with PSFs
+are shown in Figure \ref{fig:compare}. The trends of the three light
+curves are very similar. For measurement with an AFEM, the maximum
+deviation of normalized photometry point from the original is around
+0.005, which is $\sim50\%$ of the amplitude of the fitted sine
+curve. For most of the data points, the deviation is below 0.002. For
+the measurement with residual part scaling together with Tiny Tim
+PSFs, the light curve is almost identical. The maximum difference
+comparing to the original one is at $1\times10^{-4}$ level, which is
+one order of magnitude smaller than the amplitude of the sine curve.
+\begin{figure}[!h]
+  \centering
+  \includegraphics[height=0.5\textheight]{Diff}
+  \caption{light curves of the original one (1st), the one measured with an
+    AFEM applied (2nd), the one measured with residual part
+    scaling together (3rd) and their difference. In the 4th panel, red
+  points are the difference of the AFEM LC and the original LC, and
+  blue points are the difference of the residual scaling LC and the
+  original LC.}\label{fig:compare}
+\end{figure}
+
 \end{document}

### 2015-07-21 2M1207ANALYSIS/plotDiffLightCurve.py

@@ -1,0 +1,57 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+from plotLightCurve import normFlux
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+
+if __name__ == '__main__':
+    fn125_1 = '2015_Jun_24TinyTimF125Result.csv'
+    fn125_2 = '2015_Jul_14TinyTimF125Result.csv'
+    fn125_3 = '2015_Jul_16TinyTimF125Result.csv'
+
+    df125_1 = pd.read_csv(
+        fn125_1, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125_1 = df125_1.sort_index()
+    # time in ns
+    df125_1['Time'] = np.float32(
+        df125_1.index.values - df125_1.index.values[0]) / (60 * 60 * 1e9)
+    fA125_1, fB125_1 = normFlux(df125_1, normDither=True)
+
+    df125_2 = pd.read_csv(
+        fn125_2, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125_2 = df125_2.sort_index()
+    # time in ns
+    df125_2['Time'] = np.float32(
+        df125_2.index.values - df125_2.index.values[0]) / (60 * 60 * 1e9)
+    fA125_2, fB125_2 = normFlux(df125_2, normDither=True)
+
+    df125_3 = pd.read_csv(
+        fn125_3, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125_3 = df125_3.sort_index()
+    # time in ns
+    df125_3['Time'] = np.float32(
+        df125_3.index.values - df125_3.index.values[0]) / (60 * 60 * 1e9)
+    fA125_3, fB125_3 = normFlux(df125_3, normDither=True)
+
+    fig = plt.figure(figsize=(8, 10))
+    ax_1 = fig.add_subplot(411)
+    ax_1.plot(df125_1['Time'], fB125_1, 's', label='original')
+    ax_2 = fig.add_subplot(412, sharex=ax_1)
+    ax_2.plot(df125_2['Time'], fB125_2, 's', label='AFEM')
+    ax_3 = fig.add_subplot(413, sharex=ax_1)
[…]

### 2015-07-21 2M1207ANALYSIS/plotSplitedDataSet.py

@@ -93,4 +93,5 @@ if __name__ == '__main__':
         ax.set_ylabel('normed flux')
     ax4.set_xlabel('Time (hr)')
     fig160.tight_layout()
-    plt.show()
+    fig125.savefig('F125W_SplitDataSet.pdf')
+    fig160.savefig('F160W_SplitDataSet.pdf')

### 2015-08-05 summary/letter/letter_v1.tex
one extreme case needed to be look at

@@
 
-\begin{figure}[h]
+\begin{figure*}
   \centering
-  \plotone{original}
-  \plotone{subtracted}
+  \plottwo{original}{subtracted}
   \caption{WFC3 F160W images of 2M1207A system. Upper: original image,
@@
   \label{fig:1}
-\end{figure}
+\end{figure*}
 \subsection{Tiny Tim PSF Photometry}
@@
 measurement.
-\subsection{Uncertainty Analysis}
+
+\section{Result}
+
+We obtained high signal to noise photometry series for both 2M1207 A
+and B. On average, the photometric contrast is $6.52\pm0.03$ for
+F125W and $5.77\pm0.02$ for F160W. The difference of F125W contrast
+from 7.0 magnitude of J-band contrast \citep{Mohanty2007} and that of
+F160W contrast from 5.60 magnitude of NICMOS F160W contrast
+\citep{Song2006} are due to the different throughput profiles of the
+filters.
+
+Normalized light curves for both filters are presented in Figure
+\ref{fig:2}. Although the light curves are relative noisy and have a
+scattering of $\sim 3\%$, both F125W and F160W light curves for 2M1207
+B demonstrated a significant time variability.
+\begin{figure*}[h]
+  \centering
+  \plotone{sineCurveFit}
+  \caption{Normalized F125W and F160W light curves for 2M1207 B and
+    A. For companion's light curves, gray crosses are unbinned
+    photometric measurements while red circles and blue squares are
+    exposure-set-based binned data representing two halves of the data
+  set. For F160W, green curve is least square fitted sinusoidal wave
+  with period fixed to be same as the fitting result for F125W, and
+  purple curve is the one with no parameter fixed in the fitting routine.}
+  \label{fig:2}
+\end{figure*}
+
+\subsection{Uncertainty analysis}
+\begin{itemize}
+\item the source of the scattering -- 
+\item flat field uncertainty -- adding artificial flat field error mask
+\item validity of the variability\\
+  -- both filter demonstrate similar period of variability\\
+  -- split the data into two half, the trend in two halves of data
+  looks similar.
+  -- fix the position does not change the light curve
+\item uncertainty of sinusoidal curve fit
+  -- carry out a mcmc fit? is it worth doing this.
+\end{itemize}
+
 \begin{figure*}[h]
@@
     orbits.}
-  \label{fig:fig2}
+  \label{fig:3}
 \end{figure*}
-\section{Result}
-\begin{figure}[h]
-  \centering
-  \plotone{sineCurveFit}
-  \caption{Normalized light curves for F125W and F160W. Red squares
-    are the phtometric measurment for 2M1207 B, and gray dots are for
-    2M1207 A.}
-  \label{fig:3}
-\end{figure}
+
 \section{Discussion }

### 2015-08-05 2M1207ANALYSIS/contrast.py

@@ -1,0 +1,21 @@
+from __future__ import print_function, division
+import pandas as pd
+import numpy as np
+
+if __name__ == '__main__':
+    fn125 = '2015_Jun_24TinyTimF125Result.csv'
+    fn160 = '2015_Jun_24TinyTimF160Result.csv'
+    df125 = pd.read_csv(
+        fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125 = df125.sort_index()
+    df160 = pd.read_csv(
+        fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df160 = df160.sort_index()
+    contrast125 = np.log10(df125['FLUXA'] / df125['FLUXB']) * 2.5
+    contrast160 = np.log10(df160['FLUXA'] / df160['FLUXB']) * 2.5
+    print('F125W contrast: {0:.2f}$\pm${1:.2f}'.
+          format(contrast125.mean(), contrast125.std()))
+    print('F160W contrast: {0:.2f}$\pm${1:.2f}'.
+          format(contrast160.mean(), contrast160.std()))

### 2015-08-05 2M1207ANALYSIS/illustrateImage.py

@@ -3,6 +3,8 @@ from __future__ import print_function, division
 import matplotlib.pyplot as plt
 import numpy as np
 from astropy.io import fits
+import matplotlib as mpl
+from matplotlib.colors import BoundaryNorm
 
 """make an image to illustrate the 2M1207 system
 especially the difficulty
@@ -16,17 +18,29 @@ if __name__ == '__main__':
     fig2 = plt.figure(2)
     ax1 = fig1.add_subplot(111)
     ax2 = fig2.add_subplot(111)
-    cax1 = ax1.imshow(np.arcsinh(im), cmap='hot', origin='lower',
-                      interpolation='nearest', vmin=0)
-    ax1.plot(15.855, 8.204, '*', ms=14, mfc='white', mew=0.8)
+    bd1 = np.logspace(np.log10(im.min()), np.log10(im.max()), 255)
+    cax1 = ax1.imshow(im, cmap='hot', origin='lower',
+                      interpolation='nearest',
+                      norm=BoundaryNorm(bd1, ncolors=255))
+    ax1.plot(15.855, 8.204, 'o', ms=14, mfc='none', mew=1.5, mec='white')
     ax1.annotate('2M1207 B', xy=(15.855, 8.204), xytext=(17, 7),
                  fontsize=14)
     ax1.set_xlim([0, 26])
     ax1.set_ylim([0, 26])
-    cax2 = ax2.imshow(np.arcsinh(im - psf), cmap='hot', origin='lower',
-                      interpolation='nearest', vmin=0)
-    # cbar1 = fig1.colorbar(cax1)
-    # cbar2 = fig2.colorbar(cax2)
+    sub = im - psf
+    bd2 = np.concatenate((-np.logspace(-0.24, -1, 50) * 5,
+                          np.linspace(-0.1, 0.1, 5),
+                          np.logspace(-1, 1.3, 150) * 5))
+    cax2 = ax2.imshow(sub, cmap='hot', origin='lower',
+                      interpolation='nearest',
+                      norm=BoundaryNorm(bd2, ncolors=255))
+    cbar1 = fig1.colorbar(cax1, ticks=np.logspace(-1, 4, 6))
+    cbar1.formatter = mpl.ticker.LogFormatter()
+    cbar1.update_ticks()
+    cbar2 = fig2.colorbar(cax2, ticks=[-1, 0, 1, 10, 100])
[…]

### 2015-08-05 2M1207ANALYSIS/period.py

@@ -5,15 +5,27 @@ import pandas as pd
 import matplotlib.pyplot as plt
 from scipy.signal import lombscargle  # lomb scargle method
 from plotLightCurve import normFlux
-#from lmfit import Model
+# from lmfit import Model
 from scipy.optimize import leastsq
+import matplotlib as mpl
 plt.style.use('paper')
 """measure the period of light curve
 """
 
 
-# def sinFunc(x, amp, T, phi0):
-#     return amp * np.sin((2 * np.pi / T) * x + phi0) + 1
+def binNorm(df):
+    fA, fB = normFlux(df, normDither=True)
+    df['f0'] = fB  # add one column
+    tBin = []
+    fBin = []
+    for orbit in range(1, 7):
+        subdf = df[df['ORBIT'] == orbit]
+        ditherSet = set(subdf['DITHER'])
+        for dither in ditherSet:
+            fBin.append(subdf[subdf['DITHER'] == dither]['f0'].median())
+            tBin.append(subdf[subdf['DITHER'] == dither]['Time'].mean())
+    return tBin, fBin
+
 
 def fitfunc(p, x):
     return p[0] * np.sin((2 * np.pi / p[1]) * x + p[2]) + 1.0
@@ -51,32 +63,76 @@ if __name__ == '__main__':
     """
     plt.close('all')
     fig = plt.figure()
-    ax125 = fig.add_subplot(211)
-    points125, = ax125.plot(df125['Time'], f125B0, 's', ms=6)
-    ax125.plot(df125['Time'], f125A0, 'o', color='0.8', zorder=0)
+    gs = mpl.gridspec.GridSpec(3, 2)
+    ax125B = fig.add_subplot(gs[0:2, 0])
+    df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
+    df125_2 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
+    tBin_125_1, fBin_125_1 = binNorm(df125_1)
+    tBin_125_2, fBin_125_2 = binNorm(df125_2)
+    ax125B.plot(tBin_125_1, fBin_125_1, 'o')
+    ax125B.plot(tBin_125_2, fBin_125_2, 's')
     t = np.linspace(df125['Time'].min(), df125['Time'].max(), 500)
     modelFlux = 0.0139 * np.sin(2 * np.pi / 10.9765 * t + 0.5874) + 1.0001
[…]

### 2015-08-05 2M1207ANALYSIS/plotLightCurve.py

@@ -108,8 +108,8 @@ def plotLightCurve(DataFrame125, DataFrame160, applyCorr=False):
 
 
 if __name__ == '__main__':
-    fn125 = '2015_Jun_24TinyTimF125Result.csv'
-    fn160 = '2015_Jun_24TinyTimF160Result.csv'
+    fn125 = '2015_Jul_29TinyTimF125Result.csv'
+    fn160 = '2015_Jul_29TinyTimF160Result.csv'
     applyCorr = True
     plt.close('all')
     df125 = pd.read_csv(

### 2015-08-08 2M1207ANALYSIS/MCFit.m
mc fit, yay

@@ -1,0 +1,5 @@
+%% to fit the curve in a Monte Carlo way
+%% the 1 sigma error bar for one data point is given by the standard 
+%% deviation of the photometric time series
+%% for F125W it is 1.41%
+%% for F160W it is 1.08%

### 2015-08-08 2M1207ANALYSIS/aExtremeCase/imageCompare.py

@@ -1,0 +1,5 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+
+"""examine the difference of two image
+"""

### 2015-08-08 2M1207ANALYSIS/contrast.py

@@ -1,6 +1,7 @@
 from __future__ import print_function, division
 import pandas as pd
 import numpy as np
+from plotLightCurve import normFlux
 
 if __name__ == '__main__':
     fn125 = '2015_Jun_24TinyTimF125Result.csv'
@@ -9,13 +10,30 @@ if __name__ == '__main__':
         fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
         index_col='datetime')
     df125 = df125.sort_index()
+    df125['Time'] = np.float32(
+        df125.index.values - df125.index.values[0]) / (60 * 60 * 1e9)
     df160 = pd.read_csv(
         fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
         index_col='datetime')
     df160 = df160.sort_index()
+    df160['Time'] = np.float32(
+        df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
     contrast125 = np.log10(df125['FLUXA'] / df125['FLUXB']) * 2.5
     contrast160 = np.log10(df160['FLUXA'] / df160['FLUXB']) * 2.5
     print('F125W contrast: {0:.2f}$\pm${1:.2f}'.
           format(contrast125.mean(), contrast125.std()))
     print('F160W contrast: {0:.2f}$\pm${1:.2f}'.
           format(contrast160.mean(), contrast160.std()))
+
+    # standard deviation of one measurement
+    model125 = 0.0139 * np.sin(2 * np.pi / 10.9765 * df125['Time'] + 0.5874)\
+        + 1.0001
+    model160 = 0.0088 * np.sin(2 * np.pi / 9.2692 * df160['Time'] - 0.1180)\
+        + 1.0002
+    f125A0, f125B0 = normFlux(df125, normDither=True)
+    f160A0, f160B0 = normFlux(df160, normDither=True)
+    std125 = (f125B0 - model125).std()
+    std160 = (f160B0 - model160).std()
+
+    print('F125W stddev: {0:.2f}%'.format(std125 * 100))
+    print('F160W stddev: {0:.2f}%'.format(std160 * 100))

### 2015-08-14 summary/letter/letter_v1.tex
mc fit, yay
ok, roll subtraction

--- 2015-07-21 summary/letter/letter_v1.tex
@@
 \title{Variability of Planetary Mass Companion 2M1207 B}
-\author{Yifan Zhou, Daniel Apai, ...}
+\shorttitle{Variability of 2M1207 B}
+\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
 \affil{University of Arizona}
@@
 \section{Observation}
-We carried out high contrast direct imaging observation of  2M1207
+We took high contrast direct imaging observation of 2M1207
 system on UT 2014 April 11 using HST.
 (\textit{HST} Proposal GO-13418, PI: D. Apai). The data were acquired
-with the Wide Field Camera 3 (WFC3, citation needed) in filter F125W
+with the Wide Field Camera 3 (WFC3) in filter F125W
 and F160W using the $256\times256$ sub-array mode. We observed
@@
 difference of $25^{\circ}$, thus the companion would appear at
-different position relative to the primary with different roll angle
+different position relative to the primary 
 and the primary in the two data set can be subtracted from each other.
-In each orbit we will take a sequence of 13 SPARS25 exposures with
-NSAMP=10, alternating between F160W and F125W filters. To improve PSF
-sampling and reduce the influence of bad pixels, we applied standard 4
+In each orbit we took a sequence of 13 SPARS25 exposures with
+NSAMP=10, alternating between F160W and F125W filters, with 2-3
+identical exposures in one exposure sequence. To improve PSF
+sampling and reduce the risk caused by bad pixels, we applied standard 4
 point dithering. In each orbit, exposures were taken with dithering
@@
 produced by WFC3's \texttt{calwfc3} pipeline. The \flt were reduced
-with calibrations including dark current correction, non-linearity
+with calibration steps including dark current correction, non-linearity
 correction, and flat field correction. A further step of up-the-ramp
-fit was applied to combine all non-destructive read and remove cosmic
-rays. Although \citeauthor{Mandell2013} stated that WFC3 IR time series
+fit was applied to combine all non-destructive reads and remove cosmic
+rays. Although \cite{Mandell2013} stated that WFC3 IR time series
 extract from {\flt} have a rms 1.3 times larger than that obtained
 from {\ima}, \flt keeps all pixels of the image of 2M1207 A
-unsaturated while in most of non-destructive reads the cores of 2M1207
-A are saturated, so that with \flt the flux of 2M1207 B can be more
-precisely separated from that of 2M1207A.
+unsaturated, while in 80\% of non-destructive reads the cores of 2M1207
+A are saturated. Thus \flt help better align the images for primary
+subtraction, and separate the flux of 2M1207 B from that of 2M1207A.
 
@@
 very difficult. On the under-sampled WFC3 IR detector (plate scale
-$\sim 0.13$ arcsec per pixel), the primary and the secondary only
-separate by $\sim 6$ pixels, which is about 5 times of the FWHM of the
-PSF. In addition, under-sampling of the PSF causes significant
-artifacts when shifting the PSF to register images no matter what
-interpolation method is used.
+$\sim 0.13''\mbox{pixel}^{-1}$ \cite{dressel2012wide}), the primary
+and the secondary only separate by $\sim 6$ pixels, which is about 5
+times of the FWHM of the PSF. In addition, under-sampling causes
+significant artifacts when shifting the images for registration no
+matter what interpolation method is used.
 
-\begin{figure}[h]
+\begin{figure*}
   \centering
-  \plotone{original}
-  \plotone{subtracted}
+  \plottwo{original}{subtracted}
   \caption{WFC3 F160W images of 2M1207A system. Upper: original image,
@@
     (residual + Tiny Tim PSF) subtraction, the image of 2M1207 B is
-    clearly presented.}
+    clearly displayed.}
   \label{fig:1}
-\end{figure}
+\end{figure*}
+
 \subsection{Tiny Tim PSF Photometry}
@@
 significant advantage of Tiny Tim PSF over empirical PSF is that Tiny Tim can
-produce over-sampled PSF, which makes the shifting and interpolation
-rather straight forward. However, Tiny Tim model PSFs have systematic
-errors. \citeauthor{Biretta2014} demonstrated that the diffraction
-spikes and coma are not well simulated with Tiny Tim for WFC3 IR images.
+produce Nyquist sampled PSF, which makes image shifting and interpolation
+rather straight forward. One essential disadvantage of Tiny Tim is
+that the model PSFs have significant systematic
+errors. \cite{Biretta2014} demonstrated that the diffraction
+spikes and coma are not well simulated with Tiny Tim for WFC3 IR
+images. However, using the 6-orbit long time series, we are able
+to well characterize the difference of model PSFs and empirical PSFs.
+By modeling the difference and combining it with model PSFs, we can
+produce high quality hybrid PSFs to significantly improve the PSF
+simulation and PSF photometry.
 
-We start the reduction by making bad pixel masks for every
-images. Pixels with data quality flags 'bad detector pixels' (DQ = 4),
-'unstable response' (DQ = 32), and 'bad or uncertain flat value' (DQ =
+We started the reduction by making bad pixel masks for every
+image. Pixels with data quality flags ``bad detector pixels'' (DQ = 4),
+``unstable response'' (DQ = 32), and ``bad or uncertain flat value'' (DQ =
 512) were masked out and excluded from further analysis as suggested
@@
 We then produced a list of 10x over-sampled PSFs based on the
-positions and spectrum \citep{Bonnefoy2014} of 2M1207A with different telescope jitter
-ranging from 0 to 50 mini-arcsec per second in both $x$ and $y$
-direction. The focus parameter was calculated using the model listed
-on the STScI
+positions and spectrum \citep{Bonnefoy2014} of 2M1207 A with different
+telescope jitter ranging from 0 to 50 $\mbox{mini-arcsec s}^{-1}$ in
+both $x$ and $y$ directions. We used the new set of Tiny Tim
+parameters provided by \cite{Biretta2014} to better model the cold
+mask, diffraction spikes, and the coma. The focus parameters were
+calculated using the model listed on the STScI
 website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. The
 PSFs were registered with the original image by searching on a dynamic
-grid and minimizing the residual of a region centered on 2M1207 A with
-the image of 2M1207 B mostly excluded. The best fitted primary star
-position and telescope jitter were obtained in this step. Then, we
-generated the PSF for 2M1207 B based on its position on detector,
-spectrum \citep{Patience2010}, and the telescope jitter that had been obtained above. In
-the final step, we combined the two PSFs together. We fixed the
-position of the primary as it had been fitted in the first step and
-fitted for the amplitude of the two PSFs and the precise position of
-the secondary. Since the total fluxes of the model PSFs are normalized
-to unity as default, the fluxes of 2M1207 A and B are solely
-represented by the amplitude of the two PSFs coordinately.
+grid and minimizing the difference of observation and model PSF at a
+region centered on 2M1207 A with the image of 2M1207 B mostly
+excluded. The best fitted primary star position and telescope jitter
+were obtained in this step. Then, we generated the PSF for 2M1207 B
+based on its position on detector, spectrum \citep{Patience2010}, and
+the telescope jitter that had been obtained above. In the final step,
+we combined the two PSFs together. We fixed the position of the
+primary as it had been fitted in the first step and fitted for the
+amplitudes of the two PSFs and the precise position of the
+secondary. Since the total fluxes of the model PSFs were normalized to
+unity as default, the fluxes of 2M1207 A and B were solely represented
+by the amplitude of the two PSFs coordinately.
 
 Because of the systematic errors of the Tiny Tim PSF, the quality of the
-fitting is not optimistic. The reduced $\chi^{2}$ values are around
-$\sim10$. However, we found that the residual patterns were very
+fitting is not optimistic. The reduced $\chi^{2}$ values were at level
+of $\sim10$. However, we found that the residual patterns were very
 stable among the image that have the same dithering position and
@@
 residual from the original image and repeated the procedure that
-listed above. Using this extra-step, the systematic error of Tiny Tim
+listed above. Using this extra-step, the reduced $\chi^{2}$
 greatly decreased to around unity.
 
-The fluxes for both 2M1207 A and B are clearly correlated with the
-dithering position, which is primarily due to imperfection of the flat
-field. To reduce the correlation, we normalize each group of exposures
-that have the same dithering position and roll angle indivadually --
+\subsection{Uncertainty analysis}
+
+\subsubsection{White noise}
+The difficulties of high contrast photometry is finally exhibited by
+the error bars of the measurement. The scatterings of the photometric
+measurements are dominated by photon noise.  We estimated the photon
+noise by calculating the total flux within a 3-pixel (0.39 arcsec)
+aperture centered on 2M1207 B. The photon noises for F125W and F160W photometry are
+2.1\% and 1.2\%. These calculation results are at the same level of
+the scattering of the photometric time series.
+
+\subsubsection{Flat field uncertainties}
+In our observation, 2M1207 B were taken exposure at 8 different spots
+on the detector (2 rolls $\times$ 4 dithering
+positions). The uncertainties in the flat field are potential sources of variation. The uncertainty of WFC3 IR pipeline flat field
+is $\sim 1\%$ \citep{dressel2012wide} and our time resolved observation for another target
+demonstrate that aperture photometry for exposures taken at different
+dithering position have scatterings at the same level.
+
+Flat field uncertainties have smaller effects on PSF photometry since
+multiple pixels are fitted simultaneously. To verify this, we multiplied
+an artificial flat field error mask that is a uniform distributed
+Gaussian noise array with mean of 1 and sigma of 1\% to every image,
+and repeat the PSF photometry routine with the error-applied
+images. We obtained almost same photometry measurements as the
+original.
+
+However, PSF profile changes with different exposure positions due to
+pixelation, especially for the case that WFC3 IR is significantly
+under-sampled. Also, the flat fields may potentially have large scale
+structures \citep{dressel2012wide}. Because of these factors, The
+fluxes for both 2M1207 A and B are clearly correlated with the
+dithering position. To reduce the correlation, we normalize each group of exposures
+that have the same dithering position and roll angle individually --
 we took the median of the fluxes that were measured from these
-exposures as normalization factors and devided them from every flux
-measurement. 
-\subsection{Uncertainty Analysis}
-\begin{figure*}[h]
+exposures as normalization factors and devided them from every photometric
+measurement. Because the normalization factor for each group of
+exposures is calculated across the whole observation, this
+normalization step have negligible impacts on variability analysis.
+
+\subsubsection{Validity tests for the variability}
+
+\begin{figure*}
   \centering
-  \plottwo{F125_corr}{F160_corr}
-  \caption{Fluxes of the primary and the secondary is correlated with
-    the ditheirng positions. Different symbols represent different
-    orbits.}
-  \label{fig:fig2}
+  \includegraphics[width=\textwidth]{systematics}
+  \caption{Normalized light curves for 2M1207B with filter F125W
+    (left) and F160W (right). Original photometric measurements are
+    plotted with gray crosses. The two halves of data are binned
+    individually, and plotted with red points (first half) and blue
+    squares (second half). The F160W light curves are plotted with two
+  fitted sinusoidal curves, The green curve is fitted with
+  the period fixed to be same as the F125W and the purple curve is
+  fitted with all parameter set free.}
+  \label{fig:2}
 \end{figure*}
+
+Because the aim of this letter is to search for temporal change, it is
+essential to exclude the possibility that variability is systematic
+artifacts.
+
+ We fitted sinusoidal waves to both of the F125W and F160W light
+ curves to preliminarily quantify the variability. The periods of the
+ best fitted sine function of the two light curves are similar, 10.9
+ hour for F125W and 9.3 hour for F160W, and the periods fitted here
+ are not related with any WFC3 instrumental periods. The similarity of
+ the period measurements is a proof that the variability is physical.
+
+ Due to image persistence effect, the first orbit of HST observation
+ is often problematic, and is neglected by several analyses
+ (\textbf{citation?}). In our analysis, the fluxes measured from 2M1207 A are
+ significantly lower in the first lower (Figure \ref{fig:3}) than
+ those measured from rest fo the orbits. The exposure levels at the
+ pixels of the peak of the PSF of 2M1207 B are less than 10000 e$^{-}$
+ for both two colors, thus image persistence is less of an issue for
+ 2M1207 B. To further exclude this effect, we fitted sinusoidl waves
+ to the light curves without using the first orbit, and obtained
+ similar results.
+
+ To rule out the possibility that the variability is introduced by
+ data reduction, e.g., the normalization step, we split the data into
+ two halves -- the first half is the data taken at dithering position 1
+ and 3, and the second half is that for ditheirng position 2 and
+ 4. For each half, we repeat the analysis independently. For both of
+ F125W and F160W, two halves demonstrated similar trend of
+ variability as shown in Figure \ref{fig:2}.
+ % \begin{itemize}
+% \item the source of the scattering -- 
+% \item flat field uncertainty -- adding artificial flat field error mask
+% \item validity of the variability\\
+%   -- both filter demonstrate similar period of variability\\
+%   -- split the data into two half, the trend in two halves of data
+%   looks similar.
+%   -- fix the position does not change the light curve
+% \item uncertainty of sinusoidal curve fit
+%   -- carry out a mcmc fit? is it worth doing this.
+% \end{itemize}
+
 \section{Result}
-\begin{figure}[h]
+
+\begin{figure*}
   \centering
-  \plotone{sineCurveFit}
-  \caption{Normalized light curves for F125W and F160W. Red squares
-    are the phtometric measurment for 2M1207 B, and gray dots are for
-    2M1207 A.}
+  \plotone{sineCurveFit_binCombined}
+  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
+    with filter F125W (left) and F160W (right). Individual photometric
+  measurement are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoidal waves are plotted
+  with blue solid lines.}
   \label{fig:3}
-\end{figure}
-\section{Discussion }
+\end{figure*}
+
+We obtained high signal to noise photometry series for both 2M1207 A
+and B (Figure \ref{fig:3}). On average, the photometric contrast is $6.52\pm0.03$ for
+F125W and $5.77\pm0.02$ for F160W. The difference of F125W contrast
+from that measured in J-band \citep{Mohanty2007} and
+F160W contrast from that measured with NICMOS F160W 
+\citep{Song2006} is due to the different throughput profiles of the
+filters.
+
+Although the photometric time series demonstrate relatively large
+scattering, both F125W and F160W light curves demonstrate sinusoidal
+shape with clear temporal variability. We fitted sine waves to the two
+light curves using least square optimization, and determined the
+periods and variation amplitudes. The best fitted periods for F125W
+and F160W are 10.9 and 9.3 hour correspondingly. The amplitudes for
+the normalized light curves are 1.4\% and 0.9\% for F125W and F160W
+light curves.
+
+\begin{figure*}
+  \centering
+  \plottwo{periodDistr}{amplitudeDistr}
+  \caption{Distributions for periods (left) and amplitudes(right) for the light
+    curve of F125W and F160W. The bin size for histograms of period is
+  0.25 hour and for that of amplitude is 0.5\%. Histograms are
+  normalized in the way that total area of the histogram equals to
+  1. In the right panel, Gaussian profiles are fitted to the
+  histograms and plotted in solid lines.}
+  \label{fig:4}
+\end{figure*}
+
+To constrain the uncertainties of the least square optimization
+results, we used a Monte Carlo(MC) method to improve the fitting. We
+generated a series of random Gaussian noises with the standard deviation same as
+the photon noise, added them to the original light curves, and applied
+least square fit to the new light curves. We repeated above routine for 10000 times and obtained
+the distribution of the fitting parameters. The distributions for the
+periods and the amplitudes for F125W and F160W light curves are
+shown in Figure \ref{fig:4}.
+
+The distributions for the periods demonstrate long tail shaped towards
+long period. The peaks of the two distributions separated by $\sim 1$
+hour. The difference of the peaks are within $1-\sigma$. Combing the
+measurements from the two light curves, we conclude the rotation period
+of 2M1207B to be $9.0_{-1.5}^{+2.5}$ hours.
+
+The variation amplitudes in the two bands have significant
+difference. The distributions of the amplitudes are well described by
+Gaussian profiles. To fit the histogram to a Gaussian function, we
+determined that amplitude distribution of F125W peaks at 1.5\% with a
+standard deviation of 0.3\%, and that of F160W have mean and standard
+deviation of 0.9\% and 0.2\% correspondingly. The peaks of the two
+histograms separated by more than $2-\sigma$. The variation amplitude
+of F125W light curve is 1.67 times of that of F160W light curve.
+
+\section{Discussion}
 \begin{itemize}
@@
   sinusoidal curve.
-\item the atmosphere and cloud structure of 2M1207 B. How does it
+\item constrain on the amplitude of the amplitude of the
+  variability. Large amplitude can be excluded. Constraints on the
+  inhomogeniety of the cloud coverage can be inferred -- small
+  thickness variance...
+\item ? The atmosphere and cloud structure of 2M1207 B. How does it
   compare to the brown dwarf.

### 2015-08-14 2M1207ANALYSIS/PSF_generate_list.py

@@ -35,6 +35,10 @@ if __name__ == '__main__':
     yc = int(sys.argv[2]) + 380
     fileName = sys.argv[3]
     MJD = float(sys.argv[4])
+    if len(sys.argv) <= 5:
+        silent = False
+    else:
+        silent = bool(int(sys.argv[5]))
 
     aimDIR = os.path.join('.', 'PSF_temp')
     if not os.path.exists(aimDIR):
@@ -43,7 +47,8 @@ if __name__ == '__main__':
     for jitx in jitxList:
         for jity in jityList:
             psfFN = pyTinyTim(xc, yc, fileName, jitx, jity,
-                              exposureFocus(MJD), outputDIR=aimDIR)
+                              exposureFocus(MJD), outputDIR=aimDIR,
+                              silent=silent)
             PSFFNFile.write(os.path.join(aimDIR, psfFN) + '\n')
 
     PSFFNFile.close()

### 2015-08-14 2M1207ANALYSIS/PSF_generator.py

@@ -33,10 +33,15 @@ if __name__ == '__main__':
     MJD = float(sys.argv[6])
     dis = exposureFocus(MJD)
     outfn = sys.argv[7]
+    if len(sys.argv) <= 8:
+        silent = False
+    else:
+        silent = bool(int(sys.argv[8]))
     aimDIR = os.getcwd()
     xc = xc + 380
     yc = yc + 380
     if not os.path.exists(aimDIR):
         os.mkdir(aimDIR)
     psfDIR = pyTinyTim(
-        xc, yc, fileName, jitx, jity, dis, outputDIR=aimDIR, outputRoot=outfn)
+        xc, yc, fileName, jitx, jity, dis, outputDIR=aimDIR, outputRoot=outfn,
+        silent=silent)

### 2015-08-14 2M1207ANALYSIS/plotLightCurve.py

@@ -108,9 +108,9 @@ def plotLightCurve(DataFrame125, DataFrame160, applyCorr=False):
 
 
 if __name__ == '__main__':
-    fn125 = '2015_Jul_29TinyTimF125Result.csv'
-    fn160 = '2015_Jul_29TinyTimF160Result.csv'
-    applyCorr = True
+    fn125 = '2015_Aug_13TinyTimF125Result.csv'
+    fn160 = '2015_Aug_13TinyTimF160Result.csv'
+    applyCorr = False
     plt.close('all')
     df125 = pd.read_csv(
         fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
@@ -119,3 +119,4 @@ if __name__ == '__main__':
         fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
         index_col='datetime')
     fig125, fig160 = plotLightCurve(df125, df160, applyCorr)
+    plt.show()

### 2015-08-14 2M1207ANALYSIS/plotResultDistr.py

@@ -4,8 +4,13 @@ import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 plt.style.use('paper')
+from scipy.optimize import curve_fit
 """plot the distribution for period and amplitude
 """
+
+
+def gauss(x, a, x0, sigma):
+    return a * np.exp(-(x - x0)**2 / (2 * sigma**2))
 
 if __name__ == '__main__':
     plt.close('all')
@@ -14,35 +19,47 @@ if __name__ == '__main__':
     pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
                                       unpack=True)
 
-    pBins = np.linspace(6, 20, 29)
+    pBins = np.linspace(6, 20, 57)
     fig_p, ax_p = plt.subplots()
 
-    countP125, binP125 = np.histogram(pDist125, bins=pBins)
-    countP160, binP160 = np.histogram(pDist160, bins=pBins)
+    countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
+    countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
     ax_p.bar(
-        binP125[:-1], countP125 / len(pDist125), pBins[1] - pBins[0],
+        binP125[:-1], countP125, pBins[1] - pBins[0],
         alpha=0.8, label='F125W')
     ax_p.bar(
-        binP160[:-1], countP160 / len(pDist160), pBins[1] - pBins[0],
+        binP160[:-1], countP160, pBins[1] - pBins[0],
         label='F160W', alpha=0.8, fc='#e41a1c')
     ax_p.legend()
     ax_p.set_xlabel('Period (hour)')
-    ax_p.set_ylabel('Probability')
+    ax_p.set_ylabel('Probability density (hour$^{-1}$)')
 
-    ampBins = np.linspace(0.003, 0.026, 24)
+    ampBins = np.linspace(0.003, 0.026, 47)
+    fineAmpBins = np.linspace(0.003, 0.026, 470)
     fig_amp, ax_amp = plt.subplots()
-    countAmp125, binAmp125 = np.histogram(ampDist125, bins=ampBins)
-    countAmp160, binAmp160 = np.histogram(ampDist160, bins=ampBins)
-    ax_amp.bar(
-        binAmp125[:-1], countAmp125 / len(ampDist125), ampBins[1] - ampBins[0],
[…]

### 2015-08-14 2M1207ANALYSIS/systematics.py

@@ -62,17 +62,17 @@ if __name__ == '__main__':
     For F125B amp=0.0139   T=10.9765    dphi=0.5874    baseline=1.0001
     """
     plt.close('all')
-    fig = plt.figure()
-    gs = mpl.gridspec.GridSpec(3, 2)
-    ax125B = fig.add_subplot(gs[0:2, 0])
+    fig = plt.figure(figsize=(8, 4))
+    gs = mpl.gridspec.GridSpec(1, 2)
+    ax125B = fig.add_subplot(gs[0, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
     df125_2 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
     tBin_125_1, fBin_125_1 = binNorm(df125_1)
     tBin_125_2, fBin_125_2 = binNorm(df125_2)
-    # ax125B.plot(tBin_125_1, fBin_125_1, 'o')
-    # ax125B.plot(tBin_125_2, fBin_125_2, 's')
-    ax125B.plot(np.concatenate([tBin_125_1, tBin_125_2]),
-                np.concatenate([fBin_125_1, fBin_125_2]), 'o')
+    ax125B.plot(tBin_125_1, fBin_125_1, 'o')
+    ax125B.plot(tBin_125_2, fBin_125_2, 's')
+    # ax125B.plot(np.concatenate([tBin_125_1, tBin_125_2]),
+    #             np.concatenate([fBin_125_1, fBin_125_2]), 'o')
     t = np.linspace(df125['Time'].min(), df125['Time'].max(), 500)
     modelFlux = 0.0139 * np.sin(2 * np.pi / 10.9765 * t + 0.5874) + 1.0001
     line125, = ax125B.plot(t, modelFlux, linewidth=1.8)
@@ -86,60 +86,42 @@ if __name__ == '__main__':
 
     f125A0_2, f125B0_2 = normFlux(df125_2, normDither=True)
 
-    ax125A = fig.add_subplot(gs[2, 0], sharex=ax125B)
-    ax125A.plot(df125['Time'], f125A0, 'o', color='0.8', zorder=0)
     """For F160B I used two type fit,
     1. free parameter fit
     amp=0.0088    T=9.2692   dphi=-0.1180    baseline=1.0002
     2. fixed parameter fit
     amp=0.0080    T=10.9765  dphi=0.2525    baseline=0.9997
     """
[…]

### 2015-08-14 python_src/pyTinyTim.py

@@ -9,7 +9,8 @@ Use Tinytim to generate a PSFs
 """
 
 
-def pyTinyTim(xc, yc, fileName, jitx=0, jity=0, secDis=0, outputRoot=None, outputDIR='.'):
+def pyTinyTim(xc, yc, fileName, jitx=0, jity=0, secDis=0,
+              outputRoot=None, outputDIR='.', silent=False):
     """
     use a pre-defined configuration file generated by tiny1 to generate the PSF file
     xc, yc: the position of the center of the psf
@@ -36,7 +37,8 @@ def pyTinyTim(xc, yc, fileName, jitx=0, jity=0, secDis=0, outputRoot=None, outpu
     sp.call(['tiny2', 'temp.in'], stdout=FNULL, stderr=sp.STDOUT)
     sp.call(['tiny3', 'temp.in', 'sub=9'], stdout=FNULL, stderr=sp.STDOUT)
     FNULL.close()
-    print(outputRoot, '00.fits generated', sep='')
+    if not silent:
+        print(outputRoot, '00.fits generated', sep='')
     psf_fn = inFile[1].strip() + '00_psf.fits'
     # two auxiliary files generated by PSF, remove these two files to keep the
     # working directory clean

### 2015-08-17 2M1207ANALYSIS/systematics.py
maybe that is the best way to characterize the uncertainty

@@ -125,3 +125,5 @@ if __name__ == '__main__':
     fig.tight_layout()
     plt.show()
     plt.savefig('systematics.pdf')
+    chisq125 = (((f125B0 - 1.0) / 0.015)**2).sum()
+    print(chisq125)

### 2015-08-17 summary/letter/letter_v1.tex
edited several parts of the letter

@@
 \author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
-\affil{University of Arizona}
+\affil{The University of Arizona}
 
@@
 \section{Observation}
-We took high contrast direct imaging observation of 2M1207
-system on UT 2014 April 11 using HST.
-(\textit{HST} Proposal GO-13418, PI: D. Apai). The data were acquired
-with the Wide Field Camera 3 (WFC3) in filter F125W
-and F160W using the $256\times256$ sub-array mode. We observed
-2M1207 system in continuous 6 HST orbits and obtained a data-set that
-have a temporal resolution of $\sim1.5$ minutes and baseline of $\sim
-8$ hours.
+We took high contrast direct imaging observation of 2M1207 system on
+UT 2014 April 11 using HST.  (\textit{HST} Proposal GO-13418, PI:
+D. Apai). The data were acquired with the Wide Field Camera 3 (WFC3)
+in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm. FWHM = 301.5
+nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM = 287.9 nm)
+using the $256\times256$ sub-array mode. We observed 2M1207 system in
+six contiguous HST orbits and obtained a data-set that have a temporal
+resolution of $\sim1.5$ minutes and baseline of 8 hours and 40
+minutes, interrupted by Earth occultaions of 58 minutes every  94 minutes.
 
-The observation was initially designed to apply standard roll
-subtraction to remove the primary star. The telescope roll angles for
-data taken in orbit 1, 3, 5 and those taken in orbit 2, 4, 6 have a
-difference of $25^{\circ}$, thus the companion would appear at
-different position relative to the primary 
-and the primary in the two data set can be subtracted from each other.
-In each orbit we took a sequence of 13 SPARS25 exposures with
-NSAMP=10, alternating between F160W and F125W filters, with 2-3
-identical exposures in one exposure sequence. To improve PSF
-sampling and reduce the risk caused by bad pixels, we applied standard 4
-point dithering. In each orbit, exposures were taken with dithering
-position 1 -- 4 sequently. To sum, we obtained 70 multi-acuum images
-for filter F125W and 64 images for filter F160W with exposure time of
-88.4 seconds for both two filters.
+The observations was initially designed to apply two-roll
+PSF-subtraction (e.g. \cite{Song2006}) to remove the background light from the primary star. The
+telescope roll angles for data taken in orbit 1, 3, 5 and those taken
+in orbit 2, 4, 6 differed by $25^{\circ}$, thus the roll displacement
+of the companion is 0.34 .  In
+each orbit we took a sequence of 13 SPARS25 exposures with NSAMP=10,
+alternating between F160W and F125W filters, with 2-3 identical
+exposures in one exposure sequence. To improve PSF sampling and reduce
+the risk caused by bad pixels, we applied standard 4 point
+dithering. In each orbit, exposures were taken with dithering position
+1 -- 4 sequently. To sum, we obtained 70 multi-acuum images for filter
+F125W and 64 images for filter F160W with exposure time of 88.4
+seconds for both two filters.
 

### 2015-08-19 summary/letter/letter_v1.tex
let's do another mc fit

@@
 D. Apai). The data were acquired with the Wide Field Camera 3 (WFC3)
-in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm. FWHM = 301.5
+in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm, full width at
+half maximum (FWHM) = 301.5
 nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM = 287.9 nm)
@@
 The observations was initially designed to apply two-roll
-PSF-subtraction (e.g. \cite{Song2006}) to remove the background light from the primary star. The
-telescope roll angles for data taken in orbit 1, 3, 5 and those taken
-in orbit 2, 4, 6 differed by $25^{\circ}$, thus the roll displacement
-of the companion is 0.34 .  In
-each orbit we took a sequence of 13 SPARS25 exposures with NSAMP=10,
-alternating between F160W and F125W filters, with 2-3 identical
-exposures in one exposure sequence. To improve PSF sampling and reduce
-the risk caused by bad pixels, we applied standard 4 point
+point spread function (PSF) subtraction (e.g. \cite{Song2006}) to remove the background light
+from the primary star. The telescope roll angles for data taken in
+orbit 1, 3, 5 and those taken in orbit 2, 4, 6 differed by
+$25^{\circ}$, thus the roll displacement of the companion is $0.34''$
+that is 2.75 and 2.30 resolution elements in F125W and F160W respectively.
+In each orbit we took a sequence of 13 SPARS10 exposures with
+NSAMP=10, alternating between F160W and F125W filters, with 2-3
+identical exposures in one exposure sequence. To improve PSF sampling
+and reduce the risk caused by bad pixels, we applied standard 4 point
 dithering. In each orbit, exposures were taken with dithering position
-1 -- 4 sequently. To sum, we obtained 70 multi-acuum images for filter
+1 -- 4 sequently. Over the 6 orbits, we obtained 70 multi-acuum images for filter
 F125W and 64 images for filter F160W with exposure time of 88.4
@@
 
-Through the whole analysis, we used the \flt that were
-produced by WFC3's \texttt{calwfc3} pipeline. The \flt were reduced
-with calibration steps including dark current correction, non-linearity
+Through the whole analysis, we used the \flt that were produced by
+WFC3's \texttt{calwfc3} pipeline. The \flt were reduced with
+calibration steps including dark current correction, non-linearity
 correction, and flat field correction. A further step of up-the-ramp
@@
 from {\ima}, \flt keeps all pixels of the image of 2M1207 A
-unsaturated, while in 80\% of non-destructive reads the cores of 2M1207
-A are saturated. Thus \flt help better align the images for primary
-subtraction, and separate the flux of 2M1207 B from that of 2M1207A.
+unsaturated, while in 80\% of non-destructive reads the cores of
+2M1207 A are saturated. Thus \flt help better align the images for
+primary subtraction, and separate the flux of 2M1207 B from that of
+2M1207A.
 
@@
 \subsubsection{White noise}
-The difficulties of high contrast photometry is finally exhibited by
-the error bars of the measurement. The scatterings of the photometric
-measurements are dominated by photon noise.  We estimated the photon
-noise by calculating the total flux within a 3-pixel (0.39 arcsec)
-aperture centered on 2M1207 B. The photon noises for F125W and F160W photometry are
-2.1\% and 1.2\%. These calculation results are at the same level of
-the scattering of the photometric time series.
+The scatters of the photometric measurements are dominated by photon
+noise. Uncertainties of one photometric measurement was combined by
+photon noise of every pixel during the PSF fit. The photon noises for
+2M1207B photometry in F125W and F160W are 1.33\% and 1.02\%,
+respectively, and are at the same level of the scatter of the
+photometric time series.
 
@@
 
-Flat field uncertainties have smaller effects on PSF photometry since
-multiple pixels are fitted simultaneously. To verify this, we multiplied
-an artificial flat field error mask that is a uniform distributed
-Gaussian noise array with mean of 1 and sigma of 1\% to every image,
-and repeat the PSF photometry routine with the error-applied
-images. We obtained almost same photometry measurements as the
-original.
+Flat field uncertainties have smaller effects on PSF photometry than
+aperture photometry since multiple pixels are fitted
+simultaneously. To verify this, we multiplied an artificial flat field
+error mask that is a uniform distributed Gaussian noise array with
+mean of 1 and sigma of 1\% to every image, and repeat the PSF
+photometry routine with the error-applied images. We obtained almost
+same photometry measurements as the original.
 

### 2015-08-19 2M1207ANALYSIS/KLIP.py

@@ -102,3 +102,4 @@ if __name__ == '__main__':
     labels = [l.get_label() for l in ls]
     ax_res.legend(ls, labels)
     plt.show()
+    fits.writeto('KLIP_test.fits', resIm, clobber=True)

### 2015-08-19 2M1207ANALYSIS/MCFit.m

@@ -4,15 +4,18 @@
 %% for F125W it is 1.41%
 %% for F160W it is 1.08%
 
-function [pDistr, ampDistr]=MCFit(fn, stdPhot, nLoop, outputFn)
-[t, ~, fB] = textread(fn, '%f %f %f');
+function [pDistr, ampDistr]=MCFit(fn, nLoop, outputFn)
+M = csvread(fn, 1);
+t = M(:, 1);
+fB = M(:, 2);
+err = M(:, 3);
 pDistr = zeros(nLoop, 1);
 ampDistr = zeros(nLoop, 1);
 F = @(p,xdata)p(1)*sin((2*pi/p(2))*xdata+p(3)) + 1; % define the function
 p0 = [0.01, 10.0, 0];
 for i=1:nLoop 
-    err = 1 + stdPhot * randn(size(fB));
-    fB_1 = err .* fB;
+    err_1 = err .* randn(size(fB));
+    fB_1 = fB + err_1;
     [pFit,~,~,~,~] = lsqcurvefit(F,p0,t,fB_1);
     pDistr(i) = pFit(2);
     ampDistr(i) = pFit(1);

### 2015-08-19 2M1207ANALYSIS/MCFit_fixP.m

@@ -1,0 +1,27 @@
+function pDistr=MCFit_fixP(fn1, fn2, nLoop, outputFN)
+M1 = csvread(fn1, 1);
+t1 = M1(:, 1);
+fB1 = M1(:, 2);
+err1 = M1(:, 3);
+
+M2 = csvread(fn2, 1);
+t2 = M2(:, 1);
+fB2 = M2(:, 2);
+err2 = M2(:, 3);
+pDistr = zeros(nLoop, 1);
+amp125 = zeros(nLoop, 1);
+amp160 = zeros(nLoop, 1);
+p0 = [0.01 10.0, 0, 0.01, 0];
+for i=1:nLoop
+    err1_1 = err1 .* randn(size(fB1));
+    fB1_1 = fB1 + err1_1;
+    err2_1 = err2 .* randn(size(fB2));
+    fB2_1 = fB2 + err2_1;
+    F=@(p)[(p(1)*sin((2*pi/p(2))*t1+p(3)) + 1 - fB1_1)./err1; ...
+           (p(4)*sin((2*pi/p(2))*t2+p(5)) + 1 - fB2_1)./err2];
+    [p, ~] = lsqnonlin(F,p0);
+    pDistr(i) = p(2);
+    amp125(i) = p(1);
+    amp160(i) = p(4);
+end
+csvwrite(outputFN, [pDistr, amp125, amp160]);

### 2015-08-19 2M1207ANALYSIS/calPeriodRange.py

@@ -1,0 +1,43 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+"""calculate the  range of the period fitting result
+"""
+
+if __name__ == '__main__':
+    pDist125, ampDist125 = np.loadtxt('F125W_Distr.csv', delimiter=',',
+                                      unpack=True)
+    pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
+                                      unpack=True)
+    pDist = np.loadtxt('pDistr.csv', unpack=True)
+    pBins = np.linspace(6, 20, 141)
+    midBins = (pBins[:-1] + pBins[1:]) / 2
+    countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
+    countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    countP, binP = np.histogram(pDist, bins=pBins, normed=1)
+    cumCountP125 = countP125.cumsum() / countP125.sum()
+    cumCountP160 = countP160.cumsum() / countP160.sum()
+    cumCountP = countP.cumsum() / countP.sum()
+    p125 = midBins[countP125 == countP125.max()][0]
+    p160 = midBins[countP160 == countP160.max()][0]
+    p = midBins[countP == countP.max()][0]
+    p125_floor = midBins[
+        cumCountP125 <= cumCountP125[midBins == p125] - 0.32][-1]
+    p125_ceil = midBins[
+        cumCountP125 >= cumCountP125[midBins == p125] + 0.32][0]
+
+     == p160] + 0.32][0]
+    p_floor = midBins[
+        cumCountP <= cumCountP[midBins == p] - 0.32][-1]
+    p_ceil = midBins[
+        cumCountP >= cumCountP[midBins == p] + 0.32][0]
+    print(p125, p125_floor, p125_ceil)
+    print(p160, p160_floor, p160_ceil)
+    print(p, p_floor, p_ceil)
+    plt.close('all')
+    plt.plot(midBins, cumCountP125)
+    plt.plot(midBins, cumCountP160)
+    plt.plot(midBins, cumCountP)
+    plt.show()

### 2015-08-19 2M1207ANALYSIS/plotResultDistr.py

@@ -14,28 +14,31 @@ def gauss(x, a, x0, sigma):
 
 if __name__ == '__main__':
     plt.close('all')
-    pDist125, ampDist125 = np.loadtxt('F125W_Distr.csv', delimiter=',',
-                                      unpack=True)
-    pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
-                                      unpack=True)
+    # pDist125, ampDist125 = np.loadtxt('F125W_Distr.csv', delimiter=',',
+    #                                   unpack=True)
+    # pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
+    #                                   unpack=True)
 
+    pDist, ampDist125, ampDist160 = np.loadtxt('fixP_fitResult.csv',
+                                               delimiter=',', unpack=True)
     pBins = np.linspace(6, 20, 57)
     fig_p, ax_p = plt.subplots()
 
-    countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
-    countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    # countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
+    # countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    countP, binP = np.histogram(pDist, bins=pBins, normed=1)
     ax_p.bar(
-        binP125[:-1], countP125, pBins[1] - pBins[0],
-        alpha=0.8, label='F125W')
-    ax_p.bar(
-        binP160[:-1], countP160, pBins[1] - pBins[0],
-        label='F160W', alpha=0.8, fc='#e41a1c')
-    ax_p.legend()
+        (pBins[:-1] + pBins[1:]) / 2, countP, pBins[1] - pBins[0],
+        alpha=0.8, fc='#e41a1c')
+    # ax_p.bar(
+    #     binP160[:-1], countP160, pBins[1] - pBins[0],
+    #     label='F160W', alpha=0.8, fc='#377eb8')
+    # ax_p.legend()
     ax_p.set_xlabel('Period (hour)')
     ax_p.set_ylabel('Probability density (hour$^{-1}$)')
 
-    ampBins = np.linspace(0.003, 0.026, 47)
-    fineAmpBins = np.linspace(0.003, 0.026, 470)
[…]

### 2015-08-19 2M1207ANALYSIS/uncertainty.py

@@ -1,0 +1,51 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import pandas as pd
+import numpy as np
+
+from plotLightCurve import normFlux
+"""uncertainty analysis for the photometry
+"""
+
+if __name__ == '__main__':
+    fn125 = '2015_Aug_16TinyTimF125Result.csv'
+    fn160 = '2015_Aug_16TinyTimF160Result.csv'
+    df125 = pd.read_csv(
+        fn125, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df125 = df125.sort_index()
+    # time in ns
+    df125['Time'] = np.float32(
+        df125.index.values - df125.index.values[0]) / (60 * 60 * 1e9)
+
+    df160 = pd.read_csv(
+        fn160, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},
+        index_col='datetime')
+    df160 = df160.sort_index()
+    # time in ns
+    df160['Time'] = np.float32(
+        df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
+
+    df125['err0'] = df125['FLUXERRB'] / df125['FLUXB']
+    df160['err0'] = df160['FLUXERRB'] / df160['FLUXB']
+    f125A0, f125B0 = normFlux(df125, normDither=True)
+    f160A0, f160B0 = normFlux(df160, normDither=True)
+    chisq125 = (((f125B0 - 1.0) / df125['err0'])**2).sum()
+    chisq160 = (((f160B0 - 1.0) / df160['err0'])**2).sum()
+    print(chisq125 / (len(f125B0) - 1))
+    print(chisq160 / (len(f160B0) - 1))
+    model125 = 0.0139 * np.sin(2 * np.pi / 10.9765 * df125['Time'] + 0.5874)\
+        + 1.0001
+    model160 = 0.0088 * np.sin(2 * np.pi / 9.2692 * df160['Time'] - 0.1180)\
+        + 1.0002
+    chisq125_1 = (((f125B0 - model125) /
+                   df125['err0'])**2).sum()
+    chisq160_1 = (((f160B0 - model160) /
+                   df160['err0'])**2).sum()
+    print(chisq125_1 / (len(f125B0) - 3))
+    print(chisq160_1 / (len(f160B0) - 3))
+    df125['FLUXB'] = f125B0
+    df160['FLUXB'] = f160B0
[…]

### 2015-08-24 summary/letter/letter_vAA.tex
many things need to be finished

\documentclass[apj]{emulateapj}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shorttitle{Short Title}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\begin{document}
\title{Variability of Planetary Mass Companion 2M1207 B}
\shorttitle{Variability of 2M1207 B}
\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
\affil{The University of Arizona}

\begin{abstract} Rotational modulations in disk-integrated light of
brown dwarfs have recently provided powerful constraints on the
properties of ultracool atmospheres, including longitudinal and
vertical cloud structures and cloud evolution. Furthermore, detection
of periodic light curve variations can directly probe the rotational
periods of ultracool objects.

We present here, for the first time, time-resolved high-precision
photometric measurements of a planetary-mass companion, 2MASS1207b, to
a brown dwarf primary. Using HST/WFC3 and point spread function %in
combination with two spacecraft roll angles we detect photometric
modulations in the light curve. The amplitude is XXX\% in the F160W
and XXX\% in the F125W filters; we find a consistent period and
similar phase in both bands. Joint fit to the lightcurve in both bands
suggest a period of XX$\pm$XXh. The relative amplitudes in the two
filters are very similar to that found in a recent study of a field
(high-gravity) L-dwarf, suggesting that the cloud structures that
introduce the photometric modulations are similar in high- and
low-gravity objects. Importantly, our study also measures, for the
first time, the rotational period for directly imaged planetary-mass
companion.
\end{abstract}

\keywords{kw1, kw2, ...}
\maketitle
%
\section{Introduction}

Cloud properties in high- and low-gravity objects -- thick clouds: an
explanation for very red and faint near-infrared fluxes of directly
imaged planets

Rotational mapping is powerful: successes in brown dwarfs...

The target 2M1207b... contrast The key challenge of obtaining the
lightcurve of 2M1207b is the high contrast to and small separation
from 2M1207A.

In this Letter we present the first high-contrast, high-precision,
time-resolved observations of a directly imaged planet or
planetary-mass object. We successfully detect rotational modulation
and measure the amplitudes in two bands and determine the rotational
period.

\section{Observation} We obtained direct images of the 2M1207A+b
system on UT 2014 April 11 {\bf give full time stamp} using the Hubble
Space Telescope (HST) and its Wide Field Camera 3 \citep[WFC3,
][]{McKenty2010} in the frame of the HST Proposal GO-13418 (PI:
D. Apai). We acquired the observations in filters F125W
($\lambda_{\mbox{pivot}}$ = 1245.9 nm, full width at half maximum
(FWHM) = 301.5 nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM =
287.9 nm), roughly corresponding to the J and H bands. The WFC3 pixel
scale is $\approx$13mas. We used the $256\times256$ pixels sub-array
mode to avoid memory dumps during the observations.  In order to
provide a near-continuous coverage for detecting modulations we
observed the 2M1207 system in six consecutive HST orbits, obtaining
data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
40 minutes. The observations were interrupted by 58 minute-long Earth
occultations every 94 minutes.

The observations applied space craft rolls between each two orbits to
allow roll-subtraction of the primary (e.g. \citealt{Song2006}). The
telescope roll angles for orbits 1, 3, and 5, and those taken in
orbits 2, 4, and 6 differed by $25^{\circ}$. At the separation of
2M1207b this angle difference corresponds to a displacement of
$0.34''$ or 2.75 and 2.30 resolution elements in F125W and F160W,
respectively. In each orbit we took thirteen SPARS10 non-destructive
read-outs with NSAMP=10, alternating between F160W and F125W filters,
with 2--3 identical exposures in one exposure sequence. To improve PSF
sampling and reduce the risk caused by bad pixels, we applied standard
4 point dithering. Over the 6 orbits, we obtained 70 images with 10
non-destructive read-outs in F125W and 64 images in F160W with
exposure time of 88.4~s in each filters.

\section{Data Reduction and Photometry}

%Although \cite{Mandell2013} stated that WFC3 IR time series
%extract from {\flt} have a rms 1.3 times larger than that obtained
%from {\ima}, \flt keeps all pixels of the image of 2M1207 A
%unsaturated, while in 80\% of non-destructive reads the cores of
%2M1207 A are saturated. 
%Thus \flt help better align the images for
%primary subtraction, and separate the flux of 2M1207 B from that of
%2M1207A.

%The small angular separation of 2M1207 A and B (as shown in Figure
%\ref{fig:1}) makes precise primary star subtraction and photometry
%very difficult. 
%On the under-sampled WFC3 IR detector (plate scale
%$\sim 0.13''\mbox{pixel}^{-1}$ \cite{dressel2012wide}), the primary
%and the secondary only separate by $\sim 6$ pixels, which is about 5
%times of the FWHM of the PSF. In addition, under-sampling causes
%significant artifacts when shifting the images for registration no
%matter what interpolation method is used.

\begin{figure*}
  \centering
  \plottwo{original}{subtracted}
  \caption{WFC3 F160W images of 2M1207A system. {\em Upper panel}: In the original image 
    2M1207 B is hidden in the halo of the bright 2M1207A.   {\em Lower panel:} In the residual image -- after the subtraction of the hybrid PSF -- 2M1207 B is detected at a high significant level.}
  \label{fig:1}
\end{figure*}

%\subsection{Photometry}

We started the reduction from the the \flt files produced by the WFC3's \texttt{calwfc3} pipeline. We did not opt to use the more advance \ima pipeline products because these provided less information on 2M1207A, which saturated after the first few read-outs. 
The \flt are results of basic calibration, including dark current correction, non-linearity
correction, flat field correction, as well as up-the-ramp fit on the non-destructive read-outs also considering cosmic rays. We started the reduction by making bad pixel masks for every
image. Pixels with data quality flags ``bad detector pixels'' (DQ = 4),
``unstable response'' (DQ = 32), and ``bad or uncertain flat value'' (DQ =
512) were masked out and excluded from further analysis as suggested
by previous transit exoplanet
spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.

On the under-sampled WFC3 IR detector 2M1207A and 2M1207b are only separated by $\sim6$ pixels or about 5 FWHM of the PSF. To accurately measure the brightness of 2M1207b we simultaneously fit the primary and the secondary with a sum of two hybrid PSFs.

{\em Hybrid PSF Calculation:} The hybrid PSFs were generated as a linear combination of a diffraction-limited PSF (calculated with the {\em Tiny Tim}  simulator, \citealt[e.g.][]{Krist}) and a empirically determined correction map. We used {\em Tiny Tim} to calculate model PSFs for the filters used,
the spectrum of our target, the telescope's actual focus, and the telescope jitter. 
We used the new set of Tiny Tim parameters provided by \cite{Biretta2014} to better model the cold
mask, diffraction spikes, and the coma. The focus parameters were calculated using the model listed on the STScI website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. 
A significant advantage of Tiny Tim PSF over empirical PSFs is that Tiny Tim can
produce Nyquist-sampled results, which allows accurate image shifting and interpolation. However, an important limitation of Tiny Tim is that the model PSFs have significant systematic
errors. \cite{Biretta2014} demonstrated that the diffraction
spikes and coma are not accurately simulated with Tiny Tim for WFC3/IR
images. However, using the 6-orbit long time series, we are able
to accurately characterize the difference of the modeled and observed PSFs and derive an empirical correction map: Corr = Mean ( PSF_modeled - PSF_observed ) where PSF_modeled is a combination of two Tiny Tim PSFs with positions and amplitudes optimized to minimize the residuals.
By combining the model PSFs with the empirical correction map we derived
a high-quality hybrid PSF, the use of which significantly improved the PSF
subtraction and photometry.

{\em PSF Fitting:} In the next step we simultaneously fitted the positions and amplitudes of the combination of the hybrid PSFs to 2M1207A and 2M1207b. First, we determined the primary star position and telescope jitter. We produced a list of 10$\times$ over-sampled PSFs matching the spectrum \citep{Bonnefoy2014} and the position of 2M1207A with different telescope jitters ranging from 0 to 50$\mbox{mini-arcsec s}^{-1}$ along
both $x$ and $y$ detector axes. The PSFs were registered with the original image by searching on a dynamic grid and minimizing the difference in the observed and modeled PSFs at a region centered on 2M1207 A with a 5-pixel-radius aperture centered 2M1207 B excluded.

Next, we determined the position and approximate flux of 2M1207B by calculating and fitting a Tiny Tim PSF for the hybrid PSF-subtracted 2M1207 B based on its position on the detector, spectrum \citep{Patience2010}, and
the telescope jitter that had been obtained above. In the final step,
we combined the two PSFs together.

We fixed the position of the primary as it had been fitted in the first step and fitted for the
amplitudes of the two PSFs and the precise position of the
secondary. Since the total fluxes of the model PSFs were normalized to
unity as default, the fluxes of 2M1207 A and B were solely represented
by the amplitude of the two PSFs coordinately.

Because of the systematic errors of the Tiny Tim PSF, the quality of the
fit is not perfect. The reduced $\chi^{2}$ values were at level
of $\sim10$. However, we found that the residual patterns were very
stable among the image that have the same dithering position and
telescope rolling. Therefore, we median combined the residual images
that have the same dithering position and telescope rolling angle to
construct 8 residual models (4 dithering position $\times$ 2 telescope
rolling angle) for each filter. We pre-subtract the corresponding
residual from the original image and repeated the procedure that
listed above. Using this extra-step, the reduced $\chi^{2}$
greatly decreased to around unity.

However, PSF profile changes with different exposure positions due to
pixelation, especially for the case that WFC3 IR is significantly
under-sampled. Also, the flat fields may potentially have large scale
structures \citep{dressel2012wide}. Because of these factors, the
fluxes for both 2M1207 A and B are clearly correlated with the
dithering position. To reduce the correlation, we normalize each group of exposures
that have the same dithering position and roll angle individually --
we took the median of the fluxes that were measured from these
exposures as normalization factors and devided them from every photometric
measurement. Because the normalization factor for each group of
exposures is calculated across the whole observation, this
normalization step have negligible impacts on variability analysis.

%\section{Uncertainty analysis}

\subsection{Uncertainty Analysis: White noise}
We consider the primary source of uncertainty for every measurement is
photon noise. We propagated the photon noises of every single pixel
that were calculated from count rates and detector gain, to the PSF
fitting results. The photon noises for photometry in F125W and F160W
are 1.33\% and 1.02\%, respectively.

Since the primary and secondary PSFs were fitted simultaneously in our
PSF photometry procedure, the uncertainties of photometry and position
for the primary and secondary are coupled with each other. The second
order uncertainty could also contribute to the overall uncertainty,
e.g. the imperfection of position measurement of 2M1207A can affect
the photometry of 2M1207b. We used a Monte Carlo (MC) method to evaluate the complete systematic of the
PSF fitting. We applied the PSF photometry to a image that
was added random Poisson noise and repeat the procedure for 1000
time. From the distribution of the result, the uncertainty for F125W
and F160W photometry are found to be 1.34\% and 1.12\%,
respectively. We conclude that the white noise of our observation is
dominated by photon noise.

\subsection{Uncertainty Analysis: Flat field uncertainties}
In our observations 2M1207 B were observed at 8 different spots
on the detector (2 rolls $\times$ 4 dithering
positions). Imperfect flat field correction are potential sources of variation as they may introduce position-dependent differences in the count rates. The uncertainty of WFC3 IR pipeline flat field
is $\sim 1\%$ \citep{dressel2012wide}. 
% and our time resolved observations for another target
%demonstrate that aperture photometry for exposures taken at different
%dithering position are uncertain at the same level.
%Flat field uncertainties have smaller effects on 
In PSF photometry, however, multiple pixels are fitted simultaneously and we expect a lower than 1\% uncertainty from the flat field errors. To verify this we multiplied
every image by an artificial flat field error mask  -- a uniformly distributed Gaussian noise array with mean of 1 and sigma of 1\% -- and repeated the PSF photometry on the resulting images. 
The analysis of these experiments showed almost identical lightcurve to the original, verifying that the flat field errors do not affect our photometry significantly.

\section{Verification of Photometric Variations and Amplitude Estimate}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{systematics}
  \caption{Normalized light curves for 2M1207B with filter F125W
    (left) and F160W (right). Original photometric measurements are
    plotted with gray crosses. The two halves of data are binned
    individually, and plotted with red points (first half) and blue
    squares (second half). The F160W light curves are plotted with two
  fitted sinusoidal curves, The green curve is fitted with
  the period fixed to be same as the F125W and the purple curve is
  fitted with all parameter set free.}
  \label{fig:2}
\end{figure*}

\subsection{Tests and Verification}

The light curves that resulted from our photometry show apparently sinusoidal modulations,
discussed in more details in \S,\ref{Results}. To verify that these modulations are intrinsic
to the object and not result of our data reduction procedure or due to instrumental changes, we carried out three different tests.

First, we fitted sine waves independently to the two filters to verify the similarity of the signal in the two bands. Inconsistent periods or light curve shapes would argue against a genuine signal.
We found that the periods of the best fit sine waves are very similar, 10.9$\pm$XX~h
 for F125W and 9.3$\pm$~h for F160W. These periods are consistent within the uncertainty. Furthermore, these periods are not close to any timescales over which HST or WFC3 are known to changes.

As a second test we repeated the analysis neglecting the first orbit. The motivation behind this test was that, due to spacecraft thermal settling, the first orbit of HST observations
 is often slightly unstable and is often neglected in high-precision studies (\textbf{citation?}). Indeed, in our analysis 2M1207 A is significantly fainter in the first orbit (Figure \ref{fig:3}) than in the subsequent ones. 
 %The exposure levels at the pixels of the peak of the PSF of 2M1207 B are less than 10,000 e$^{-}$
 %for both two colors, thus image persistence is less of an issue for
 %2M1207 B. 
Our analysis based on orbits 2--6 only found essentially identical results to our analysis of orbits 1--6, based on which we conclude that the first less reliable orbit does not affect our results significantly.

As a third test we explored whether a subset of images, perhaps imperfectly normalized or correlated with specific instrument states, could be driving the light curves into an apparently sinusoidal shape. To test this possibility we split the data into two temporally overlapping halves: sub-dataset one from dithering positions 1 and 3, and sub-dataset two from dithering positions 2 and 4. For both datasets we repeated our analysis independently. 
For both of F125W and F160W, two halves demonstrated similar trend of
 variability as shown in Figure \ref{fig:2}.
 Our analysis detected sinusoidal modulations in {\em both} sub-datasets and in {\em both} filters, with periods and amplitudes consistent with those derived from the complete data set.

 These tests demonstrate that the modulation seen in our data are consistently present in the different filters, in the different time segments of the data, and in data obtained in different dithering positions. 
 % \begin{itemize}
% \item the source of the scattering -- 
% \item flat field uncertainty -- adding artificial flat field error mask
% \item validity of the variability\\
%   -- both filter demonstrate similar period of variability\\
%   -- split the data into two half, the trend in two halves of data
%   looks similar.
%   -- fix the position does not change the light curve
% \item uncertainty of sinusoidal curve fit
%   -- carry out a mcmc fit? is it worth doing this.
% \end{itemize}

\subsection{Amplitude and Period Measurements}

To constrain the uncertainties of the least square optimization
results, we used a Monte Carlo(MC) method to improve the fitting. We
generated a series of random Gaussian noises with the standard deviation same as
the photon noise, added them to the original light curves, and applied
least square fit to the new light curves. We repeated above routine for 10000 times and obtained
the distribution of the fitting parameters. The distributions for the
periods and the amplitudes for F125W and F160W light curves are
shown in Figure \ref{fig:4}.

The distributions for the periods demonstrate long tail shaped towards
long period. The peaks of the two distributions separated by $\sim 1$
hour. The difference of the peaks are within $1-\sigma$. Combing the
measurements from the two light curves, we conclude the rotation period
of 2M1207B to be $9.0_{-1.5}^{+2.5}$ hours.

The variation amplitudes in the two bands have significant
difference. The distributions of the amplitudes are well described by
Gaussian profiles. To fit the histogram to a Gaussian function, we
determined that amplitude distribution of F125W peaks at 1.5\% with a
standard deviation of 0.3\%, and that of F160W have mean and standard
deviation of 0.9\% and 0.2\% correspondingly. The peaks of the two
histograms separated by more than $2-\sigma$. The variation amplitude
of F125W light curve is 1.67 times of that of F160W light curve.

\section{Result}

We present the first high-contrast, high-resolution, high-cadence, and high-precision photometry of a directly imaged planet or planetary-mass companion. Our observations reveal a modulation in the light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection of modulations in directly imaged ultracool objects.  The best fit periods for F125W and F160W are 10.9 and 9.3 hour correspondingly. The amplitudes for the normalized light curves are 1.4\% and 0.9\% for F125W and F160W light curves. Periods..

We obtained high signal to noise photometry series for both 2M1207 A
and B (Figure \ref{fig:3}). On average, the photometric contrast is $6.52\pm0.03$ for
F125W and $5.77\pm0.02$ for F160W. The difference of F125W contrast
from that measured in J-band \citep{Mohanty2007} and
F160W contrast from that measured with NICMOS F160W 
\citep{Song2006} is due to the different throughput profiles of the
filters.

In the following we will discuss the amplitude and period of 2M1207B and place this object in the broader context of ultracool atmospheres.

\begin{figure*}
  \centering
  \plotone{sineCurveFit_binCombined}
  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
    with filter F125W (left) and F160W (right). Individual photometric
  measurement are plotted in gray crosses and binned photometry are
  plotted with red points. Best fitted sinusoidal waves are plotted
  with blue solid lines.}
  \label{fig:3}
\end{figure*}

%Although the photometric time series demonstrate relatively large
%scattering, both F125W and F160W light curves demonstrate sinusoidal
%shape with clear temporal variability. We fitted sine waves to the two
%light curves using least square optimization, and determined the
%periods and variation amplitudes.

\begin{figure*}
  \centering
  \plottwo{periodDistr}{amplitudeDistr}
  \caption{Distributions for periods (left) and amplitudes(right) for the light
    curve of F125W and F160W. The bin size for histograms of period is
  0.25 hour and for that of amplitude is 0.5\%. Histograms are
  normalized in the way that total area of the histogram equals to
  1. In the right panel, Gaussian profiles are fitted to the
  histograms and plotted in solid lines.}
  \label{fig:4}
\end{figure*}

\section{Discussion}
Amplitude and Relative Amplitudes: Comparison to other brown dwarfs

Rotation Period: Comparison to Brown Dwarfs and Beta Pic

Method: Opens a new window, successful demonstration, how could it be improved?
Mapping different pressure levels, atmospheric dynamics?

\section{Conclusions}
\begin{itemize}
\item a data-reduction pipeline is developed to obtain high precision
  photometry measurement from high contrast WFC3 IR data. For a
  contrast of $\sim 7$ magnitudes at an angular separation of
  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
  precision of about 2-3\%. 
\item time variability for 2M1207 B was discovered, the light curve of
  2M1207 B for both two colors can be fitted with a T=10.7 hr
  sinusoidal curve.
\item constrain on the amplitude of the amplitude of the
  variability. Large amplitude can be excluded. Constraints on the
  inhomogeniety of the cloud coverage can be inferred -- small
  thickness variance...
\item ? The atmosphere and cloud structure of 2M1207 B. How does it
  compare to the brown dwarf.
\end{itemize}

\bibliography{ref.bib}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-08-24 summary/letter/letter_vAB.tex
many things need to be finished

--- 2015-08-24 summary/letter/letter_vAA.tex
@@
 \newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
+\newcommand{\tinytim}{\textit{Tiny Tim}}
 \begin{document}
@@
 combination with two spacecraft roll angles we detect photometric
-modulations in the light curve. The amplitude is XXX\% in the F160W
-and XXX\% in the F125W filters; we find a consistent period and
+modulations in the light curve. The amplitude is 0.9\% in the F160W
+and 1.5\% in the F125W filters; we find a consistent period and
 similar phase in both bands. Joint fit to the lightcurve in both bands
-suggest a period of XX$\pm$XXh. The relative amplitudes in the two
+suggest a period of 10.0$\pm$0.9h. The relative amplitudes in the two
 filters are very similar to that found in a recent study of a field
@@
 
-\keywords{kw1, kw2, ...}
+\keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
+  and satellites: individual (2M1207b) -- techniques: photometric}
 \maketitle
@@
 \section{Observation} We obtained direct images of the 2M1207A+b
-system on UT 2014 April 11 {\bf give full time stamp} using the Hubble
+system on UT 2014 April 11from 08:07:47 to 16:53:18 using the Hubble
 Space Telescope (HST) and its Wide Field Camera 3 \citep[WFC3,
-][]{McKenty2010} in the frame of the HST Proposal GO-13418 (PI:
+][]{Kimble2008} in the frame of the HST Proposal GO-13418 (PI:
 D. Apai). We acquired the observations in filters F125W
@@
 The observations applied space craft rolls between each two orbits to
-allow roll-subtraction of the primary (e.g. \citealt{Song2006}). The
+allow roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
 telescope roll angles for orbits 1, 3, and 5, and those taken in
@@
 
-\section{Data Reduction and Photometry}
+\section{Data Reduction}
 
@@
 
-%\subsection{Photometry}
+\subsection{Photometry}
 
-We started the reduction from the the \flt files produced by the WFC3's \texttt{calwfc3} pipeline.
-We did not opt to use the more advance \ima pipeline products because these provided less information on 2M1207A, which saturated after the first few read-outs.
-The \flt are results of basic calibration, including dark current correction, non-linearity
-correction, flat field correction, as well as up-the-ramp fit on the non-destructive read-outs also considering cosmic rays. We started the reduction by making bad pixel masks for every
-image. Pixels with data quality flags ``bad detector pixels'' (DQ = 4),
-``unstable response'' (DQ = 32), and ``bad or uncertain flat value'' (DQ =
-512) were masked out and excluded from further analysis as suggested
-by previous transit exoplanet
+We started the reduction from the the \flt files produced by the
+WFC3's \texttt{calwfc3} pipeline. We did not opt to use the more
+advance \ima pipeline products because these provided less information
+on 2M1207A, which saturated after the first few read-outs.  The \flt
+are results of basic calibration, including dark current correction,
+non-linearity correction, flat field correction, as well as
+up-the-ramp fit on the non-destructive read-outs also considering
+cosmic rays. From the beginning, pixels with data quality flags ``bad
+detector pixels'' (DQ = 4), ``unstable response'' (DQ = 32), and ``bad
+or uncertain flat value'' (DQ = 512) were masked out and excluded from
+further analysis as suggested by previous transit exoplanet
 spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.
 
-On the under-sampled WFC3 IR detector 2M1207A and 2M1207b are only separated by $\sim6$ pixels or about 5 FWHM of the PSF.
-To accurately measure the brightness of 2M1207b we simultaneously fit the primary and the secondary with a sum of two hybrid PSFs.
+One major challenge of high contrast imaging observation using WFC3/IR
+is significant under-sampling of the detector.  2M1207 A and b are
+only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF. When
+applying roll subtraction, notable artifact structures are generated
+by image interpolation and shifting. On the other hand, \tinytim{} PSF
+simulator\citep{Krist1995} offers a solution by providing Nyquist
+sampled PSF, but significant systematic errors of \tinytim{} PSF
+ limits its ability in high precision
+photometry\citep{Biretta2014}. However, 6 orbits of observation provides us a chance to
+fully characterize the difference of model and observed PSFs. To obtain
+robust \tinytim{} PSF photometry,  we designed a 2-round PSF fitting strategy: 1. calculating
+correction map for \tinytim{}; 2. hybrid PSF photometry.
 
-{\em Hybrid PSF Calculation:} The hybrid PSFs were generated as a linear combination of a diffraction-limited PSF (calculated with the {\em Tiny Tim}  simulator, \citealt[e.g.][]{Krist}) and a empirically determined correction map.
-We used {\em Tiny Tim} to calculate model PSFs for the filters used,
-the spectrum of our target, the telescope's actual focus, and the telescope jitter. 
-We used the new set of Tiny Tim parameters provided by \cite{Biretta2014} to better model the cold
-mask, diffraction spikes, and the coma. The focus parameters were calculated using the model listed on the STScI website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. 
-A significant advantage of Tiny Tim PSF over empirical PSFs is that Tiny Tim can
-produce Nyquist-sampled results, which allows accurate image shifting and interpolation. However, an important limitation of Tiny Tim is that the model PSFs have significant systematic
-errors. \cite{Biretta2014} demonstrated that the diffraction
-spikes and coma are not accurately simulated with Tiny Tim for WFC3/IR
-images. However, using the 6-orbit long time series, we are able
-to accurately characterize the difference of the modeled and observed PSFs and derive an empirical correction map: Corr = Mean ( PSF_modeled - PSF_observed ) where PSF_modeled is a combination of two Tiny Tim PSFs with positions and amplitudes optimized to minimize the residuals.
-By combining the model PSFs with the empirical correction map we derived
-a high-quality hybrid PSF, the use of which significantly improved the PSF
-subtraction and photometry.
+For both of 2 rounds, we used {\em Tiny Tim} to calculate 10$\times$
+over-sampled model PSFs based the filters, the spectra 
+\citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
+the telescope jitter.  We used the new set of Tiny Tim parameters
+provided by \cite{Biretta2014} to better model the cold mask,
+diffraction spikes, and the coma. The focus parameters were calculated
+using the model listed on the STScI
+website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
+We determined the exact position of 2M1207A first by fitting the PSF
+on a dynamic coordinate grid and minimizing the difference in the
+observed and modeled PSFs at a region centered on 2M1207 A with a
+5-pixel-radius aperture centered 2M1207 b excluded.Then we fit the
+position of 2M1207 b and the photometries of 2M1207 A and b together
+by least square optimization. From our data set, we discovered that
+the difference of observed PSFs and model PSFs are very stable for
+given PSF position. Therefore at the end of the first round PSF
+fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
+empirical correction maps for each filter:
+\begin{equation}
+  \mathrm{Corr = Median(PSF_{model} - PSF_{obs} )}
+\end{equation}
+where $\mathrm{PSF_{model}}$ is a combination of two \tinytim{} PSFs
+for 2M1207 A and b. In the second round, we combined the correction
+term linearly with the two \tinytim{} PSFs to generate hybrid PSFs, and fitted for their
+amplitudes together. We found that by including the correction term,
+the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
+around unity. Because the total fluxes of the model PSFs were
+normalized to unity as default, the fluxes of 2M1207 A and B were
+solely represented by the amplitude of the two PSFs coordinately.
 
-{\em PSF Fitting:} In the next step we simultaneously fitted the positions and amplitudes of the combination of the hybrid PSFs to 2M1207A and 2M1207b.
-First, we determined the primary star position and telescope jitter.
-We produced a list of 10$\times$ over-sampled PSFs matching the spectrum \citep{Bonnefoy2014} and the position of 2M1207A with different telescope jitters ranging from 0 to 50$\mbox{mini-arcsec s}^{-1}$ along
-both $x$ and $y$ detector axes.
-The PSFs were registered with the original image by searching on a dynamic grid and minimizing the difference in the observed and modeled PSFs at a region centered on 2M1207 A with a 5-pixel-radius aperture centered 2M1207 B excluded.
-
-Next, we determined the position and approximate flux of 2M1207B by calculating and fitting a Tiny Tim PSF for the hybrid PSF-subtracted 2M1207 B based on its position on the detector, spectrum \citep{Patience2010}, and
-the telescope jitter that had been obtained above. In the final step,
-we combined the two PSFs together.
-
-We fixed the position of the primary as it had been fitted in the first step and fitted for the
-amplitudes of the two PSFs and the precise position of the
-secondary. Since the total fluxes of the model PSFs were normalized to
-unity as default, the fluxes of 2M1207 A and B were solely represented
-by the amplitude of the two PSFs coordinately.
-
-Because of the systematic errors of the Tiny Tim PSF, the quality of the
-fit is not perfect. The reduced $\chi^{2}$ values were at level
-of $\sim10$. However, we found that the residual patterns were very
-stable among the image that have the same dithering position and
-telescope rolling. Therefore, we median combined the residual images
-that have the same dithering position and telescope rolling angle to
-construct 8 residual models (4 dithering position $\times$ 2 telescope
-rolling angle) for each filter. We pre-subtract the corresponding
-residual from the original image and repeated the procedure that
-listed above. Using this extra-step, the reduced $\chi^{2}$
-greatly decreased to around unity.
-
-However, PSF profile changes with different exposure positions due to
+However, PSF profiles change with different exposure positions due to
 pixelation, especially for the case that WFC3 IR is significantly
@@
 structures \citep{dressel2012wide}. Because of these factors, the
-fluxes for both 2M1207 A and B are clearly correlated with the
-dithering position. To reduce the correlation, we normalize each group of exposures
-that have the same dithering position and roll angle individually --
-we took the median of the fluxes that were measured from these
-exposures as normalization factors and devided them from every photometric
-measurement. Because the normalization factor for each group of
-exposures is calculated across the whole observation, this
-normalization step have negligible impacts on variability analysis.
+fluxes for both 2M1207 A and B are correlated with the dithering
+position. To break the correlation, we normalize each group of
+exposures that have the same dithering position and roll angle
+individually -- we took the median of the fluxes that were measured
+from these exposures as normalization factors and devided them from
+every photometric measurement. Because the normalization factor for
+each group of exposures is calculated across the whole observation,
+this normalization step have negligible impacts on variability
+analysis.
 
-%\section{Uncertainty analysis}
+% {\em Hybrid PSF Calculation:} The hybrid PSFs were generated as a
+% linear combination of a diffraction-limited PSF (calculated with the
+% {\em Tiny Tim} simulator\citep{Krist1995}, and a empirically
+% determined correction map. We used {\em Tiny Tim} to calculate model
+% PSFs for the filters used, the spectrum of our target, the telescope's
+% actual focus, and the telescope jitter.  We used the new set of Tiny
+% Tim parameters provided by \cite{Biretta2014} to better model the cold
+% mask, diffraction spikes, and the coma. The focus parameters were
+% calculated using the model listed on the STScI
+% website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
+% A significant advantage of Tiny Tim PSF over empirical PSFs is that
+% Tiny Tim can produce Nyquist-sampled results, which allows accurate
+% image shifting and interpolation. However, an important limitation of
+% Tiny Tim is that the model PSFs have significant systematic
+% errors. \cite{Biretta2014} demonstrated that the diffraction spikes
+% and coma are not accurately simulated with Tiny Tim for WFC3/IR
+% images. However, using the 6-orbit long time series, we are able to
+% accurately characterize the difference of the modeled and observed
+% PSFs and derive an empirical correction map: Corr = Mean (
+% PSF\_modeled - PSF\_observed ) where PSF\_modeled is a combination of
+% two Tiny Tim PSFs with positions and amplitudes optimized to minimize
+% the residuals.  By combining the model PSFs with the empirical
+% correction map we derived a high-quality hybrid PSF, the use of which
+% significantly improved the PSF subtraction and photometry.
+
+% {\em PSF Fitting:} In the next step we simultaneously fitted the positions and amplitudes of the combination of the hybrid PSFs to 2M1207A and 2M1207b.
+First, we determined the primary star position and telescope jitter.
+We produced a list of 10$\times$ over-sampled PSFs matching the spectrum \citep{Bonnefoy2014} and the position of 2M1207A with different telescope jitters ranging from 0 to 50$\mbox{mini-arcsec s}^{-1}$ along
+% both $x$ and $y$ detector axes.
+The PSFs were registered with the original image by searching on a dynamic grid and minimizing the difference in the observed and modeled PSFs at a region centered on 2M1207 A with a 5-pixel-radius aperture centered 2M1207 B excluded.
+
+% Next, we determined the position and approximate flux of 2M1207B by calculating and fitting a Tiny Tim PSF for the hybrid PSF-subtracted 2M1207 B based on its position on the detector, spectrum \citep{Patience2010}, and
+% the telescope jitter that had been obtained above. In the final step,
+% we combined the two PSFs together.
+
+% We fixed the position of the primary as it had been fitted in the first step and fitted for the
+% amplitudes of the two PSFs and the precise position of the
+% secondary. Since the total fluxes of the model PSFs were normalized to
+% unity as default, the fluxes of 2M1207 A and B were solely represented
+% by the amplitude of the two PSFs coordinately.
+
+% Because of the systematic errors of the Tiny Tim PSF, the quality of the
+% fit is not perfect. The reduced $\chi^{2}$ values were at level
+% of $\sim10$. However, we found that the residual patterns were very
+% stable among the image that have the same dithering position and
+% telescope rolling. Therefore, we median combined the residual images
+% that have the same dithering position and telescope rolling angle to
+% construct 8 residual models (4 dithering position $\times$ 2 telescope
+% rolling angle) for each filter. We pre-subtract the corresponding
+% residual from the original image and repeated the procedure that
+% listed above. Using this extra-step, the reduced $\chi^{2}$
+% greatly decreased to around unity.
+
+% %\section{Uncertainty analysis}
 
@@
 the photometry of 2M1207b. We used a Monte Carlo (MC) method to evaluate the complete systematic of the
-PSF fitting. We applied the PSF photometry to a image that
-was added random Poisson noise and repeat the procedure for 1000
+PSF fitting. We applied the PSF photometry to images that
+were added with random Poisson noise and repeat the procedure for 1000
 time. From the distribution of the result, the uncertainty for F125W
@@
 \subsection{Uncertainty Analysis: Flat field uncertainties}
-In our observations 2M1207 B were observed at 8 different spots
-on the detector (2 rolls $\times$ 4 dithering
-positions). Imperfect flat field correction are potential sources of variation as they may introduce position-dependent differences in the count rates. The uncertainty of WFC3 IR pipeline flat field
-is $\sim 1\%$ \citep{dressel2012wide}. 
+
+ \begin{figure*}
+  \centering
+  \plotone{systematics}
+  \caption{F125W (left) and F160W (right) light curves under different
+  verification tests. Individual measurements are plotted with gray
+  crosses. Photometries of the same exposure sequence are binned, and
+  binned data are plotted with points and squares. Fitted sinusoidal
+  waves are plotted with solid lines. {\em Upper}: binned photometries taken
+in dithering position 1 and 3 (red points) and that taken in 2 and 4
+(blue squares) are plotted differently. They demonstrate same trend of
+variation. In upper left panel, sinusoidal wave fitted with all
+parameter set free, and that fitted with period set the same as that
+of F125W are plotted with green and purple lines, respectively. {\em
+  Middle}: sinusoidal waves fitted without using the data taken in
+Orbit 1 are plotted. These curves are almost identical to the curves
+plotted in upper panel. {\em Lower}: photometry measured with
+AFEM-applied images and their best fitted sinusoidal curves are
+plotted. These photometries and curves are also almost identical to
+those plotted in upper panel.}
+  \label{fig:2}
+\end{figure*}
+
+In our observations 2M1207 B were observed at 8 different spots on the
+detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
+field correction are potential sources of variation as they may
+introduce position-dependent differences in the count rates. The
+uncertainty of WFC3 IR pipeline flat field is $\sim 1\%$
+\citep{dressel2012wide}.
 % and our time resolved observations for another target
@@
 %Flat field uncertainties have smaller effects on 
-In PSF photometry, however, multiple pixels are fitted simultaneously and we expect a lower than 1\% uncertainty from the flat field errors. To verify this we multiplied
-every image by an artificial flat field error mask  -- a uniformly distributed Gaussian noise array with mean of 1 and sigma of 1\% -- and repeated the PSF photometry on the resulting images. 
-The analysis of these experiments showed almost identical lightcurve to the original, verifying that the flat field errors do not affect our photometry significantly.
+In PSF photometry, however, multiple pixels are fitted simultaneously
+and we expect a lower than 1\% uncertainty from the flat field
+errors. To verify this we multiplied every image by an artificial flat
+field error mask (AFEM) -- a uniformly distributed Gaussian noise array with
+mean of 1 and sigma of 1\% -- and repeated the PSF photometry on the
+resulting images.  The analysis of these experiments showed almost
+identical lightcurve to the original, verifying that the flat field
+errors do not affect our photometry significantly (Figure
+\ref{fig:2}).
 
-\section{Verification of Photometric Variations and Amplitude Estimate}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{systematics}
-  \caption{Normalized light curves for 2M1207B with filter F125W
-    (left) and F160W (right). Original photometric measurements are
-    plotted with gray crosses. The two halves of data are binned
-    individually, and plotted with red points (first half) and blue
-    squares (second half). The F160W light curves are plotted with two
-  fitted sinusoidal curves, The green curve is fitted with
-  the period fixed to be same as the F125W and the purple curve is
-  fitted with all parameter set free.}
-  \label{fig:2}
-\end{figure*}
+\section{Verification of Photometric Variations and Amplitude
+  Estimate}
 
@@
 
-The light curves that resulted from our photometry show apparently sinusoidal modulations,
-discussed in more details in \S,\ref{Results}. To verify that these modulations are intrinsic
-to the object and not result of our data reduction procedure or due to instrumental changes, we carried out three different tests.
+The light curves that resulted from our photometry show apparently
+sinusoidal modulations, discussed in more details in
+\S,\ref{Results}. To verify that these modulations are intrinsic to
+the object and not result of our data reduction procedure or due to
+instrumental changes, we carried out three different tests.
 
-First, we fitted sine waves independently to the two filters to verify the similarity of the signal in the two bands. Inconsistent periods or light curve shapes would argue against a genuine signal.
-We found that the periods of the best fit sine waves are very similar, 10.9$\pm$XX~h
- for F125W and 9.3$\pm$~h for F160W. These periods are consistent within the uncertainty. Furthermore, these periods are not close to any timescales over which HST or WFC3 are known to changes.
+First, we fitted sine waves independently to the two filters to verify
+the similarity of the signal in the two bands (Figure \ref{fig:2}). Inconsistent periods or
+light curve shapes would argue against a genuine signal.  We found
+that the periods of the best fit sine waves are very similar,
+$10.45^{+1.2}_{-1.3}$h for F125W and $9.0^{+1.1}_{-1.2}$h for
+F160W. These periods are consistent within the
+uncertainty. Furthermore, these periods are not close to any
+timescales over which HST or WFC3 are known to changes.
 
-As a second test we repeated the analysis neglecting the first orbit. The motivation behind this test was that, due to spacecraft thermal settling, the first orbit of HST observations
- is often slightly unstable and is often neglected in high-precision studies (\textbf{citation?}).
-Indeed, in our analysis 2M1207 A is significantly fainter in the first orbit (Figure \ref{fig:3}) than in the subsequent ones.
+ As a second test we repeated the analysis neglecting the first
+ orbit. The motivation behind this test was that, due to spacecraft
+ thermal settling, the first orbit of HST observations is often
+ slightly unstable and is often neglected in high-precision studies
+ (\textbf{citation?}). Indeed, in our analysis 2M1207 A is
+ significantly fainter in the first orbit (Figure \ref{fig:3}) than in
+ the subsequent ones.
  %The exposure levels at the pixels of the peak of the PSF of 2M1207 B are less than 10,000 e$^{-}$
@@
  %2M1207 B. 
-Our analysis based on orbits 2--6 only found essentially identical results to our analysis of orbits 1--6, based on which we conclude that the first less reliable orbit does not affect our results significantly.
+ Our analysis based on orbits 2--6 only found essentially identical
+ results to our analysis of orbits 1--6, based on which we conclude
+ that the first less reliable orbit does not affect our results
+ significantly (Figure \ref{fig:2}, middle panel).
 
-As a third test we explored whether a subset of images, perhaps imperfectly normalized or correlated with specific instrument states, could be driving the light curves into an apparently sinusoidal shape.
-To test this possibility we split the data into two temporally overlapping halves: sub-dataset one from dithering positions 1 and 3, and sub-dataset two from dithering positions 2 and 4.
-For both datasets we repeated our analysis independently.
-For both of F125W and F160W, two halves demonstrated similar trend of
- variability as shown in Figure \ref{fig:2}.
- Our analysis detected sinusoidal modulations in {\em both} sub-datasets and in {\em both} filters, with periods and amplitudes consistent with those derived from the complete data set.
+As a third test we explored whether a subset of images, perhaps
+imperfectly normalized or correlated with specific instrument states,
+could be driving the light curves into an apparently sinusoidal
+shape. To test this possibility we split the data into two temporally
+overlapping halves: sub-dataset one from dithering positions 1 and 3,
+and sub-dataset two from dithering positions 2 and 4. For both
+datasets we repeated our analysis independently.  For both of F125W
+and F160W, two halves demonstrated similar trend of variability as
+shown in Figure \ref{fig:2}.  Our analysis detected sinusoidal
+modulations in {\em both} sub-datasets and in {\em both} filters, with
+periods and amplitudes consistent with those derived from the complete
+data set (\ref{fig:2}, upper panel).
 
- These tests demonstrate that the modulation seen in our data are consistently present in the different filters, in the different time segments of the data, and in data obtained in different dithering positions.
+ These tests demonstrate that the modulation seen in our data are
+ consistently present in the different filters, in the different time
+ segments of the data, and in data obtained in different dithering
+ positions.
+
  % \begin{itemize}
@@
 
+  \begin{figure*}
+  \centering
+  \plotone{sineCurveFit_binCombined}
+  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
+    with filter F125W (left) and F160W (right). Individual photometric
+  measurement are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoidal waves are plotted
+  with blue solid lines.}
+  \label{fig:3}
+\end{figure*}
+
 \subsection{Amplitude and Period Measurements}
@@
 
-The distributions for the periods demonstrate long tail shaped towards
-long period. The peaks of the two distributions separated by $\sim 1$
-hour. The difference of the peaks are within $1-\sigma$. Combing the
-measurements from the two light curves, we conclude the rotation period
-of 2M1207B to be $9.0_{-1.5}^{+2.5}$ hours.
-
-The variation amplitudes in the two bands have significant
-difference. The distributions of the amplitudes are well described by
-Gaussian profiles. To fit the histogram to a Gaussian function, we
-determined that amplitude distribution of F125W peaks at 1.5\% with a
-standard deviation of 0.3\%, and that of F160W have mean and standard
-deviation of 0.9\% and 0.2\% correspondingly. The peaks of the two
-histograms separated by more than $2-\sigma$. The variation amplitude
-of F125W light curve is 1.67 times of that of F160W light curve.
-
 \section{Result}
-
-We present the first high-contrast, high-resolution, high-cadence, and high-precision photometry of a directly imaged planet or planetary-mass companion.
-Our observations reveal a modulation in the light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection of modulations in directly imaged ultracool objects.
-The best fit periods for F125W and F160W are 10.9 and 9.3 hour correspondingly.
-The amplitudes for the normalized light curves are 1.4\% and 0.9\% for F125W and F160W light curves.
-Periods..
-
-We obtained high signal to noise photometry series for both 2M1207 A
-and B (Figure \ref{fig:3}). On average, the photometric contrast is $6.52\pm0.03$ for
-F125W and $5.77\pm0.02$ for F160W. The difference of F125W contrast
-from that measured in J-band \citep{Mohanty2007} and
-F160W contrast from that measured with NICMOS F160W 
-\citep{Song2006} is due to the different throughput profiles of the
-filters.
-
-In the following we will discuss the amplitude and period of 2M1207B and place this object in the broader context of ultracool atmospheres.
-
-\begin{figure*}
-  \centering
-  \plotone{sineCurveFit_binCombined}
-  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Individual photometric
-  measurement are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoidal waves are plotted
-  with blue solid lines.}
-  \label{fig:3}
-\end{figure*}
-
-%Although the photometric time series demonstrate relatively large
-%scattering, both F125W and F160W light curves demonstrate sinusoidal
-%shape with clear temporal variability. We fitted sine waves to the two
-%light curves using least square optimization, and determined the
-%periods and variation amplitudes.
 
@@
 \end{figure*}
+
+\label{Results}
+We present the first high-contrast, high-resolution, high-cadence, and
+high-precision photometry of a directly imaged planet or
+planetary-mass companion. Our observations reveal a modulation in the
+light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection
+of modulations in directly imaged ultracool objects.  The best fit
+periods for F125W and F160W are 10.4 and 9.0 hour correspondingly. The
+amplitudes for the normalized light curves are 1.4\% and 0.9\% for
+F125W and F160W light curves.
+
+We obtained high signal to noise photometry series for both 2M1207 A
+and B (Figure \ref{fig:3}). On average, the photometric contrast is
+$6.52\pm0.01$ mag for
+F125W and $5.77\pm0.01$ mag for F160W. The difference of F125W contrast
+from that measured in J-band \citep{Mohanty2007} and
+F160W contrast from that measured with NICMOS F160W 
+\citep{Song2006} is due to the different throughput profiles of the
+filters.
+
+In the following we will discuss the amplitude and period of 2M1207B
+and place this object in the broader context of ultracool atmospheres.
+
+The distributions for the periods demonstrate long tail shaped towards
+long period, with core region roughly Gaussian. With probability range
+of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ standard
+deviations for the periods of F125W and F160W to be 1.2 h and 1.5 h. The period for best
+fitted sine wave of F125W light curve is longer than that of F160W for
+1.4 h that is around 1-$\sigma$ standard deviation. We also
+performed a joint MC fit with the two light curves with the assumption
+that the periods of the variation of the two bands are the same. We
+derived a period of $10.0\pm0.9$ h.
+
+The variation amplitudes in the two bands have significant
+difference. The distributions of the amplitudes are well described by
+Gaussian profiles. Fitting the histogram to a Gaussian function, we
+determined that amplitude distribution of F125W peaks at 1.5\% with a
+standard deviation of 0.3\%, and that of F160W have mean and standard
+deviation of 0.9\% and 0.2\%, respectively. The peaks of the two
+histograms separated by more than 2-$\sigma$. The variation amplitude
+of F125W light curve is 1.67 times of that of F160W light curve.
+
+%Although the photometric time series demonstrate relatively large
+%scattering, both F125W and F160W light curves demonstrate sinusoidal
+%shape with clear temporal variability. We fitted sine waves to the two
+%light curves using least square optimization, and determined the
+%periods and variation amplitudes.
 

### 2015-08-24 2M1207ANALYSIS/KLIP.py

@@ -4,6 +4,7 @@ import numpy as np
 from scipy.io import readsav  # read IDL save file
 import matplotlib.pyplot as plt
 from astropy.io import fits
+import pandas as pd
 """KLIP pipe line
    reference:  Sourmer 2012
 adapted from Neil Zimmerman's code
@@ -68,10 +69,26 @@ def getEffCoord(imShape, annulusList):
     return np.where(mask == 1)
 
 
+def getRelativePos(DF, imageIndex):
+    """get the relative position of companion from the dataframe"""
+    return DF[['SECONDARY_X', 'SECONDARY_Y']].values[imageIndex] -\
+        DF[['PRIMARY_X', 'PRIMARY_Y']].values[imageIndex]
+
+
+def KLIP_Photometry(im, im_KLIP, pos1, pos2):
+    """im: original image
+       im_KLIP: klip combined image, to be subtracted
+       pos1
+    """
+
 if __name__ == '__main__':
     savFile = readsav('F125W_KLIP_PSF_library.sav')
+    infoDF = pd.read_csv('2015_Jun_24TinyTimF125Result.csv')
+    angle0DF = infoDF[infoDF['POSANGLE'] == 0]
+    angle1DF = infoDF[infoDF['POSANGLE'] == 1]
     cube0 = savFile['angle0cube']
     cube1 = savFile['angle1cube']
+    imageIndex = 0  # image to process
     # get effective coordinate
     coord_eff = getEffCoord(cube0[0].shape, [[17, 9, 0, 4], [17, 9, 10, 100],
                                              [13, 13, 0, 3]])
@@ -79,27 +96,31 @@ if __name__ == '__main__':
     Z = KLtrans(cube0, id_eff)
     residual = np.zeros((cube1.shape[0], cube0.shape[0] - 3))
     maxValue = np.zeros((cube1.shape[0], cube0.shape[0] - 3))
-    klipList = range(3, cube0.shape[0])
-    for i in range(cube1.shape[0]):
-        for j, klip in enumerate(klipList):
-            im = KLIP(cube1[i], Z, id_eff, klip)
-            resIm = cube1[i] - im
-            residual[i, j] = np.sqrt((resIm[coord_eff]**2).sum())
-            maxValue[i, j] = resIm[8, 16]
-    residual0 = np.mean(residual, axis=0)
-    maxValue0 = np.mean(maxValue, axis=0)
-    plt.close('all')
[…]

### 2015-08-24 2M1207ANALYSIS/MCFit_fixP.m

@@ -1,16 +1,17 @@
-function pDistr=MCFit_fixP(fn1, fn2, nLoop, outputFN)
+function pDistr=MCFit_fixP(fn1, fn2, err1, err2, nLoop, outputFN)
 M1 = csvread(fn1, 1);
 t1 = M1(:, 1);
 fB1 = M1(:, 2);
-err1 = M1(:, 3);
 
 M2 = csvread(fn2, 1);
 t2 = M2(:, 1);
 fB2 = M2(:, 2);
-err2 = M2(:, 3);
+
 pDistr = zeros(nLoop, 1);
 amp125 = zeros(nLoop, 1);
 amp160 = zeros(nLoop, 1);
+phase125 = zeros(nLoop, 1);
+phase160 = zeros(nLoop, 1);
 p0 = [0.01 10.0, 0, 0.01, 0];
 for i=1:nLoop
     err1_1 = err1 .* randn(size(fB1));
@@ -23,5 +24,7 @@ for i=1:nLoop
     pDistr(i) = p(2);
     amp125(i) = p(1);
     amp160(i) = p(4);
+    phase125(i) = p(3);
+    phase160(i) = p(5);
 end
-csvwrite(outputFN, [pDistr, amp125, amp160]);
+csvwrite(outputFN, [pDistr, amp125, phase125, amp160, phase160]);

### 2015-08-24 2M1207ANALYSIS/period.py

@@ -64,6 +64,9 @@ if __name__ == '__main__':
     plt.close('all')
     fig = plt.figure()
     gs = mpl.gridspec.GridSpec(3, 2)
+    axOut = fig.add_subplot(gs[:, :])
+    axOut.set_xlabel('Time (h)', labelpad=24)
+    axOut.set_ylabel('Normalized flux', labelpad=42)
     ax125B = fig.add_subplot(gs[0:2, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
     df125_2 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
@@ -86,7 +89,7 @@ if __name__ == '__main__':
 
     f125A0_2, f125B0_2 = normFlux(df125_2, normDither=True)
 
-    ax125A = fig.add_subplot(gs[2, 0], sharex=ax125B)
+    ax125A = fig.add_subplot(gs[2, 0])
     ax125A.plot(df125['Time'], f125A0, 'o', color='0.8', zorder=0)
     """For F160B I used two type fit,
     1. free parameter fit
@@ -94,7 +97,7 @@ if __name__ == '__main__':
     2. fixed parameter fit
     amp=0.0080    T=10.9765  dphi=0.2525    baseline=0.9997
     """
-    ax160B = fig.add_subplot(gs[0:2, 1], sharey=ax125B)
+    ax160B = fig.add_subplot(gs[0:2, 1])
 
     df160_1 = df160[(df160['DITHER'] == 0) | (df160['DITHER'] == 2)]
     df160_2 = df160[(df160['DITHER'] == 1) | (df160['DITHER'] == 3)]
@@ -113,19 +116,21 @@ if __name__ == '__main__':
                              ms=8, mec='0.8', zorder=0)
     ax160B.set_title('F160W light curve')
     # ax160B.legend()
-    ax160A = fig.add_subplot(gs[2, 1], sharex=ax160B)
+    ax160A = fig.add_subplot(gs[2, 1])
     ax160A.plot(df160['Time'], f160A0, 'o', color='0.8', zorder=0)
 
     # adjust the labels and gridspec
-    for ax in [ax125B, ax160B]:
-        ax.get_xaxis().set_visible(False)
+    for ax in [ax125B, ax160B, axOut]:
+        # ax.get_xaxis().set_visible(False)
+        ax.set_xticks([])
         ax.set_ylim([0.95, 1.05])
[…]

### 2015-08-24 2M1207ANALYSIS/plotDiffLightCurve.py

@@ -6,9 +6,9 @@ import pandas as pd
 import numpy as np
 
 if __name__ == '__main__':
-    fn125_1 = '2015_Jun_24TinyTimF125Result.csv'
-    fn125_2 = '2015_Jul_14TinyTimF125Result.csv'
-    fn125_3 = '2015_Jul_16TinyTimF125Result.csv'
+    fn125_1 = '2015_Jun_24TinyTimF125Result.csv'  # original
+    fn125_2 = '2015_Jul_14TinyTimF125Result.csv'  # AFEM
+#    fn125_3 = '2015_Jul_16TinyTimF125Result.csv'
 
     df125_1 = pd.read_csv(
         fn125_1, parse_dates={'datetime': ['OBSDATE', 'OBSTIME']},

### 2015-08-24 2M1207ANALYSIS/plotResultDistr.py

@@ -14,28 +14,28 @@ def gauss(x, a, x0, sigma):
 
 if __name__ == '__main__':
     plt.close('all')
-    # pDist125, ampDist125 = np.loadtxt('F125W_Distr.csv', delimiter=',',
-    #                                   unpack=True)
-    # pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
-    #                                   unpack=True)
+    pDist125, ampDist125, phaseDist125 = np.loadtxt(
+        'F125W_Distr.csv', delimiter=',', unpack=True)
+    pDist160, ampDist160, phaseDist160 = np.loadtxt(
+        'F160W_Distr.csv', delimiter=',', unpack=True)
 
-    pDist, ampDist125, ampDist160 = np.loadtxt('fixP_fitResult.csv',
-                                               delimiter=',', unpack=True)
-    pBins = np.linspace(6, 20, 57)
-    fig_p, ax_p = plt.subplots()
+    # pDist, ampDist125, ampDist160 = np.loadtxt('fixP_fitResult.csv',
+    #                                            delimiter=',', unpack=True)
+    # pBins = np.linspace(6, 20, 57)
+    # fig_p, ax_p = plt.subplots()
 
-    # countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
-    # countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
-    countP, binP = np.histogram(pDist, bins=pBins, normed=1)
-    ax_p.bar(
-        (pBins[:-1] + pBins[1:]) / 2, countP, pBins[1] - pBins[0],
-        alpha=0.8, fc='#e41a1c')
+    # # countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
+    # # countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    # countP, binP = np.histogram(pDist, bins=pBins, normed=1)
     # ax_p.bar(
-    #     binP160[:-1], countP160, pBins[1] - pBins[0],
-    #     label='F160W', alpha=0.8, fc='#377eb8')
-    # ax_p.legend()
-    ax_p.set_xlabel('Period (hour)')
-    ax_p.set_ylabel('Probability density (hour$^{-1}$)')
+    #     (pBins[:-1] + pBins[1:]) / 2, countP, pBins[1] - pBins[0],
[…]

### 2015-08-24 2M1207ANALYSIS/systematics.py

@@ -27,6 +27,10 @@ def binNorm(df):
     return tBin, fBin
 
 
+def normedSin(t, p):
+    return p[0] * np.sin((2 * np.pi / p[1]) * t + p[2]) + 1
+
+
 def fitfunc(p, x):
     return p[0] * np.sin((2 * np.pi / p[1]) * x + p[2]) + 1.0
 
@@ -54,6 +58,7 @@ if __name__ == '__main__':
         df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
     f125A0, f125B0 = normFlux(df125, normDither=True)
     f160A0, f160B0 = normFlux(df160, normDither=True)
+
     # I quit, trying matlab ...
     np.savetxt('F125Result.dat', np.c_[df125['Time'].values, f125A0, f125B0])
     np.savetxt('F160Result.dat', np.c_[df160['Time'].values, f160A0, f160B0])
@@ -62,8 +67,11 @@ if __name__ == '__main__':
     For F125B amp=0.0139   T=10.9765    dphi=0.5874    baseline=1.0001
     """
     plt.close('all')
-    fig = plt.figure(figsize=(8, 4))
-    gs = mpl.gridspec.GridSpec(1, 2)
+    fig = plt.figure(figsize=(12, 9))
+    gs = mpl.gridspec.GridSpec(3, 2)
+    axOut = fig.add_subplot(gs[:, :])
+    axOut.set_xlabel('Time (h)', labelpad=24)
+    axOut.set_ylabel('Normalized flux', labelpad=42)
     ax125B = fig.add_subplot(gs[0, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
     df125_2 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
@@ -81,10 +89,43 @@ if __name__ == '__main__':
                              ms=8, mec='0.8', zorder=0)
 
     ax125B.set_title('F125W light curve')
+    # remove the data from the first orbit
+    df125 = df125[df125['ORBIT'] > 1]
+    f125A0, f125B0 = normFlux(df125, normDither=True)
+    f160A0, f160B0 = normFlux(df160, normDither=True)
+    tBin_125_no1, fBin_125_no1 = binNorm(df125)
[…]

### 2015-08-24 2M1207ANALYSIS/uncertainty.py

@@ -30,8 +30,8 @@ if __name__ == '__main__':
     df160['err0'] = df160['FLUXERRB'] / df160['FLUXB']
     f125A0, f125B0 = normFlux(df125, normDither=True)
     f160A0, f160B0 = normFlux(df160, normDither=True)
-    chisq125 = (((f125B0 - 1.0) / df125['err0'])**2).sum()
-    chisq160 = (((f160B0 - 1.0) / df160['err0'])**2).sum()
+    chisq125 = (((f125B0 - 1.0) / 0.0134)**2).sum()
+    chisq160 = (((f160B0 - 1.0) / 0.0112)**2).sum()
     print(chisq125 / (len(f125B0) - 1))
     print(chisq160 / (len(f160B0) - 1))
     model125 = 0.0139 * np.sin(2 * np.pi / 10.9765 * df125['Time'] + 0.5874)\
@@ -39,9 +39,9 @@ if __name__ == '__main__':
     model160 = 0.0088 * np.sin(2 * np.pi / 9.2692 * df160['Time'] - 0.1180)\
         + 1.0002
     chisq125_1 = (((f125B0 - model125) /
-                   df125['err0'])**2).sum()
+                   0.0134)**2).sum()
     chisq160_1 = (((f160B0 - model160) /
-                   df160['err0'])**2).sum()
+                   0.0112)**2).sum()
     print(chisq125_1 / (len(f125B0) - 3))
     print(chisq160_1 / (len(f160B0) - 3))
     df125['FLUXB'] = f125B0

### 2015-08-25 summary/letter/letter_vAB.tex
including more pixels

@@
 similar phase in both bands. Joint fit to the lightcurve in both bands
-suggest a period of 10.0$\pm$0.9h. The relative amplitudes in the two
+suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative amplitudes in the two
 filters are very similar to that found in a recent study of a field
@@
 light curve shapes would argue against a genuine signal.  We found
-that the periods of the best fit sine waves are very similar,
-$10.45^{+1.2}_{-1.3}$h for F125W and $9.0^{+1.1}_{-1.2}$h for
-F160W. These periods are consistent within the
+that the periods of the best fit sine waves are similar,
+$10.5^{+1.2}_{-1.3}$h for F125W and $9.1^{+1.1}_{-1.0}$h for
+F160W. These periods are roughly consistent within the
 uncertainty. Furthermore, these periods are not close to any
@@
 long period, with core region roughly Gaussian. With probability range
-of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ standard
-deviations for the periods of F125W and F160W to be 1.2 h and 1.5 h. The period for best
+of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ range for
+the periods of F125W and F160W to be  $10.5_{-1.2}^{+1.3}$ and
+$9.1_{-1.0}^{+1.1}$ h, respectively. The period for best
 fitted sine wave of F125W light curve is longer than that of F160W for
-1.4 h that is around 1-$\sigma$ standard deviation. We also
+1.5 h that is slight larger 1-$\sigma$ standard deviation. We also
 performed a joint MC fit with the two light curves with the assumption
 that the periods of the variation of the two bands are the same. We
-derived a period of $10.0\pm0.9$ h.
+derived a period of $10.2^{+0.9}_{-0.8}$ h.
 

### 2015-08-25 2M1207ANALYSIS/calPeriodRange.py

@@ -3,20 +3,38 @@ from __future__ import print_function, division
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+from scipy.interpolate import splev, splrep
+# using spline to fit for the histogram, and find the period
 """calculate the  range of the period fitting result
 """
 
+
+def PeriodRange(pDensity, bins):
+    tck = splrep(bins, pDensity)
+    return tck
+
+
 if __name__ == '__main__':
     pDist125, ampDist125 = np.loadtxt('F125W_Distr.csv', delimiter=',',
-                                      unpack=True)
+                                      unpack=True, usecols=(0, 1))
     pDist160, ampDist160 = np.loadtxt('F160W_Distr.csv', delimiter=',',
-                                      unpack=True)
-    pDist = np.loadtxt('pDistr.csv', unpack=True)
-    pBins = np.linspace(6, 20, 141)
+                                      unpack=True, usecols=(0, 1))
+    pDist = np.loadtxt('fixP_fitResult.csv', delimiter=',',
+                       unpack=True, usecols=(0,))
+    pBins = np.linspace(6, 20, 200)
     midBins = (pBins[:-1] + pBins[1:]) / 2
+    dBin = pBins[1] - pBins[0]
     countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
     countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
     countP, binP = np.histogram(pDist, bins=pBins, normed=1)
+    # fig, ax = plt.subplots()
+    # bars125 = ax.bar(
+    #     midBins, countP125, dBin,
+    #     alpha=0.8, label='F125W', fc='#377eb8')
+    # finerBins = np.linspace(6, 20, 500)
+    # interpFunc = PeriodRange(countP125, midBins)
+    # ax.plot(finerBins, splev(finerBins, interpFunc))
+    # plt.show()
     cumCountP125 = countP125.cumsum() / countP125.sum()
     cumCountP160 = countP160.cumsum() / countP160.sum()
     cumCountP = countP.cumsum() / countP.sum()
@@ -28,7 +46,11 @@ if __name__ == '__main__':
     p125_ceil = midBins[
         cumCountP125 >= cumCountP125[midBins == p125] + 0.32][0]
 
-     == p160] + 0.32][0]
+    p160_floor = midBins[
[…]

### 2015-08-25 2M1207ANALYSIS/plotResultDistr.py

@@ -2,7 +2,7 @@
 from __future__ import print_function, division
 import numpy as np
 import matplotlib.pyplot as plt
-import matplotlib as mpl
+# import matplotlib as mpl
 plt.style.use('paper')
 from scipy.optimize import curve_fit
 """plot the distribution for period and amplitude
@@ -12,6 +12,8 @@ from scipy.optimize import curve_fit
 def gauss(x, a, x0, sigma):
     return a * np.exp(-(x - x0)**2 / (2 * sigma**2))
 
+# def plotPeriodDistr()
+
 if __name__ == '__main__':
     plt.close('all')
     pDist125, ampDist125, phaseDist125 = np.loadtxt(
@@ -19,23 +21,21 @@ if __name__ == '__main__':
     pDist160, ampDist160, phaseDist160 = np.loadtxt(
         'F160W_Distr.csv', delimiter=',', unpack=True)
 
-    # pDist, ampDist125, ampDist160 = np.loadtxt('fixP_fitResult.csv',
-    #                                            delimiter=',', unpack=True)
-    # pBins = np.linspace(6, 20, 57)
-    # fig_p, ax_p = plt.subplots()
+    pBins = np.linspace(6, 20, 57)
+    fig_p, ax_p = plt.subplots()
 
-    # # countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
-    # # countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
+    countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
     # countP, binP = np.histogram(pDist, bins=pBins, normed=1)
-    # ax_p.bar(
-    #     (pBins[:-1] + pBins[1:]) / 2, countP, pBins[1] - pBins[0],
-    #     alpha=0.8, fc='#e41a1c')
-    # # ax_p.bar(
-    # #     binP160[:-1], countP160, pBins[1] - pBins[0],
-    # #     label='F160W', alpha=0.8, fc='#377eb8')
-    # # ax_p.legend()
-    # ax_p.set_xlabel('Period (hour)')
-    # ax_p.set_ylabel('Probability density (hour$^{-1}$)')
+    ax_p.bar(
[…]

### 2015-08-29 summary/letter/letter_vAC.tex
new bugs, never stop

--- 2015-08-25 summary/letter/letter_vAB.tex
@@
 \usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
-\shorttitle{Short Title}
 \shortauthors{Zhou et al.}
@@
 \newcommand{\tinytim}{\textit{Tiny Tim}}
+\newcommand{\bpic}{$\beta$ Pic}
+\newcommand{\vsini}{$v\sin i$}
+\newcommand{\mjup}{M$_{\mbox{Jup}}$}
 \begin{document}
+
 \title{Variability of Planetary Mass Companion 2M1207 B}
@@
  limits its ability in high precision
-photometry\citep{Biretta2014}. However, 6 orbits of observation provides us a chance to
+photometry\citep{Biretta2014}. However, 6 orbits of observation
+provides us an opportunity to
 fully characterize the difference of model and observed PSFs. To obtain
@@
 observed and modeled PSFs at a region centered on 2M1207 A with a
-5-pixel-radius aperture centered 2M1207 b excluded.Then we fit the
+5-pixel-radius aperture centered on 2M1207 b excluded. Then introduce
+another \tinytim{} PSF for 2M1207b and  fit the
 position of 2M1207 b and the photometries of 2M1207 A and b together
@@
 for 2M1207 A and b. In the second round, we combined the correction
-term linearly with the two \tinytim{} PSFs to generate hybrid PSFs, and fitted for their
-amplitudes together. We found that by including the correction term,
+term linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
+and scaled the three component together to get best fit. We found that by including the correction term,
 the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
@@
 normalized to unity as default, the fluxes of 2M1207 A and B were
-solely represented by the amplitude of the two PSFs coordinately.
+solely represented by the amplitude of the two PSFs.
 
@@
   \caption{F125W (left) and F160W (right) light curves under different
-  verification tests. Individual measurements are plotted with gray
+  variability verification tests. Individual measurements are plotted with gray
   crosses. Photometries of the same exposure sequence are binned, and
-  binned data are plotted with points and squares. Fitted sinusoidal
+  binned data are plotted with points or squares. Fitted sinusoidal
   waves are plotted with solid lines. {\em Upper}: binned photometries taken
@@
 \ref{fig:2}).
+
+  \begin{figure*}
+  \centering
+  \plotone{sineCurveFit_binCombined}
+  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
+    with filter F125W (left) and F160W (right). Individual photometric
+  measurement are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoidal waves are plotted
+  with blue solid lines.}
+  \label{fig:3}
+\end{figure*}
 
@@
 
-  \begin{figure*}
-  \centering
-  \plotone{sineCurveFit_binCombined}
-  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Individual photometric
-  measurement are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoidal waves are plotted
-  with blue solid lines.}
-  \label{fig:3}
-\end{figure*}
-
 \subsection{Amplitude and Period Measurements}
@@
 To constrain the uncertainties of the least square optimization
-results, we used a Monte Carlo(MC) method to improve the fitting. We
+results, we used a MC method to improve the fitting. We
 generated a series of random Gaussian noises with the standard deviation same as
 the photon noise, added them to the original light curves, and applied
-least square fit to the new light curves. We repeated above routine for 10000 times and obtained
+least square fit to the new light curves. We repeated above routine for 100,000 times and obtained
 the distribution of the fitting parameters. The distributions for the
@@
 
-\section{Result}
-
 \begin{figure*}
   \centering
-  \plottwo{periodDistr}{amplitudeDistr}
+  \includegraphics[width=0.45\textwidth]{periodDistr}
+  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
   \caption{Distributions for periods (left) and amplitudes(right) for the light
@@
   1. In the right panel, Gaussian profiles are fitted to the
-  histograms and plotted in solid lines.}
+  histograms of periods and plotted in solid lines.}
   \label{fig:4}
 \end{figure*}
+
+\section{Result}
 
@@
 of modulations in directly imaged ultracool objects.  The best fit
-periods for F125W and F160W are 10.4 and 9.0 hour correspondingly. The
-amplitudes for the normalized light curves are 1.4\% and 0.9\% for
+periods for F125W and F160W are 10.5 and 9.1 hour correspondingly. The
+amplitudes for the normalized light curves are 1.45\% and 0.92\% for
 F125W and F160W light curves.
@@
 
-In the following we will discuss the amplitude and period of 2M1207B
-and place this object in the broader context of ultracool atmospheres.
+% In the following we will discuss the amplitude and period of 2M1207B
+% and place this object in the broader context of ultracool atmospheres.
 
 The distributions for the periods demonstrate long tail shaped towards
-long period, with core region roughly Gaussian. With probability range
-of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ range for
-the periods of F125W and F160W to be  $10.5_{-1.2}^{+1.3}$ and
-$9.1_{-1.0}^{+1.1}$ h, respectively. The period for best
-fitted sine wave of F125W light curve is longer than that of F160W for
-1.5 h that is slight larger 1-$\sigma$ standard deviation. We also
-performed a joint MC fit with the two light curves with the assumption
-that the periods of the variation of the two bands are the same. We
-derived a period of $10.2^{+0.9}_{-0.8}$ h.
+long period, with core region roughly Gaussian. With 64\% confidence,
+we estimated the 1-$\sigma$ range for the periods of F125W and F160W
+to be $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ h,
+respectively. The period of best fitted sine wave of F125W light
+curve is 1.5h longer than that of F160W  that is slight larger
+1-$\sigma$ standard deviation. We also jointly fit the two band light
+curve together forcing the periods of two sine waves to be the
+same. We derived a modulation period of $10.2^{+0.9}_{-0.8}$ h in this
+circumstance.
 
-The variation amplitudes in the two bands have significant
-difference. The distributions of the amplitudes are well described by
-Gaussian profiles. Fitting the histogram to a Gaussian function, we
-determined that amplitude distribution of F125W peaks at 1.5\% with a
-standard deviation of 0.3\%, and that of F160W have mean and standard
-deviation of 0.9\% and 0.2\%, respectively. The peaks of the two
+We discovered that  the variation amplitudes in the two bands were significantly
+different. The distributions of the amplitudes are well described by
+Gaussian profiles. By fitting a Gaussian function to the distribution, we
+determined that amplitude distribution of F125W peaks at 1.45\% with a
+standard deviation of 0.22\%, and that of F160W have mean and standard
+deviation of 0.92\% and 0.20\%, respectively. The peaks of the two
 histograms separated by more than 2-$\sigma$. The variation amplitude
-of F125W light curve is 1.67 times of that of F160W light curve.
+of F125W light curve is 1.58 times of that of F160W light curve.
 
@@
 \section{Discussion}
-Amplitude and Relative Amplitudes: Comparison to other brown dwarfs
 
-Rotation Period: Comparison to Brown Dwarfs and Beta Pic
+\begin{figure*}
+  \centering
+  \plottwo{rotationDiagram}{JH}
+  \caption{comparison of 2M1207's rotation period and color change with brown
+    dwarfs, \bpic{} b, and solar system planets. {\em Left}: period vs. mass
+  plot for 2M1207b (red square), solar system planets and \bpic{} b
+  (blue squares), and brown dwarfs (black circles, gray shade). The mass of brown
+  dwarfs are assumed to be 30 \mjup{}. The gray rectangle
+  ranging from 15 \mjup{} to 50 \mjup{} in $x$, and $\pm\sigma$
+  with the center at mean rotation period of brown dwarfs in $y$, indicates a
+region where brown dwarfs most likely to appear in this diagram. {\em Right}: ratio
+of variation amplitude in J and H band vs. spectral type for 2M1207b
+and brown dwarfs. Points are
+color coded with their J$-$H colors. }
+  \label{fig:5}
+\end{figure*}
 
-Method: Opens a new window, successful demonstration, how could it be improved?
-Mapping different pressure levels, atmospheric dynamics?
+A fundamental result of our study is the direct determination of the
+rotation period of a directly imaged planetary-mass object. In
+Figure~\ref{fig:5} we compare the rotation period of 2M1207b to the
+solar system planets, field brown dwarfs that have well defined
+rotation period from the study of
+\citep[][]{Metchev2015}, and \bpic{} b the only other directly imaged
+planet with an estimated period from measured \vsini{}.  The study by
+\citep[][]{Snellen2014} succeeded in mesuring \vsini{} for \bpic{} b
+and demonstrated that it fits a trend defined by Solar System planets
+in which more massive planets have faster rotation rates. The
+interesting finding that \bpic{} b, an exoplanet that formed in a
+protoplanetary disk, follows this trend suggests a possibly connection
+between planet mass, initial angular momentum, and formation in a
+disk.
+
+Excitingly, our measurement of the rotation period of 2M1207b, an
+object with similar mass and age to \bpic{} b, show that their rotation
+periods are very similar, {\em in spite } of the fact that 2M1207b 
+most likely not formed in a circumstellar (or circumsubstellar) disk
+but is a result of gravitational fragmentation. This suggests
+that rotation periods are not good tracers of the formation pathways
+and may not contribute important evidence for a formation in a disk
+vs. in a cloud core environment.
+
+Our observations, furthermore, allow us to compare the relative
+amplitudes in the J- and H-bands between the handful of brown dwarfs
+for which high-quality near-infrared time-resolved observations have
+been obtained. In the right panel of Figure \ref{fig:5}, we plot the
+relative amplitude of J- and H-bands of 2M1207b with brown dwarfs
+\citep{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014} that
+have different spectral types and J$-$H colors.
+
+We found a strong correlation between the spectral type of the object
+and the J to H variation amplitude ratio. Figure \ref{fig:5}
+demonstrates that earlier spectral type objects -- independent of
+their surface gravity -- have larger variations at shorter wavelength
+than at longer wavelengths. Importantly, although the J$-$H color of
+2M1207b is significantly redder the other L5 dwarfs, we note that its
+relative variation amplitude ratio is almost identical to the matching
+spectral type mid-L dwarf 2M1821. This suggests that the upper cloud
+layers, probed through variability, may be more influenced by spectral
+type and less by cloud thickness, which is thought to influence the
+J$-$H color.
+
+{\bf Two questions: What processes sets the relative J vs H amplitude
+  and why is it tied to the pectral type and not to the NIR colors or
+  surface gravity? What does this tell us about the cloud structure
+  as a function of spectral type / gravity (even if speculation)?}
 
 \section{Conclusions}
-\begin{itemize}
-\item a data-reduction pipeline is developed to obtain high precision
-  photometry measurement from high contrast WFC3 IR data. For a
-  contrast of $\sim 7$ magnitudes at an angular separation of
-  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
-  precision of about 2-3\%. 
-\item time variability for 2M1207 B was discovered, the light curve of
-  2M1207 B for both two colors can be fitted with a T=10.7 hr
-  sinusoidal curve.
-\item constrain on the amplitude of the amplitude of the
-  variability. Large amplitude can be excluded. Constraints on the
-  inhomogeniety of the cloud coverage can be inferred -- small
-  thickness variance...
-\item ? The atmosphere and cloud structure of 2M1207 B. How does it
-  compare to the brown dwarf.
-\end{itemize}
+In summary from our J- and H-band high precision,
+high-cadence lightcurves we discovered sinusoidal modulations in the  planetary mass object
+2M1207b. This is the first detection of rotational modulations in a
+directly imaged planetary mass object.  
+The period is  $10.2^{+0.9}_{-0.8}$, very similar to that derived from
+{\em v sin i} measurements for  the direct imaged exoplanet \bpic{} b and significantly longer than
+most field brown dwarfs with known rotation periods. The
+relative modulation amplitude of J and H band is almost identical to
+one matching spectral type L5 dwarf, although they have very different
+J$-$H colors, and it is markedly different form later spectral type
+brown dwarfs.
+
+Finally, we note that the observations presented here open an exciting
+new window on directly imaged exoplanets and planetary-mass
+objects. Our study demonstrates a successful application of high-cadence,
+high-precision, high-contrast photometry with planetary mass
+companion. We also show that these observations can be carried out simultaneously
+at multiple wavelengths, allowing us to prove multiple pressure
+levels. With observation of a larger sample and at multiple wavelengths, we will be
+able to explore  the detailed structures of atmospheres of directly
+imaged exoplanets, and identify the key parameters that determine these.
+% % \begin{itemize}
+% % \item a data-reduction pipeline is developed to obtain high precision
+% %   photometry measurement from high contrast WFC3 IR data. For a
+% %   contrast of $\sim 7$ magnitudes at an angular separation of
+% %   $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
+% %   precision of about 2-3\%. 
+% % \item time variability for 2M1207 B was discovered, the light curve of
+% %   2M1207 B for both two colors can be fitted with a T=10.7 hr
+% %   sinusoidal curve.
+% % \item constrain on the amplitude of the amplitude of the
+% %   variability. Large amplitude can be excluded. Constraints on the
+% %   inhomogeniety of the cloud coverage can be inferred -- small
+% %   thickness variance...
+% % \item ? The atmosphere and cloud structure of 2M1207 B. How does it
+% %   compare to the brown dwarf.
+% \end{itemize}
 

### 2015-08-29 2M1207ANALYSIS/plotJHratio.py

@@ -1,0 +1,36 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import matplotlib.pyplot as plt
+import numpy as np
+plt.style.use('paper')
+"""plot J-H ratio
+"""
+
+if __name__ == '__main__':
+    tgName, specType, specPos, JHratio, JH = np.genfromtxt(
+        'JHratio.dat', delimiter=',', unpack=True, dtype=str
+    )
+
+    specPos = np.float32(specPos)
+    JHratio = np.float32(JHratio)
+    JH = np.float32(JH)
+    JHDeltaMag = -2.5 * np.log10(JHratio)
+    plt.close('all')
+    plt.scatter(specPos, JHratio, s=160, c=JH, cmap='coolwarm')
+    cbar = plt.colorbar()
+    cbar.set_label('J-H (mag)')
+    # plt.plot(specPos, JHDeltaMag, 's')
+    # plt.plot(5, -0.49, 'o', mec='b', mfc='none', ms=10, mew=1.5)
+#    plt.plot(JH, JHDeltaMag, 's')
+    # plt.plot(1.9, -0.55, 'o')
+    # plt.xlabel('J-H')
+
+    plt.xticks([5, 10.5, 12, 16.5], ['L5', 'T0.5', 'T2', 'T6.5'])
+    plt.xlabel('Spectral type')
+    plt.ylabel('Amptude$_{\mathrm{J}}$/Amptude$_{\mathrm{H}}$')
+    for i in range(len(specPos)):
+        plt.text(
+            specPos[i] + 0.1, JHratio[i] + 0.02, tgName[i], fontsize=12)
+    # plt.text(5.2, -0.58, '2M1207b', color='b')
+    plt.show()
+    plt.savefig('JH.pdf')

### 2015-08-29 2M1207ANALYSIS/plotRotation.py

@@ -1,0 +1,65 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import patches
+"""plot the rotation rate vs mass
+"""
+
+if __name__ == '__main__':
+    name, mass, radius, period, label = np.genfromtxt(
+        'rotationRate.dat', delimiter=',', dtype=str, skip_header=1,
+        unpack=True
+    )
+    mass = np.float32(mass)  # in Mjup
+    radius = np.float32(radius)  # in R_jup
+    period = np.float32(period)  # in hours
+    v_equ = 2 * np.pi * (radius * 69911) / (period * 3600)  # in km/s
+    plt.close('all')
+    fig_p, ax_p = plt.subplots()
+    ax_p.set_xscale('log')
+    # ax_p.set_yscale('log')
+
+    ax_p.plot(mass[0], period[0], 's', ms=10)
+    ax_p.plot(mass[1:], period[1:], 's', ms=10)
+    ax_p.errorbar(
+        [0.00017, 0.00256], [25, 25], yerr=2, lolims=True, color='k', ls='')
+    ax_p.set_ylim(0, 30)
+    # ax.arrow(x0, y0, 0, -0.3, fc='b', lw=0.2, head_width=0.05,
+    # head_length=0.1)
+
+    ax_p.set_xlabel('M (M$_{\mathrm{Jup}}$)')
+    ax_p.set_ylabel('Period (hour)')
+    BDperiod = np.array([2.7, 1.55, 2.7, 3.8, 4.1, 3.2, 13,
+                         2.5, 11, 3.9, 2.6, 4.2, 18, 19, 3.5, 1.41])
+    ax_p.plot(np.zeros(len(BDperiod)) + 30, BDperiod,
+              'o', mec='k', mfc='none', ms=10)
+    ax_p.add_patch(patches.Rectangle((15, BDperiod.mean() - BDperiod.std()),
+                                     35, 2 * BDperiod.std(),
+                                     fc='0.8', alpha=0.8))
+
+    for i in range(len(name)):
+        if i == 4:
+            ax_p.text(mass[i] * 1.3, period[i] - 1.5, label[i])
+        elif i == 5:
+            ax_p.text(mass[i] * 1.3, period[i], label[i])
+        elif i == 6:
[…]

### 2015-09-08 summary/letter/letter_vAC.tex
do remember to bring the adapter!!

@@
 \shorttitle{Variability of 2M1207 B}
-\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
-\affil{The University of Arizona}
+\author{Yifan Zhou, Daniel Apai, Glenn Schneider}
+\affil{Steward Observatory, the University of Arizona}
+\author{Mark Marley}
+\affil{NASA Ames Research Center}
 
@@
 read-outs with NSAMP=10, alternating between F160W and F125W filters,
-with 2--3 identical exposures in one exposure sequence. To improve PSF
-sampling and reduce the risk caused by bad pixels, we applied standard
-4 point dithering. Over the 6 orbits, we obtained 70 images with 10
+with 2--3 identical exposures in one exposure sequence. To improve
+sampling and reduce the risk that point spread funciton (PSF) lays on
+bad pixels, we applied a 4-point dither patternwith differential "X/Y"
+offsets of 1.375" in the detector frame, providing optimal
+non-integral (half pixel) stepping of 10.5 and 8.5 pixels in F125W and
+F160W, respectively.. Over the 6 orbits, we obtained 70 images with 10
 non-destructive read-outs in F125W and 64 images in F160W with
@@
   \plottwo{original}{subtracted}
-  \caption{WFC3 F160W images of 2M1207A system. {\em Upper panel}: In the original image 
-    2M1207 B is hidden in the halo of the bright 2M1207A.   {\em Lower panel:} In the residual image -- after the subtraction of the hybrid PSF -- 2M1207 B is detected at a high significant level.}
+  \caption{WFC3 F160W images for 2M1207 system. {\em Upper panel}:
+    original image, the position of 2M1207b is indicated using white
+    circle.   {\em Lower panel:} residual image -- after the
+    subtraction of the hybrid PSF, 2M1207 B is detected at a high significant level.}
   \label{fig:1}
@@
 cosmic rays. From the beginning, pixels with data quality flags ``bad
-detector pixels'' (DQ = 4), ``unstable response'' (DQ = 32), and ``bad
-or uncertain flat value'' (DQ = 512) were masked out and excluded from
+detector pixels'', ``unstable response'', and ``bad
+or uncertain flat value'' were masked out and excluded from
 further analysis as suggested by previous transit exoplanet
@@
 by image interpolation and shifting. On the other hand, \tinytim{} PSF
-simulator\citep{Krist1995} offers a solution by providing Nyquist
-sampled PSF, but significant systematic errors of \tinytim{} PSF
- limits its ability in high precision
-photometry\citep{Biretta2014}. However, 6 orbits of observation
-provides us an opportunity to
-fully characterize the difference of model and observed PSFs. To obtain
-robust \tinytim{} PSF photometry,  we designed a 2-round PSF fitting strategy: 1. calculating
+simulator\citep{Krist1995} offers a solution by providing Nyquist or better
+sampled PSF, but systematic errors of \tinytim{} PSF for WFC3 limits
+its ability in high precision photometry\citep{Biretta2014}. However,
+we are able to fully characterize the difference of model and observed
+PSFs with 6 orbits time-resolved observation data. To obtain robust \tinytim{} PSF
+photometry, we designed a 2-round PSF fitting strategy: 1. calculating
 correction map for \tinytim{}; 2. hybrid PSF photometry.
@@
 For both of 2 rounds, we used {\em Tiny Tim} to calculate 10$\times$
-over-sampled model PSFs based the filters, the spectra 
+over-sampled model PSFs based on the filters, the spectra 
 \citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
 the telescope jitter.  We used the new set of Tiny Tim parameters
-provided by \cite{Biretta2014} to better model the cold mask,
-diffraction spikes, and the coma. The focus parameters were calculated
+provided by \cite{Biretta2014} to improve model of the cold mask,
+OTA spikes, and the coma. The focus parameters were calculated
 using the model listed on the STScI
-website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
-We determined the exact position of 2M1207A first by fitting the PSF
-on a dynamic coordinate grid and minimizing the difference in the
-observed and modeled PSFs at a region centered on 2M1207 A with a
-5-pixel-radius aperture centered on 2M1207 b excluded. Then introduce
+website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. To
+register \tinytim{} PSF to observed PSF of 2M1207A, we moved the
+over-sampled PSF over a coordinate grid (gird size=0.001 pixel) using
+cubic interpolation and minimize the rms difference of the
+observed and re-binned \tinytim{} PSFs over a region centered on 2M1207A with a
+5-pixel-radius aperture centered on 2M1207b excluded. Then we introduce
 another \tinytim{} PSF for 2M1207b and  fit the
-position of 2M1207 b and the photometries of 2M1207 A and b together
+position of 2M1207 b and the photometries of 2M1207 A and b simultaneously
 by least square optimization. From our data set, we discovered that
-the difference of observed PSFs and model PSFs are very stable for
-given PSF position. Therefore at the end of the first round PSF
+the difference of observed PSFs and model PSFs were very stable for
+given PSF positions. Therefore at the end of the first round PSF
 fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
-empirical correction maps for each filter:
+observationally derived correction maps for each filter:
 \begin{equation}
-  \mathrm{Corr = Median(PSF_{model} - PSF_{obs} )}
+  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
 \end{equation}
@@
 term linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
-and scaled the three component together to get best fit. We found that by including the correction term,
+and fitted the three components together. We found that by including the correction term,
 the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
-around unity. Because the total fluxes of the model PSFs were
-normalized to unity as default, the fluxes of 2M1207 A and B were
-solely represented by the amplitude of the two PSFs.
+around unity. Relative photometry is acquired from the scaling
+parameters of the model PSFs.
 
-However, PSF profiles change with different exposure positions due to
+PSF profiles change with exposure positions due to
 pixelation, especially for the case that WFC3 IR is significantly
 under-sampled. Also, the flat fields may potentially have large scale
-structures \citep{dressel2012wide}. Because of these factors, the
-fluxes for both 2M1207 A and B are correlated with the dithering
-position. To break the correlation, we normalize each group of
+structures \citep{dressel2012wide}. We found a correlation of
+photometry with PSF positions on detector frame for both 2M1207 A and
+b. Correction were made by normalizing each group of
 exposures that have the same dithering position and roll angle
 individually -- we took the median of the fluxes that were measured
-from these exposures as normalization factors and devided them from
+from these exposures as normalization factors and divided them from
 every photometric measurement. Because the normalization factor for
@@
 
-% %\section{Uncertainty analysis}
-
-\subsection{Uncertainty Analysis: White noise}
-We consider the primary source of uncertainty for every measurement is
-photon noise. We propagated the photon noises of every single pixel
-that were calculated from count rates and detector gain, to the PSF
-fitting results. The photon noises for photometry in F125W and F160W
-are 1.33\% and 1.02\%, respectively.
-
-Since the primary and secondary PSFs were fitted simultaneously in our
-PSF photometry procedure, the uncertainties of photometry and position
-for the primary and secondary are coupled with each other. The second
-order uncertainty could also contribute to the overall uncertainty,
-e.g. the imperfection of position measurement of 2M1207A can affect
-the photometry of 2M1207b. We used a Monte Carlo (MC) method to evaluate the complete systematic of the
-PSF fitting. We applied the PSF photometry to images that
-were added with random Poisson noise and repeat the procedure for 1000
-time. From the distribution of the result, the uncertainty for F125W
-and F160W photometry are found to be 1.34\% and 1.12\%,
-respectively. We conclude that the white noise of our observation is
-dominated by photon noise.
-
-\subsection{Uncertainty Analysis: Flat field uncertainties}
-
  \begin{figure*}
@@
   crosses. Photometries of the same exposure sequence are binned, and
-  binned data are plotted with points or squares. Fitted sinusoidal
-  waves are plotted with solid lines. {\em Upper}: binned photometries taken
+  binned photometry are  plotted with points or squares. Best fitted sinusoidal
+  curves are plotted with solid lines. {\em Upper}: binned photometries taken
 in dithering position 1 and 3 (red points) and that taken in 2 and 4
-(blue squares) are plotted differently. They demonstrate same trend of
-variation. In upper left panel, sinusoidal wave fitted with all
-parameter set free, and that fitted with period set the same as that
-of F125W are plotted with green and purple lines, respectively. {\em
+(blue squares) are plotted with different symbols. They demonstrate same trend of
+variation. In upper left panel, green line is sinusoidal wave fitted with all
+parameter set free, and purple line is sinusoidal wave fitted with period set the same as that
+of F125W. {\em
   Middle}: sinusoidal waves fitted without using the data taken in
-Orbit 1 are plotted. These curves are almost identical to the curves
+Orbit \#1. These curves are almost identical to the curves
 plotted in upper panel. {\em Lower}: photometry measured with
-AFEM-applied images and their best fitted sinusoidal curves are
-plotted. These photometries and curves are also almost identical to
-those plotted in upper panel.}
+AFEM-added images and best fitted sinusoidal curves. These photometries and curves are also almost identical to
+those plotted in the upper panel.}
   \label{fig:2}
@@
 
-In our observations 2M1207 B were observed at 8 different spots on the
+\subsection{Uncertainty Analysis: White noise}
+First we estimated the photon noises for the photometry of 2M1207b. We
+propagated the photon noises of every single pixel that were
+calculated from count rates and detector gain, to the PSF fitting
+results. The photon noises for photometry in F125W and F160W are
+1.33\% and 1.02\%, respectively.
+
+Since the PSFs for the 2M1207 A and b were fitted simultaneously in our
+PSF photometry procedure, the uncertainties of photometry and position
+for the primary and secondary are coupled. Imperfection of position
+measurement of 2M1207A could potentially affect the photometry of
+2M1207b. We used a Monte Carlo (MC) method to
+evaluate the overall systematic of the PSF fitting. We applied the
+PSF photometry to images that were added with random Poisson noises and
+repeat the photometry procedure for 1000 times. From the distribution of the
+result, the uncertainty for F125W and F160W photometry are 
+1.34\% and 1.12\%, respectively. We conclude that the white noise of
+our observation is dominated by photon noise.
+
+\subsection{Uncertainty Analysis: Flat field uncertainties}
+
+2M1207b were observed at 8 different spots on the
 detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
@@
 introduce position-dependent differences in the count rates. The
-uncertainty of WFC3 IR pipeline flat field is $\sim 1\%$
+uncertainty of WFC3 IR pipeline flat field is typically $\sim 1\%$
 \citep{dressel2012wide}.

### 2015-09-08 2M1207ANALYSIS/calJHMagRatio/calJHMag.py

@@ -1,0 +1,75 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+from scipy.io import readsav
+from squareMean import squareMean
+"""comment
+"""
+
+
+def JHratio1(jlc, hlc, jerr, herr):
+    jarg = np.argsort(jlc)
+    harg = np.argsort(hlc)
+    jlc = jlc[jarg]
+    jerr = jerr[jarg]  # relative uncertainty
+    hlc = hlc[harg]
+    herr = herr[harg]  # relative uncertainty
+    Jmin = jlc[0:5].mean()  # mean value of maximum 5
+    Jmin_err = (jerr[0:5]**2).mean()**0.5
+    Jmax = jlc[-5:].mean()  # mean value of maximum 5
+    Jmax_err = (jerr[-5:]**2).mean()**0.5
+
+    Hmin = hlc[0:5].mean()  # mean value of maximum 5
+    Hmin_err = herr[0:5].mean()
+    Hmax = hlc[-5:].mean()  # mean value of maximum 5
+    Hmax_err = herr[-5:].mean()
+
+    JHratio = ((Jmax - Jmin) / jlc.mean()) / ((Hmax - Hmin) / hlc.mean())
+    Jerr = np.sqrt(Jmax_err**2 + Jmin_err**2) / (Jmax - Jmin)
+    Herr = np.sqrt(Hmax_err**2 + Hmin_err**2) / (Hmax - Hmin)
+    JHratio_err = np.sqrt(Jerr**2 + Herr**2)
+
+    return JHratio, JHratio_err
+
+
+if __name__ == '__main__':
+    M2139 = readsav('2MASSJ2139_spec_bin.sav')
+    jh2139 = JHratio1(M2139['jlc'], M2139['hlc'],
+                      M2139['jlcerr'], M2139['hlcerr'])
+    S0136 = readsav('SIMP0136_spec_bin.sav')
+    jh0136 = JHratio1(S0136['jlc'], S0136['hlc'],
+                      S0136['jlcerr'], S0136['hlcerr'])
+
+    M1821 = readsav('2m1821spectralratio.sav')
+    min1821spec = M1821.minspec5est[M1821.xxx]
+    max1821spec = M1821.maxspec5est[M1821.xxx]
+    wl1821 = M1821.westher[M1821.xxx]
+    snr1821 = M1821.snr1821
[…]

### 2015-09-08 2M1207ANALYSIS/plotJHratio.py

@@ -3,11 +3,17 @@ from __future__ import print_function, division
 import matplotlib.pyplot as plt
 import numpy as np
 plt.style.use('paper')
+from linearFit import linearFit
 """plot J-H ratio
 """
 
+
+def chisq(y, mody, sigma):
+    return np.sum((y - mody)**2 / sigma**2)
+
+
 if __name__ == '__main__':
-    tgName, specType, specPos, JHratio, JH = np.genfromtxt(
+    tgName, specType, specPos, JHratio, JH, ampJ, ampH, err = np.genfromtxt(
         'JHratio.dat', delimiter=',', unpack=True, dtype=str
     )
 
@@ -15,22 +21,49 @@ if __name__ == '__main__':
     JHratio = np.float32(JHratio)
     JH = np.float32(JH)
     JHDeltaMag = -2.5 * np.log10(JHratio)
+    ampJ = np.float32(ampJ)
+    ampH = np.float32(ampH)
+    err = np.float32(err)
     plt.close('all')
-    plt.scatter(specPos, JHratio, s=160, c=JH, cmap='coolwarm')
-    cbar = plt.colorbar()
+    fig, ax = plt.subplots()
+    cax = ax.scatter(
+        specPos, JHratio, s=np.sqrt(ampJ) * 500, c=JH, cmap='coolwarm')
+    cbar = fig.colorbar(cax)
+    ax.errorbar(specPos, JHratio, yerr=JHratio * err, color='k', ls='')
     cbar.set_label('J-H (mag)')
-    # plt.plot(specPos, JHDeltaMag, 's')
-    # plt.plot(5, -0.49, 'o', mec='b', mfc='none', ms=10, mew=1.5)
-#    plt.plot(JH, JHDeltaMag, 's')
-    # plt.plot(1.9, -0.55, 'o')
-    # plt.xlabel('J-H')
+#     plt.plot(specPos, JHDeltaMag, 's')
+#     plt.plot(5, -0.49, 'o', mec='b', mfc='none', ms=10, mew=1.5)
+# #    plt.plot(JH, JHDeltaMag, 's')
+#     plt.plot(1.9, -0.55, 'o')
+#     plt.xlabel('J-H')
 
-    plt.xticks([5, 10.5, 12, 16.5], ['L5', 'T0.5', 'T2', 'T6.5'])
-    plt.xlabel('Spectral type')
[…]

### 2015-09-08 2M1207ANALYSIS/plotLightCurve.py

@@ -108,8 +108,8 @@ def plotLightCurve(DataFrame125, DataFrame160, applyCorr=False):
 
 
 if __name__ == '__main__':
-    fn125 = '2015_Aug_13TinyTimF125Result.csv'
-    fn160 = '2015_Aug_13TinyTimF160Result.csv'
+    fn125 = '2015_Aug_28TinyTimF125Result.csv'
+    fn160 = '2015_Aug_28TinyTimF160Result.csv'
     applyCorr = False
     plt.close('all')
     df125 = pd.read_csv(

### 2015-09-08 python_src/squareMean.py

@@ -1,0 +1,9 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+"""sqaure Mean
+"""
+
+
+def squareMean(a):
+    return np.sqrt((np.array(a)**2).mean())

### 2015-09-15 summary/letter/letter_vAD.tex
its been a long time since last commitment

--- 2015-09-08 summary/letter/letter_vAC.tex
@@
 
-\title{Variability of Planetary Mass Companion 2M1207 B}
+\title{Discovery of Rotational Modulations in the Planetary-mass
+  Companion 2M1207b: A Slow Rotation Period and Cloud Height in a Low
+  Gravity Atmosphere}
 \shorttitle{Variability of 2M1207 B}
@@
 
-\begin{abstract} Rotational modulations in disk-integrated light of
-brown dwarfs have recently provided powerful constraints on the
-properties of ultracool atmospheres, including longitudinal and
-vertical cloud structures and cloud evolution. Furthermore, detection
-of periodic light curve variations can directly probe the rotational
-periods of ultracool objects.
+\begin{abstract}
+  Rotational modulations of brown dwarfs have recently provided
+  powerful constraints on the properties of ultra-cool atmospheres,
+  including longitudinal and vertical cloud structures and cloud
+  evolution. Furthermore, detection of periodic light curve variations
+  can directly probe the rotational periods of ultra-cool objects.
 
   We present here, for the first time, time-resolved high-precision
-photometric measurements of a planetary-mass companion, 2MASS1207b, to
-a brown dwarf primary. Using HST/WFC3 and point spread function %in
+  photometric measurements of a planetary-mass companion, 2MASS1207b,
+  to a brown dwarf primary. Using HST/WFC3 and point spread
+  function %in
   combination with two spacecraft roll angles we detect photometric
@@
   and 1.5\% in the F125W filters; we find a consistent period and
-similar phase in both bands. Joint fit to the lightcurve in both bands
-suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative amplitudes in the two
-filters are very similar to that found in a recent study of a field
-(high-gravity) L-dwarf, suggesting that the cloud structures that
-introduce the photometric modulations are similar in high- and
-low-gravity objects. Importantly, our study also measures, for the
-first time, the rotational period for directly imaged planetary-mass
-companion.
+  similar phase in both bands. Joint fit to the light curve in both
+  bands suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative
+  amplitudes in the two filters are very similar to that found in a
+  recent study of a field (high-gravity) L-dwarf, suggesting that the
+  cloud structures that introduce the photometric modulations are
+  similar in high- and low-gravity objects. Importantly, our study
+  also measures, for the first time, the rotational period for
+  directly imaged planetary-mass companion.
 \end{abstract}
@@
 
-Cloud properties in high- and low-gravity objects -- thick clouds: an
-explanation for very red and faint near-infrared fluxes of directly
-imaged planets
+% Cloud properties in high- and low-gravity objects -- thick clouds: an
+% explanation for very red and faint near-infrared fluxes of directly
+% imaged planets
+Presence of condensate clouds is one the most unique and essential
+features of the ultra-cool atmosphere of direct imaged exoplanet and brown
+dwarfs. The formation and properties of condensate clouds of are
+intensively studied in recent years \citep[e.g.][]{Ackerman2001,
+  Helling2008, Allard2012}, and great improvement has been
+achieved in understanding the cloud behavior across different spectral
+types, especially in the explanation of L-T transition \citep{Marley2010}.
+Surface gravity is suggested to be another key parameters 
+in defining cloud structures. Low surface gravity objects (e.g. HR8799 bcd, 2M1207
+b) have significantly redder color compared to their spectral type
+matched brown dwarfs, which are best explained by the existence of 
+thick clouds \citep{Barman2011, Skemer2011, Skemer2012}. However, due to lack of observational constraint, the
+behavior of clouds in the atmospheres of low surface gravity objects
+are not as well as modeled as high surface gravity counterpart.
 
-Rotational mapping is powerful: successes in brown dwarfs...
+Intensity modulations introduced by heterogeneous clouds can be
+directly observed and studied via time resolved observation and
+rotational mapping. These techniques isolate the effect of cloud
+properties and obtained great success in determining the rotation
+period and unveiling the structures of the atmosphere of brown dwarfs
+\citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014,Metchev2015}. \cite{Kostov2013}
+demonstrated the great potential of these techniques in the study of the cloud properties of
+direct imaged exoplanets and planetary mass companions. However, high
+brightness contrast makes it much more challenging for direct
+imaged exoplanet and planetary mass companions than brown
+dwarfs to acquire high-precision light curves.
 
-The target 2M1207b... contrast The key challenge of obtaining the
-lightcurve of 2M1207b is the high contrast to and small separation
-from 2M1207A.
+2M1207 b \citep{Chauvin2005} is a planetary mass companion that has mass of
+$\sim 4M_{\mathrm{Jup}}$ and an angular separation of $0.78''$ to its host
+2M1207 A,
+an M8 brown dwarf. Relative moderate contrast (6.7 mag in J band, \cite{Mohanty2007}) makes it one
+the most feasible planetary mass companions for high-precision
+time-resolved observation and the best starting points for developing
+strategies for time-resolved observation and data reduction in high
+contrast case.
 
-In this Letter we present the first high-contrast, high-precision,
-time-resolved observations of a directly imaged planet or
+In this {\em Letter} we present the first, high-cadence, high-precision,
+time-resolved {\em Hubble Space Telescope} (HST) photometric time
+series of 2M1207 b, a directly imaged planet or
 planetary-mass object. We successfully detect rotational modulation
@@
 
-\section{Observation} We obtained direct images of the 2M1207A+b
-system on UT 2014 April 11from 08:07:47 to 16:53:18 using the Hubble
-Space Telescope (HST) and its Wide Field Camera 3 \citep[WFC3,
+\section{Observation}
+
+\begin{figure*}
+  \centering
+  \plottwo{original}{subtracted}
+  \caption{WFC3 F160W images for 2M1207 system. {\em Upper panel}:
+    original image, the position of 2M1207b is indicated using white
+    circle.   {\em Lower panel:} residual image -- after the
+    subtraction of the hybrid PSF, 2M1207 B is detected at a high significant level.}
+  \label{fig:1}
+\end{figure*}
+
+We obtained direct images of the 2M1207A+b
+system on UT 2014 April 11from 08:07:47 to 16:53:18 using HST and its Wide Field Camera 3 \citep[WFC3,
 ][]{Kimble2008} in the frame of the HST Proposal GO-13418 (PI:
@@
 data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
-40 minutes. The observations were interrupted by 58 minute-long Earth
+40 minutes. The observations were interrupted by 58 minutes long Earth
 occultations every 94 minutes.
@@
 sampling and reduce the risk that point spread funciton (PSF) lays on
-bad pixels, we applied a 4-point dither patternwith differential "X/Y"
+bad pixels, we applied a 4-point dither pattern with differential "X/Y"
 offsets of 1.375" in the detector frame, providing optimal
 non-integral (half pixel) stepping of 10.5 and 8.5 pixels in F125W and
-F160W, respectively.. Over the 6 orbits, we obtained 70 images with 10
+F160W, respectively. Over the 6 orbits, we obtained 70 images with 10
 non-destructive read-outs in F125W and 64 images in F160W with
@@
 %matter what interpolation method is used.
-
  \begin{figure*}
   \centering
-  \plottwo{original}{subtracted}
-  \caption{WFC3 F160W images for 2M1207 system. {\em Upper panel}:
-    original image, the position of 2M1207b is indicated using white
-    circle.   {\em Lower panel:} residual image -- after the
-    subtraction of the hybrid PSF, 2M1207 B is detected at a high significant level.}
-  \label{fig:1}
+  \plotone{systematics}
+  \caption{F125W (left) and F160W (right) light curves under different
+    variability verification tests. Individual measurements are
+    plotted with gray crosses. Photometric measurements of the same exposure
+    sequence are binned, and binned photometry are plotted with points
+    or squares. Best fitted sinusoidal curves are plotted with solid
+    lines. {\em Upper}: binned measurements taken in dithering
+    position 1 and 3 (red points) and that taken in 2 and 4 (blue
+    squares) are plotted with different symbols. They demonstrate same
+    trend of variation. In upper left panel, green line is sinusoidal
+    wave fitted with all parameter set free, and purple line is
+    sinusoidal wave fitted with period set the same as that of
+    F125W. {\em Middle}: sinusoidal waves fitted without using the
+    data taken in Orbit \#1. These curves are almost identical to the
+    curves plotted in upper panel. {\em Lower}: photometry measured
+    with AFEM-added images and best fitted sinusoidal curves. These
+    points and curves are also almost identical to those plotted
+    in the upper panel.}
+  \label{fig:2}
 \end{figure*}
@@
 the difference of observed PSFs and model PSFs were very stable for
-given PSF positions. Therefore at the end of the first round PSF
+given PSF positions. Therefore, at the end of the first round PSF
 fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
@@
 each group of exposures is calculated across the whole observation,
-this normalization step have negligible impacts on variability
+this normalization step has negligible impacts on variability
 analysis.
-
-% {\em Hybrid PSF Calculation:} The hybrid PSFs were generated as a
-% linear combination of a diffraction-limited PSF (calculated with the
-% {\em Tiny Tim} simulator\citep{Krist1995}, and a empirically
-% determined correction map. We used {\em Tiny Tim} to calculate model
-% PSFs for the filters used, the spectrum of our target, the telescope's
-% actual focus, and the telescope jitter.  We used the new set of Tiny
-% Tim parameters provided by \cite{Biretta2014} to better model the cold
-% mask, diffraction spikes, and the coma. The focus parameters were
-% calculated using the model listed on the STScI
-% website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
-% A significant advantage of Tiny Tim PSF over empirical PSFs is that
-% Tiny Tim can produce Nyquist-sampled results, which allows accurate
-% image shifting and interpolation. However, an important limitation of
-% Tiny Tim is that the model PSFs have significant systematic
-% errors. \cite{Biretta2014} demonstrated that the diffraction spikes
-% and coma are not accurately simulated with Tiny Tim for WFC3/IR
-% images. However, using the 6-orbit long time series, we are able to
-% accurately characterize the difference of the modeled and observed
-% PSFs and derive an empirical correction map: Corr = Mean (
-% PSF\_modeled - PSF\_observed ) where PSF\_modeled is a combination of
-% two Tiny Tim PSFs with positions and amplitudes optimized to minimize
-% the residuals.  By combining the model PSFs with the empirical
-% correction map we derived a high-quality hybrid PSF, the use of which
-% significantly improved the PSF subtraction and photometry.
-
-% {\em PSF Fitting:} In the next step we simultaneously fitted the positions and amplitudes of the combination of the hybrid PSFs to 2M1207A and 2M1207b.
-First, we determined the primary star position and telescope jitter.
-We produced a list of 10$\times$ over-sampled PSFs matching the spectrum \citep{Bonnefoy2014} and the position of 2M1207A with different telescope jitters ranging from 0 to 50$\mbox{mini-arcsec s}^{-1}$ along
-% both $x$ and $y$ detector axes.
-The PSFs were registered with the original image by searching on a dynamic grid and minimizing the difference in the observed and modeled PSFs at a region centered on 2M1207 A with a 5-pixel-radius aperture centered 2M1207 B excluded.
-
-% Next, we determined the position and approximate flux of 2M1207B by calculating and fitting a Tiny Tim PSF for the hybrid PSF-subtracted 2M1207 B based on its position on the detector, spectrum \citep{Patience2010}, and
-% the telescope jitter that had been obtained above. In the final step,
-% we combined the two PSFs together.
-
-% We fixed the position of the primary as it had been fitted in the first step and fitted for the
-% amplitudes of the two PSFs and the precise position of the
-% secondary. Since the total fluxes of the model PSFs were normalized to
-% unity as default, the fluxes of 2M1207 A and B were solely represented
-% by the amplitude of the two PSFs coordinately.
-
-% Because of the systematic errors of the Tiny Tim PSF, the quality of the
-% fit is not perfect. The reduced $\chi^{2}$ values were at level
-% of $\sim10$. However, we found that the residual patterns were very
-% stable among the image that have the same dithering position and
-% telescope rolling. Therefore, we median combined the residual images
-% that have the same dithering position and telescope rolling angle to
-% construct 8 residual models (4 dithering position $\times$ 2 telescope
-% rolling angle) for each filter. We pre-subtract the corresponding
-% residual from the original image and repeated the procedure that
-% listed above. Using this extra-step, the reduced $\chi^{2}$
-% greatly decreased to around unity.
 
@@
   \centering
-  \plotone{systematics}
-  \caption{F125W (left) and F160W (right) light curves under different
-  variability verification tests. Individual measurements are plotted with gray
-  crosses. Photometries of the same exposure sequence are binned, and
-  binned photometry are  plotted with points or squares. Best fitted sinusoidal
-  curves are plotted with solid lines. {\em Upper}: binned photometries taken
-in dithering position 1 and 3 (red points) and that taken in 2 and 4
-(blue squares) are plotted with different symbols. They demonstrate same trend of
-variation. In upper left panel, green line is sinusoidal wave fitted with all
-parameter set free, and purple line is sinusoidal wave fitted with period set the same as that
-of F125W. {\em
-  Middle}: sinusoidal waves fitted without using the data taken in
-Orbit \#1. These curves are almost identical to the curves
-plotted in upper panel. {\em Lower}: photometry measured with
-AFEM-added images and best fitted sinusoidal curves. These photometries and curves are also almost identical to
-those plotted in the upper panel.}
-  \label{fig:2}
+  \plotone{sineCurveFit_binCombined}
+  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
+    with filter F125W (left) and F160W (right). Individual photometric
+  measurement are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoidal waves are plotted
+  with blue solid lines.}
+  \label{fig:3}
 \end{figure*}
@@
 \subsection{Uncertainty Analysis: White noise}
+
 First we estimated the photon noises for the photometry of 2M1207b. We
@@
 
-Since the PSFs for the 2M1207 A and b were fitted simultaneously in our
+Since the PSFs for the 2M1207 A and b were fitted simultaneously in the
 PSF photometry procedure, the uncertainties of photometry and position
@@
 \citep{dressel2012wide}.
-% and our time resolved observations for another target
-%demonstrate that aperture photometry for exposures taken at different
-%dithering position are uncertain at the same level.
-%Flat field uncertainties have smaller effects on 
+
 In PSF photometry, however, multiple pixels are fitted simultaneously
 and we expect a lower than 1\% uncertainty from the flat field
-errors. To verify this we multiplied every image by an artificial flat
+errors. To verify this, we multiplied every image by an artificial flat
 field error mask (AFEM) -- a uniformly distributed Gaussian noise array with
@@
 resulting images.  The analysis of these experiments showed almost
-identical lightcurve to the original, verifying that the flat field
+identical light curve to the original, verifying that the flat field
 errors do not affect our photometry significantly (Figure
@@
 
+\section{Verification of Photometric Variations and Amplitude
+  Estimate}
+
 \begin{figure*}
   \centering
-  \plotone{sineCurveFit_binCombined}
-  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Individual photometric
-  measurement are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoidal waves are plotted
-  with blue solid lines.}
-  \label{fig:3}
+  \includegraphics[width=0.45\textwidth]{periodDistr}
+  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
+  \caption{Distributions for periods (left) and amplitudes(right) for the light
+    curve of F125W and F160W. The bin size for histograms of period is
+  0.25 hour and for that of amplitude is 0.5\%. Histograms are
+  normalized in the way that total area of the histogram equals to
+  1. In the right panel, Gaussian profiles are fitted to the
+  histograms of periods and plotted in solid lines.}
+  \label{fig:4}
 \end{figure*}
-
-\section{Verification of Photometric Variations and Amplitude
-  Estimate}
 
@@
  the subsequent ones.
- %The exposure levels at the pixels of the peak of the PSF of 2M1207 B are less than 10,000 e$^{-}$
- %for both two colors, thus image persistence is less of an issue for
- %2M1207 B. 
  Our analysis based on orbits 2--6 only found essentially identical
@@
 
- % \begin{itemize}
-% \item the source of the scattering -- 
-% \item flat field uncertainty -- adding artificial flat field error mask
-% \item validity of the variability\\
-%   -- both filter demonstrate similar period of variability\\
-%   -- split the data into two half, the trend in two halves of data
-%   looks similar.
-%   -- fix the position does not change the light curve
-% \item uncertainty of sinusoidal curve fit
-%   -- carry out a mcmc fit? is it worth doing this.
-% \end{itemize}
-
 \subsection{Amplitude and Period Measurements}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{periodDistr}
-  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
-  \caption{Distributions for periods (left) and amplitudes(right) for the light
-    curve of F125W and F160W. The bin size for histograms of period is
-  0.25 hour and for that of amplitude is 0.5\%. Histograms are
-  normalized in the way that total area of the histogram equals to
-  1. In the right panel, Gaussian profiles are fitted to the
-  histograms of periods and plotted in solid lines.}
-  \label{fig:4}
-\end{figure*}
-
 \section{Result}
@@
 \label{Results}
-We present the first high-contrast, high-resolution, high-cadence, and
+We present the first  high-resolution, high-cadence, and
 high-precision photometry of a directly imaged planet or
 planetary-mass companion. Our observations reveal a modulation in the
-light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection
-of modulations in directly imaged ultracool objects.  The best fit
+light curve of the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
+of modulations in directly imaged planetary mass objects.  The best fit
 periods for F125W and F160W are 10.5 and 9.1 hour correspondingly. The
@@
 
-% In the following we will discuss the amplitude and period of 2M1207B
-% and place this object in the broader context of ultracool atmospheres.
-
 The distributions for the periods demonstrate long tail shaped towards
@@
 respectively. The period of best fitted sine wave of F125W light
-curve is 1.5h longer than that of F160W  that is slight larger
+curve is 1.5h longer than that of F160W, and 0.3--0.4 h larger
 1-$\sigma$ standard deviation. We also jointly fit the two band light
-curve together forcing the periods of two sine waves to be the
-same. We derived a modulation period of $10.2^{+0.9}_{-0.8}$ h in this
-circumstance.
+curves together forcing the periods of two sinusoids to be the
+same. We derived a modulation period of $10.2^{+0.9}_{-0.8}$ h.
 
-We discovered that  the variation amplitudes in the two bands were significantly
-different. The distributions of the amplitudes are well described by
-Gaussian profiles. By fitting a Gaussian function to the distribution, we
-determined that amplitude distribution of F125W peaks at 1.45\% with a
-standard deviation of 0.22\%, and that of F160W have mean and standard
-deviation of 0.92\% and 0.20\%, respectively. The peaks of the two
-histograms separated by more than 2-$\sigma$. The variation amplitude
-of F125W light curve is 1.58 times of that of F160W light curve.
-
-%Although the photometric time series demonstrate relatively large
-%scattering, both F125W and F160W light curves demonstrate sinusoidal
-%shape with clear temporal variability. We fitted sine waves to the two
-%light curves using least square optimization, and determined the
-%periods and variation amplitudes.
+We discover that the variation amplitudes in the two bands are significantly
+different. By fitting Gaussians to the MC fit result distributions, we
+determined that variation amplitude of F125W is 1.45\% with a
+standard deviation of 0.22\%, and that of F160W is 0.92\% with a
+standard deviation of 0.20\%. The peaks of the two
+histograms separate by more than 2-$\sigma$. The variation amplitude
+for F125W is 1.58 times of that of F160W light curve.
 
@@
   (blue squares), and brown dwarfs (black circles, gray shade). The mass of brown
-  dwarfs are assumed to be 30 \mjup{}. The gray rectangle
-  ranging from 15 \mjup{} to 50 \mjup{} in $x$, and $\pm\sigma$
-  with the center at mean rotation period of brown dwarfs in $y$, indicates a
-region where brown dwarfs most likely to appear in this diagram. {\em Right}: ratio
+  dwarfs are assumed to be 30 \mjup{}. The gray rectangle that has
+a  $\pm$15 \mjup range in $x$, and a $\pm \sigma$ of brown dwarf
+periods range in $y$, indicates a
+region where brown dwarfs most likely to appear in this
+diagram. Rotation period monotonically decreases with the increase of
+mass. {\em Right}: ratio
 of variation amplitude in J and H band vs. spectral type for 2M1207b
-and brown dwarfs. Points are
-color coded with their J$-$H colors. }
-  \label{fig:5}
+and brown dwarfs. The colors of the points represent J$-$H magnitude,
+and the sizes of the points are proportional to the J band variation
+amplitudes. The gray dashed line is the result of a linear fit to
+these points. Tight linear correlation of J- and H-band variation ratio
+and spectral type is demonstrated in this diagram.}
+x \label{fig:5}
 \end{figure*}
 
+% A fundamental result of our study is the direct determination of the
+% rotation period of a directly imaged planetary-mass object. We
+% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
+% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
+% brown dwarfs with well defined rotation period from the study of
+% \cite{Metchev2015}, and compare their rotation velocities with solar
+% system planets and \bpic{} b in the left
+% panel of Figure \ref{fig:5}.  The study by
+% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
+% and demonstrated that it fits a trend defined by Solar System planets
+% in which more massive planets have faster rotation rates. They suggested
+% that this relation is linked to the accretion processes during planet
+% formation.
+
 A fundamental result of our study is the direct determination of the
-rotation period of a directly imaged planetary-mass object. In
-Figure~\ref{fig:5} we compare the rotation period of 2M1207b to the
-solar system planets, field brown dwarfs that have well defined
-rotation period from the study of
-\citep[][]{Metchev2015}, and \bpic{} b the only other directly imaged
-planet with an estimated period from measured \vsini{}.  The study by
-\citep[][]{Snellen2014} succeeded in mesuring \vsini{} for \bpic{} b
-and demonstrated that it fits a trend defined by Solar System planets
-in which more massive planets have faster rotation rates. The
-interesting finding that \bpic{} b, an exoplanet that formed in a
-protoplanetary disk, follows this trend suggests a possibly connection
-between planet mass, initial angular momentum, and formation in a
-disk.
+rotation period of a directly imaged planetary mass object. In the
+left panel of Figure~\ref{fig:5} we compare the rotation period of
+2M1207b to the solar system planets, \bpic b the only other directly
+imaged planet with an estimated period and measured {\em v sin i}, and
+field brown dwarfs from the study of \citep[][]{Metchev2015}.  The
+study by \citep[][]{Snellen2014} succeeded in measuring {\em v sin i}
+for \bpic b and demonstrated that it fits a trend defined by Solar
+System planets in which more massive planets have faster rotation
+rates. The interesting finding that \bpic b, an exoplanet that formed
+in a protoplanetary disk, follows this trend suggests a possibly
+connection between planet mass, initial angular momentum, and
+formation in a disk.
 
-Excitingly, our measurement of the rotation period of 2M1207b, an
-object with similar mass and age to \bpic{} b, show that their rotation
-periods are very similar, {\em in spite } of the fact that 2M1207b 
-most likely not formed in a circumstellar (or circumsubstellar) disk
-but is a result of gravitational fragmentation. This suggests
-that rotation periods are not good tracers of the formation pathways
-and may not contribute important evidence for a formation in a disk
-vs. in a cloud core environment.
+Excitingly, our measurement of the rotation period of 2M1207b, a
+planet mass companion that has similar age to \bpic b, has a rotation
+period that fits in the same trend, as well as majority of brown
+dwarfs.  We note that 2M1207 b is most likely formed in the same way as
+brown dwarfs by gravitational fragmentation. The result that objects
+formed in different scenarios share the same trend of period vs. mass suggests that
+rotation periods -- in absence of well-determined ages -- are not good tracers of the formation pathways and
+may not contribute important evidence for a formation in a disk vs. in
+a cloud core environment.
+{\em Add younger BDs and this may change}
+% Excitingly, our measurement of the rotation period demonstrates that
+% 2M1207b, a planetary mass companion  with similar age to \bpic{} b, has a rotation velocity
+% that fits in the same trend, as well as majority of brown
+% dwarfs. We note that 2M1207b is most likely formed in the same way as brown
+% dwarfs by gravitational fragmentation, which suggests
+% that rotation periods are not good tracers of the formation pathways
+% and may not contribute important evidence for a formation in a disk
+% vs. in a cloud core environment.
 
-Our observations, furthermore, allow us to compare the relative
-amplitudes in the J- and H-bands between the handful of brown dwarfs
+Furthermore, our observations allow us to compare the relative
+amplitudes in the J- and H-bands with the handful of brown dwarfs
 for which high-quality near-infrared time-resolved observations have
-been obtained. In the right panel of Figure \ref{fig:5}, we plot the
-relative amplitude of J- and H-bands of 2M1207b with brown dwarfs
+been obtained. In the right panel of Figure \ref{fig:5}, we compare the
+relative amplitude of J- and H-bands of 2M1207b and brown dwarfs
 \citep{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014} that
@@
 
-We found a strong correlation between the spectral type of the object
-and the J to H variation amplitude ratio. Figure \ref{fig:5}
-demonstrates that earlier spectral type objects -- independent of
-their surface gravity -- have larger variations at shorter wavelength
-than at longer wavelengths. Importantly, although the J$-$H color of
-2M1207b is significantly redder the other L5 dwarfs, we note that its
+We find a tight correlation between the spectral type of the object
+and the J- to H-band variation amplitude ratio. In the right panel of
+Figure \ref{fig:5}, we demonstrate that earlier spectral type
+objects, independent of their surface gravity, have larger variations
+at shorter wavelength than at longer wavelengths. Importantly,
+although the J$-$H color of 2M1207b is significantly redder, its
 relative variation amplitude ratio is almost identical to the matching
-spectral type mid-L dwarf 2M1821. This suggests that the upper cloud
-layers, probed through variability, may be more influenced by spectral
-type and less by cloud thickness, which is thought to influence the
-J$-$H color.
+spectral type mid-L dwarf 2M1821.
 
-{\bf Two questions: What processes sets the relative J vs H amplitude
-  and why is it tied to the pectral type and not to the NIR colors or
-  surface gravity? What does this tell us about the cloud structure
-  as a function of spectral type / gravity (even if speculation)?}
+This trend can be qualitatively explained using the toy model proposed
+in \cite{Yang2014} within the spectral type range of mid-L to L-T
+transition. Assuming that intensity modulations are introduced by a
+refractory cloud whose upper layer locates at altitude $z$, the
+variation amplitude ratio for J and H band can be expressed as
+$\mathrm{Amp_{J}}/\mathrm{Amp_{H}} =
+\exp\left[-(\tau_{\mathrm{J}}(z)/\tau_{{\mathrm{H}}}(z)\right]$,
+where $\tau_{\mathrm{J}}(z)$ and $\tau_{\mathrm{H}}(z)$ are the
+optical depths of upper cloud layer for J and H bands. The opacity for
+J band is smaller than that for H, therefore from mid-L to L-T
+transition, as the cloud upper boundary appears higher in the
+atmosphere, the optical depth difference for the two bands gets
+smaller, and the amplitude ratio decreases.  We note, that the late T
+dwarf 2M2228 falls exactly on this trend, but whose variations are
+likely to emerge from a different mechanism as their silicate clouds
+are below the visible photosphere \citep[e.g.][]{Stephens2009}.
+
+We infer that the upper cloud layer of 2M1207b is at a similar optical
+depth as that of a matching spectral type field brown dwarf from the fact
+that they share similar J- and H-bands light curve amplitude ratio.
+
+%The
+%two processes that atmosphere opacity at certain pressure level
+%enhances and the cloud thickness increases with the decrease of surface
+%gravity have to counterbalance with each other to maintain the optical
+%depth of the cloud upper layer.
 
 \section{Conclusions}
-In summary from our J- and H-band high precision,
-high-cadence lightcurves we discovered sinusoidal modulations in the  planetary mass object
-2M1207b. This is the first detection of rotational modulations in a
-directly imaged planetary mass object.  
-The period is  $10.2^{+0.9}_{-0.8}$, very similar to that derived from
-{\em v sin i} measurements for  the direct imaged exoplanet \bpic{} b and significantly longer than
-most field brown dwarfs with known rotation periods. The
-relative modulation amplitude of J and H band is almost identical to
-one matching spectral type L5 dwarf, although they have very different
-J$-$H colors, and it is markedly different form later spectral type
-brown dwarfs.
+In summary, from our J- and H-band high precision, high-cadence
+light curves we discovered sinusoidal modulations in the planetary mass
+object 2M1207b. This is the first detection of rotational modulations
+in a directly imaged planetary mass object.  The period is
+$10.2^{+0.9}_{-0.8}$,  similar to that derived from {\em v sin i}
+measurements for the direct imaged exoplanet \bpic{} b and
+significantly longer than most field brown dwarfs with known rotation
+periods. The modulation amplitude ratio of J and H band is almost
+identical to one matching spectral type L5 dwarf, although they have
+very different J$-$H colors.
 
@@
 new window on directly imaged exoplanets and planetary-mass
-objects. Our study demonstrates a successful application of high-cadence,
+companions. Our study demonstrates a successful application of high-cadence,
 high-precision, high-contrast photometry with planetary mass
@@
 imaged exoplanets, and identify the key parameters that determine these.
-% % \begin{itemize}
-% % \item a data-reduction pipeline is developed to obtain high precision
-% %   photometry measurement from high contrast WFC3 IR data. For a
-% %   contrast of $\sim 7$ magnitudes at an angular separation of
-% %   $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
-% %   precision of about 2-3\%. 
-% % \item time variability for 2M1207 B was discovered, the light curve of
-% %   2M1207 B for both two colors can be fitted with a T=10.7 hr
-% %   sinusoidal curve.
-% % \item constrain on the amplitude of the amplitude of the
-% %   variability. Large amplitude can be excluded. Constraints on the
-% %   inhomogeniety of the cloud coverage can be inferred -- small
-% %   thickness variance...
-% % \item ? The atmosphere and cloud structure of 2M1207 B. How does it
-% %   compare to the brown dwarf.
-% \end{itemize}
 

### 2015-09-15 summary/science_ms/_region_.tex
its been a long time since last commitment

--- 2015-08-25 summary/letter/letter_vAB.tex
@@
-\documentclass[apj]{emulateapj}
+\message{ !name(ms_vAA.tex)}% Use only LaTeX2e, calling the article.cls class and 12-point type.
 
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{natbib}
-\bibliographystyle{apj}
-\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
-\shorttitle{Short Title}
-\shortauthors{Zhou et al.}
+\documentclass[12pt]{article}
 
-%%% new command %%%
-\newcommand{\ima}{\texttt{ima} files }
-\newcommand{\flt}{\texttt{flt} files }
-\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
-\newcommand{\tinytim}{\textit{Tiny Tim}}
+% Users of the {thebibliography} environment or BibTeX should use the
+% scicite.sty package, downloadable from *Science* at
+% www.sciencemag.org/about/authors/prep/TeX_help/ .
+% This package should properly format in-text
+% reference calls and reference-list numbers.
+
+\usepackage{scicite}
+
+% Use times if you have the font installed; otherwise, comment out the
+% following line.
+
+\usepackage{times}
+
+% The preamble here sets up a lot of new/revised commands and
+% environments.  It's annoying, but please do *not* try to strip these
+% out into a separate .sty file (which could lead to the loss of some
+% information when we convert the file to other formats).  Instead, keep
+% them in the preamble of your main LaTeX source file.
+
+% The following parameters seem to provide a reasonable page setup.
+
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
+
+%The next command sets up an environment for the abstract to your paper.
+
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
+
+% If your reference list includes text notes as well as references,
+% include the following line; otherwise, comment it out.
+
+\renewcommand\refname{References and Notes}
+
+% The following lines set up an environment for the last note in the
+% reference list, which commonly includes acknowledgments of funding,
+% help, etc.  It's intended for users of BibTeX or the {thebibliography}
+% environment.  Users who are hand-coding their references at the end
+% using a list environment such as {enumerate} can simply add another
+% item at the end, and it will be numbered automatically.
+
+\newcounter{lastnote}
+\newenvironment{scilastnote}{%
+\setcounter{lastnote}{\value{enumiv}}%
+\addtocounter{lastnote}{+1}%
+\begin{list}%
+{\arabic{lastnote}.}
+{\setlength{\leftmargin}{.22in}}
+{\setlength{\labelsep}{.5em}}}
+{\end{list}}
+
+% Include your paper's title here
+
+\title{First discovery of variability of direct imaged exoplanet 2M1207b}
+
+% Place the author information here.  Please hand-code the contact
+% information and notecalls; do *not* use \footnote commands.  Let the
+% author contact information appear immediately below the author names
+% as shown.  We would also prefer that you don't change the type-size
+% settings shown here.
+
+\author
+{Yifan Zhou,$^{1\ast}$ Daniel Apai,$^{1}$ Glenn Schneider$^{1}$ Mark
+  Marley$^{2}$ Adam Showman$^{3}$\\
+\\
+\normalsize{$^{1}$Department of Astronomy, the University of Arizona}\\
+\normalsize{933 N. Cherry Ave., Tucson 85721, USA}\\
+\normalsize{$^{2}$NASA Ames Research Center}\\
+\normalsize{$^{3}$Department of Planetary Science, the University of Arizona}\\
+\\
+\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:
+  yifzhou@email.arizona.edu.}
+}
+
+% Include the date command, but leave its argument blank.
+
+\date{}
+
+%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
+
 \begin{document}
-\title{Variability of Planetary Mass Companion 2M1207 B}
-\shorttitle{Variability of 2M1207 B}
-\author{Yifan Zhou, Daniel Apai, Glenn Schneider, ...}
-\affil{The University of Arizona}
 
-\begin{abstract} Rotational modulations in disk-integrated light of
+\message{ !name(ms_vAA.tex) !offset(-3) }
+
+% Double-space the manuscript.
+
+\baselineskip24pt
+
+% Make the title.
+
+\maketitle
+
+% Place your abstract within the special {sciabstract} environment.
+
+\begin{sciabstract}
+Rotational modulations in disk-integrated light of
 brown dwarfs have recently provided powerful constraints on the
@@
 of periodic light curve variations can directly probe the rotational
-periods of ultracool objects.
-
-We present here, for the first time, time-resolved high-precision
+periods of ultracool objects. We present here, for the first time, time-resolved high-precision
 photometric measurements of a planetary-mass companion, 2MASS1207b, to
@@
 companion.
-\end{abstract}
+\end{sciabstract}
 
-\keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
-  and satellites: individual (2M1207b) -- techniques: photometric}
-\maketitle
-%
-\section{Introduction}
+\textbf{Introduction}
 
-Cloud properties in high- and low-gravity objects -- thick clouds: an
-explanation for very red and faint near-infrared fluxes of directly
-imaged planets
-
-Rotational mapping is powerful: successes in brown dwarfs...
-
-The target 2M1207b... contrast The key challenge of obtaining the
-lightcurve of 2M1207b is the high contrast to and small separation
-from 2M1207A.
-
-In this Letter we present the first high-contrast, high-precision,
-time-resolved observations of a directly imaged planet or
-planetary-mass object. We successfully detect rotational modulation
-and measure the amplitudes in two bands and determine the rotational
-period.
-
-\section{Observation} We obtained direct images of the 2M1207A+b
+\textbf{Observation}We obtained direct images of the 2M1207A+b
 system on UT 2014 April 11from 08:07:47 to 16:53:18 using the Hubble
@@
 
-The observations applied space craft rolls between each two orbits to
-allow roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
-telescope roll angles for orbits 1, 3, and 5, and those taken in
-orbits 2, 4, and 6 differed by $25^{\circ}$. At the separation of
-2M1207b this angle difference corresponds to a displacement of
-$0.34''$ or 2.75 and 2.30 resolution elements in F125W and F160W,
-respectively. In each orbit we took thirteen SPARS10 non-destructive
-read-outs with NSAMP=10, alternating between F160W and F125W filters,
-with 2--3 identical exposures in one exposure sequence. To improve PSF
-sampling and reduce the risk caused by bad pixels, we applied standard
-4 point dithering. Over the 6 orbits, we obtained 70 images with 10
-non-destructive read-outs in F125W and 64 images in F160W with
-exposure time of 88.4~s in each filters.
-
-\section{Data Reduction}
-
-%Although \cite{Mandell2013} stated that WFC3 IR time series
-%extract from {\flt} have a rms 1.3 times larger than that obtained
-%from {\ima}, \flt keeps all pixels of the image of 2M1207 A
-%unsaturated, while in 80\% of non-destructive reads the cores of
-%2M1207 A are saturated. 
-%Thus \flt help better align the images for
-%primary subtraction, and separate the flux of 2M1207 B from that of
-%2M1207A.
-
-%The small angular separation of 2M1207 A and B (as shown in Figure
-%\ref{fig:1}) makes precise primary star subtraction and photometry
-%very difficult. 
-%On the under-sampled WFC3 IR detector (plate scale
-  %$\sim 0.13''\mbox{pixel}^{-1}$ \cite{dressel2012wide}), the primary
-%and the secondary only separate by $\sim 6$ pixels, which is about 5
-%times of the FWHM of the PSF. In addition, under-sampling causes
-%significant artifacts when shifting the images for registration no
-%matter what interpolation method is used.
-
-\begin{figure*}
-  \centering
-  \plottwo{original}{subtracted}
-  \caption{WFC3 F160W images of 2M1207A system. {\em Upper panel}: In the original image 
-    2M1207 B is hidden in the halo of the bright 2M1207A.   {\em Lower panel:} In the residual image -- after the subtraction of the hybrid PSF -- 2M1207 B is detected at a high significant level.}
-  \label{fig:1}
-\end{figure*}
-
-\subsection{Photometry}
-
-We started the reduction from the the \flt files produced by the
-WFC3's \texttt{calwfc3} pipeline. We did not opt to use the more
-advance \ima pipeline products because these provided less information
-on 2M1207A, which saturated after the first few read-outs.  The \flt
-are results of basic calibration, including dark current correction,
-non-linearity correction, flat field correction, as well as
-up-the-ramp fit on the non-destructive read-outs also considering
-cosmic rays. From the beginning, pixels with data quality flags ``bad
-detector pixels'' (DQ = 4), ``unstable response'' (DQ = 32), and ``bad
-or uncertain flat value'' (DQ = 512) were masked out and excluded from
-further analysis as suggested by previous transit exoplanet
-spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.
+\textbf{Data reduction}
+\textbf{Hybrid PSF photometry}
 
@@
 by image interpolation and shifting. On the other hand, \tinytim{} PSF
-simulator\citep{Krist1995} offers a solution by providing Nyquist
-sampled PSF, but significant systematic errors of \tinytim{} PSF
- limits its ability in high precision
-photometry\citep{Biretta2014}. However, 6 orbits of observation provides us a chance to
-fully characterize the difference of model and observed PSFs. To obtain
-robust \tinytim{} PSF photometry,  we designed a 2-round PSF fitting strategy: 1. calculating
+simulator\citep{Krist1995} offers a solution by providing Nyquist or better
+sampled PSF, but systematic errors of \tinytim{} PSF for WFC3 limits
+its ability in high precision photometry\citep{Biretta2014}. However,
+we are able to fully characterize the difference of model and observed
+PSFs with 6 orbits time-resolved observation data. To obtain robust \tinytim{} PSF
+photometry, we designed a 2-round PSF fitting strategy: 1. calculating
 correction map for \tinytim{}; 2. hybrid PSF photometry.
@@
 For both of 2 rounds, we used {\em Tiny Tim} to calculate 10$\times$
-over-sampled model PSFs based the filters, the spectra 
+over-sampled model PSFs based on the filters, the spectra 
 \citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
 the telescope jitter.  We used the new set of Tiny Tim parameters
-provided by \cite{Biretta2014} to better model the cold mask,
-diffraction spikes, and the coma. The focus parameters were calculated
+provided by \cite{Biretta2014} to improve model of the cold mask,
+OTA spikes, and the coma. The focus parameters were calculated
 using the model listed on the STScI
-website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
-We determined the exact position of 2M1207A first by fitting the PSF
-on a dynamic coordinate grid and minimizing the difference in the
-observed and modeled PSFs at a region centered on 2M1207 A with a
-5-pixel-radius aperture centered 2M1207 b excluded.Then we fit the
-position of 2M1207 b and the photometries of 2M1207 A and b together
+website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. To
+register \tinytim{} PSF to observed PSF of 2M1207A, we moved the
+over-sampled PSF over a coordinate grid (gird size=0.001 pixel) using
+cubic interpolation and minimize the rms difference of the
+observed and re-binned \tinytim{} PSFs over a region centered on 2M1207A with a
+5-pixel-radius aperture centered on 2M1207b excluded. Then we introduce
+another \tinytim{} PSF for 2M1207b and  fit the
+position of 2M1207 b and the photometries of 2M1207 A and b simultaneously
 by least square optimization. From our data set, we discovered that
-the difference of observed PSFs and model PSFs are very stable for
-given PSF position. Therefore at the end of the first round PSF
+the difference of observed PSFs and model PSFs were very stable for
+given PSF positions. Therefore at the end of the first round PSF
 fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
-empirical correction maps for each filter:
+observationally derived correction maps for each filter:
 \begin{equation}
-  \mathrm{Corr = Median(PSF_{model} - PSF_{obs} )}
+  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
 \end{equation}
@@
 for 2M1207 A and b. In the second round, we combined the correction
-term linearly with the two \tinytim{} PSFs to generate hybrid PSFs, and fitted for their
-amplitudes together. We found that by including the correction term,
+term linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
+and fitted the three components together. We found that by including the correction term,
 the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
-around unity. Because the total fluxes of the model PSFs were
-normalized to unity as default, the fluxes of 2M1207 A and B were
-solely represented by the amplitude of the two PSFs coordinately.
+around unity. Relative photometry is acquired from the scaling
+parameters of the model PSFs.
 
-However, PSF profiles change with different exposure positions due to
+PSF profiles change with exposure positions due to
 pixelation, especially for the case that WFC3 IR is significantly
 under-sampled. Also, the flat fields may potentially have large scale
-structures \citep{dressel2012wide}. Because of these factors, the
-fluxes for both 2M1207 A and B are correlated with the dithering
-position. To break the correlation, we normalize each group of
+structures \citep{dressel2012wide}. We found a correlation of
+photometry with PSF positions on detector frame for both 2M1207 A and
+b. Correction were made by normalizing each group of
 exposures that have the same dithering position and roll angle
 individually -- we took the median of the fluxes that were measured
-from these exposures as normalization factors and devided them from
+from these exposures as normalization factors and divided them from
 every photometric measurement. Because the normalization factor for
@@
 
-% {\em Hybrid PSF Calculation:} The hybrid PSFs were generated as a
-% linear combination of a diffraction-limited PSF (calculated with the
-% {\em Tiny Tim} simulator\citep{Krist1995}, and a empirically
-% determined correction map. We used {\em Tiny Tim} to calculate model
-% PSFs for the filters used, the spectrum of our target, the telescope's
-% actual focus, and the telescope jitter.  We used the new set of Tiny
-% Tim parameters provided by \cite{Biretta2014} to better model the cold
-% mask, diffraction spikes, and the coma. The focus parameters were
-% calculated using the model listed on the STScI
-% website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
-% A significant advantage of Tiny Tim PSF over empirical PSFs is that
-% Tiny Tim can produce Nyquist-sampled results, which allows accurate
-% image shifting and interpolation. However, an important limitation of
-% Tiny Tim is that the model PSFs have significant systematic
-% errors. \cite{Biretta2014} demonstrated that the diffraction spikes
-% and coma are not accurately simulated with Tiny Tim for WFC3/IR
-% images. However, using the 6-orbit long time series, we are able to
-% accurately characterize the difference of the modeled and observed
-% PSFs and derive an empirical correction map: Corr = Mean (
-% PSF\_modeled - PSF\_observed ) where PSF\_modeled is a combination of
-% two Tiny Tim PSFs with positions and amplitudes optimized to minimize
-% the residuals.  By combining the model PSFs with the empirical
-% correction map we derived a high-quality hybrid PSF, the use of which
-% significantly improved the PSF subtraction and photometry.
-
-% {\em PSF Fitting:} In the next step we simultaneously fitted the positions and amplitudes of the combination of the hybrid PSFs to 2M1207A and 2M1207b.
-First, we determined the primary star position and telescope jitter.
-We produced a list of 10$\times$ over-sampled PSFs matching the spectrum \citep{Bonnefoy2014} and the position of 2M1207A with different telescope jitters ranging from 0 to 50$\mbox{mini-arcsec s}^{-1}$ along
-% both $x$ and $y$ detector axes.
-The PSFs were registered with the original image by searching on a dynamic grid and minimizing the difference in the observed and modeled PSFs at a region centered on 2M1207 A with a 5-pixel-radius aperture centered 2M1207 B excluded.
-
-% Next, we determined the position and approximate flux of 2M1207B by calculating and fitting a Tiny Tim PSF for the hybrid PSF-subtracted 2M1207 B based on its position on the detector, spectrum \citep{Patience2010}, and
-% the telescope jitter that had been obtained above. In the final step,
-% we combined the two PSFs together.
-
-% We fixed the position of the primary as it had been fitted in the first step and fitted for the
-% amplitudes of the two PSFs and the precise position of the
-% secondary. Since the total fluxes of the model PSFs were normalized to
-% unity as default, the fluxes of 2M1207 A and B were solely represented
-% by the amplitude of the two PSFs coordinately.
-
-% Because of the systematic errors of the Tiny Tim PSF, the quality of the
-% fit is not perfect. The reduced $\chi^{2}$ values were at level
-% of $\sim10$. However, we found that the residual patterns were very
-% stable among the image that have the same dithering position and
-% telescope rolling. Therefore, we median combined the residual images
-% that have the same dithering position and telescope rolling angle to
-% construct 8 residual models (4 dithering position $\times$ 2 telescope
-% rolling angle) for each filter. We pre-subtract the corresponding
-% residual from the original image and repeated the procedure that
-% listed above. Using this extra-step, the reduced $\chi^{2}$
-% greatly decreased to around unity.
-
-% %\section{Uncertainty analysis}
-
-\subsection{Uncertainty Analysis: White noise}
-We consider the primary source of uncertainty for every measurement is
-photon noise. We propagated the photon noises of every single pixel
-that were calculated from count rates and detector gain, to the PSF
-fitting results. The photon noises for photometry in F125W and F160W
-are 1.33\% and 1.02\%, respectively.
-
-Since the primary and secondary PSFs were fitted simultaneously in our
-PSF photometry procedure, the uncertainties of photometry and position
-for the primary and secondary are coupled with each other. The second
-order uncertainty could also contribute to the overall uncertainty,
-e.g. the imperfection of position measurement of 2M1207A can affect
-the photometry of 2M1207b. We used a Monte Carlo (MC) method to evaluate the complete systematic of the
-PSF fitting. We applied the PSF photometry to images that
-were added with random Poisson noise and repeat the procedure for 1000
-time. From the distribution of the result, the uncertainty for F125W
-and F160W photometry are found to be 1.34\% and 1.12\%,
-respectively. We conclude that the white noise of our observation is
-dominated by photon noise.
-
-\subsection{Uncertainty Analysis: Flat field uncertainties}
-
- \begin{figure*}
-  \centering
-  \plotone{systematics}
-  \caption{F125W (left) and F160W (right) light curves under different
-  verification tests. Individual measurements are plotted with gray
-  crosses. Photometries of the same exposure sequence are binned, and
-  binned data are plotted with points and squares. Fitted sinusoidal
-  waves are plotted with solid lines. {\em Upper}: binned photometries taken
-in dithering position 1 and 3 (red points) and that taken in 2 and 4
-(blue squares) are plotted differently. They demonstrate same trend of
-variation. In upper left panel, sinusoidal wave fitted with all
-parameter set free, and that fitted with period set the same as that
-of F125W are plotted with green and purple lines, respectively. {\em
-  Middle}: sinusoidal waves fitted without using the data taken in
-Orbit 1 are plotted. These curves are almost identical to the curves
-plotted in upper panel. {\em Lower}: photometry measured with
-AFEM-applied images and their best fitted sinusoidal curves are
-plotted. These photometries and curves are also almost identical to
-those plotted in upper panel.}
-  \label{fig:2}
-\end{figure*}
-
-In our observations 2M1207 B were observed at 8 different spots on the
-detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
-field correction are potential sources of variation as they may
-introduce position-dependent differences in the count rates. The
-uncertainty of WFC3 IR pipeline flat field is $\sim 1\%$
-\citep{dressel2012wide}.
-% and our time resolved observations for another target
-%demonstrate that aperture photometry for exposures taken at different
-%dithering position are uncertain at the same level.
-%Flat field uncertainties have smaller effects on 
-In PSF photometry, however, multiple pixels are fitted simultaneously
-and we expect a lower than 1\% uncertainty from the flat field
-errors. To verify this we multiplied every image by an artificial flat
-field error mask (AFEM) -- a uniformly distributed Gaussian noise array with
-mean of 1 and sigma of 1\% -- and repeated the PSF photometry on the
-resulting images.  The analysis of these experiments showed almost
-identical lightcurve to the original, verifying that the flat field
-errors do not affect our photometry significantly (Figure
-\ref{fig:2}).
-
-\section{Verification of Photometric Variations and Amplitude
-  Estimate}
-
-\subsection{Tests and Verification}
-
-The light curves that resulted from our photometry show apparently
-sinusoidal modulations, discussed in more details in
-\S,\ref{Results}. To verify that these modulations are intrinsic to
-the object and not result of our data reduction procedure or due to
-instrumental changes, we carried out three different tests.
-
-First, we fitted sine waves independently to the two filters to verify
-the similarity of the signal in the two bands (Figure \ref{fig:2}). Inconsistent periods or
-light curve shapes would argue against a genuine signal.  We found
-that the periods of the best fit sine waves are similar,
-$10.5^{+1.2}_{-1.3}$h for F125W and $9.1^{+1.1}_{-1.0}$h for
-F160W. These periods are roughly consistent within the
-uncertainty. Furthermore, these periods are not close to any
-timescales over which HST or WFC3 are known to changes.
-
- As a second test we repeated the analysis neglecting the first
- orbit. The motivation behind this test was that, due to spacecraft
- thermal settling, the first orbit of HST observations is often
- slightly unstable and is often neglected in high-precision studies
- (\textbf{citation?}). Indeed, in our analysis 2M1207 A is
- significantly fainter in the first orbit (Figure \ref{fig:3}) than in
- the subsequent ones.
- %The exposure levels at the pixels of the peak of the PSF of 2M1207 B are less than 10,000 e$^{-}$
- %for both two colors, thus image persistence is less of an issue for
- %2M1207 B. 
- Our analysis based on orbits 2--6 only found essentially identical
- results to our analysis of orbits 1--6, based on which we conclude
- that the first less reliable orbit does not affect our results
- significantly (Figure \ref{fig:2}, middle panel).
-
-As a third test we explored whether a subset of images, perhaps
-imperfectly normalized or correlated with specific instrument states,
-could be driving the light curves into an apparently sinusoidal
-shape. To test this possibility we split the data into two temporally
-overlapping halves: sub-dataset one from dithering positions 1 and 3,
-and sub-dataset two from dithering positions 2 and 4. For both
-datasets we repeated our analysis independently.  For both of F125W
-and F160W, two halves demonstrated similar trend of variability as
-shown in Figure \ref{fig:2}.  Our analysis detected sinusoidal
-modulations in {\em both} sub-datasets and in {\em both} filters, with
-periods and amplitudes consistent with those derived from the complete
-data set (\ref{fig:2}, upper panel).
-
- These tests demonstrate that the modulation seen in our data are
- consistently present in the different filters, in the different time
- segments of the data, and in data obtained in different dithering
- positions.
-
- % \begin{itemize}
-% \item the source of the scattering -- 
-% \item flat field uncertainty -- adding artificial flat field error mask
-% \item validity of the variability\\
-%   -- both filter demonstrate similar period of variability\\
-%   -- split the data into two half, the trend in two halves of data
-%   looks similar.
-%   -- fix the position does not change the light curve
-% \item uncertainty of sinusoidal curve fit
-%   -- carry out a mcmc fit? is it worth doing this.
-% \end{itemize}
-
-  \begin{figure*}
-  \centering
-  \plotone{sineCurveFit_binCombined}
-  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Individual photometric
-  measurement are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoidal waves are plotted
-  with blue solid lines.}
-  \label{fig:3}
-\end{figure*}
-
-\subsection{Amplitude and Period Measurements}
-
-To constrain the uncertainties of the least square optimization
-results, we used a Monte Carlo(MC) method to improve the fitting. We
-generated a series of random Gaussian noises with the standard deviation same as
-the photon noise, added them to the original light curves, and applied
-least square fit to the new light curves. We repeated above routine for 10000 times and obtained
-the distribution of the fitting parameters. The distributions for the
-periods and the amplitudes for F125W and F160W light curves are
-shown in Figure \ref{fig:4}.
-
-\section{Result}
-
-\begin{figure*}
-  \centering
-  \plottwo{periodDistr}{amplitudeDistr}
-  \caption{Distributions for periods (left) and amplitudes(right) for the light
-    curve of F125W and F160W. The bin size for histograms of period is
-  0.25 hour and for that of amplitude is 0.5\%. Histograms are
-  normalized in the way that total area of the histogram equals to
-  1. In the right panel, Gaussian profiles are fitted to the
-  histograms and plotted in solid lines.}
-  \label{fig:4}
-\end{figure*}
-
-\label{Results}
-We present the first high-contrast, high-resolution, high-cadence, and
-high-precision photometry of a directly imaged planet or
-planetary-mass companion. Our observations reveal a modulation in the
-light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection
-of modulations in directly imaged ultracool objects.  The best fit
-periods for F125W and F160W are 10.4 and 9.0 hour correspondingly. The
-amplitudes for the normalized light curves are 1.4\% and 0.9\% for
-F125W and F160W light curves.
-
-We obtained high signal to noise photometry series for both 2M1207 A
-and B (Figure \ref{fig:3}). On average, the photometric contrast is
-$6.52\pm0.01$ mag for
-F125W and $5.77\pm0.01$ mag for F160W. The difference of F125W contrast
-from that measured in J-band \citep{Mohanty2007} and
-F160W contrast from that measured with NICMOS F160W 
-\citep{Song2006} is due to the different throughput profiles of the
-filters.
-
-In the following we will discuss the amplitude and period of 2M1207B
-and place this object in the broader context of ultracool atmospheres.
-
-The distributions for the periods demonstrate long tail shaped towards
-long period, with core region roughly Gaussian. With probability range
-of 64\%(1-$\sigma$ Gaussian), we estimated the 1-$\sigma$ range for
-the periods of F125W and F160W to be  $10.5_{-1.2}^{+1.3}$ and
-$9.1_{-1.0}^{+1.1}$ h, respectively. The period for best
-fitted sine wave of F125W light curve is longer than that of F160W for
-1.5 h that is slight larger 1-$\sigma$ standard deviation. We also
-performed a joint MC fit with the two light curves with the assumption
-that the periods of the variation of the two bands are the same. We
-derived a period of $10.2^{+0.9}_{-0.8}$ h.
-
-The variation amplitudes in the two bands have significant
-difference. The distributions of the amplitudes are well described by
-Gaussian profiles. Fitting the histogram to a Gaussian function, we
-determined that amplitude distribution of F125W peaks at 1.5\% with a
-standard deviation of 0.3\%, and that of F160W have mean and standard
-deviation of 0.9\% and 0.2\%, respectively. The peaks of the two
-histograms separated by more than 2-$\sigma$. The variation amplitude
-of F125W light curve is 1.67 times of that of F160W light curve.
-
-%Although the photometric time series demonstrate relatively large
-%scattering, both F125W and F160W light curves demonstrate sinusoidal
-%shape with clear temporal variability. We fitted sine waves to the two
-%light curves using least square optimization, and determined the
-%periods and variation amplitudes.
-
-\section{Discussion}
-Amplitude and Relative Amplitudes: Comparison to other brown dwarfs
-
-Rotation Period: Comparison to Brown Dwarfs and Beta Pic
-
-Method: Opens a new window, successful demonstration, how could it be improved?
-Mapping different pressure levels, atmospheric dynamics?
-
-\section{Conclusions}
-\begin{itemize}
-\item a data-reduction pipeline is developed to obtain high precision
-  photometry measurement from high contrast WFC3 IR data. For a
-  contrast of $\sim 7$ magnitudes at an angular separation of
-  $\sim0.7''$, we obtained photometry measurement for 2M1207 B at
-  precision of about 2-3\%. 
-\item time variability for 2M1207 B was discovered, the light curve of
-  2M1207 B for both two colors can be fitted with a T=10.7 hr
-  sinusoidal curve.
-\item constrain on the amplitude of the amplitude of the
-  variability. Large amplitude can be excluded. Constraints on the
-  inhomogeniety of the cloud coverage can be inferred -- small
-  thickness variance...
-\item ? The atmosphere and cloud structure of 2M1207 B. How does it
-  compare to the brown dwarf.
-\end{itemize}
+% In setting up this template for *Science* papers, we've used both
+% the \section* command and the \paragraph* command for topical
+% divisions.  Which you use will of course depend on the type of paper
+% you're writing.  Review Articles tend to have displayed headings, for
+% which \section* is more appropriate; Research Articles, when they have
+% formal topical divisions at all, tend to signal them with bold text
+% that runs into the paragraph, for which \paragraph* is the right
+% choice.  Either way, use the asterisk (*) modifier, as shown, to
+% suppress numbering.
 
 \bibliography{ref.bib}
+
+\bibliographystyle{Science}
+
 \end{document}
@@
 %%% End:
+
+\message{ !name(ms_vAA.tex) !offset(-264) }

### 2015-09-15 summary/science_ms/ms_vAA.tex
its been a long time since last commitment

--- 2015-09-15 summary/science_ms/_region_.tex
@@
-\message{ !name(ms_vAA.tex)}% Use only LaTeX2e, calling the article.cls class and 12-point type.
+% Use only LaTeX2e, calling the article.cls class and 12-point type.
 
@@
 \usepackage{times}
-
+\usepackage{hyperref}
 % The preamble here sets up a lot of new/revised commands and
@@
 
+\newcommand{\ima}{\texttt{ima} files }
+\newcommand{\flt}{\texttt{flt} files }
+\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
+\newcommand{\tinytim}{\textit{Tiny Tim}}
+\newcommand{\bpic}{$\beta$ Pic}
+\newcommand{\vsini}{$v\sin i$}
+\newcommand{\mjup}{M$_{\mbox{Jup}}$}
 % Include your paper's title here
@@
 \begin{document}
-
-\message{ !name(ms_vAA.tex) !offset(-3) }
 
@@
 system on UT 2014 April 11from 08:07:47 to 16:53:18 using the Hubble
-Space Telescope (HST) and its Wide Field Camera 3 \citep[WFC3,
+Space Telescope (HST) and its Wide Field Camera 3 \cite[WFC3,
 ][]{Kimble2008} in the frame of the HST Proposal GO-13418 (PI:
@@
 by image interpolation and shifting. On the other hand, \tinytim{} PSF
-simulator\citep{Krist1995} offers a solution by providing Nyquist or better
+simulator\cite{Krist1995} offers a solution by providing Nyquist or better
 sampled PSF, but systematic errors of \tinytim{} PSF for WFC3 limits
-its ability in high precision photometry\citep{Biretta2014}. However,
+its ability in high precision photometry\cite{Biretta2014}. However,
 we are able to fully characterize the difference of model and observed
@@
 over-sampled model PSFs based on the filters, the spectra 
-\citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
+\cite{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
 the telescope jitter.  We used the new set of Tiny Tim parameters
@@
 under-sampled. Also, the flat fields may potentially have large scale
-structures \citep{dressel2012wide}. We found a correlation of
+structures \cite{dressel2012wide}. We found a correlation of
 photometry with PSF positions on detector frame for both 2M1207 A and
@@
 analysis.
+
+\textbf{Result}
+We present the first high-contrast, high-resolution, high-cadence, and
+high-precision photometry of a directly imaged planet or
+planetary-mass companion. Our observations reveal a modulation in the
+light curve of the 5--7~M$_{J}$ companion 2M1207b, the first detection
+of modulations in directly imaged ultracool objects.  The best fit
+periods for F125W and F160W are 10.5 and 9.1 hour correspondingly. The
+amplitudes for the normalized light curves are 1.45\% and 0.92\% for
+F125W and F160W light curves.
+
+The distributions for the periods demonstrate long tail shaped towards
+long period, with core region roughly Gaussian. With 64\% confidence,
+we estimated the 1-$\sigma$ range for the periods of F125W and F160W
+to be $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ h,
+respectively. The period of best fitted sine wave of F125W light
+curve is 1.5h longer than that of F160W  that is slight larger
+1-$\sigma$ standard deviation. We also jointly fit the two band light
+curve together forcing the periods of two sine waves to be the
+same. We derived a modulation period of $10.2^{+0.9}_{-0.8}$ h in this
+circumstance.
+
+We discovered that  the variation amplitudes in the two bands were significantly
+different. The distributions of the amplitudes are well described by
+Gaussian profiles. By fitting a Gaussian function to the distribution, we
+determined that amplitude distribution of F125W peaks at 1.45\% with a
+standard deviation of 0.22\%, and that of F160W have mean and standard
+deviation of 0.92\% and 0.20\%, respectively. The peaks of the two
+histograms separated by more than 2-$\sigma$. The variation amplitude
+of F125W light curve is 1.58 times of that of F160W light curve.
+
+\textbf{Discussion}
+A fundamental result of our study is the direct determination of the
+rotation period of a directly imaged planetary-mass object. We
+convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
+$R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
+brown dwarfs with well defined rotation period from the study of
+\cite{Metchev2015}, and compare their rotation velocities with solar
+system planets and \bpic{} b in the left
+panel of Figure \ref{fig:5}.  The study by
+\cite[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
+and demonstrated that it fits a trend defined by Solar System planets
+in which more massive planets have faster rotation rates. They suggested
+that this relation is linked to the accretion processes during planet formation.
+
+Excitingly, our measurement of the rotation period demonstrates that
+2M1207b, a planetary mass companion  with similar age to \bpic{} b, has a rotation velocity
+that fits in the same trend, as well as majority of brown
+dwarfs.
+% % Periods are converted to equatorial rotation velocity by adopting a radius of 1 -- 1.4
+% % $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for brown dwarfs with rotation period
+% % measurement listed in \cite{Metchev2015}.
+% In left panel of Figure \ref{fig:5}, we demonstrate that 2M1207b and
+% most of the brown dwarfs falls on the same linear relationship with
+% solar system planets and \bpic{} b on a
+% $\log-\log$ plot of equatorial relationship vs. mass. 
+We note that 2M1207b is most likely formed in the same way as brown
+dwarfs by gravitational fragmentation, which suggests
+that rotation periods are not good tracers of the formation pathways
+and may not contribute important evidence for a formation in a disk
+vs. in a cloud core environment.
+
+Furthermore, our observations allow us to compare the relative
+amplitudes in the J- and H-bands between the handful of brown dwarfs
+for which high-quality near-infrared time-resolved observations have
+been obtained. In the right panel of Figure \ref{fig:5}, we plot the
+relative amplitude of J- and H-bands of 2M1207b with brown dwarfs
+\cite{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014} that
+have different spectral types and J$-$H colors.
+
+We found a strong correlation between the spectral type of the object
+and the J to H variation amplitude ratio. Figure \ref{fig:5}
+demonstrates that earlier spectral type objects -- independent of
+their surface gravity -- have larger variations at shorter wavelength
+than at longer wavelengths. Importantly, although the J$-$H color of
+2M1207b is significantly redder the other L5 dwarfs, we note that its
+relative variation amplitude ratio is almost identical to the matching
+spectral type mid-L dwarf 2M1821.
 
@@
 
+\textbf{Summary}In summary from our J- and H-band high precision,
+high-cadence lightcurves we discovered sinusoidal modulations in the  planetary mass object
+2M1207b. This is the first detection of rotational modulations in a
+directly imaged planetary mass object.  
+The period is  $10.2^{+0.9}_{-0.8}$, very similar to that derived from
+{\em v sin i} measurements for  the direct imaged exoplanet \bpic{} b and significantly longer than
+most field brown dwarfs with known rotation periods. The
+relative modulation amplitude of J and H band is almost identical to
+one matching spectral type L5 dwarf, although they have very different
+J$-$H colors, and it is markedly different form later spectral type
+brown dwarfs.
+
+Finally, we note that the observations presented here open an exciting
+new window on directly imaged exoplanets and planetary-mass
+objects. Our study demonstrates a successful application of high-cadence,
+high-precision, high-contrast photometry with planetary mass
+companion. We also show that these observations can be carried out simultaneously
+at multiple wavelengths, allowing us to prove multiple pressure
+levels. With observation of a larger sample and at multiple wavelengths, we will be
+able to explore  the detailed structures of atmospheres of directly
+imaged exoplanets, and identify the key parameters that determine these.
+
 \bibliography{ref.bib}
@@
 %%% End:
-
-\message{ !name(ms_vAA.tex) !offset(-264) }

### 2015-09-15 summary/science_ms/scifile.tex
its been a long time since last commitment

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{A simple {\it Science\/} Template}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
\\
\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
  This document presents a number of hints about how to set up your
  {\it Science\/} paper in \LaTeX\ .  We provide a template file,
  \texttt{scifile.tex}, that you can use to set up the \LaTeX\ source
  for your article.  An example of the style is the special
  \texttt{\{sciabstract\}} environment used to set up the abstract you
  see here.
\end{sciabstract}

% In setting up this template for *Science* papers, we've used both
% the \section* command and the \paragraph* command for topical
% divisions.  Which you use will of course depend on the type of paper
% you're writing.  Review Articles tend to have displayed headings, for
% which \section* is more appropriate; Research Articles, when they have
% formal topical divisions at all, tend to signal them with bold text
% that runs into the paragraph, for which \paragraph* is the right
% choice.  Either way, use the asterisk (*) modifier, as shown, to
% suppress numbering.

\section*{Introduction}

In this file, we present some tips and sample mark-up to assure your
\LaTeX\ file of the smoothest possible journey from review manuscript
to published {\it Science\/} paper.  We focus here particularly on
issues related to style files, citation, and math, tables, and
figures, as those tend to be the biggest sticking points.  Please use
the source file for this document, \texttt{scifile.tex}, as a template
for your manuscript, cutting and pasting your content into the file at
the appropriate places.

{\it Science\/}'s publication workflow relies on Microsoft Word.  To
translate \LaTeX\ files into Word, we use an intermediate MS-DOS
routine \cite{tth} that converts the \TeX\ source into HTML\@.  The
routine is generally robust, but it works best if the source document
is clean \LaTeX\ without a significant freight of local macros or
\texttt{.sty} files.  Use of the source file \texttt{scifile.tex} as a
template, and calling {\it only\/} the \texttt{.sty} and \texttt{.bst}
files specifically mentioned here, will generate a manuscript that
should be eminently reviewable, and yet will allow your paper to
proceed quickly into our production flow upon acceptance \cite{use2e}.

\section*{Formatting Citations}

Citations can be handled in one of three ways.  The most
straightforward (albeit labor-intensive) would be to hardwire your
citations into your \LaTeX\ source, as you would if you were using an
ordinary word processor.  Thus, your code might look something like
this:

\begin{quote}
\begin{verbatim}
However, this record of the solar nebula may have been
partly erased by the complex history of the meteorite
parent bodies, which includes collision-induced shock,
thermal metamorphism, and aqueous alteration
({\it 1, 2, 5--7\/}).
\end{verbatim}
\end{quote}

\noindent Compiled, the last two lines of the code above, of course, would give notecalls in {\it Science\/} style:

\begin{quote}
\ldots thermal metamorphism, and aqueous alteration ({\it 1, 2, 5--7\/}).
\end{quote}

Under the same logic, the author could set up his or her reference list as a simple enumeration,

\begin{quote}
\begin{verbatim}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei
and Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ 
Physik\/} {\bf 56}, 1 (1929).
\end{enumerate}
\end{verbatim}
\end{quote}

\noindent yielding

\begin{quote}
{\bf References and Notes}

\begin{enumerate}
\item G. Gamow, {\it The Constitution of Atomic Nuclei and
Radioactivity\/} (Oxford Univ. Press, New York, 1931).
\item W. Heisenberg and W. Pauli, {\it Zeitschr.\ f.\ Physik} {\bf 56},
1 (1929).
\end{enumerate}
\end{quote}

That's not a solution that's likely to appeal to everyone, however ---
especially not to users of B{\small{IB}}\TeX\ \cite{inclme}.  If you
are a B{\small{IB}}\TeX\ user, we suggest that you use the
\texttt{Science.bst} bibliography style file and the
\texttt{scicite.sty} package, both of which we are downloadable from our author help site.  You can also
generate your reference lists by using the list environment
\texttt{\{thebibliography\}} at the end of your source document; here
again, you may find the \texttt{scicite.sty} file useful.

Whether you use B{\small{IB}}\TeX\ or \texttt{\{thebibliography\}}, be
very careful about how you set up your in-text reference calls and
notecalls.  In particular, observe the following requirements:

\begin{enumerate}
\item Please follow the style for references outlined at our author
  help site and embodied in recent issues of {\it Science}.  Each
  citation number should refer to a single reference; please do not
  concatenate several references under a single number.
\item Please cite your references and notes in text {\it only\/} using
  the standard \LaTeX\ \verb+\cite+ command, not another command
  driven by outside macros.
\item Please separate multiple citations within a single \verb+\cite+
  command using commas only; there should be {\it no space\/}
  between reference keynames.  That is, if you are citing two
  papers whose bibliography keys are \texttt{keyname1} and
  \texttt{keyname2}, the in-text cite should read
  \verb+\cite{keyname1,keyname2}+, {\it not\/}
  \verb+\cite{keyname1, keyname2}+.
\end{enumerate}

\noindent Failure to follow these guidelines could lead
to the omission of the references in an accepted paper when the source
file is translated to Word via HTML.

\section*{Handling Math, Tables, and Figures}

Following are a few things to keep in mind in coding equations,
tables, and figures for submission to {\it Science}.

\paragraph*{In-line math.}  The utility that we use for converting
from \LaTeX\ to HTML handles in-line math relatively well.  It is best
to avoid using built-up fractions in in-line equations, and going for
the more boring ``slash'' presentation whenever possible --- that is,
for \verb+$a/b$+ (which comes out as $a/b$) rather than
\verb+$\frac{a}{b}$+ (which compiles as $\frac{a}{b}$).  Likewise,
HTML isn't tooled to handle certain overaccented special characters
in-line; for $\hat{\alpha}$ (coded \verb+$\hat{\alpha}$+), for
example, the HTML translation code will return [\^{}$(\alpha)$].
Don't drive yourself crazy --- but if it's possible to avoid such
constructs, please do so.  Please do not code arrays or matrices as
in-line math; display them instead.  And please keep your coding as
\TeX-y as possible --- avoid using specialized math macro packages
like \texttt{amstex.sty}.

\paragraph*{Displayed math.} Our HTML converter sets up \TeX\
displayed equations using nested HTML tables.  That works well for an
HTML presentation, but Word chokes when it comes across a nested
table in an HTML file.  We surmount that problem by simply cutting the
displayed equations out of the HTML before it's imported into Word,
and then replacing them in the Word document using either images or
equations generated by a Word equation editor.  Strictly speaking,
this procedure doesn't bear on how you should prepare your manuscript
--- although, for reasons best consigned to a note \cite{nattex}, we'd
prefer that you use native \TeX\ commands within displayed-math
environments, rather than \LaTeX\ sub-environments.

\paragraph*{Tables.}  The HTML converter that we use seems to handle
reasonably well simple tables generated using the \LaTeX\
\texttt{\{tabular\}} environment.  For very complicated tables, you
may want to consider generating them in a word processing program and
including them as a separate file.

\paragraph*{Figures.}  Figure callouts within the text should not be
in the form of \LaTeX\ references, but should simply be typed in ---
that is, \verb+(Fig. 1)+ rather than \verb+\ref{fig1}+.  For the
figures themselves, treatment can differ depending on whether the
manuscript is an initial submission or a final revision for acceptance
and publication.  For an initial submission and review copy, you can
use the \LaTeX\ \verb+{figure}+ environment and the
\verb+\includegraphics+ command to include your PostScript figures at
the end of the compiled PostScript file.  For the final revision,
however, the \verb+{figure}+ environment should {\it not\/} be used;
instead, the figure captions themselves should be typed in as regular
text at the end of the source file (an example is included here), and
the figures should be uploaded separately according to the Art
Department's instructions.

\section*{What to Send In}

What you should send to {\it Science\/} will depend on the stage your manuscript is in:

\begin{itemize}
\item {\bf Important:} If you're sending in the initial submission of
  your manuscript (that is, the copy for evaluation and peer review),
  please send in {\it only\/} a PostScript or PDF version of the
  compiled file (including figures).  Please do not send in the \TeX\ 
  source, \texttt{.sty}, \texttt{.bbl}, or other associated files with
  your initial submission.  (For more information, please see the
  instructions at our Web submission site,
  http://www.submit2science.org/ .)
\item When the time comes for you to send in your revised final
  manuscript (i.e., after peer review), we require that you include
  all source files and generated files in your upload.  Thus, if the
  name of your main source document is \texttt{ltxfile.tex}, you
  need to include:
\begin{itemize}
\item \texttt{ltxfile.tex}.
\item \texttt{ltxfile.aux}, the auxilliary file generated by the
  compilation.
\item A PostScript file (compiled using \texttt{dvips} or some other
  driver) of the \texttt{.dvi} file generated from
  \texttt{ltxfile.tex}, or a PDF file distilled from that
  PostScript.  You do not need to include the actual \texttt{.dvi}
  file in your upload.
\item From B{\small{IB}}\TeX\ users, your bibliography (\texttt{.bib})
  file, {\it and\/} the generated file \texttt{ltxfile.bbl} created
  when you run B{\small{IB}}\TeX.
\item Any additional \texttt{.sty} and \texttt{.bst} files called by
  the source code (though, for reasons noted earlier, we {\it
    strongly\/} discourage the use of such files beyond those
  mentioned in this document).
\end{itemize}
\end{itemize}

% Your references go at the end of the main text, and before the
% figures.  For this document we've used BibTeX, the .bib file
% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
% was included to format the reference numbers according to *Science*
% style.

\bibliography{scibib}

\bibliographystyle{Science}

% Following is a new environment, {scilastnote}, that's defined in the
% preamble and that allows authors to add a reference at the end of the
% list that's not signaled in the text; such references are used in
% *Science* for acknowledgments of funding, help, etc.

\begin{scilastnote}
\item We've included in the template file \texttt{scifile.tex} a new
environment, \texttt{\{scilastnote\}}, that generates a numbered final
citation without a corresponding signal in the text.  This environment
can be used to generate a final numbered reference containing
acknowledgments, sources of funding, and the like, per {\it Science\/}
style.
\end{scilastnote}

% For your review copy (i.e., the file you initially send in for
% evaluation), you can use the {figure} environment and the
% \includegraphics command to stream your figures into the text, placing
% all figures at the end.  For the final, revised manuscript for
% acceptance and production, however, PostScript or other graphics
% should not be streamed into your compliled file.  Instead, set
% captions as simple paragraphs (with a \noindent tag), setting them
% off from the rest of the text with a \clearpage as shown  below, and
% submit figures as separate files according to the Art Department's
% instructions.

\clearpage

\noindent {\bf Fig. 1.} Please do not use figure environments to set
up your figures in the final (post-peer-review) draft, do not include graphics in your
source code, and do not cite figures in the text using \LaTeX\
\verb+\ref+ commands.  Instead, simply refer to the figure numbers in
the text per {\it Science\/} style, and include the list of captions at
the end of the document, coded as ordinary paragraphs as shown in the
\texttt{scifile.tex} template file.  Your actual figure files should
be submitted separately.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-09-15 2M1207ANALYSIS/JHtoy.py

@@ -1,0 +1,23 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+import matplotlib.pyplot as plt
+
+"""a toy model to show the JH band difference
+"""
+
+
+def changeRatio(tauRatio, length):
+    return np.exp(-(tauRatio - 1) * length)
+
+if __name__ == '__main__':
+    l = np.logspace(-1, 1, 20)
+    r = changeRatio(0.1, l)
+    plt.close('all')
+    plt.plot(l, r, '-', lw=2)
+    plt.gca().set_xscale('log')
+    plt.xlabel('Cloud Depth')
+    plt.ylabel('Amplitude$_{J}$/Amplitude$_{H}$')
+    plt.gca().set_ylim([1, 3])
+    plt.show()
+    plt.savefig('JHratio_toyModel.pdf')

### 2015-09-15 2M1207ANALYSIS/calJHMagRatio/calJHMag.py

@@ -11,9 +11,11 @@ def JHratio1(jlc, hlc, jerr, herr):
     jarg = np.argsort(jlc)
     harg = np.argsort(hlc)
     jlc = jlc[jarg]
-    jerr = jerr[jarg]  # relative uncertainty
+    # jerr = jerr[jarg]  # relative uncertainty
+    jerr = jlc * jerr
     hlc = hlc[harg]
-    herr = herr[harg]  # relative uncertainty
+    # herr = herr[harg]  # relative uncertainty
+    herr = hlc * herr
     Jmin = jlc[0:5].mean()  # mean value of maximum 5
     Jmin_err = (jerr[0:5]**2).mean()**0.5
     Jmax = jlc[-5:].mean()  # mean value of maximum 5
@@ -35,10 +37,10 @@ def JHratio1(jlc, hlc, jerr, herr):
 if __name__ == '__main__':
     M2139 = readsav('2MASSJ2139_spec_bin.sav')
     jh2139 = JHratio1(M2139['jlc'], M2139['hlc'],
-                      M2139['jlcerr'], M2139['hlcerr'])
+                      0.0027, 0.0027)
     S0136 = readsav('SIMP0136_spec_bin.sav')
     jh0136 = JHratio1(S0136['jlc'], S0136['hlc'],
-                      S0136['jlcerr'], S0136['hlcerr'])
+                      0.0011, 0.0011)
 
     M1821 = readsav('2m1821spectralratio.sav')
     min1821spec = M1821.minspec5est[M1821.xxx]

### 2015-09-15 2M1207ANALYSIS/plotJHratio.py

@@ -13,9 +13,10 @@ def chisq(y, mody, sigma):
 
 
 if __name__ == '__main__':
-    tgName, specType, specPos, JHratio, JH, ampJ, ampH, err = np.genfromtxt(
-        'JHratio.dat', delimiter=',', unpack=True, dtype=str
-    )
+    tgName, specType, specPos, JHratio, JH, ampJ, ampH, err, textPos\
+        = np.genfromtxt(
+            'JHratio.dat', delimiter=',', unpack=True, dtype=str
+        )
 
     specPos = np.float32(specPos)
     JHratio = np.float32(JHratio)
@@ -29,7 +30,8 @@ if __name__ == '__main__':
     cax = ax.scatter(
         specPos, JHratio, s=np.sqrt(ampJ) * 500, c=JH, cmap='coolwarm')
     cbar = fig.colorbar(cax)
-    ax.errorbar(specPos, JHratio, yerr=JHratio * err, color='k', ls='')
+    ax.errorbar(specPos, JHratio, yerr=JHratio * err, color='0.4', ls='',
+                elinewidth=2)
     cbar.set_label('J-H (mag)')
 #     plt.plot(specPos, JHDeltaMag, 's')
 #     plt.plot(5, -0.49, 'o', mec='b', mfc='none', ms=10, mew=1.5)
@@ -40,11 +42,11 @@ if __name__ == '__main__':
     ax.set_xticks([5, 10.5, 12, 16.5])
     ax.set_xticklabels(['L5', 'T0.5', 'T2', 'T6.5'])
     ax.set_xlabel('Spectral type')
-    ax.set_ylabel('Amptude$_{\mathrm{J}}$/Amptude$_{\mathrm{H}}$')
+    ax.set_ylabel('Amplitude$_{\mathrm{J}}$/Amplitude$_{\mathrm{H}}$')
 
     for i in range(len(specPos)):
         ax.text(
-            specPos[i] + 0.1, JHratio[i] + 0.02, tgName[i], fontsize=12)
+            textPos[i], JHratio[i] + 0.02, tgName[i], fontsize=12, zorder=10)
 
     # fig1, ax1 = plt.subplots()
     # ax1.plot(specPos, ampJ, '+', label='J', ms=12, mew=1.5)
@@ -59,11 +61,14 @@ if __name__ == '__main__':
     b, m, _, _, _ = linearFit(specPos, JHratio, err * JHratio)
[…]

### 2015-09-15 2M1207ANALYSIS/plotRotation.py

@@ -22,33 +22,47 @@ if __name__ == '__main__':
 
     ax_p.plot(mass[0], period[0], 's', ms=10)
     ax_p.plot(mass[1:], period[1:], 's', ms=10)
+    # ax_p.plot(mass[0], v_equ[0], 's', ms=10)
+    # ax_p.plot(mass[1:], v_equ[1:], 's', ms=10)
     ax_p.errorbar(
-        [0.00017, 0.00256], [25, 25], yerr=2, lolims=True, color='k', ls='')
-    ax_p.set_ylim(0, 30)
+        [0.00017, 0.00256], [26, 26], yerr=2.0,
+        lolims=True, color='k', ls='')
+    ax_p.errorbar(4, 10.05, xerr=1, yerr=2.9, color='k')
+    # ax_p.set_ylim(0, 30)
     # ax.arrow(x0, y0, 0, -0.3, fc='b', lw=0.2, head_width=0.05,
     # head_length=0.1)
 
     ax_p.set_xlabel('M (M$_{\mathrm{Jup}}$)')
     ax_p.set_ylabel('Period (hour)')
+    # ax_p.set_ylabel('Equatorial rotation velocity (km$\cdot$s$^{-1}$)')
     BDperiod = np.array([2.7, 1.55, 2.7, 3.8, 4.1, 3.2, 13,
                          2.5, 11, 3.9, 2.6, 4.2, 18, 19, 3.5, 1.41])
+    vBD = 2 * np.pi * (1 * 69911) / (BDperiod * 3600)
+    # suppose BD has period of 1 Mjup
     ax_p.plot(np.zeros(len(BDperiod)) + 30, BDperiod,
               'o', mec='k', mfc='none', ms=10)
+    # ax_p.plot(np.zeros(len(BDperiod)) + 30, vBD,
+    #           'o', mec='k', mfc='none', ms=10)
     ax_p.add_patch(patches.Rectangle((15, BDperiod.mean() - BDperiod.std()),
                                      35, 2 * BDperiod.std(),
                                      fc='0.8', alpha=0.8))
+    # ax_p.add_patch(patches.Rectangle((15, vBD.mean() - vBD.std()),
+    #                                  35, 2 * vBD.std(),
+    #                                  fc='0.8', alpha=0.8))
 
     for i in range(len(name)):
         if i == 4:
-            ax_p.text(mass[i] * 1.3, period[i] - 1.5, label[i])
[…]

### 2015-09-15 2M1207ANALYSIS/systematics.py

@@ -88,7 +88,7 @@ if __name__ == '__main__':
     points125, = ax125B.plot(df125['Time'], f125B0, '+',
                              ms=8, mec='0.8', zorder=0)
 
-    ax125B.set_title('F125W light curve')
+    ax125B.set_title('Validation Test: F125W')
     # remove the data from the first orbit
     df125 = df125[df125['ORBIT'] > 1]
     f125A0, f125B0 = normFlux(df125, normDither=True)
@@ -150,7 +150,7 @@ if __name__ == '__main__':
     line160_2, = ax160B.plot(t, modelFlux2, label='P=9.0', linewidth=1.8)
     points160, = ax160B.plot(df160['Time'], f160B0, '+',
                              ms=8, mec='0.8', zorder=0)
-    ax160B.set_title('F160W light curve')
+    ax160B.set_title('Validation Test: F160W')
     ax160B.legend()
 
     df160 = df160[df160['ORBIT'] > 1]

### 2015-09-25 summary/letter/_region_.tex
submitted

\message{ !name(letter_vAE.tex)}
\documentclass[apj]{emulateapj}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mbox{Jup}}$}
\begin{document}

\message{ !name(letter_vAE.tex) !offset(-3) }

\title{Discovery of Rotational Modulations in the Planetary-mass
  Companion 2M1207b: A Slow Rotation Period and Cloud Height in a Low
  Gravity Atmosphere}
\shorttitle{Variability of 2M1207 b}
\author{Yifan Zhou\altaffilmark{1}, D\'aniel Apai\altaffilmark{1,2,3},
  Glenn Schneider\altaffilmark{1},  Mark S. Marley\altaffilmark{4}}

\altaffiltext{1}{Department of Astronomy/Steward Observatory, The
  University of Arizona, 933 N. Cherry Ave., Tucson, AZ, 85721, USA,
  \href{mailto:yifzhou@email.arizona.edu}{yifzhou@email.arizona.edu}
}
\altaffiltext{2}{Lunar and Planetary Laboratory, The University of
  Arizona, 1640 E. University Blvd., Tucson, AZ 85718, USA}
\altaffiltext{3}{Earths in Other Solar Systems Team, NASA Nexus for
  Exoplanet System Science}
\altaffiltext{4}{NASA Ames Research Center, Naval Air Station,
  Moffett Field,Mountain View, CA 94035, USA}

\begin{abstract}
  Rotational modulations of brown dwarfs have recently provided
  powerful constraints on the properties of ultra-cool atmospheres,
  including longitudinal and vertical cloud structures and cloud
  evolution. Furthermore, periodic light curve directly probes the rotational periods of ultra-cool objects.

  We present here, for the first time, time-resolved high-precision
  photometric measurements of a planetary-mass companion, 2MASS1207b,
  to a brown dwarf primary.  We observed the binary system with
  HST/WFC3 in two bands and with two spacecraft roll angles. Using
  point spread function-based photometry we reach a nearly
  photon-noise limited photometric accuracy for both components. While
  the primary is consistent with a flat lightcurve, the secondary
  shows modulations that are clearly detected in the combined
  lightcurve as well as in different subsets of the data.  The
  amplitudes are 1.45\% in the F125W and 0.92\% in the F160W filters;
  we find a consistent period of $10.2^{+0.9}_{-0.8}$ h and similar
  phase in both bands. {\color{red}The relative amplitudes in the two filters are
    very similar to that found in a recent study of a field
    (high-gravity) L-dwarf, suggesting that the cloud structures that
    introduce the photometric modulations are similar in high- and
    low-gravity objects.} Importantly, our study also measures, for
  the first time, the rotational period for directly an imaged
  planetary-mass companion.
\end{abstract}

\keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
  and satellites: individual (2M1207 b) -- techniques: photometric}
\maketitle
%

\message{ !name(letter_vAE.tex) !offset(494) }

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-09-25 summary/letter/letter_vAD.tex
submitted

@@
 \usepackage{natbib}
+\usepackage{color}
 \bibliographystyle{apj}
@@
   Gravity Atmosphere}
-\shorttitle{Variability of 2M1207 B}
-\author{Yifan Zhou, Daniel Apai, Glenn Schneider}
-\affil{Steward Observatory, the University of Arizona}
-\author{Mark Marley}
-\affil{NASA Ames Research Center}
+\shorttitle{Variability of 2M1207 b}
+\author{Yifan Zhou\altaffilmark{1}, D\'aniel Apai\altaffilmark{1,2,3},
+  Glenn Schneider\altaffilmark{1},  Mark S. Marley\altaffilmark{4}}
+
+\altaffiltext{1}{Department of Astronomy/Steward Observatory, The
+  University of Arizona, 933 N. Cherry Ave., Tucson, AZ, 85721, USA,
+  \href{mailto:yifzhou@email.arizona.edu}{yifzhou@email.arizona.edu}
+}
+\altaffiltext{2}{Lunar and Planetary Laboratory, The University of
+  Arizona, 1640 E. University Blvd., Tucson, AZ 85718, USA}
+\altaffiltext{3}{Earths in Other Solar Systems Team, NASA Nexus for
+  Exoplanet System Science}
+\altaffiltext{4}{NASA Ames Research Center, Naval Air Station,
+  Moffett Field,Mountain View, CA 94035, USA}
 
@@
   including longitudinal and vertical cloud structures and cloud
-  evolution. Furthermore, detection of periodic light curve variations
-  can directly probe the rotational periods of ultra-cool objects.
+  evolution. Furthermore, detection of periodic light curve  can directly probe the rotational periods of ultra-cool objects.
 
@@
   photometric measurements of a planetary-mass companion, 2MASS1207b,
-  to a brown dwarf primary. Using HST/WFC3 and point spread
-  function %in
-  combination with two spacecraft roll angles we detect photometric
-  modulations in the light curve. The amplitude is 0.9\% in the F160W
-  and 1.5\% in the F125W filters; we find a consistent period and
-  similar phase in both bands. Joint fit to the light curve in both
-  bands suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative
-  amplitudes in the two filters are very similar to that found in a
-  recent study of a field (high-gravity) L-dwarf, suggesting that the
-  cloud structures that introduce the photometric modulations are
-  similar in high- and low-gravity objects. Importantly, our study
-  also measures, for the first time, the rotational period for
-  directly imaged planetary-mass companion.
+  to a brown dwarf primary. Using HST/WFC3 observation and point
+  spread function fitting photometry with two spacecraft roll angles,
+  we detect photometric modulations in the light curve. The amplitudes
+  are 1.45\% in the F125W and 0.92\% in the F160W filters; we find a
+  consistent period of $10.2^{+0.9}_{-0.8}$
+  h and similar phase in both bands by fitting sinusoids to the light curves. {\color{red}The relative amplitudes in the two filters are very similar to
+  that found in a recent study of a field (high-gravity) L-dwarf,
+  suggesting that the cloud structures that introduce the photometric
+  modulations are similar in high- and low-gravity
+  objects.} Importantly, our study also measures, for the first time,
+  the rotational period for directly an imaged planetary-mass companion.
 \end{abstract}
@@
 \keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
-  and satellites: individual (2M1207b) -- techniques: photometric}
+  and satellites: individual (2M1207 b) -- techniques: photometric}
 \maketitle
@@
 
-% Cloud properties in high- and low-gravity objects -- thick clouds: an
-% explanation for very red and faint near-infrared fluxes of directly
-% imaged planets
 Presence of condensate clouds is one the most unique and essential
-features of the ultra-cool atmosphere of direct imaged exoplanet and brown
-dwarfs. The formation and properties of condensate clouds of are
-intensively studied in recent years \citep[e.g.][]{Ackerman2001,
-  Helling2008, Allard2012}, and great improvement has been
-achieved in understanding the cloud behavior across different spectral
-types, especially in the explanation of L-T transition \citep{Marley2010}.
-Surface gravity is suggested to be another key parameters 
-in defining cloud structures. Low surface gravity objects (e.g. HR8799 bcd, 2M1207
-b) have significantly redder color compared to their spectral type
-matched brown dwarfs, which are best explained by the existence of 
-thick clouds \citep{Barman2011, Skemer2011, Skemer2012}. However, due to lack of observational constraint, the
-behavior of clouds in the atmospheres of low surface gravity objects
-are not as well as modeled as high surface gravity counterpart.
+features of the ultra-cool atmosphere of direct imaged exoplanet and
+brown dwarfs. The studies of formation and properties of condensate
+clouds \citep[e.g.][]{Ackerman2001, Burrows2006a, Helling2008,
+  Allard2012} have achieved great improvement in understanding the
+cloud behavior across different spectral types, especially in the
+explanation of L-T transition \citep[e.g.][]{Burrows2006a,
+  Marley2010}.  Surface gravity is suggested to be another key
+parameters in defining cloud structures besides spectral type. Low
+surface gravity objects (e.g. HR8799 bcd, \cite{Marois2008a}, 2M1207
+b, \cite{Chauvin2005}) show significantly redder color compared to
+their spectral type matched brown dwarfs.  The anomalous colors of low
+surface gravity objects are best explained by the existence of thick
+clouds \citep{Barman2011, Skemer2011, Skemer2012}. However, due to
+lack of observational constraint, the dependence of cloud properties
+on surface gravity is not very well modeled.
 
@@
 \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014,Metchev2015}. \cite{Kostov2013}
-demonstrated the great potential of these techniques in the study of the cloud properties of
-direct imaged exoplanets and planetary mass companions. However, high
-brightness contrast makes it much more challenging for direct
-imaged exoplanet and planetary mass companions than brown
-dwarfs to acquire high-precision light curves.
+demonstrated the great potential of these techniques in the study of
+the cloud properties of direct imaged exoplanets and planetary mass
+companions. However, high contrast magnifies
+the challenges for direct imaged exoplanets and planetary mass
+companions to acquire high-precision light curves comparing to brown dwarfs.
 
-2M1207 b \citep{Chauvin2005} is a planetary mass companion that has mass of
-$\sim 4M_{\mathrm{Jup}}$ and an angular separation of $0.78''$ to its host
-2M1207 A,
-an M8 brown dwarf. Relative moderate contrast (6.7 mag in J band, \cite{Mohanty2007}) makes it one
-the most feasible planetary mass companions for high-precision
-time-resolved observation and the best starting points for developing
-strategies for time-resolved observation and data reduction in high
-contrast case.
+2M1207 b is a planetary mass companion that has mass of
+$\sim 2.3-4.8M_{\mathrm{Jup}}$ \citep[][]{Barman2011} and an angular separation of $0.78''$ to its
+host 2M1207 A, an M8 brown dwarf. Moderate contrast  \citep[6.7 mag
+in J-band,][]{Mohanty2007} makes it one the most feasible
+planetary mass companions for high-precision time-resolved observation.
 
@@
 
-We obtained direct images of the 2M1207A+b
-system on UT 2014 April 11from 08:07:47 to 16:53:18 using HST and its Wide Field Camera 3 \citep[WFC3,
-][]{Kimble2008} in the frame of the HST Proposal GO-13418 (PI:
-D. Apai). We acquired the observations in filters F125W
-($\lambda_{\mbox{pivot}}$ = 1245.9 nm, full width at half maximum
-(FWHM) = 301.5 nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM =
-287.9 nm), roughly corresponding to the J and H bands. The WFC3 pixel
-scale is $\approx$13mas. We used the $256\times256$ pixels sub-array
-mode to avoid memory dumps during the observations.  In order to
-provide a near-continuous coverage for detecting modulations we
-observed the 2M1207 system in six consecutive HST orbits, obtaining
+We obtained direct images of the 2M1207A+b system on UT 2014 April 11
+from 08:07:47 to 16:53:18 using HST and its Wide Field Camera 3
+\citep[WFC3, pixel scale=$\sim0.13''$, ][]{Kimble2008} in the frame of
+the HST Proposal GO-13418 (PI: D. Apai). We acquired the observations
+in filters F125W ($\lambda_{\mathrm{pivot}}$ = 1245.9 nm, full width
+at half maximum (FWHM) = 301.5 nm) and F160W
+($\lambda_{\mathrm{pivot}}$ 1540.52, FWHM = 287.9 nm), roughly
+corresponding to the J and H bands. We used the $256\times256$ pixels
+sub-array mode to avoid memory dumps during the observations.  In
+order to provide a near-continuous coverage for detecting modulations
+we observed the 2M1207 system in 6 consecutive HST orbits, obtaining
 data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
@@
 allow roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
-telescope roll angles for orbits 1, 3, and 5, and those taken in
-orbits 2, 4, and 6 differed by $25^{\circ}$. At the separation of
-2M1207b this angle difference corresponds to a displacement of
-$0.34''$ or 2.75 and 2.30 resolution elements in F125W and F160W,
-respectively. In each orbit we took thirteen SPARS10 non-destructive
-read-outs with NSAMP=10, alternating between F160W and F125W filters,
-with 2--3 identical exposures in one exposure sequence. To improve
-sampling and reduce the risk that point spread funciton (PSF) lays on
-bad pixels, we applied a 4-point dither pattern with differential "X/Y"
-offsets of 1.375" in the detector frame, providing optimal
-non-integral (half pixel) stepping of 10.5 and 8.5 pixels in F125W and
-F160W, respectively. Over the 6 orbits, we obtained 70 images with 10
-non-destructive read-outs in F125W and 64 images in F160W with
-exposure time of 88.4~s in each filters.
+telescope roll angles for orbit 1, 3, and 5, and those for 2, 4, and
+6 differ by $25^{\circ}$. At the separation of 2M1207 b, this angle
+difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
+resolution elements in F125W and F160W, respectively. In each orbit we
+took 8 SPARS10 exposure sequence with NSAMP=10,
+alternating between F160W and F125W filters, with 2--3 identical
+exposures in one exposure sequence. To improve sampling and reduce the
+risk that point spread function (PSF) lays on bad pixels, we applied a
+4-point dither pattern with differential "X/Y" offsets of 1.375" in
+the detector frame, providing optimal non-integral (half pixel)
+stepping of 10.5 and 8.5 pixels in F125W and F160W, respectively. Over
+the 6 orbits, we obtained 70 images with 10 non-destructive read-outs
+in F125W and 64 images in F160W with exposure time of 88.4~s for both
+filters.
 
@@
 
-%Although \cite{Mandell2013} stated that WFC3 IR time series
-%extract from {\flt} have a rms 1.3 times larger than that obtained
-%from {\ima}, \flt keeps all pixels of the image of 2M1207 A
-%unsaturated, while in 80\% of non-destructive reads the cores of
-%2M1207 A are saturated. 
-%Thus \flt help better align the images for
-%primary subtraction, and separate the flux of 2M1207 B from that of
-%2M1207A.
-
-%The small angular separation of 2M1207 A and B (as shown in Figure
-%\ref{fig:1}) makes precise primary star subtraction and photometry
-%very difficult. 
-%On the under-sampled WFC3 IR detector (plate scale
-  %$\sim 0.13''\mbox{pixel}^{-1}$ \cite{dressel2012wide}), the primary
-%and the secondary only separate by $\sim 6$ pixels, which is about 5
-%times of the FWHM of the PSF. In addition, under-sampling causes
-%significant artifacts when shifting the images for registration no
-%matter what interpolation method is used.
  \begin{figure*}
@@
     squares) are plotted with different symbols. They demonstrate same
-    trend of variation. In upper left panel, green line is sinusoidal
+    trend of modulation. In upper left panel, green line is sinusoidal
     wave fitted with all parameter set free, and purple line is
@@
     curves plotted in upper panel. {\em Lower}: photometry measured
-    with AFEM-added images and best fitted sinusoidal curves. These
+    with AFEM-added images and best fitted sinul curves. These
     points and curves are also almost identical to those plotted
@@
 
-We started the reduction from the the \flt files produced by the
-WFC3's \texttt{calwfc3} pipeline. We did not opt to use the more
-advance \ima pipeline products because these provided less information
-on 2M1207A, which saturated after the first few read-outs.  The \flt
+We start the reduction from the \flt{} produced by the WFC3's
+\texttt{calwfc3} pipeline. We do not opt to use \ima{} that contain
+all non-destructive read-outs, because these provided less information
+on 2M1207A, which saturated after the first few samples.  The \flt{}
 are results of basic calibration, including dark current correction,
 non-linearity correction, flat field correction, as well as
-up-the-ramp fit on the non-destructive read-outs also considering
-cosmic rays. From the beginning, pixels with data quality flags ``bad
-detector pixels'', ``unstable response'', and ``bad
-or uncertain flat value'' were masked out and excluded from
-further analysis as suggested by previous transit exoplanet
-spectroscopic observations\citep[e.g.][]{Berta2012, Kreidberg2014}.
+up-the-ramp fit on the non-destructive read-outs. From the beginning,
+pixels with data quality flags ``bad detector pixels'', ``unstable
+response'', and ``bad or uncertain flat value'' are masked out and
+excluded from further analysis as suggested by previous transit
+exoplanet spectroscopic observations\citep[e.g.][]{Berta2012,
+  Kreidberg2014}.
 
@@
 only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF. When
-applying roll subtraction, notable artifact structures are generated
-by image interpolation and shifting. On the other hand, \tinytim{} PSF
+applying roll subtraction, notable artifacts are generated
+by image shifting and interpolation. On the other hand, \tinytim{} PSF
 simulator\citep{Krist1995} offers a solution by providing Nyquist or better
@@
 PSFs with 6 orbits time-resolved observation data. To obtain robust \tinytim{} PSF
-photometry, we designed a 2-round PSF fitting strategy: 1. calculating
+photometry, we design a 2-round PSF fitting strategy: 1. calculating
 correction map for \tinytim{}; 2. hybrid PSF photometry.
 
-For both of 2 rounds, we used {\em Tiny Tim} to calculate 10$\times$
+For both of 2 rounds, we use \tinytim{} to calculate 10$\times$
 over-sampled model PSFs based on the filters, the spectra
 \citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
-the telescope jitter.  We used the new set of Tiny Tim parameters
-provided by \cite{Biretta2014} to improve model of the cold mask,
-OTA spikes, and the coma. The focus parameters were calculated
-using the model listed on the STScI
-website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. To
-register \tinytim{} PSF to observed PSF of 2M1207A, we moved the
-over-sampled PSF over a coordinate grid (gird size=0.001 pixel) using
-cubic interpolation and minimize the rms difference of the
-observed and re-binned \tinytim{} PSFs over a region centered on 2M1207A with a
-5-pixel-radius aperture centered on 2M1207b excluded. Then we introduce
-another \tinytim{} PSF for 2M1207b and  fit the
-position of 2M1207 b and the photometries of 2M1207 A and b simultaneously
-by least square optimization. From our data set, we discovered that
-the difference of observed PSFs and model PSFs were very stable for
-given PSF positions. Therefore, at the end of the first round PSF
-fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
-observationally derived correction maps for each filter:
+the telescope jitter.  We use the set of \tinytim{} parameters
+provided by \cite{Biretta2014} to improve modeling  the cold mask, OTA
+spikes, and the coma. The focus parameters are calculated using the
+model listed on the STScI
+website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
+To register the \tinytim{} PSF to the observed PSF of 2M1207 A, we move the
+over-sampled PSF on a coordinate grid (gird size=0.001 pixel) using
+cubic interpolation, and search for the position that minimizes the
+rms difference of the observed and re-binned \tinytim{} PSFs over a
+region centered on 2M1207 A with a 5-pixel-radius aperture centered on
+2M1207 b excluded.  Then we introduce another \tinytim{} PSF for
+2M1207 b and fit the position of 2M1207 b and the scales of the
+/tinytim{} PSFs of 
+2M1207 A and b simultaneously with least square optimization. From the
+first round fit, we discover that the difference of observed PSFs and model
+PSFs are very stable for given PSF positions. Therefore, at the end
+of the first round PSF fitting, we derive 8 (2 roll angles $\times$ 4
+dithering positions)  correction maps for each
+filter:
 \begin{equation}
@@
 where $\mathrm{PSF_{model}}$ is a combination of two \tinytim{} PSFs
-for 2M1207 A and b. In the second round, we combined the correction
+for 2M1207 A and b. In the second round, we combine the correction
 term linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
-and fitted the three components together. We found that by including the correction term,
+and fit the three components together. We find that by introducing the correction term,
 the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
-around unity. Relative photometry is acquired from the scaling
-parameters of the model PSFs.
+$\sim 1$. Relative photometry is acquired from the scaling
+parameters of the \tinytim{} PSFs.
 
@@
 under-sampled. Also, the flat fields may potentially have large scale
-structures \citep{dressel2012wide}. We found a correlation of
+structures \citep{dressel2012wide}. We find a correlation of
 photometry with PSF positions on detector frame for both 2M1207 A and
-b. Correction were made by normalizing each group of
-exposures that have the same dithering position and roll angle
-individually -- we took the median of the fluxes that were measured
+b. Correction is made by normalizing each group of
+exposures that have the same dithering position and telescope roll angle
+individually -- we take the median of the fluxes that are measured
 from these exposures as normalization factors and divided them from
 every photometric measurement. Because the normalization factor for
-each group of exposures is calculated across the whole observation,
-this normalization step has negligible impacts on variability
+each group of exposures is calculated across the whole observation in
+time domain,
+this step has negligible impacts on variability
 analysis.
@@
 
-First we estimated the photon noises for the photometry of 2M1207b. We
-propagated the photon noises of every single pixel that were
-calculated from count rates and detector gain, to the PSF fitting
-results. The photon noises for photometry in F125W and F160W are
-1.33\% and 1.02\%, respectively.
+First we estimated the photon noises for the photometry of
+2M1207b. The total photon noise of the photometry is calculated by
+combining the photon noise of every single pixel that is calculated
+from count rates and detector gain. The photon noises for photometry
+in F125W and F160W are 1.33\% and 1.02\%, respectively.
 
-Since the PSFs for the 2M1207 A and b were fitted simultaneously in the
-PSF photometry procedure, the uncertainties of photometry and position
-for the primary and secondary are coupled. Imperfection of position
-measurement of 2M1207A could potentially affect the photometry of
-2M1207b. We used a Monte Carlo (MC) method to
-evaluate the overall systematic of the PSF fitting. We applied the
-PSF photometry to images that were added with random Poisson noises and
-repeat the photometry procedure for 1000 times. From the distribution of the
-result, the uncertainty for F125W and F160W photometry are 
-1.34\% and 1.12\%, respectively. We conclude that the white noise of
-our observation is dominated by photon noise.
+Since the PSFs for the 2M1207 A and b are fitted simultaneously, the
+uncertainties of photometry and position for the primary and secondary
+are coupled. Imperfection of position measurement of 2M1207 A could
+potentially significantly affects the photometry of 2M1207 b. We used a Monte Carlo
+(MC) method to evaluate the overall systematic of the PSF fitting. We
+applied the PSF photometry to images that were added with random
+Poisson noises and repeat the photometry procedure for 1000
+times. From the distribution of the result, the uncertainties for F125W
+and F160W photometry are 1.34\% and 1.12\%, respectively. We conclude
+that the white noise of our observation is dominated by photon noise.
 
@@
 
-2M1207b were observed at 8 different spots on the
+2M1207 b were observed at 8 different spots on the
 detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
-field correction are potential sources of variation as they may
-introduce position-dependent differences in the count rates. The
+field correction can potentially introduce position-dependent differences in the count rates. The
 uncertainty of WFC3 IR pipeline flat field is typically $\sim 1\%$
@@
 In PSF photometry, however, multiple pixels are fitted simultaneously
-and we expect a lower than 1\% uncertainty from the flat field
+and we expect to be less affected by high spatial frequency flat field
+noise, and a lower than 1\% uncertainty from the flat field
 errors. To verify this, we multiplied every image by an artificial flat
@@
 errors do not affect our photometry significantly (Figure
-\ref{fig:2}).
+\ref{fig:2}, bottom panel).
 
-\section{Verification of Photometric Variations and Amplitude
+\section{Verification of Photometric Modulations and Amplitude
   Estimate}
@@
 
-The light curves that resulted from our photometry show apparently
+The light curves that result from our photometry show apparently
 sinusoidal modulations, discussed in more details in
 \S,\ref{Results}. To verify that these modulations are intrinsic to
-the object and not result of our data reduction procedure or due to
-instrumental changes, we carried out three different tests.
+the object and not results of our data reduction procedures or due to
+instrumental changes, we carry out three different tests.
 
-First, we fitted sine waves independently to the two filters to verify
-the similarity of the signal in the two bands (Figure \ref{fig:2}). Inconsistent periods or
-light curve shapes would argue against a genuine signal.  We found
+First, we fit sinusoids independently to the light curves of two filters to verify
+the similarity of the signal in the two bands (Figure \ref{fig:2}, top
+panel). Inconsistent periods or
+light curve shapes would argue against a genuine signal.  We find
 that the periods of the best fit sine waves are similar,
@@
 
- As a second test we repeated the analysis neglecting the first
- orbit. The motivation behind this test was that, due to spacecraft
- thermal settling, the first orbit of HST observations is often
- slightly unstable and is often neglected in high-precision studies
- (\textbf{citation?}). Indeed, in our analysis 2M1207 A is
+As a second test, we repeat the analysis neglecting the first
+orbit. The motivation behind this test is that, due to spacecraft
+thermal settling, the first orbits of HST observations are often
+slightly unstable, and neglected in high-precision studies
+\citep[e.g.][]{Mandell2013}. Indeed, in our analysis 2M1207 A is
 significantly fainter in the first orbit (Figure \ref{fig:3}) than in
- the subsequent ones.
- Our analysis based on orbits 2--6 only found essentially identical
- results to our analysis of orbits 1--6, based on which we conclude
- that the first less reliable orbit does not affect our results
- significantly (Figure \ref{fig:2}, middle panel).
+the subsequent ones.  Our analysis based on orbits 2--6 finds
+essentially identical results to our analysis using the whole 6 orbits, based on
+which we conclude that the first less reliable orbit does not affect
+our results significantly (Figure \ref{fig:2}, middle panel).
 
-As a third test we explored whether a subset of images, perhaps
+As a third test, we explore whether a subset of images, perhaps due to
 imperfectly normalized or correlated with specific instrument states,
-could be driving the light curves into an apparently sinusoidal
-shape. To test this possibility we split the data into two temporally
-overlapping halves: sub-dataset one from dithering positions 1 and 3,
-and sub-dataset two from dithering positions 2 and 4. For both
-datasets we repeated our analysis independently.  For both of F125W
-and F160W, two halves demonstrated similar trend of variability as
-shown in Figure \ref{fig:2}.  Our analysis detected sinusoidal
-modulations in {\em both} sub-datasets and in {\em both} filters, with
-periods and amplitudes consistent with those derived from the complete
-data set (\ref{fig:2}, upper panel).
+can drive the light curves into an apparently sinusoidal shape. To
+test this possibility, we split the data into two temporally
+overlapping halves: subset one are images taken at dithering position
+1 and 3, and subset two are those taken at dithering position 2 and
+4. For both data-sets, we repeated our analysis independently.  For
+both of F125W and F160W, two halves demonstrated similar trend of
+variability.  Our analysis detect sinusoidal modulations in {\em
+  both} subsets and in {\em both} filters, with periods and
+amplitudes consistent with those derived from the complete data set
+(Figure \ref{fig:2}, upper panel).
 
@@
  segments of the data, and in data obtained in different dithering
- positions.
+ positions. All of the three tests support the modulation signal to be
+ intrinsic to the target.
 
@@
 
-To constrain the uncertainties of the least square optimization
-results, we used a MC method to improve the fitting. We
-generated a series of random Gaussian noises with the standard deviation same as
-the photon noise, added them to the original light curves, and applied
-least square fit to the new light curves. We repeated above routine for 100,000 times and obtained
-the distribution of the fitting parameters. The distributions for the
-periods and the amplitudes for F125W and F160W light curves are
-shown in Figure \ref{fig:4}.
+We use a MC method to analyze the light curve, and provide amplitudes
+and periods as well as their uncertainties for both filters. We
+generate series of random Gaussian noises with the standard deviation
+same as the photon noises, add them to the original light curves, and
+fit sinusoids to the newly combined light curves. We repeat above
+routine for 100,000 times and obtain the distribution of the fitting
+parameters (Figure \ref{fig:4}).
 
 \section{Result}
+\label{Results}
 
-\label{Results}
-We present the first  high-resolution, high-cadence, and
-high-precision photometry of a directly imaged planet or
-planetary-mass companion. Our observations reveal a modulation in the
-light curve of the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
-of modulations in directly imaged planetary mass objects.  The best fit
-periods for F125W and F160W are 10.5 and 9.1 hour correspondingly. The
-amplitudes for the normalized light curves are 1.45\% and 0.92\% for
-F125W and F160W light curves.
+We present the first high-resolution, high-cadence, and high-precision
+photometry of a directly imaged planet or planetary-mass
+companion. Our observations reveal a modulation in the light curve of
+the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
+of modulations in directly imaged planetary mass objects.  The best
+fitted periods for F125W and F160W are 10.5 and 9.1 hour,
+respectively. The modulation amplitudes for the normalized light
+curves are 1.45\% and 0.92\% for F125W and F160W light curves.
 
-We obtained high signal to noise photometry series for both 2M1207 A
+We obtain high signal to noise photometry series for both 2M1207 A
 and B (Figure \ref{fig:3}). On average, the photometric contrast is
-$6.52\pm0.01$ mag for
-F125W and $5.77\pm0.01$ mag for F160W. The difference of F125W contrast
-from that measured in J-band \citep{Mohanty2007} and
-F160W contrast from that measured with NICMOS F160W 
-\citep{Song2006} is due to the different throughput profiles of the
-filters.
+$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W. The
+difference of F125W contrast from that measured in J-band
+\citep{Mohanty2007} and F160W contrast from that measured with NICMOS
+F160W \citep{Song2006} is due to the different throughput profiles of
+the filters.
 
@@
 long period, with core region roughly Gaussian. With 64\% confidence,
-we estimated the 1-$\sigma$ range for the periods of F125W and F160W
+we estimate the 1-$\sigma$ range for the periods of F125W and F160W
 to be $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ h,
-respectively. The period of best fitted sine wave of F125W light
-curve is 1.5h longer than that of F160W, and 0.3--0.4 h larger
-1-$\sigma$ standard deviation. We also jointly fit the two band light
-curves together forcing the periods of two sinusoids to be the
-same. We derived a modulation period of $10.2^{+0.9}_{-0.8}$ h.
+respectively. The period of best fitted sinusoid for F125W light curve
+is 1.5h longer than that for F160W, which is $\sim 20\%$ larger than
+1-$\sigma$. We also jointly fit the two band light curves forcing the
+periods of two sinusoids to be the same. We derive a modulation period of $10.2^{+0.9}_{-0.8}$ h.
 
-We discover that the variation amplitudes in the two bands are significantly
+We discover that the modulation amplitudes in the two bands are significantly
 different. By fitting Gaussians to the MC fit result distributions, we
-determined that variation amplitude of F125W is 1.45\% with a
+determine that modulation amplitude of F125W is 1.45\% with a
 standard deviation of 0.22\%, and that of F160W is 0.92\% with a
 standard deviation of 0.20\%. The peaks of the two
-histograms separate by more than 2-$\sigma$. The variation amplitude
-for F125W is 1.58 times of that of F160W light curve.
+histograms separate by more than 2-$\sigma$. The modulation amplitude
+for F125W is 1.58 times of that for F160W light curve.
 
@@
   \plottwo{rotationDiagram}{JH}
-  \caption{comparison of 2M1207's rotation period and color change with brown
-    dwarfs, \bpic{} b, and solar system planets. {\em Left}: period vs. mass
-  plot for 2M1207b (red square), solar system planets and \bpic{} b
-  (blue squares), and brown dwarfs (black circles, gray shade). The mass of brown
-  dwarfs are assumed to be 30 \mjup{}. The gray rectangle that has
-a  $\pm$15 \mjup range in $x$, and a $\pm \sigma$ of brown dwarf
-periods range in $y$, indicates a
-region where brown dwarfs most likely to appear in this
-diagram. Rotation period monotonically decreases with the increase of
-mass. {\em Right}: ratio
-of variation amplitude in J and H band vs. spectral type for 2M1207b
-and brown dwarfs. The colors of the points represent J$-$H magnitude,
-and the sizes of the points are proportional to the J band variation
-amplitudes. The gray dashed line is the result of a linear fit to
-these points. Tight linear correlation of J- and H-band variation ratio
-and spectral type is demonstrated in this diagram.}
-x \label{fig:5}
+  \caption{comparison of 2M1207's rotation period and color change
+    with brown dwarfs, \bpic{} b, and solar system planets. {\em
+      Left}: period vs. mass plot for 2M1207 b (red square), solar
+    system planets and \bpic{} b (blue squares), and brown dwarfs
+    (black circles, gray shade). The mass of brown dwarfs are assumed
+    to be 30 \mjup{}. The gray rectangle that has a $\pm$15 \mjup
+    range in $x$, and a $\pm \sigma$ of brown dwarf periods range in
+    $y$, indicates a region where brown dwarfs most likely to appear
+    in this diagram. Rotation period monotonically decreases with the
+    increase of mass. {\em Right}: ratio of modulation amplitude in J
+    and H band vs. spectral type for 2M1207b and brown dwarfs. The
+    point for 2M1207 b is shifted to +$x$ for half spectral type for
+    clarification.  The colors of the points represent J$-$H
+    magnitude, and the sizes of the points are proportional to the
+    J-band modulation amplitudes. The gray dashed line is the result
+    of a linear fit to these points. Tight correlation of J- and
+    H-band modulation amplitude ratio and spectral type is shown.}
+ \label{fig:5}
 \end{figure*}
@@
 left panel of Figure~\ref{fig:5} we compare the rotation period of
-2M1207b to the solar system planets, \bpic b the only other directly
-imaged planet with an estimated period and measured {\em v sin i}, and
+2M1207 b to the solar system planets, \bpic{} b the only other directly
+imaged planet with an estimated period and measured \vsini, and
 field brown dwarfs from the study of \citep[][]{Metchev2015}.  The
-study by \citep[][]{Snellen2014} succeeded in measuring {\em v sin i}
-for \bpic b and demonstrated that it fits a trend defined by Solar
+study by \citep[][]{Snellen2014} succeeded in measuring \vsini{} 
+for \bpic{} b and demonstrated that it fits a trend defined by Solar
 System planets in which more massive planets have faster rotation
-rates. The interesting finding that \bpic b, an exoplanet that formed
+rates. The interesting finding that \bpic{} b, an exoplanet that formed
 in a protoplanetary disk, follows this trend suggests a possibly
@@
 period that fits in the same trend, as well as majority of brown
-dwarfs.  We note that 2M1207 b is most likely formed in the same way as
-brown dwarfs by gravitational fragmentation. The result that objects
-formed in different scenarios share the same trend of period vs. mass suggests that
-rotation periods -- in absence of well-determined ages -- are not good tracers of the formation pathways and
-may not contribute important evidence for a formation in a disk vs. in
-a cloud core environment.
-{\em Add younger BDs and this may change}
+dwarfs.  We note that 2M1207 b is most likely formed in the same way
+as brown dwarfs by gravitational fragmentation. The result that
+objects formed in different scenarios share the same trend of period
+vs. mass suggests that rotation periods -- in absence of
+well-determined ages -- are not good tracers of the formation pathways
+and may not contribute important evidence for a formation in a disk
+vs. in a cloud core environment.
+%{\em Add younger BDs and this may change}
 % Excitingly, our measurement of the rotation period demonstrates that
@@
 We find a tight correlation between the spectral type of the object
-and the J- to H-band variation amplitude ratio. In the right panel of
-Figure \ref{fig:5}, we demonstrate that earlier spectral type
-objects, independent of their surface gravity, have larger variations
-at shorter wavelength than at longer wavelengths. Importantly,
-although the J$-$H color of 2M1207b is significantly redder, its
-relative variation amplitude ratio is almost identical to the matching
+and the J- to H-band modulation amplitude ratio. In the right panel of
+Figure \ref{fig:5}, we demonstrate that earlier spectral type objects,
+independent of their surface gravity, have larger amplitudes at
+shorter wavelength than at longer wavelengths. Importantly, although
+the J$-$H color of 2M1207b is significantly redder, its relative
+modulation amplitude ratio is almost identical to the matching
 spectral type mid-L dwarf 2M1821.
 
-This trend can be qualitatively explained using the toy model proposed
+{\color{red}This trend can be qualitatively explained using the toy model proposed
 in \cite{Yang2014} within the spectral type range of mid-L to L-T
@@
 that they share similar J- and H-bands light curve amplitude ratio.
-
-%The
-%two processes that atmosphere opacity at certain pressure level
-%enhances and the cloud thickness increases with the decrease of surface
-%gravity have to counterbalance with each other to maintain the optical
-%depth of the cloud upper layer.
+The
+two processes that atmosphere opacity at certain pressure level
+enhances and the cloud thickness increases with the decrease of surface
+gravity have to counterbalance with each other to maintain the optical
+depth of the cloud upper layer.}
 
 \section{Conclusions}
-In summary, from our J- and H-band high precision, high-cadence
-light curves we discovered sinusoidal modulations in the planetary mass
+In summary, from our J- and H-band high precision, high-cadence light
+curves we discovered sinusoidal modulations in the planetary mass
 object 2M1207b. This is the first detection of rotational modulations
 in a directly imaged planetary mass object.  The period is
-$10.2^{+0.9}_{-0.8}$,  similar to that derived from {\em v sin i}
+$10.2^{+0.9}_{-0.8}$, similar to that derived from \vsini{} 
 measurements for the direct imaged exoplanet \bpic{} b and
@@
 new window on directly imaged exoplanets and planetary-mass
-companions. Our study demonstrates a successful application of high-cadence,
-high-precision, high-contrast photometry with planetary mass
-companion. We also show that these observations can be carried out simultaneously
-at multiple wavelengths, allowing us to prove multiple pressure
-levels. With observation of a larger sample and at multiple wavelengths, we will be
-able to explore the detailed structures of atmospheres of directly
-imaged exoplanets, and identify the key parameters that determine these.
+companions. Our study demonstrates a successful application of
+high-cadence, high-precision, high-contrast photometry with planetary
+mass companion. We also show that these observations can be carried
+out simultaneously at multiple wavelengths, allowing us to prove
+multiple pressure levels. With observation of a larger sample and at
+multiple wavelengths, we will be able to explore the detailed
+structures of atmospheres of directly imaged exoplanets, and identify
+the key parameters that determine these.
 

### 2015-09-25 summary/letter/letter_vAE.tex
submitted

\documentclass[apj]{emulateapj}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mbox{Jup}}$}
\begin{document}

\title{Discovery of Rotational Modulations in the Planetary-mass
  Companion 2M1207b: A Slow Rotation Period and Heterogeneous Clouds in a Low
  Gravity Atmosphere}
\shorttitle{Variability of 2M1207 b}
\author{Yifan Zhou\altaffilmark{1}, D\'aniel Apai\altaffilmark{1,2,3},
  Glenn Schneider\altaffilmark{1},  Mark S. Marley\altaffilmark{4}}

\altaffiltext{1}{Department of Astronomy/Steward Observatory, The
  University of Arizona, 933 N. Cherry Ave., Tucson, AZ, 85721, USA,
  \href{mailto:yifzhou@email.arizona.edu}{yifzhou@email.arizona.edu}
}
\altaffiltext{2}{Lunar and Planetary Laboratory, The University of
  Arizona, 1640 E. University Blvd., Tucson, AZ 85718, USA}
\altaffiltext{3}{Earths in Other Solar Systems Team, NASA Nexus for
  Exoplanet System Science}
\altaffiltext{4}{NASA Ames Research Center, Naval Air Station,
  Moffett Field,Mountain View, CA 94035, USA}

\begin{abstract}
  Rotational modulations of brown dwarfs have recently provided
  powerful constraints on the properties of ultra-cool atmospheres,
  including longitudinal and vertical cloud structures and cloud
  evolution. Furthermore, periodic light curve directly probes the rotational periods of ultra-cool objects.

  We present here, for the first time, time-resolved high-precision
  photometric measurements of a planetary-mass companion, 2MASS1207b,
  to a brown dwarf primary.  We observed the binary system with
  HST/WFC3 in two bands and with two spacecraft roll angles. Using
  point spread function-based photometry we reach a nearly
  photon-noise limited photometric accuracy for both components. While
  the primary is consistent with a flat lightcurve, the secondary
  shows modulations that are clearly detected in the combined
  lightcurve as well as in different subsets of the data.  The
  amplitudes are 1.45\% in the F125W and 0.92\% in the F160W filters;
  we find a consistent period of $10.2^{+0.9}_{-0.8}$ h and similar
  phase in both bands. The J- and H-band amplitude ratio of 2M1207 bis very
  similar to a field brown dwarf that has identical spectral type but
  different J-H color.  Importantly, our study also measures, for
  the first time, the rotational period for directly an imaged
  planetary-mass companion.
\end{abstract}

\keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
  and satellites: individual (2M1207 b) -- techniques: photometric}
\maketitle
%
\section{Introduction}

\begin{figure*}
  \centering
  \plottwo{original}{subtracted}
  \caption{Point spread function subtraction allows isolating the
    secondary and accurately measuring its brightness in our WFC3
    F160W images. {\em Upper}: original image, the position of 2M1207
    b is indicated by a white circle.  {\em Lower:} residual image --
    after the subtraction of the hybrid PSF, 2M1207 b is detected at a
    high significant level.}
  \label{fig:1}
\end{figure*}

Presence of condensate clouds is one the most unique features of the
ultra-cool atmosphere of directly imaged exoplanet and brown
dwarfs. Studies of formation and properties of condensate clouds
\citep[e.g.][]{Ackerman2001, Burrows2006a, Helling2008, Allard2012}
have achieved great improvement in understanding the cloud behavior
across different spectral types, especially in the explanation of L-T
transition \citep[e.g.][]{Burrows2006a, Marley2010}.  Surface gravity
is suggested to be the second key parameters in defining cloud
structures \citep[e.g.][]{Marley2012} after effective temperature. Low
surface gravity objects (e.g. HR8799 bcd, \cite{Marois2008a}, 2M1207
b, \cite{Chauvin2004}) are significantly redder and under-luminous
compared to brown dwarfs.  The anomalous color and luminosity of low surface gravity
objects supports model including unusually thick clouds
\citep{Currie2011, Madhusudhan2011,Skemer2011, Skemer2012}. However, due to lack of observational
constraint, the dependence of cloud properties on surface gravity is
not very well modeled.

Intensity modulations introduced by heterogeneous clouds can be
directly observed and studied via time resolved observation and
rotational mapping. These techniques isolate the effect of cloud
properties and obtained great success in determining the rotation
period and unveiling the structures of the atmosphere of brown dwarfs
\citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014,Metchev2015,Heinze2015}. \cite{Kostov2013}
demonstrated that these techniques can be applied to directly imaged
exoplanets, too, allowing comparative studies of objects with
different surface gravities. However, high contrast magnifies the
challenges for directly imaged exoplanets and planetary-mass
companions to acquire high-precision light curves comparing to brown
dwarfs.

  2M1207 b \cite{Chauvin2004} is the first directly imaged
planetary-mass companion. \cite{Chauvin2005,Song2006} confirmed that 2M1207 b and
its host 2M1207 A form a bound, co-moving system. 2M1207 A and
b have an angular separation of $0.78''$, which is corresponding to a
projected separation of 41.2 AU at a distance of 52.4 pc
\citep[e.g.][]{Ducourant2008}. Combining 2M1207 b's age and near infrared
luminosity with  brown dwarf cooling models
\citep[e.g.][]{Baraffe2003}, the object's mass is estimated to be
2.3-4.8 M$_{\mathrm{Jup}}$ \citep{Barman2011b}. Even though a
circumsubstellar disk was discovered around 2M1207A
\citep[][]{Sterzik2004}, the high companion-to-host
mass ratio and large separation argue for binary-like gravitational fragmentation
formation\citep{Mohanty2007}.

Early observations revealed that 2M1207 b's color is much redder and
its near-infrared luminosity is much lower than those of field brown
dwarfs with similar spectra\citep[e.g][]{Mohanty2007, Skemer2011,
  Barman2011b}. 2M1207b's luminosity -- as derived from near-infrared
photometry -- is $\sim2.5$ mag lower than that predicted based on its
mid- to late L spectral type and effective temperature of $\sim 1600$
\citep{Patience2010}.  Based multi-band near-infrared photometry
\citet{Skemer2011} argued that the apparent under-luminosity of 2M1207
b may be explained by a model of a spatially heterogeneous atmosphere
composed of patches of thin and patches of unusually thick clouds.
Similarly, \cite{Barman2011b} argued that non-local chemical
equilibrium could play an equally important role as thick clouds in
defining 2M1207b's color and luminosity.

The discovery of additional planetary-mass companions with similarly
red colors and apparent under-luminosity have highlighted 2M1207b as a
template of low gravity ultra-cool atmospheres but as of now
understanding the composition and structure of clouds and their
gravity-dependence remained elusive.

In this {\em Letter} we present the first, high-cadence,
high-precision, time-resolved {\em Hubble Space Telescope} (HST)
photometric time series of 2M1207 b, a directly imaged planetary-mass
object. We successfully detect rotational modulation and measure the
amplitudes in two bands and determine the rotational period. These observations probe the spatial heterogeneity and
vertical structure of clouds in planetary mass objects for the first
time.

\section{Observation}

We obtained direct images of the 2M1207A+b system on UT 2014 April 11
from 08:07:47 to 16:53:18 using HST and its Wide Field Camera 3
\citep[WFC3, pixel scale=$0.130$mas/pixel, ][]{Mackenty2008} in the frame of
the HST Program GO-13418 (PI: D. Apai). We acquired the observations
in filters F125W ($\lambda_{\mathrm{pivot}}$ = 1245.9 nm, full width
at half maximum (FWHM) = 301.5 nm) and F160W
($\lambda_{\mathrm{pivot}}$ 1540.52, FWHM = 287.9 nm), roughly
corresponding to the J and H bands. We used the $256\times256$ pixels
sub-array mode to avoid memory dumps during the observations.  In
order to provide a near-continuous coverage for detecting modulations
we observed the 2M1207 system in 6 consecutive HST orbits, obtaining
data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
40 minutes. The observations were interrupted by 58 minutes long Earth
occultations every 94 minutes.

The observations applied space craft rolls each two orbit to allow
roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
telescope roll angles for orbit 1, 3, and 5, and those for 2, 4, and 6
differ by $25^{\circ}$. At the separation of 2M1207 b, this angle
difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
resolution elements in F125W and F160W, respectively. In each orbit we
took 8 SPARS10 exposure sequence with NSAMP=10, alternating between
F160W and F125W filters, with 2--3 identical exposures in each
exposure sequence. To improve sampling and reduce the risk that the
core of point spread function (PSF) is affected by bad pixels, we
applied a 4-point dither pattern with differential "X/Y" offsets of
1.375" in the detector frame, providing optimal non-integral (half
pixel) step of 10.5 and 8.5 pixels in F125W and F160W,
respectively. In total, we obtained 70 images with 10 non-destructive
read-outs in F125W and 64 images in F160W with exposure time of 88.4~s
for both filters.

\section{Data Reduction}

\subsection{Photometry}

We started the reduction from the \flt{} produced by the WFC3's
\texttt{calwfc3} pipeline. We did not opt to use \ima{} that contain
all non-destructive read-outs, because they provided less information
on 2M1207A, which saturated after the first few samples.  The \flt{}
are results of basic calibration, including dark current correction,
non-linearity correction, flat field correction, as well as
up-the-ramp fit on the non-destructive read-outs. 
Pixels with data quality flags ``bad detector pixels'', ``unstable
response'', and ``bad or uncertain flat value'' were masked out and
excluded from further analysis as suggested by previous transit
exoplanet spectroscopic observations\citep[e.g.][]{Berta2012,
  Kreidberg2014}.

The major challenge of high contrast observation with WFC3/IR is the
fact that the detector is significantly under-sampled.  2M1207 A and b
are only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF on the
detector. When
applying roll subtraction, notable artifacts are introduced by image
shifting and interpolation.  \tinytim{} PSF
simulator\citep{Krist1995} offers a solution by providing Nyquist or
better sampled PSF, but systematic errors of \tinytim{} PSF for WFC3
limits its ability in high precision photometry\citep{Biretta2014}.
Building on the large number of PSFs obtained in our program at two
different roll angles, we followed a novel, two-step approach that
uses a hybrid PSF, {\color{blue}which combined the strengths of the roll
subtraction-based and the simulated PSF-based approaches.}
First, based on our observations we observationally derived correction maps
for \tinytim{} that accurately described the scattered light component
for the primary at the correct location on the detector. Second, we
carried out a PSF-photometry using hybrid PSFs composed by \tinytim{}
PSFs and the correction map  by simultaneously
minimizing the residuals from the primary and the secondary.
% However, we are able to fully characterize the difference of model
% and observed PSFs with 6 orbits time-resolved observation data. To
% obtain robust \tinytim{} PSF photometry, we design a 2-round PSF
% fitting strategy: 1. calculating correction map for \tinytim{};
% 2. hybrid PSF photometry.

For both of 2 steps, we used \tinytim{} to calculate 10$\times$
over-sampled model PSFs based on the filters, the spectra (2M1207A:
\cite{Bonnefoy2014}, 2M1207 b: \cite{Patience2010}), the telescope's
actual focus, and the telescope jitter.  We used the set of \tinytim{}
parameters provided by \cite{Biretta2014} to improve modeling the cold
mask, diffraction spikes, and the coma. The focus parameters are are
interpolated to the precise time of the observations using the
tabulated values provided by
STScI\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
To align the \tinytim{} PSF to the observed PSF of 2M1207 A, we
moved the over-sampled PSF on a coordinate grid (gird size=0.001 pixel)
using cubic interpolation, and searched for the position that minimizes
the rms difference of the observed and the re-binned \tinytim{} PSF over
a region centered on 2M1207 A with a 5-pixel-radius aperture centered
on 2M1207 b excluded.  Then we introduced another \tinytim{} PSF for
2M1207 b and fit the position of 2M1207 b and the scales of the
\tinytim{} PSFs of 2M1207 A and b simultaneously by minimizing the
residual from both primary and secondary. In the first step, we discovered that the
difference of observed PSFs and model PSFs were very stable for a
specified telescope roll angle and dithering position. Therefore, at the end of the first step,
we derive 8 (2 roll angles $\times$ 4 dithering positions) correction
maps for each filter:
\begin{equation}
  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
\end{equation}
where $\mathrm{PSF_{model}}$ was a combination of two scaled \tinytim{} PSFs
for 2M1207 A and b. In the second round, we combined the correction
map linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
and scaled the correction map together with the two PSFs so that the
residual which is expressed as
\begin{equation}
  \mathrm{residual} = \mathrm{Image} - a\cdot \mathrm{PSF_{A}} - b\cdot
    \mathrm{PSF_{b}}- c\cdot\mathrm{ Corr}
  \end{equation}
  is minimized by least square fitting.
We found that by introducing the correction term,
the reduced $\chi^{2}$ was decreased from $\sim 10$ to
$\sim 1$. Relative photometry was acquired from the scaling
parameters of the \tinytim{} PSFs.

Our final step was to correct for a slight apparent trend between the
position of the targets on the detector and their flux. We attributed
this to a combination of slight changes in the PSF profile due to
pixelation and to the effect of imperfectly corrected pixel-to-pixel
sensitivity variations. We corrected for these apparent
position-dependent flux changes by normalizing each photometric point
by the median of all fluxes measured when the target was at the
same position, i.e. combining data over 6 orbits.  We note that this
correction is small and, as we demonstrate in the next sections,
cannot introduce artificial modulations that resemble the long-period
variations we identify in 2M1207b.

% PSF profiles change with exposure positions due to
% pixelation, especially for the case that WFC3 IR is significantly
% under-sampled. Also, the flat fields may potentially have large scale
% structures \citep{dressel2012wide}. We find a correlation of
% photometry with PSF positions on detector frame for both 2M1207 A and
% b. Correction is made by normalizing each group of
% exposures that have the same dithering position and telescope roll angle
% individually -- we take the median of the fluxes that are measured
% from these exposures as normalization factors and divided them from
% every photometric measurement. Because the normalization factor for
% each group of exposures is calculated across the whole observation in
% time domain,
% this step has negligible impacts on variability
% analysis.

As our study is the first to present high-contrast, high-cadence
observations, we provide a detailed analysis of the uncertainties and
their impact on our results.

\subsection{Uncertainty Analysis: White noise}

First we estimated the photon noise for the photometry of
2M1207 b. The total photon noise of the photometry was calculated by
combining the photon noise of every pixel, which was derived
from count rates and detector gain. The photon noises 
in F125W and F160W are 1.33\% and 1.02\%, respectively.

Since the PSFs for the 2M1207 A and b were fitted simultaneously, the
uncertainties for photometry and position of the primary and secondary
were coupled. Errors in position measurements of 2M1207 A could
potentially affect the photometry of 2M1207 b. We used a Monte Carlo
(MC) method to evaluate the overall systematic of the PSF fitting. We
applied photometry to images that were added with random
Poisson noise and repeated the photometry procedure for 1000 times. The
uncertainties for F125W and F160W photometry were found to be 1.34\% and 1.12\%,
respectively.

\subsection{Uncertainty Analysis: Flat field uncertainties}

A further contribution to photometric uncertainties may be introduced
by imperfectly corrected pixel-to-pixel sensitivity
differences. 2M1207 b were observed at 8 different positions on the
detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
field correction could introduce position-dependent
differences in the count rates. The uncertainty of WFC3 IR flat field
is typically $\sim 1\%$ \citep{dressel2012wide}.

In PSF photometry, however, multiple pixels are fitted simultaneously,
so that we expect the photometry to be less affected by high spatial frequency flat field
noise, and have a lower than 1\% uncertainty from the flat field
errors. To verify this, we multiplied every image by an artificial flat
field error mask (AFEM) -- a uniformly distributed Gaussian noise array with
mean of 1 and sigma of 1\% -- and repeated the PSF photometry on the
resulting images.  The analysis of these experiments resulted in almost
identical light curve to the original, verifying that the flat field
errors did not affect our photometry significantly (Figure
\ref{fig:2}, bottom panel).

\section{Verification of Photometric Modulations and Amplitude
  Estimate}

 \begin{figure*}
  \centering
  \plotone{systematics}
  \caption{F125W (left) and F160W (right) light curves under different
    variability verification tests. Individual measurements are
    plotted with gray crosses. Photometric measurements of the same exposure
    sequence are binned, and binned photometry are plotted with points
    or squares. Best fitted sinusoidal curves are plotted with solid
    lines. {\em Upper}: binned measurements taken in dithering
    position 1 and 3 (red points) and that taken in 2 and 4 (blue
    squares) are plotted with different symbols. They demonstrate same
    trend of modulation. In upper left panel, green line is sinusoidal
    wave fitted with all parameter set free, and purple line is
    sinusoidal wave fitted with period set the same as that of
    F125W. {\em Middle}: sinusoidal waves fitted without using the
    data taken in Orbit \#1. These curves are almost identical to the
    curves plotted in upper panel. {\em Lower}: photometry measured
    with AFEM-added images and best fitted sinul curves. These
    points and curves are also almost identical to those plotted
    in the upper panel.}
  \label{fig:2}
\end{figure*}

\subsection{Tests and Verification}

The light curves that resulted from our photometry showed apparently
sinusoidal modulations, discussed in more details in
\S,\ref{Results}. To verify that these modulations are intrinsic to
the object and not results of our data reduction procedures or due to
instrumental changes, we carried out three different tests.

First, we fitted sinusoids independently to the light curves of two
filters to verify the similarity of the signal in the two bands
(Figure \ref{fig:2}, top panel). Inconsistent periods or light curve
shapes would argue against a genuine signal.  We found that the periods
of the best fit sine waves were similar, $10.5^{+1.2}_{-1.3}$h for
F125W and $9.1^{+1.1}_{-1.0}$h for F160W. These periods are consistent
within the uncertainty. Furthermore, these periods are not close to
any timescales over which HST or WFC3 changes, and are
very different from all timescales present in our observations
(dithering timescales, integration times, and orbital timescales).

As a second test, we repeated the analysis neglecting the first
orbit. The motivation behind this test is that, due to spacecraft
thermal settling, the first orbits of HST observations are often
slightly unstable, and neglected in high-precision studies
\citep[e.g.][]{Mandell2013}. Indeed, in our analysis 2M1207 A is
significantly fainter in the first orbit (Figure \ref{fig:3}) than in
the subsequent ones.  Our analysis based on orbits 2--6 found
essentially identical results to our analysis using the whole 6 orbits, based on
which we conclude that the first less reliable orbit does not affect
our results significantly (Figure \ref{fig:2}, middle panel).

As a third test, we explored whether a subset of images, perhaps due to
imperfectly normalized or correlated with specific instrument states,
could drive the light curves into an apparently sinusoidal shape. To
test this possibility, we split the data into two temporally
overlapping halves: subset one were images taken at dithering position
1 and 3, and subset two were those taken at dithering position 2 and
4. For both subsets, we repeated our analysis independently.  For both
of F125W and F160W, two halves demonstrated similar sinusoidal
modulations.  Our analysis detect sinusoidal modulations in {\em both}
subsets and in {\em both} filters, with periods and amplitudes
consistent with those derived from the complete data set (Figure
\ref{fig:2}, upper panel).

 These tests demonstrate that the modulation seen in our data are
 consistently present in the different filters, in the different time
 segments of the data, and in data obtained in different dithering
 positions. All of the three tests support the signal to be
 intrinsic to the target.

\subsection{Amplitude and Period Measurements}

We used a MC method to analyze the light curve, and provided amplitudes
and periods as well as their uncertainties for both filters. We
generated series of Gaussian distributed random noise with standard deviation
same as the photon noise, add the noise to the original light curves, and
fit sinusoids to the newly combined light curves. We repeated these
procedures  for 100,000 times and obtain the distributions of period
and amplitude (Figure \ref{fig:4}).

\section{Result}
\label{Results}

  \begin{figure*}
  \centering
  \plotone{sineCurveFit_binCombined}
  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
    with filter F125W (left) and F160W (right). Individual photometric
  measurement are plotted in gray crosses and binned photometry are
  plotted with red points. Best fitted sinusoidal waves are plotted
  with blue solid lines.}
  \label{fig:3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{periodDistr}
  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
  \caption{Distributions for periods (left) and amplitudes(right) for the light
    curve of F125W and F160W. The bin size for histograms of period is
  0.25 hour and for that of amplitude is 0.5\%. Histograms are
  normalized to the maximum. In the right panel, Gaussian profiles are fitted to the
  histograms of periods and plotted in solid lines.}
  \label{fig:4}
\end{figure*}

We present the first high-resolution, high-cadence, and high-precision
photometry of a directly imaged planet or planetary-mass
companion. Our observations reveal a modulation in the light curve of
the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207 b, the first detection
of modulations in directly imaged planetary-mass objects.  The best
fit periods for F125W and F160W are $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ hour,
respectively. We also fit the two band light curves together forcing the
periods of two sinusoids to be the same, and obtained a period
of $10.2^{+0.9}_{-0.8}$. The amplitudes for the normalized light
curves are 1.45\% and 0.92\% for F125W and F160W, respectively.

We obtained high signal to noise photometry for both 2M1207 A
and B (Figure \ref{fig:3}). On average, the photometric contrast is
$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W.

%  With 64\% confidence,
% we estimate the 1-$\sigma$ range for the periods of F125W and F160W
% to be  and  h,
% respectively. The period of best fitted sinusoid for F125W light curve
% is 1.5h longer than that for F160W, which is $\sim 20\%$ larger than
% 1-$\sigma$. We also jointly fit the two band light curves forcing the
% periods of two sinusoids to be the same. We derive a modulation period of $10.2^{+0.9}_{-0.8}$ h.

We  found that the amplitudes in the two bands are
significantly different. By fitting Gaussians to the MC fit result
distributions, we determined that the  amplitude for F125W is
1.45\% with a standard deviation of 0.22\%, and  the amplitude for F160W is
0.92\% with a standard deviation of 0.20\%. The amplitudes of two
bands are separated by more than 2-$\sigma$ The amplitude
for F125W is 1.58 times of that for F160W light curve.

\section{Discussion}

\begin{figure*}
  \centering
  \plottwo{rotationDiagram}{JH}
  \caption{comparison of 2M1207's rotation period and color change
    with brown dwarfs, \bpic{} b, and solar system planets. {\em
      Left}: period vs. mass plot for 2M1207 b (red square), solar
    system planets and \bpic{} b (blue squares), and brown dwarfs
    (black circles, gray shade). Final rotation rates for 2M1207 b and
    \bpic{} b estimated by conservation of angular momentum are
    plotted with faint red and blue squares, respectively. The mass of brown dwarfs are assumed
    to be 30 \mjup{}. The gray rectangle that has a $\pm$15 \mjup
    range in $x$, and a $\pm \sigma$ of brown dwarf periods range in
    $y$, indicates a region where brown dwarfs most likely to appear
    in this diagram. Rotation period monotonically decreases with the
    increase of mass. {\em Right}: ratio of modulation amplitude in J
    and H band vs. spectral type for 2M1207 b and brown dwarfs. The
    point for 2M1207 b is shifted to +$x$ for half spectral type for
    clarification.  The colors of the points represent J$-$H
    magnitude, and the sizes of the points are proportional to the
    J-band modulation amplitudes. The gray dashed line is the result
    of a linear fit to these points. Tight correlation of J- and
    H-band modulation amplitude ratio and spectral type is shown.}
 \label{fig:5}
\end{figure*}

% A fundamental result of our study is the direct determination of the
% rotation period of a directly imaged planetary-mass object. We
% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
% $R_{\mathrm{Jup}}$ for 2M1207 b, and 1 $R_{\mathrm{Jup}}$ for field
% brown dwarfs with well defined rotation period from the study of
% \cite{Metchev2015}, and compare their rotation velocities with solar
% system planets and \bpic{} b in the left
% panel of Figure \ref{fig:5}.  The study by
% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
% and demonstrated that it fits a trend defined by Solar System planets
% in which more massive planets have faster rotation rates. They suggested
% that this relation is linked to the accretion processes during planet
% formation.

An important result of our study is the direct measurement of the
rotation period of a directly imaged planetary-mass object. In the
left panel of Figure~\ref{fig:5} we compare the rotation period of
2M1207 b to the solar system planets, \bpic{} b the only other directly
imaged planet with an estimated period and measured \vsini, and
field brown dwarfs from the study of
\cite[][]{Metchev2015}. \cite[][]{Snellen2014} measured \vsini{} 
for \bpic{} b and demonstrated that it fits a trend defined by Solar
System planets in which more massive planets have faster rotation
rates. The interesting finding that \bpic{} b, an exoplanet that formed
in a protoplanetary disk, follows this trend suggests a possibly
connection between planet mass, initial angular momentum, and
formation in a disk.

Excitingly, our measurement of the rotation period of 2M1207 b, a
planet mass companion that has similar age to \bpic{} b, has a
rotation period that fits in the same trend, as well as majority of
brown dwarfs. As 2M1207 b and \bpic{} b evolve and cool down, they are
expected to shrink to the size of Jupiter. Order of magnitude
estimation based on the conservation of angular momentum results in
final rotation periods of $\sim 5$ h and $\sim 3$ h
\citep{Snellen2014} for 2M1207 b and \bpic{} b, respectively, which
still fit to the period vs. mass trend. Although 2M1207 A is known to
host a circumsubstellar disk \citep{Sterzik2004}, the low mass of
typical brown dwarf disks \citep[e.g.]{Klein2003, Mohanty2013} and its
large separation argue against the possibility that 2M1207b has formed
in a protoplanetary disk.  The result that objects formed in different
scenarios share the same trend of period vs. mass suggests that
rotation periods -- in absence of well-determined ages -- may
contribute insufficient evidence for a formation in a disk vs. in a
cloud core environment. Although rotation rates may have limited value
for deciphering formation pathways, measurements of mass, age, and
rotation periods will map the angular momentum evolution of
planetary-mass objects and may place powerful constraints on the
evolution of the internal structures of these contracting objects.
%{\em Add younger BDs and this may change}
% Excitingly, our measurement of the rotation period demonstrates that
% 2M1207 b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
% that fits in the same trend, as well as majority of brown
% dwarfs. We note that 2M1207 b is most likely formed in the same way as brown
% dwarfs by gravitational fragmentation, which suggests
% that rotation periods are not good tracers of the formation pathways
% and may not contribute important evidence for a formation in a disk
% vs. in a cloud core environment.

Our inferred rotation period is very similar to those of Jupiter and Saturn, which
have periods of 9.9 and 10.5 hours, respectively.   Moreover, our inferred rotation 
is sufficiently fast that--just as with Jupiter and Saturn--the atmospheric dynamics 
is likely to be rotationally dominated at regional to global scales \citep[][]{Showman2013}.  
The importance of rotation can be characterized by the Rossby number 
$Ro = U/\Omega L$, where $U$ is the characteristic wind speed, $\Omega$ is the 
angular rotation rate ($1.7\times10^{-4}\rm\,s^{-1}$ for a 10-hour rotation period), 
and $L$ is the characteristic horizontal length scale.   Although the wind speeds are 
unknown, \citet[][]{Showman2013} presented a theory of the atmospheric circulation 
on brown dwarfs and directly imaged giant planets, which predicts wind speeds in the 
range of tens to hundreds of $\rm m\,s^{-1}$ depending on parameters.   Global 
simulations of the atmospheric circulation using a one-layer model by 
\citet{Zhang2014} predict a similar range.  Considering wind speeds ranging 
from  10 to $1000\rm\,m\,s^{-1}$, a circulation that is global in scale (L=Jupiter radius) 
implies Rossby numbers of 0.001 to 0.1 on 2M1207b (see Figure 1 in \citet{Showman2013}).  For a circulation whose length scale is 0.1 Jupiter radii, the Rossby numbers 
would range from 0.01 to 1 depending on wind speed.  Thus, over almost the full 
range of plausible parameters, we expect that the large-scale circulation on 
2M1207b---like Jupiter, Saturn, and most brown dwarfs---exhibits a Rossby number 
much less than one.  This implies that the atmospheric circulation is rotationally dominated 
and that the horizontal force balance is approximately geostrophic, that is, a balance 
between Coriolis and pressure-gradient forces.

From the perspective of atmospheric dynamics, 2M1207b exhibits other important 
similarities to brown dwarfs.  Its high effective temperature indicates that--like most 
brown dwarfs--2M1207b exhibit a strong interior heat flux presumably transported by 
convection, and that, by comparison, the external irradiation is negligible to the circulation.  
These similarities suggests that the overall dynamical mechanisms for driving an atmospheric 
circulation on 2M1207b should be similar to those on brown dwarfs.  Thus, given the
prevalence of IR light curve variability observed on brown dwarfs, it is unsurprising to
find such variability on directly imaged planets like 2M1207b.  Nevertheless, directly
imaged planets generally have lower gravity than field brown dwarfs, and this will 
affect the details of the atmospheric circulation, potentially including the cloud patchiness.  
Further observations of 2M1207b and other directly imaged planets will help to 
elucidate these differences.   Key questions for the future will include assessing the 
extent to which the atmospheric circulation on 2M1207b--including the 
existence of absence of zonal (east-west) jet streams, vortices, storms, and turbulence, 
and their effect on cloud patchiness--are similar or different than that on typical field 
brown dwarfs.

Furthermore, our observations allow us to compare the relative
amplitudes in the J- and H-bands with the handful of brown dwarfs
for which high-quality near-infrared time-resolved observations have
been obtained. In the right panel of Figure \ref{fig:5}, we compare the
relative amplitude of J- and H-bands of 2M1207 b and brown dwarfs
\citep{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014} that
have different spectral types and J$-$H colors.

We also find an interesting possible correlation between the spectral types of the
objects and their J- to H-band amplitude ratios. In the right panel of
Figure \ref{fig:5}, we show that earlier spectral type objects
have larger amplitudes at shorter wavelength than at longer
wavelengths. Interestingly, although the J$-$H color of 2M1207 b is
significantly redder, its relative amplitude ratio is very similar to
that of 2M1821, which also has an L5 spectral type \cite{Yang2014}.
This exciting, but tentative trend must be confirmed on a larger sample of source that also
sample a broader range of surface gravities as well as spectral types.
If the larger sample verifies the trend suggested by our small sample,
the amplitude ratio will provide a powerful probe of the spectral type
and surface gravity dependence of vertical cloud structure.

% {\color{red}This trend can be qualitatively explained using the toy model proposed
% in \cite{Yang2014} within the spectral type range of mid-L to L-T
% transition. Assuming that intensity modulations are introduced by a
% refractory cloud whose upper layer locates at altitude $z$, the
% amplitude ratio for J and H band can be expressed as
% $\mathrm{Amp_{J}}/\mathrm{Amp_{H}} =
% \exp\left[-(\tau_{\mathrm{J}}(z)/\tau_{{\mathrm{H}}}(z)\right]$,
% where $\tau_{\mathrm{J}}(z)$ and $\tau_{\mathrm{H}}(z)$ are the
% optical depths of upper cloud layer for J and H bands. The opacity for
% J band is smaller than that for H, therefore from mid-L to L-T
% transition, as the cloud upper boundary appears higher in the
% atmosphere, the optical depth difference for the two bands gets
% smaller, and the amplitude ratio decreases.  We note, that the late T
% dwarf 2M2228 falls exactly on this trend, but whose variations are
% likely to emerge from a different mechanism as their silicate clouds
% are below the visible photosphere \citep[e.g.][]{Stephens2009}.

% We infer that the upper cloud layer of 2M1207 b is at a similar optical
% depth as that of a matching spectral type field brown dwarf from the fact
% that they share similar J- and H-bands light curve amplitude ratio.
% The
% two processes that atmosphere opacity at certain pressure level
% enhances and the cloud thickness increases with the decrease of surface
% gravity have to counterbalance with each other to maintain the optical
% depth of the cloud upper layer.}

\section{Conclusions}
In summary, from our J- and H-band high precision, high-cadence light
curves we discovered sinusoidal modulations in the planetary-mass
object 2M1207 b. This is the first detection of rotational modulations
in a directly imaged planetary-mass object.  The period is
$10.2^{+0.9}_{-0.8}$, similar to that derived from \vsini{} 
measurements for the directly imaged exoplanet \bpic{} b and
significantly longer than most field brown dwarfs with known rotation
periods. The amplitude ratio of J and H band is very
similar to that of a field brown dwarf with identical L5 spectral type, although they have
very different J$-$H colors.

Finally, we note that the observations presented here open an exciting
new window on directly imaged exoplanets and planetary-mass
companions. Our study demonstrates a successful application of
high-cadence, high-precision, high-contrast photometry with planetary
mass companion. We also show that these observations can be carried
out simultaneously at multiple wavelengths, allowing us to prove
multiple pressure levels. With observation of a larger sample and at
multiple wavelengths, we will be able to explore the detailed
structures of atmospheres of directly imaged exoplanets, and identify
the key parameters that determine these.

Support for program number 13418 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the
Association of Universities for Research in Astronomy, Inc., under
NASA contract NAS5-26555. The results reported herein benefitted from
collaborations and/or information exchange within NASA's Nexus for
Exoplanet System Science (NExSS) research coordination network
sponsored by NASA's Science Mission Directorate. M.S.M. acknowledges
support from the NASA Astrophysics Theory Program.
\bibliography{ref.bib}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-09-25 summary/letter/letter_vAF.tex
submitted

--- 2015-09-25 summary/letter/letter_vAE.tex
@@
 \title{Discovery of Rotational Modulations in the Planetary-mass
-  Companion 2M1207b: A Slow Rotation Period and Heterogeneous Clouds in a Low
+  Companion 2M1207\lowercase{b}: An intermediate Rotation Period and Heterogeneous Clouds in a Low
   Gravity Atmosphere}
-\shorttitle{Variability of 2M1207 b}
+\shorttitle{Variability of 2M1207b}
 \author{Yifan Zhou\altaffilmark{1}, D\'aniel Apai\altaffilmark{1,2,3},
-  Glenn Schneider\altaffilmark{1},  Mark S. Marley\altaffilmark{4}}
+  Glenn H Schneider\altaffilmark{1},  Mark S. Marley\altaffilmark{4},
+  Adam P. Showman\altaffilmark{2}}
 
@@
 }
-\altaffiltext{2}{Lunar and Planetary Laboratory, The University of
+\altaffiltext{2}{Department of Planetary Science/Lunar and Planetary Laboratory, The University of
   Arizona, 1640 E. University Blvd., Tucson, AZ 85718, USA}
@@
   including longitudinal and vertical cloud structures and cloud
-  evolution. Furthermore, periodic light curve directly probes the rotational periods of ultra-cool objects.
-
-  We present here, for the first time, time-resolved high-precision
-  photometric measurements of a planetary-mass companion, 2MASS1207b,
-  to a brown dwarf primary.  We observed the binary system with
-  HST/WFC3 in two bands and with two spacecraft roll angles. Using
-  point spread function-based photometry we reach a nearly
-  photon-noise limited photometric accuracy for both components. While
-  the primary is consistent with a flat lightcurve, the secondary
-  shows modulations that are clearly detected in the combined
-  lightcurve as well as in different subsets of the data.  The
-  amplitudes are 1.45\% in the F125W and 0.92\% in the F160W filters;
-  we find a consistent period of $10.2^{+0.9}_{-0.8}$ h and similar
-  phase in both bands. The J- and H-band amplitude ratio of 2M1207 bis very
-  similar to a field brown dwarf that has identical spectral type but
-  different J-H color.  Importantly, our study also measures, for
-  the first time, the rotational period for directly an imaged
-  planetary-mass companion.
+  evolution. Furthermore, periodic light curves directly probe the
+  rotational periods of ultra-cool objects.  We present here, for the
+  first time, time-resolved high-precision photometric measurements of
+  a planetary-mass companion, 2M1207b.  We observed the binary
+  system with HST/WFC3 in two bands and with two spacecraft roll
+  angles. Using point spread function-based photometry, we reach a
+  nearly photon-noise limited accuracy for both the primary and the
+  secondary. While the primary is consistent with a flat light curve,
+  the secondary shows modulations that are clearly detected in the
+  combined light curve as well as in different subsets of the data.
+  The amplitudes are 1.45\% in the F125W and 0.92\% in the F160W
+  filters, respectively. We find a consistent period of
+  $10.2^{+0.9}_{-0.8}$ hours and
+  similar phases in both bands. The J- and H-band amplitude ratio of
+  2M1207b is very similar to a field brown dwarf that has identical
+  spectral type but different J-H color.  Importantly, our study also
+  measures, for the first time, the rotation period for a directly 
+  imaged planetary-mass companion to another star.
 \end{abstract}
@@
 \keywords{brown dwarfs -- planets and satellites: atmospheres -- planets
-  and satellites: individual (2M1207 b) -- techniques: photometric}
+  and satellites: individual (2M1207b) -- techniques: photometric}
 \maketitle
@@
     b is indicated by a white circle.  {\em Lower:} residual image --
-    after the subtraction of the hybrid PSF, 2M1207 b is detected at a
-    high significant level.}
+    after the subtraction of the hybrid PSF, 2M1207b is detected at a
+    high significance level.}
   \label{fig:1}
@@
 \citep[e.g.][]{Ackerman2001, Burrows2006a, Helling2008, Allard2012}
-have achieved great improvement in understanding the cloud behavior
-across different spectral types, especially in the explanation of L-T
+have made great progress on the cloud behaviors across different
+spectral types, especially the role that clouds play in the L-T
 transition \citep[e.g.][]{Burrows2006a, Marley2010}.  Surface gravity
@@
 structures \citep[e.g.][]{Marley2012} after effective temperature. Low
-surface gravity objects (e.g. HR8799 bcd, \cite{Marois2008a}, 2M1207
-b, \cite{Chauvin2004}) are significantly redder and under-luminous
-compared to brown dwarfs.  The anomalous color and luminosity of low surface gravity
-objects supports model including unusually thick clouds
-\citep{Currie2011, Madhusudhan2011,Skemer2011, Skemer2012}. However, due to lack of observational
-constraint, the dependence of cloud properties on surface gravity is
-not very well modeled.
+surface gravity objects (e.g. HR8799 bcd, \cite{Marois2008a}, 2M1207b, \cite{Chauvin2004}) are significantly redder and under-luminous
+compared to field brown dwarfs.  The anomalous color and luminosity of
+low surface gravity objects support models including unusually thick
+clouds \citep{Currie2011, Madhusudhan2011,Skemer2011,
+  Skemer2012}. However, due to lack of observational constraint, the
+dependence of cloud properties on surface gravity is not very well
+modeled.
 
@@
 directly observed and studied via time resolved observation and
-rotational mapping. These techniques isolate the effect of cloud
+rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
 properties and obtained great success in determining the rotation
 period and unveiling the structures of the atmosphere of brown dwarfs
-\citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014,Metchev2015,Heinze2015}. \cite{Kostov2013}
+. \citet{Kostov2013}
 demonstrated that these techniques can be applied to directly imaged
@@
 
-  2M1207 b \cite{Chauvin2004} is the first directly imaged
-planetary-mass companion. \cite{Chauvin2005,Song2006} confirmed that 2M1207 b and
-its host 2M1207 A form a bound, co-moving system. 2M1207 A and
-b have an angular separation of $0.78''$, which is corresponding to a
-projected separation of 41.2 AU at a distance of 52.4 pc
-\citep[e.g.][]{Ducourant2008}. Combining 2M1207 b's age and near infrared
-luminosity with  brown dwarf cooling models
+2M1207b \citet{Chauvin2004} is the first directly imaged extra-solar
+planetary-mass companion. \citet{Chauvin2005} and \citet{Song2006}
+confirmed that 2M1207b and its host 2M1207A form a bound, co-moving
+system. 2M1207A and b have an angular separation of $0.78''$, which
+corresponds to a projected separation of 41.2 AU at a distance of 52.4
+pc \citep[e.g.][]{Ducourant2008}. Combining 2M1207b's age and near
+infrared luminosity with brown dwarf cooling models
 \citep[e.g.][]{Baraffe2003}, the object's mass is estimated to be
@@
 circumsubstellar disk was discovered around 2M1207A
-\citep[][]{Sterzik2004}, the high companion-to-host
-mass ratio and large separation argue for binary-like gravitational fragmentation
+\citep[][]{Sterzik2004}, the high companion-to-host mass ratio and
+large separation argue for binary-like gravitational fragmentation
 formation\citep{Mohanty2007}.
 
-Early observations revealed that 2M1207 b's color is much redder and
+Early observations revealed that 2M1207b's color is much redder and
 its near-infrared luminosity is much lower than those of field brown
@@
 mid- to late L spectral type and effective temperature of $\sim 1600$
-\citep{Patience2010}.  Based multi-band near-infrared photometry
+ K\citep{Patience2010}.  Based on multi-band, near-infrared photometry,
 \citet{Skemer2011} argued that the apparent under-luminosity of 2M1207
-b may be explained by a model of a spatially heterogeneous atmosphere
+b could be explained by a model of a spatially heterogeneous atmosphere
 composed of patches of thin and patches of unusually thick clouds.
@@
 
-In this {\em Letter} we present the first, high-cadence,
+In this {\em Letter} we present the first, high-contrast, high-cadence,
 high-precision, time-resolved {\em Hubble Space Telescope} (HST)
-photometric time series of 2M1207 b, a directly imaged planetary-mass
+photometric time series of 2M1207b, a directly imaged planetary-mass
 object. We successfully detect rotational modulation and measure the
-amplitudes in two bands and determine the rotational period. These observations probe the spatial heterogeneity and
-vertical structure of clouds in planetary mass objects for the first
-time.
+amplitudes in two bands and determine the rotational period. These
+observations probe the spatial heterogeneity and vertical structure of
+clouds in planetary mass objects for the first time.
 
@@
 data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
-40 minutes. The observations were interrupted by 58 minutes long Earth
+40 minutes. The observations were interrupted by 58-minute long Earth
 occultations every 94 minutes.
 
-The observations applied space craft rolls each two orbit to allow
+The observations applied space craft rolls each two orbits to allow
 roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
 telescope roll angles for orbit 1, 3, and 5, and those for 2, 4, and 6
-differ by $25^{\circ}$. At the separation of 2M1207 b, this angle
+differed by $25^{\circ}$. At the separation of 2M1207b, this angle
 difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
@@
 core of point spread function (PSF) is affected by bad pixels, we
-applied a 4-point dither pattern with differential "X/Y" offsets of
+applied a 4-point dither pattern with differential ``X/Y'' offsets of
 1.375" in the detector frame, providing optimal non-integral (half
 pixel) step of 10.5 and 8.5 pixels in F125W and F160W,
-respectively. In total, we obtained 70 images with 10 non-destructive
-read-outs in F125W and 64 images in F160W with exposure time of 88.4~s
-for both filters.
+respectively. In total, we obtained 70 and 64 images with 10 non-destructive
+read-outs in F125W and F160W, respectively.
 
@@
 excluded from further analysis as suggested by previous transit
-exoplanet spectroscopic observations\citep[e.g.][]{Berta2012,
+exoplanet spectroscopic observations \citep[e.g.][]{Berta2012,
   Kreidberg2014}.
@@
 The major challenge of high contrast observation with WFC3/IR is the
-fact that the detector is significantly under-sampled.  2M1207 A and b
+fact that the detector is significantly under-sampled.  2M1207A and b
 are only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF on the
-detector. When
-applying roll subtraction, notable artifacts are introduced by image
-shifting and interpolation.  \tinytim{} PSF
-simulator\citep{Krist1995} offers a solution by providing Nyquist or
+detector. When applying roll subtraction, notable artifacts are
+introduced by image shifting and interpolation.  \tinytim{} PSF
+simulator \citep{Krist1995} offers a solution by providing Nyquist or
 better sampled PSF, but systematic errors of \tinytim{} PSF for WFC3
-limits its ability in high precision photometry\citep{Biretta2014}.
+limits its ability in high precision photometry \citep{Biretta2014}.
 Building on the large number of PSFs obtained in our program at two
 different roll angles, we followed a novel, two-step approach that
-uses a hybrid PSF, {\color{blue}which combined the strengths of the roll
-subtraction-based and the simulated PSF-based approaches.}
-First, based on our observations we observationally derived correction maps
-for \tinytim{} that accurately described the scattered light component
-for the primary at the correct location on the detector. Second, we
-carried out a PSF-photometry using hybrid PSFs composed by \tinytim{}
-PSFs and the correction map  by simultaneously
+uses a hybrid PSF.  First, based on our observations, we derived
+correction maps for \tinytim{} that accurately described the scattered
+light component for the primary at the correct location on the
+detector. Second, we carried out a PSF-photometry using hybrid PSFs
+composed by \tinytim{} PSFs and the correction map by simultaneously
 minimizing the residuals from the primary and the secondary.
@@
 over-sampled model PSFs based on the filters, the spectra (2M1207A:
-\cite{Bonnefoy2014}, 2M1207 b: \cite{Patience2010}), the telescope's
+\cite{Bonnefoy2014}, 2M1207b: \cite{Patience2010}), the telescope's
 actual focus, and the telescope jitter.  We used the set of \tinytim{}
 parameters provided by \cite{Biretta2014} to improve modeling the cold
-mask, diffraction spikes, and the coma. The focus parameters are are
+mask, diffraction spikes, and the coma. The focus parameters are 
 interpolated to the precise time of the observations using the
@@
 STScI\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
-To align the \tinytim{} PSF to the observed PSF of 2M1207 A, we
+To align the \tinytim{} PSF to the observed PSF of 2M1207A, we
 moved the over-sampled PSF on a coordinate grid (gird size=0.001 pixel)
@@
 the rms difference of the observed and the re-binned \tinytim{} PSF over
-a region centered on 2M1207 A with a 5-pixel-radius aperture centered
-on 2M1207 b excluded.  Then we introduced another \tinytim{} PSF for
-2M1207 b and fit the position of 2M1207 b and the scales of the
-\tinytim{} PSFs of 2M1207 A and b simultaneously by minimizing the
+a region centered on 2M1207A with a 5-pixel-radius aperture centered
+on 2M1207b excluded.  Then we introduced another \tinytim{} PSF for
+2M1207b and fit the position of 2M1207b and the scales of the
+\tinytim{} PSFs of 2M1207A and b simultaneously by minimizing the
 residual from both primary and secondary. In the first step, we discovered that the
-difference of observed PSFs and model PSFs were very stable for a
+difference of observed PSFs and model PSFs was very stable for a
 specified telescope roll angle and dithering position. Therefore, at the end of the first step,
@@
 where $\mathrm{PSF_{model}}$ was a combination of two scaled \tinytim{} PSFs
-for 2M1207 A and b. In the second round, we combined the correction
+for 2M1207A and b. In the second round, we combined the correction
 map linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
 and scaled the correction map together with the two PSFs so that the
-residual which is expressed as
+residual, which is expressed as
 \begin{equation}
@@
 same position, i.e. combining data over 6 orbits.  We note that this
-correction is small and, as we demonstrate in the next sections,
-cannot introduce artificial modulations that resemble the long-period
-variations we identify in 2M1207b.
+correction was small and, as we demonstrate in the next sections,
+could not introduce artificial modulations that resemble the long-period
+variations that we identified in 2M1207b.
 
@@
 % structures \citep{dressel2012wide}. We find a correlation of
-% photometry with PSF positions on detector frame for both 2M1207 A and
+% photometry with PSF positions on detector frame for both 2M1207A and
 % b. Correction is made by normalizing each group of
@@
 First we estimated the photon noise for the photometry of
-2M1207 b. The total photon noise of the photometry was calculated by
+2M1207b. The total photon noise of the photometry was calculated by
 combining the photon noise of every pixel, which was derived
@@
 
-Since the PSFs for the 2M1207 A and b were fitted simultaneously, the
+Since the PSFs for the 2M1207A and b were fitted simultaneously, the
 uncertainties for photometry and position of the primary and secondary
-were coupled. Errors in position measurements of 2M1207 A could
-potentially affect the photometry of 2M1207 b. We used a Monte Carlo
-(MC) method to evaluate the overall systematic of the PSF fitting. We
+were coupled. Errors in position measurements of 2M1207A could
+potentially affect the photometry of 2M1207b. We used a Monte Carlo
+(MC) method to evaluate the overall systematics of the PSF fitting. We
 applied photometry to images that were added with random
@@
 by imperfectly corrected pixel-to-pixel sensitivity
-differences. 2M1207 b were observed at 8 different positions on the
+differences. 2M1207b were observed at 8 different positions on the
 detector (2 rolls $\times$ 4 dithering positions). Imperfect flat
@@
     sequence are binned, and binned photometry are plotted with points
-    or squares. Best fitted sinusoidal curves are plotted with solid
+    or squares. Best fitted sinusoids are plotted with solid
     lines. {\em Upper}: binned measurements taken in dithering
@@
     squares) are plotted with different symbols. They demonstrate same
-    trend of modulation. In upper left panel, green line is sinusoidal
-    wave fitted with all parameter set free, and purple line is
-    sinusoidal wave fitted with period set the same as that of
-    F125W. {\em Middle}: sinusoidal waves fitted without using the
+    trend of modulation. In upper left panel, the green line a sinusoid
+    fitted with all parameters freely varying, and the purple line is
+    a sinusoid fitted with the period set the same as that of
+    F125W. {\em Middle}: sinusoids fitted without using the
     data taken in Orbit \#1. These curves are almost identical to the
@@
 The light curves that resulted from our photometry showed apparently
-sinusoidal modulations, discussed in more details in
-\S,\ref{Results}. To verify that these modulations are intrinsic to
-the object and not results of our data reduction procedures or due to
+sinusoidal modulations, discussed in more detail in
+\S\ref{Results}. To verify that these modulations are intrinsic to
+the object and not the result of our data reduction procedures or 
 instrumental changes, we carried out three different tests.
@@
 thermal settling, the first orbits of HST observations are often
-slightly unstable, and neglected in high-precision studies
-\citep[e.g.][]{Mandell2013}. Indeed, in our analysis 2M1207 A is
+slightly unstable, and are neglected in high-precision studies
+\citep[e.g.][]{Mandell2013}. Indeed, in our analysis, 2M1207A is
 significantly fainter in the first orbit (Figure \ref{fig:3}) than in
@@
 As a third test, we explored whether a subset of images, perhaps due to
-imperfectly normalized or correlated with specific instrument states,
-could drive the light curves into an apparently sinusoidal shape. To
+imperfect normalization or correlation with specific instrument states,
+could drive the light curves into apparently sinusoidal shapes. To
 test this possibility, we split the data into two temporally
 overlapping halves: subset one were images taken at dithering position
-1 and 3, and subset two were those taken at dithering position 2 and
+1 and 3; subset two were those taken at dithering position 2 and
 4. For both subsets, we repeated our analysis independently.  For both
@@
 generated series of Gaussian distributed random noise with standard deviation
-same as the photon noise, add the noise to the original light curves, and
-fit sinusoids to the newly combined light curves. We repeated these
+same as the photon noise, added the noise to the original light curves, and
+fitted sinusoids to the newly combined light curves. We repeated these
 procedures  for 100,000 times and obtain the distributions of period
@@
   \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Individual photometric
-  measurement are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoidal waves are plotted
+    with filter F125W (left) and F160W (right). Unbinned
+  measurements are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoids are plotted
   with blue solid lines.}
@@
   \includegraphics[width=0.45\textwidth]{amplitudeDistr}
-  \caption{Distributions for periods (left) and amplitudes(right) for the light
-    curve of F125W and F160W. The bin size for histograms of period is
-  0.25 hour and for that of amplitude is 0.5\%. Histograms are
-  normalized to the maximum. In the right panel, Gaussian profiles are fitted to the
-  histograms of periods and plotted in solid lines.}
+  \caption{Distributions for period (left) and amplitude (right) for the light
+    curves of F125W and F160W. The bin sizes for the histograms of
+    period  and amplitude are
+  0.25 hours and 0.5\%, respectively. Histograms are
+  normalized to the maxima. In the right panel, Gaussian profiles are fitted to the
+  histograms and plotted in solid lines.}
   \label{fig:4}
@@
 
-We present the first high-resolution, high-cadence, and high-precision
+We present the first high-contrast, high-cadence, and high-precision
 photometry of a directly imaged planet or planetary-mass
-companion. Our observations reveal a modulation in the light curve of
-the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207 b, the first detection
+companion around another star. Our observations reveal a modulation in the light curve of
+the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
 of modulations in directly imaged planetary-mass objects.  The best
-fit periods for F125W and F160W are $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ hour,
-respectively. We also fit the two band light curves together forcing the
+fit periods for F125W and F160W are $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ hours,
+respectively. We also fitted the two band light curves together forcing the
 periods of two sinusoids to be the same, and obtained a period
-of $10.2^{+0.9}_{-0.8}$. The amplitudes for the normalized light
-curves are 1.45\% and 0.92\% for F125W and F160W, respectively.
+of $10.2^{+0.9}_{-0.8}$ hours.
 
-We obtained high signal to noise photometry for both 2M1207 A
+We obtained high signal to noise photometry for both 2M1207A
 and B (Figure \ref{fig:3}). On average, the photometric contrast is
@@
 
-We  found that the amplitudes in the two bands are
+We find that the amplitudes in the two bands are
 significantly different. By fitting Gaussians to the MC fit result
-distributions, we determined that the  amplitude for F125W is
+distributions, we determin that the  amplitude for F125W is
 1.45\% with a standard deviation of 0.22\%, and  the amplitude for F160W is
 0.92\% with a standard deviation of 0.20\%. The amplitudes of two
-bands are separated by more than 2-$\sigma$ The amplitude
-for F125W is 1.58 times of that for F160W light curve.
+bands are separated by more than 2-$\sigma$. The amplitude
+for F125W is $1.58\pm0.27$ times of that for F160W light curve.
 
@@
     with brown dwarfs, \bpic{} b, and solar system planets. {\em
-      Left}: period vs. mass plot for 2M1207 b (red square), solar
+      Left}: period vs. mass plot for 2M1207b (red square), solar
     system planets and \bpic{} b (blue squares), and brown dwarfs
-    (black circles, gray shade). Final rotation rates for 2M1207 b and
-    \bpic{} b estimated by conservation of angular momentum are
+    (black circles, gray shade). Final rotation rates for 2M1207b and
+    \bpic{} b estimated based on conservation of angular momentum are
     plotted with faint red and blue squares, respectively. The mass of brown dwarfs are assumed
@@
     increase of mass. {\em Right}: ratio of modulation amplitude in J
-    and H band vs. spectral type for 2M1207 b and brown dwarfs. The
-    point for 2M1207 b is shifted to +$x$ for half spectral type for
+    and H band vs. spectral type for 2M1207b and brown dwarfs. The
+    point for 2M1207b is shifted to +$x$ for half spectral type for
     clarification.  The colors of the points represent J$-$H
@@
     J-band modulation amplitudes. The gray dashed line is the result
-    of a linear fit to these points. Tight correlation of J- and
+    of a linear fit to these points.  Correlation of J- and
     H-band modulation amplitude ratio and spectral type is shown.}
@@
 % convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
-% $R_{\mathrm{Jup}}$ for 2M1207 b, and 1 $R_{\mathrm{Jup}}$ for field
+% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
 % brown dwarfs with well defined rotation period from the study of
@@
 An important result of our study is the direct measurement of the
-rotation period of a directly imaged planetary-mass object. In the
-left panel of Figure~\ref{fig:5} we compare the rotation period of
-2M1207 b to the solar system planets, \bpic{} b the only other directly
-imaged planet with an estimated period and measured \vsini, and
-field brown dwarfs from the study of
-\cite[][]{Metchev2015}. \cite[][]{Snellen2014} measured \vsini{} 
-for \bpic{} b and demonstrated that it fits a trend defined by Solar
+photometric modulation period of a directly imaged planetary-mass
+object. We infer the rotation period of 2M1207b to be the same as
+the period of photometric variation. Although horizontal winds can cause the
+measured period to differ from true rotation period, it is
+unlikely that the difference is greater than the uncertainty of the
+measurement, since for Jupiter and Saturn, typical wind speeds are
+more than one order of magnitude smaller than the equatorial rotation speeds.
+% Our
+% inferred rotation period of 2M1207b is typical among those of brown dwarfs
+% \citep{Reiners2008}.
+In the left panel of Figure~\ref{fig:5} we
+compare the rotation period of 2M1207b to the solar system planets,
+\bpic{} b the only other directly imaged planet with an estimated
+period and measured \vsini, and field brown dwarfs from the study of
+\cite[][]{Metchev2015}. \citet[][]{Snellen2014} measured \vsini{} for
+\bpic{} b and demonstrated that it fits a trend defined by Solar
 System planets in which more massive planets have faster rotation
-rates. The interesting finding that \bpic{} b, an exoplanet that formed
-in a protoplanetary disk, follows this trend suggests a possibly
-connection between planet mass, initial angular momentum, and
+rates. The interesting finding that \bpic{} b, an exoplanet that
+formed in a protoplanetary disk, follows this trend suggests a
+possibly connection between planet mass, initial angular momentum, and
 formation in a disk.
 
-Excitingly, our measurement of the rotation period of 2M1207 b, a
+Excitingly, our measurement of the rotation period of 2M1207b, a
 planet mass companion that has similar age to \bpic{} b, has a
 rotation period that fits in the same trend, as well as majority of
-brown dwarfs. As 2M1207 b and \bpic{} b evolve and cool down, they are
+the brown dwarfs. As 2M1207b and \bpic{} b evolve and cool down, they are
 expected to shrink to the size of Jupiter. Order of magnitude
 estimation based on the conservation of angular momentum results in
-final rotation periods of $\sim 5$ h and $\sim 3$ h
-\citep{Snellen2014} for 2M1207 b and \bpic{} b, respectively, which
-still fit to the period vs. mass trend. Although 2M1207 A is known to
+final rotation periods of $\sim 5$ h and $\sim 3$ hours
+\citep{Snellen2014} for 2M1207b and \bpic{} b, respectively, which
+still fit to the period vs. mass trend. Although 2M1207A is known to
 host a circumsubstellar disk \citep{Sterzik2004}, the low mass of
@@
 % Excitingly, our measurement of the rotation period demonstrates that
-% 2M1207 b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
+% 2M1207b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
 % that fits in the same trend, as well as majority of brown
-% dwarfs. We note that 2M1207 b is most likely formed in the same way as brown
+% dwarfs. We note that 2M1207b is most likely formed in the same way as brown
 % dwarfs by gravitational fragmentation, which suggests
@@
 
-Our inferred rotation period is very similar to those of Jupiter and Saturn, which
-have periods of 9.9 and 10.5 hours, respectively.   Moreover, our inferred rotation 
-is sufficiently fast that--just as with Jupiter and Saturn--the atmospheric dynamics 
-is likely to be rotationally dominated at regional to global scales \citep[][]{Showman2013}.  
-The importance of rotation can be characterized by the Rossby number 
-$Ro = U/\Omega L$, where $U$ is the characteristic wind speed, $\Omega$ is the 
-angular rotation rate ($1.7\times10^{-4}\rm\,s^{-1}$ for a 10-hour rotation period), 
-and $L$ is the characteristic horizontal length scale.   Although the wind speeds are 
-unknown, \citet[][]{Showman2013} presented a theory of the atmospheric circulation 
-on brown dwarfs and directly imaged giant planets, which predicts wind speeds in the 
-range of tens to hundreds of $\rm m\,s^{-1}$ depending on parameters.   Global 
-simulations of the atmospheric circulation using a one-layer model by 
-\citet{Zhang2014} predict a similar range.  Considering wind speeds ranging 
-from  10 to $1000\rm\,m\,s^{-1}$, a circulation that is global in scale (L=Jupiter radius) 
-implies Rossby numbers of 0.001 to 0.1 on 2M1207b (see Figure 1 in \citet{Showman2013}).  For a circulation whose length scale is 0.1 Jupiter radii, the Rossby numbers 
-would range from 0.01 to 1 depending on wind speed.  Thus, over almost the full 
-range of plausible parameters, we expect that the large-scale circulation on 
-2M1207b---like Jupiter, Saturn, and most brown dwarfs---exhibits a Rossby number 
-much less than one.  This implies that the atmospheric circulation is rotationally dominated 
-and that the horizontal force balance is approximately geostrophic, that is, a balance 
-between Coriolis and pressure-gradient forces.
+Our inferred rotation period is very similar to those of Jupiter and
+Saturn, which have periods of 9.9 and 10.5 hours, respectively.
+Moreover, our inferred rotation is sufficiently fast that -- just as
+with Jupiter and Saturn -- the atmospheric dynamics is likely to be
+rotationally dominated at regional to global scales
+\citep[][]{Showman2013}.  The importance of rotation can be
+characterized by the Rossby number $Ro = U/\Omega L$, where $U$ is the
+characteristic wind speed, $\Omega$ is the angular rotation rate
+($1.7\times10^{-4}\rm\,s^{-1}$ for a 10-hour rotation period), and $L$
+is the characteristic horizontal length scale.
+\citet[][]{Showman2013} presented a theory of the
+atmospheric circulation on brown dwarfs and directly imaged giant
+planets, which predicts wind speeds in the range of tens to hundreds
+of $\rm m\,s^{-1}$ depending on parameters. Using similar arguments,
+\citet[][]{Apai2013}  argued for wind speeds of a few hundreds $\mathrm{m\,s^{-1}}$
+(somewhat faster than typical in Jupiter) in two L/T transition brown
+dwarfs.
+Global simulations of the
+atmospheric circulation using a one-layer model by \citet{Zhang2014}
+predict a similar range.  Considering wind speeds ranging from 10 to
+$1000\rm\,m\,s^{-1}$, a circulation that is global in scale
+(L=$R_{\mathrm{Jup}}$) implies Rossby numbers of 0.001 to 0.1 on
+2M1207b (see Figure 1 in \citet{Showman2013}).  For a circulation
+whose length scale is 0.1 $R_{\mathrm{Jup}}$, the Rossby numbers would
+range from 0.01 to 1 depending on wind speed.  Thus, over almost the
+full range of plausible parameters, we expect that the large-scale
+circulation on 2M1207b --- like Jupiter, Saturn, and most brown
+dwarfs --- exhibits a Rossby number much less than one.  This implies
+that the atmospheric circulation is rotationally dominated and that
+the horizontal force balance is approximately geostrophic, that is, a
+balance between Coriolis and pressure-gradient forces.
 
-From the perspective of atmospheric dynamics, 2M1207b exhibits other important 
-similarities to brown dwarfs.  Its high effective temperature indicates that--like most 
-brown dwarfs--2M1207b exhibit a strong interior heat flux presumably transported by 
-convection, and that, by comparison, the external irradiation is negligible to the circulation.  
-These similarities suggests that the overall dynamical mechanisms for driving an atmospheric 
-circulation on 2M1207b should be similar to those on brown dwarfs.  Thus, given the
-prevalence of IR light curve variability observed on brown dwarfs, it is unsurprising to
-find such variability on directly imaged planets like 2M1207b.  Nevertheless, directly
-imaged planets generally have lower gravity than field brown dwarfs, and this will 
-affect the details of the atmospheric circulation, potentially including the cloud patchiness.  
-Further observations of 2M1207b and other directly imaged planets will help to 
-elucidate these differences.   Key questions for the future will include assessing the 
-extent to which the atmospheric circulation on 2M1207b--including the 
-existence of absence of zonal (east-west) jet streams, vortices, storms, and turbulence, 
-and their effect on cloud patchiness--are similar or different than that on typical field 
+From the perspective of atmospheric dynamics, 2M1207b exhibits other
+important similarities to brown dwarfs.  Its high effective
+temperature indicates that -- like most brown dwarfs -- 2M1207b exhibit a
+strong interior heat flux presumably transported by convection, and
+that, by comparison, the external irradiation is negligible to the
+circulation.  These similarities suggest that the overall dynamical
+mechanisms for driving an atmospheric circulation on 2M1207b should be
+similar to those on brown dwarfs.  Thus, given the prevalence of
+infrared light curve variability observed on brown dwarfs, it is expected
+to find such variability on directly imaged planets like 2M1207b.
+Nevertheless, directly imaged planets generally have lower surface gravity
+than field brown dwarfs, and this will affect the details of the
+atmospheric circulation, potentially including the cloud patchiness.
+Further observations of 2M1207b and other directly imaged planets will
+help to elucidate these differences.  Key questions for the future
+will include assessing the extent to which the atmospheric circulation
+on 2M1207b -- including the existence of absence of zonal (east-west)
+jet streams, vortices, storms, and turbulence, and their effect on
+cloud patchiness -- are similar or different than that on typical field
 brown dwarfs.
 
-Furthermore, our observations allow us to compare the relative
-amplitudes in the J- and H-bands with the handful of brown dwarfs
-for which high-quality near-infrared time-resolved observations have
-been obtained. In the right panel of Figure \ref{fig:5}, we compare the
-relative amplitude of J- and H-bands of 2M1207 b and brown dwarfs
-\citep{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2014} that
-have different spectral types and J$-$H colors.
-
-We also find an interesting possible correlation between the spectral types of the
-objects and their J- to H-band amplitude ratios. In the right panel of
-Figure \ref{fig:5}, we show that earlier spectral type objects
-have larger amplitudes at shorter wavelength than at longer
-wavelengths. Interestingly, although the J$-$H color of 2M1207 b is
-significantly redder, its relative amplitude ratio is very similar to
-that of 2M1821, which also has an L5 spectral type \cite{Yang2014}.
-This exciting, but tentative trend must be confirmed on a larger sample of source that also
-sample a broader range of surface gravities as well as spectral types.
-If the larger sample verifies the trend suggested by our small sample,
-the amplitude ratio will provide a powerful probe of the spectral type
-and surface gravity dependence of vertical cloud structure.
+Our observations also allow us to compare the relative amplitudes in
+the J- and H-bands with the handful of brown dwarfs for which
+high-quality near-infrared time-resolved observations have been
+obtained. In the right panel of Figure \ref{fig:5}, we compare the
+relative amplitude of J- and H-bands of 2M1207b and brown dwarfs
+\citep{Apai2013,Buenzli2012,Buenzli2015,Yang2015} that have different
+spectral types and J$-$H colors.  J and H band fluxes for brown dwarfs
+are integrated from WFC3 grism spectra using standard J and H filter
+transmission profile. We find an interesting possible correlation
+between the spectral types of the objects and their J- to H-band
+amplitude ratios. In the right panel of Figure \ref{fig:5}, we show
+that earlier spectral type objects have larger amplitudes at shorter
+wavelength than at longer wavelengths. Interestingly, although the
+J$-$H color of 2M1207b is significantly redder, its relative amplitude
+ratio is very similar to that of 2M1821, which also has an L5 spectral
+type \citep{Yang2015}.  This exciting, but tentative trend must be
+confirmed with a larger sample of sources that also sample a broader
+range of surface gravities as well as spectral types.  If the larger
+sample verifies the trend suggested by our small sample, the amplitude
+ratio will provide a powerful probe of the spectral type and surface
+gravity dependence of vertical cloud structure.
 
@@
 
-% We infer that the upper cloud layer of 2M1207 b is at a similar optical
+% We infer that the upper cloud layer of 2M1207b is at a similar optical
 % depth as that of a matching spectral type field brown dwarf from the fact
@@
 curves we discovered sinusoidal modulations in the planetary-mass
-object 2M1207 b. This is the first detection of rotational modulations
+object 2M1207b. This is the first detection of rotational modulations
 in a directly imaged planetary-mass object.  The period is
-$10.2^{+0.9}_{-0.8}$, similar to that derived from \vsini{} 
+$10.2^{+0.9}_{-0.8}$ hours, similar to that derived from \vsini{} 
 measurements for the directly imaged exoplanet \bpic{} b and
 significantly longer than most field brown dwarfs with known rotation
-periods. The amplitude ratio of J and H band is very
+periods. The amplitude ratio of J- and H-band is very
 similar to that of a field brown dwarf with identical L5 spectral type, although they have
@@
 companions. Our study demonstrates a successful application of
-high-cadence, high-precision, high-contrast photometry with planetary
+high contrast, high-cadence, high-precision photometry with planetary
 mass companion. We also show that these observations can be carried
-out simultaneously at multiple wavelengths, allowing us to prove
+out simultaneously at multiple wavelengths, allowing us to probe
 multiple pressure levels. With observation of a larger sample and at
@@
 
+\acknowledgments
+
 Support for program number 13418 was provided by NASA through a grant
@@
 Association of Universities for Research in Astronomy, Inc., under
-NASA contract NAS5-26555. The results reported herein benefitted from
+NASA contract NAS5-26555. The results reported herein benefited from
 collaborations and/or information exchange within NASA's Nexus for
@@
 sponsored by NASA's Science Mission Directorate. M.S.M. acknowledges
-support from the NASA Astrophysics Theory Program.
+support from the NASA Astrophysics Theory Program. A.P.S. acknowledges
+support from NSF grant AST1313444.
 \bibliography{ref.bib}

### 2015-09-25 summary/submission/ms.tex
submitted

--- 2015-09-25 summary/letter/letter_vAF.tex
@@
 \usepackage{color}
-\bibliographystyle{apj}
+%\bibliographystyle{apj}
 \usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
@@
 \newcommand{\vsini}{$v\sin i$}
-\newcommand{\mjup}{M$_{\mbox{Jup}}$}
+\newcommand{\mjup}{M$_{\mathrm{Jup}}$}
 \begin{document}
@@
 \centering
-  \plottwo{original}{subtracted}
+  \plottwo{f1a}{f1b}
   \caption{Point spread function subtraction allows isolating the
@@
 directly observed and studied via time resolved observation and
-rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
+rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
 properties and obtained great success in determining the rotation
@@
 
-In this {\em Letter} we present the first, high-contrast, high-cadence,
+In this {\em Paper} we present the first, high-contrast, high-cadence,
 high-precision, time-resolved {\em Hubble Space Telescope} (HST)
@@
 minimizing the residuals from the primary and the secondary.
-% However, we are able to fully characterize the difference of model
-% and observed PSFs with 6 orbits time-resolved observation data. To
-% obtain robust \tinytim{} PSF photometry, we design a 2-round PSF
-% fitting strategy: 1. calculating correction map for \tinytim{};
-% 2. hybrid PSF photometry.
 
@@
 
-% PSF profiles change with exposure positions due to
-% pixelation, especially for the case that WFC3 IR is significantly
-% under-sampled. Also, the flat fields may potentially have large scale
-% structures \citep{dressel2012wide}. We find a correlation of
-% photometry with PSF positions on detector frame for both 2M1207A and
-% b. Correction is made by normalizing each group of
-% exposures that have the same dithering position and telescope roll angle
-% individually -- we take the median of the fluxes that are measured
-% from these exposures as normalization factors and divided them from
-% every photometric measurement. Because the normalization factor for
-% each group of exposures is calculated across the whole observation in
-% time domain,
-% this step has negligible impacts on variability
-% analysis.
-
 As our study is the first to present high-contrast, high-cadence
@@
 their impact on our results.
+
+\begin{figure*}
+  \centering
+  \plotone{f2}
+  \caption{F125W (left) and F160W (right) light curves under different
+    variability verification tests. Individual measurements are
+    plotted with gray crosses.  and binned photometry are plotted with points
+    or squares. Best fitted sinusoids are plotted with solid
+    lines. {\em Upper}: binned measurements taken in dithering
+    position 1 and 3 (red points) and that taken in 2 and 4 (blue
+    squares) are plotted with different symbols. They demonstrate same
+    trend of modulation. In upper left panel, the green line a sinusoid
+    fitted with all parameters freely varying, and the purple line is
+    a sinusoid fitted with the period set the same as that of
+    F125W. {\em Middle}: sinusoids fitted without using the
+    data taken in Orbit \#1. These curves are almost identical to the
+    curves plotted in upper panel. {\em Lower}: photometry measured
+    with AFEM-added images and best fitted sinul curves. These
+    points and curves are also almost identical to those plotted
+    in the upper panel.}
+  \label{fig:2}
+\end{figure*}
 
@@
   Estimate}
-
- \begin{figure*}
-  \centering
-  \plotone{systematics}
-  \caption{F125W (left) and F160W (right) light curves under different
-    variability verification tests. Individual measurements are
-    plotted with gray crosses. Photometric measurements of the same exposure
-    sequence are binned, and binned photometry are plotted with points
-    or squares. Best fitted sinusoids are plotted with solid
-    lines. {\em Upper}: binned measurements taken in dithering
-    position 1 and 3 (red points) and that taken in 2 and 4 (blue
-    squares) are plotted with different symbols. They demonstrate same
-    trend of modulation. In upper left panel, the green line a sinusoid
-    fitted with all parameters freely varying, and the purple line is
-    a sinusoid fitted with the period set the same as that of
-    F125W. {\em Middle}: sinusoids fitted without using the
-    data taken in Orbit \#1. These curves are almost identical to the
-    curves plotted in upper panel. {\em Lower}: photometry measured
-    with AFEM-added images and best fitted sinul curves. These
-    points and curves are also almost identical to those plotted
-    in the upper panel.}
-  \label{fig:2}
-\end{figure*}
 
@@
   \centering
-  \plotone{sineCurveFit_binCombined}
+  \plotone{f3}
   \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{periodDistr}
-  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
+  \includegraphics[width=0.45\textwidth]{f4a}
+  \includegraphics[width=0.45\textwidth]{f4b}
+
   \caption{Distributions for period (left) and amplitude (right) for the light
@@
 
-\section{Discussion}
-
 \begin{figure*}
   \centering
-  \plottwo{rotationDiagram}{JH}
+    \includegraphics[width=0.45\textwidth]{f5a}
+  \includegraphics[width=0.45\textwidth]{f5b}
   \caption{comparison of 2M1207's rotation period and color change
@@
 
-% A fundamental result of our study is the direct determination of the
-% rotation period of a directly imaged planetary-mass object. We
-% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
-% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
-% brown dwarfs with well defined rotation period from the study of
-% \cite{Metchev2015}, and compare their rotation velocities with solar
-% system planets and \bpic{} b in the left
-% panel of Figure \ref{fig:5}.  The study by
-% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
-% and demonstrated that it fits a trend defined by Solar System planets
-% in which more massive planets have faster rotation rates. They suggested
-% that this relation is linked to the accretion processes during planet
-% formation.
+\section{Discussion}
 
@@
 photometric modulation period of a directly imaged planetary-mass
-object. We infer the rotation period of 2M1207b to be the same as
-the period of photometric variation. Although horizontal winds can cause the
-measured period to differ from true rotation period, it is
+object. We infer the rotation period of 2M1207b to be the same as the
+period of photometric variation. Although horizontal winds can cause
+the measured period to differ from true rotation period, it is
 unlikely that the difference is greater than the uncertainty of the
 measurement, since for Jupiter and Saturn, typical wind speeds are
-more than one order of magnitude smaller than the equatorial rotation speeds.
-% Our
-% inferred rotation period of 2M1207b is typical among those of brown dwarfs
-% \citep{Reiners2008}.
-In the left panel of Figure~\ref{fig:5} we
-compare the rotation period of 2M1207b to the solar system planets,
-\bpic{} b the only other directly imaged planet with an estimated
-period and measured \vsini, and field brown dwarfs from the study of
+more than one order of magnitude smaller than the equatorial rotation
+speeds.  In the left panel of Figure~\ref{fig:5} we compare the
+rotation period of 2M1207b to the solar system planets, \bpic{} b the
+only other directly imaged planet with an estimated period and
+measured \vsini, and field brown dwarfs from the study of
 \cite[][]{Metchev2015}. \citet[][]{Snellen2014} measured \vsini{} for
@@
 evolution of the internal structures of these contracting objects.
-%{\em Add younger BDs and this may change}
-% Excitingly, our measurement of the rotation period demonstrates that
-% 2M1207b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
-% that fits in the same trend, as well as majority of brown
-% dwarfs. We note that 2M1207b is most likely formed in the same way as brown
-% dwarfs by gravitational fragmentation, which suggests
-% that rotation periods are not good tracers of the formation pathways
-% and may not contribute important evidence for a formation in a disk
-% vs. in a cloud core environment.
 
@@
 
-% {\color{red}This trend can be qualitatively explained using the toy model proposed
-% in \cite{Yang2014} within the spectral type range of mid-L to L-T
-% transition. Assuming that intensity modulations are introduced by a
-% refractory cloud whose upper layer locates at altitude $z$, the
-% amplitude ratio for J and H band can be expressed as
-% $\mathrm{Amp_{J}}/\mathrm{Amp_{H}} =
-% \exp\left[-(\tau_{\mathrm{J}}(z)/\tau_{{\mathrm{H}}}(z)\right]$,
-% where $\tau_{\mathrm{J}}(z)$ and $\tau_{\mathrm{H}}(z)$ are the
-% optical depths of upper cloud layer for J and H bands. The opacity for
-% J band is smaller than that for H, therefore from mid-L to L-T
-% transition, as the cloud upper boundary appears higher in the
-% atmosphere, the optical depth difference for the two bands gets
-% smaller, and the amplitude ratio decreases.  We note, that the late T
-% dwarf 2M2228 falls exactly on this trend, but whose variations are
-% likely to emerge from a different mechanism as their silicate clouds
-% are below the visible photosphere \citep[e.g.][]{Stephens2009}.
-
-% We infer that the upper cloud layer of 2M1207b is at a similar optical
-% depth as that of a matching spectral type field brown dwarf from the fact
-% that they share similar J- and H-bands light curve amplitude ratio.
-% The
-% two processes that atmosphere opacity at certain pressure level
-% enhances and the cloud thickness increases with the decrease of surface
-% gravity have to counterbalance with each other to maintain the optical
-% depth of the cloud upper layer.}
-
 \section{Conclusions}
@@
 support from NSF grant AST1313444.
-\bibliography{ref.bib}
+%\bibliography{ref.bib}
+
+\begin{thebibliography}{42}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{Ackerman \& Marley(2001)}]{Ackerman2001}
+Ackerman, A.~S. \& Marley, M.~S. 2001, ApJ, 556, 872
+
+\bibitem[{{Allard} {et~al.}(2012)}]{Allard2012}
+{Allard}, et al. 2012, Royal Society of London
+  Philosophical Transactions Series A, 370, 2765
+
+\bibitem[{Apai {et~al.}(2013)}]{Apai2013}
+Apai, D., et al. 2013, ApJ, 768, 121
+
+\bibitem[{{Baraffe} {et~al.}(2003)}]{Baraffe2003}
+{Baraffe}, I., {Chabrier}, G., {Barman}, T.~S., {Allard}, F., \& {Hauschildt},
+  P.~H. 2003, \aap, 402, 701
+
+\bibitem[{{Barman} {et~al.}(2011)}]{Barman2011b}
+{Barman}, T.~S., et al. 2011,
+  \apjl, 735, L39
+
+\bibitem[{Berta {et~al.}(2012)}]{Berta2012}
+Berta, Z.~K., Charbonneau, D., D\'{e}sert, J.-M., {et~al.} 2012, ApJ, 747, 35
+
+\bibitem[{Biretta(2014)}]{Biretta2014}
+Biretta, J. 2014, Space Telescope WFC Instrument Science Report, 1, 10
+
+\bibitem[{Bonnefoy {et~al.}(2014)}]{Bonnefoy2014}
+Bonnefoy, M., Chauvin, G., et al. 2014, A\&A, 562, A127
+
+\bibitem[{Buenzli {et~al.}(2012)}]{Buenzli2012}
+Buenzli, E., Apai, D., et al. 2012, ApJ, 760, L31
+
+\bibitem[{Buenzli {et~al.}(2015)}]{Buenzli2015}
+Buenzli, E., Saumon, D., et al. 2015, ApJ, 798, 127
+
+\bibitem[{Burrows {et~al.}(2006)}]{Burrows2006a}
+Burrows, A., Sudarsky, D., \& Hubeny, I. 2006, ApJ, 640, 1063
+
+\bibitem[{{Chauvin} {et~al.}(2004)}]{Chauvin2004}
+{Chauvin}, G., {Lagrange}, A.-M., et al. 2004, \aap, 425, L29
+
+\bibitem[{{Chauvin} {et~al.}(2005)}]{Chauvin2005}
+---. 2005, \aap, 438, L25
+
+\bibitem[{{Currie} {et~al.}(2011)}]{Currie2011}
+{Currie}, T., {Burrows}, A., {Itoh}, Y., et al. 2011, \apj, 729, 128
+
+\bibitem[{Dressel(2012)}]{dressel2012wide}
+Dressel, L. 2012, Wide Field Camera 3, HST Instrument Handbook, 1
+
+\bibitem[{Ducourant {et~al.}(2008)}]{Ducourant2008}
+Ducourant, C., Teixeira, R., et al. 2008, \aap, 477, L1
+
+\bibitem[{{Heinze} {et~al.}(2015)}]{Heinze2015}
+{Heinze}, A.~N., {Metchev}, S., \& {Kellogg}, K. 2015, \apj, 801, 104
+
+\bibitem[{Helling {et~al.}(2008)}]{Helling2008}
+Helling, C., Ackerman, A., Allard, F., et al. 2008,
+  MNRAS, 391, 1854
+
+\bibitem[{{Klein} {et~al.}(2003)}]{Klein2003}
+{Klein}, R., {Apai}, D., {Pascucci}, I., {Henning}, T., \& {Waters},
+  L.~B.~F.~M. 2003, \apjl, 593, L57
+
+\bibitem[{{Kostov} \& {Apai}(2013)}]{Kostov2013}
+{Kostov}, V. \& {Apai}, D. 2013, \apj, 762, 47
+
+\bibitem[{Kreidberg {et~al.}(2014)}]{Kreidberg2014}
+Kreidberg, L., Bean, J.~L., D\'{e}sert, J.-M., {et~al.} 2014, Nature, 505, 69
+
+\bibitem[{Krist(1995)}]{Krist1995}
+Krist, J. 1995, in Astronomical Data Analysis Software and Systems IV, Vol.~77,
+  349
+
+\bibitem[{{MacKenty} {et~al.}(2008)}]{Mackenty2008}
+{MacKenty}, J.~W., {Kimble}, R.~A., {O'Connell}, R.~W., \& {Townsend}, J.~A.
+  2008,  Vol. 7010,  SPIE
+  Conference Series, 1
+
+\bibitem[{{Madhusudhan} {et~al.}(2011)}]{Madhusudhan2011}
+{Madhusudhan}, N., {Burrows}, A., \& {Currie}, T. 2011, \apj, 737, 34
+
+\bibitem[{Mandell {et~al.}(2013)}]{Mandell2013}
+Mandell, A.~M., Haynes, K., Sinukoff, E., {et~al.} 2013, ApJ, 779, 128
+
+\bibitem[{{Marley} {et~al.}(2012)}]{Marley2012}
+{Marley}, M.~S., {Saumon}, D., et al. 2012, \apj, 754, 135
+
+\bibitem[{{Marley} {et~al.}(2010)}]{Marley2010}
+{Marley}, M.~S., {Saumon}, D., \& {Goldblatt}, C. 2010, \apjl, 723, L117
+
+\bibitem[{Marois {et~al.}(2008)}]{Marois2008a}
+Marois, C., Macintosh, B., et al. 2008, Science, 322, 1348
+
+\bibitem[{Metchev {et~al.}(2015)}]{Metchev2015}
+Metchev, S.~A., Heinze, A., et al. 2015, ApJ, 799, 154
+
+\bibitem[{{Mohanty} {et~al.}(2013)}]{Mohanty2013}
+{Mohanty}, S., {Greaves}, J., et al. 2013, \apj, 773,
+  168
+
+\bibitem[{Mohanty {et~al.}(2007)}]{Mohanty2007}
+Mohanty, S., Jayawardhana, R., Huelamo, N., \& Mamajek, E. 2007, ApJ, 657, 1064
+
+\bibitem[{Patience {et~al.}(2010)}]{Patience2010}
+Patience, J., King, R.~R., {De Rosa}, R.~J., \& Marois, C. 2010, A\&A, 517, A76
+
+\bibitem[{Radigan {et~al.}(2012)}]{Radigan2012}
+Radigan, J., Jayawardhana, R., Lafreni\`{e}re, D., Artigau, E., Marley, M., \&
+  Saumon, D. 2012, ApJ, 750, 105
+
+\bibitem[{{Showman} \& {Kaspi}(2013)}]{Showman2013}
+{Showman}, A.~P. \& {Kaspi}, Y. 2013, \apj, 776, 85
+
+\bibitem[{{Skemer} {et~al.}(2011)}]{Skemer2011}
+{Skemer}, A.~J., {Close}, L.~M., et al. 2011, \apj, 732, 107
+
+\bibitem[{{Skemer} {et~al.}(2012)}]{Skemer2012}
+{Skemer}, A.~J., {Hinz}, P.~M., {Esposito}, S., {Burrows}, A., {et~al.} 2012,
+  \apj, 753, 14
+
+\bibitem[{Snellen {et~al.}(2014)}]{Snellen2014}
+Snellen, I. A.~G., Brandl, B.~R., et al. 2014, Nature, 509, 63
+
+\bibitem[{Song {et~al.}(2006)}]{Song2006}
+Song, I., Schneider, G., et al. 2006, ApJ, 652, 724
+
+\bibitem[{{Sterzik} {et~al.}(2004)}]{Sterzik2004}
+{Sterzik}, M.~F., {Pascucci}, I., {Apai}, D., {van der Bliek}, N., \&
+  {Dullemond}, C.~P. 2004, \aap, 427, 245
+
+\bibitem[{{Yang} {et~al.}(2015)}]{Yang2015}
+{Yang}, H., {Apai}, D., et~al. 2015, \apjl, 798, L13
+
+\bibitem[{{Zhang} \& {Showman}(2014)}]{Zhang2014}
+{Zhang}, X. \& {Showman}, A.~P. 2014, \apjl, 788, L6
+
+\end{thebibliography}
+
 \end{document}

### 2015-09-25 2M1207ANALYSIS/illustrateImage.py

@@ -5,7 +5,7 @@ import numpy as np
 from astropy.io import fits
 import matplotlib as mpl
 from matplotlib.colors import BoundaryNorm
-
+plt.style.use('paper')
 """make an image to illustrate the 2M1207 system
 especially the difficulty
 """
@@ -22,9 +22,10 @@ if __name__ == '__main__':
     cax1 = ax1.imshow(im, cmap='hot', origin='lower',
                       interpolation='nearest',
                       norm=BoundaryNorm(bd1, ncolors=255))
-    ax1.plot(15.855, 8.204, 'o', ms=14, mfc='none', mew=1.5, mec='white')
-    ax1.annotate('2M1207 B', xy=(15.855, 8.204), xytext=(17, 7),
-                 fontsize=14)
+    ax1.plot(15.855, 8.204, 'o', ms=36, mfc='none', mew=2.5, mec='white')
+    ax1.annotate('2M1207b', xy=(18.855, 8.204), xytext=(18.5, 7),
+                 fontsize='18', color='white', weight='bold')
+    ax1.set_title('F160W Image of 2M1207 A and b')
     ax1.set_xlim([0, 26])
     ax1.set_ylim([0, 26])
     sub = im - psf
@@ -34,6 +35,7 @@ if __name__ == '__main__':
     cax2 = ax2.imshow(sub, cmap='hot', origin='lower',
                       interpolation='nearest',
                       norm=BoundaryNorm(bd2, ncolors=255))
+    ax2.set_title('Primary Subtraction Reveals 2M1207 b')
     cbar1 = fig1.colorbar(cax1, ticks=np.logspace(-1, 4, 6))
     cbar1.formatter = mpl.ticker.LogFormatter()
     cbar1.update_ticks()
@@ -45,6 +47,6 @@ if __name__ == '__main__':
         ax.set_xlabel('X (pixel)')
         ax.set_ylabel('Y (pixel)')
 
-    # plt.show()
+    plt.show()
     fig1.savefig('original.pdf')
     fig2.savefig('subtracted.pdf')

### 2015-09-25 2M1207ANALYSIS/period.py

@@ -65,8 +65,8 @@ if __name__ == '__main__':
     fig = plt.figure()
     gs = mpl.gridspec.GridSpec(3, 2)
     axOut = fig.add_subplot(gs[:, :])
-    axOut.set_xlabel('Time (h)', labelpad=24)
-    axOut.set_ylabel('Normalized flux', labelpad=42)
+    axOut.set_xlabel('Time (h)', labelpad=30)
+    axOut.set_ylabel('Normalized flux', labelpad=56)
     ax125B = fig.add_subplot(gs[0:2, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]
     df125_2 = df125[(df125['DITHER'] == 1) | (df125['DITHER'] == 3)]
@@ -83,7 +83,7 @@ if __name__ == '__main__':
     points125, = ax125B.plot(df125['Time'], f125B0, '+',
                              ms=8, mec='0.8', zorder=0)
 
-    ax125B.set_title('F125W light curve')
+    ax125B.set_title('F125W Light Curve')
 
     # split the data
 
@@ -114,7 +114,7 @@ if __name__ == '__main__':
     line160_2, = ax160B.plot(t, modelFlux2, label='P=9.3', linewidth=1.8)
     points160, = ax160B.plot(df160['Time'], f160B0, '+',
                              ms=8, mec='0.8', zorder=0)
-    ax160B.set_title('F160W light curve')
+    ax160B.set_title('F160W Light Curve')
     # ax160B.legend()
     ax160A = fig.add_subplot(gs[2, 1])
     ax160A.plot(df160['Time'], f160A0, 'o', color='0.8', zorder=0)
@@ -133,13 +133,13 @@ if __name__ == '__main__':
         #        ax.set_xlabel('Time (h)')
         ax.set_ylim([0.975, 1.025])
     for ax in [ax125A, ax160A]:
-        ax.text(0.05, 0.05, 'Host',
+        ax.text(0.05, 0.05, '2M1207 A',
                 verticalalignment='bottom', horizontalalignment='left',
                 transform=ax.transAxes)
 
     ax125A.yaxis.set_ticks([0.98, 1.00, 1.02])
     for ax in [ax125B, ax160B]:
-        ax.text(0.05, 0.05, 'Companion',
+        ax.text(0.05, 0.05, '2M1207 b',
                 verticalalignment='bottom', horizontalalignment='left',
                 transform=ax.transAxes)
     gs.update(hspace=0, wspace=0)

### 2015-09-25 2M1207ANALYSIS/plotJHratio.py

@@ -46,7 +46,7 @@ if __name__ == '__main__':
 
     for i in range(len(specPos)):
         ax.text(
-            textPos[i], JHratio[i] + 0.02, tgName[i], fontsize=12, zorder=10)
+            textPos[i], JHratio[i] + 0.02, tgName[i], fontsize=16, zorder=10)
 
     # fig1, ax1 = plt.subplots()
     # ax1.plot(specPos, ampJ, '+', label='J', ms=12, mew=1.5)
@@ -68,7 +68,7 @@ if __name__ == '__main__':
     ax.plot(np.linspace(4.5, 17, 10),
             np.linspace(4.5, 17, 10) * m + b, ls='--', lw=2.0, color='0.2',
             zorder=0)
-    ax.set_title('J and H variation amplitude ratios')
+    ax.set_title('J and H Amplitude Ratio vs. Spectral Type')
     plt.show()
     fig.savefig('JH.pdf')
     # fig1.savefig('AmpvsSpecType.pdf')

### 2015-09-25 2M1207ANALYSIS/plotLightCurve.py

@@ -77,14 +77,14 @@ def plotLightCurve(DataFrame125, DataFrame160, applyCorr=False):
         fluxB1250 = fluxB1250 / (fluxA1250 * corr125[1] + corr125[0])
         fluxB1600 = fluxB1600 / (fluxA1600 * corr160[1] + corr160[0])
     ax_F125.plot(DataFrame125.index, fluxA1250,
-                 linewidth=0, marker='s', label='priamry')
+                 linewidth=0, marker='s', label='2M1207 A')
     ax_F125.plot(DataFrame125.index, fluxB1250,
-                 linewidth=0, marker='o', label='secondary')
+                 linewidth=0, marker='o', label='2M1207 b')
     ax_F125.set_title('F125W')
     ax_F160.plot(DataFrame160.index, fluxA1600,
-                 linewidth=0, marker='s', label='primary')
+                 linewidth=0, marker='s', label='2M1207 A')
     ax_F160.plot(DataFrame160.index, fluxB1600,
-                 linewidth=0, marker='o', label='secondary')
+                 linewidth=0, marker='o', label='2M1207 b')
     ax_F160.set_title('F160W')
     # fluxA1250 = (DataFrame125['FLUXA'] / DataFrame125['FLUXA'].mean()).values
     # fluxA1600 = (DataFrame160['FLUXA'] / DataFrame160['FLUXA'].mean()).values

### 2015-09-25 2M1207ANALYSIS/plotResultDistr.py

@@ -24,45 +24,56 @@ if __name__ == '__main__':
     pBins = np.linspace(6, 20, 57)
     fig_p, ax_p = plt.subplots()
 
-    countP125, binP125 = np.histogram(pDist125, bins=pBins, normed=1)
-    countP160, binP160 = np.histogram(pDist160, bins=pBins, normed=1)
+    countP125, binP125 = np.histogram(pDist125, bins=pBins)
+    countP160, binP160 = np.histogram(pDist160, bins=pBins)
+    countP125 = countP125 / countP125.max()
+    countP160 = countP160 / countP160.max()
     # countP, binP = np.histogram(pDist, bins=pBins, normed=1)
     ax_p.bar(
         (binP125[:-1] + binP125[1:]) / 2, countP125, binP125[1] - binP125[0],
-        alpha=0.8, fc='#e41a1c')
+        alpha=0.8, fc='#377eb8', label='F125W')
     ax_p.bar(
         (binP160[:-1] + binP160[1:]) / 2, countP160, pBins[1] - pBins[0],
-        label='F160W', alpha=0.8, fc='#377eb8')
+        label='F160W', alpha=0.8, fc='#e41a1c')
     ax_p.legend()
     ax_p.set_xlabel('Period (hour)')
-    ax_p.set_ylabel('Probability density (hour$^{-1}$)')
+    ax_p.set_ylabel('Normalized probability')
+    ax_p.set_title('Probability Distribution: Period')
 
     ampBins = np.linspace(0.00, 0.025, 51)
     fineAmpBins = np.linspace(0.00, 0.025, 510)
     fig_amp, ax_amp = plt.subplots()
-    countAmp125, binAmp125 = np.histogram(ampDist125, bins=ampBins, normed=1)
-    countAmp160, binAmp160 = np.histogram(ampDist160, bins=ampBins, normed=1)
+    countAmp125, binAmp125 = np.histogram(ampDist125, bins=ampBins)
+    countAmp160, binAmp160 = np.histogram(ampDist160, bins=ampBins)
+    countAmp125 = countAmp125 / countAmp125.max()
+    countAmp160 = countAmp160 / countAmp160.max()
+    binAmp125 = binAmp125 * 100
+    binAmp160 = binAmp160 * 100
+
     gpAmp125, cov125 = curve_fit(gauss, (binAmp125[1:] + binAmp125[:-1]) / 2,
[…]

### 2015-09-25 2M1207ANALYSIS/plotRotation.py

@@ -27,8 +27,8 @@ if __name__ == '__main__':
     ax_p.errorbar(
         [0.00017, 0.00256], [26, 26], yerr=2.0,
         lolims=True, color='k', ls='')
-    ax_p.errorbar(4, 10.05, xerr=1, yerr=2.9, color='k')
-    # ax_p.set_ylim(0, 30)
+    ax_p.errorbar(4, 10.05, xerr=[1], yerr=[[0.9], [0.8]], color='k')
+
     # ax.arrow(x0, y0, 0, -0.3, fc='b', lw=0.2, head_width=0.05,
     # head_length=0.1)
 
@@ -41,6 +41,7 @@ if __name__ == '__main__':
     # suppose BD has period of 1 Mjup
     ax_p.plot(np.zeros(len(BDperiod)) + 30, BDperiod,
               'o', mec='k', mfc='none', ms=10)
+    ax_p.text(45, 10, 'Brown dwarfs', rotation=90)
     # ax_p.plot(np.zeros(len(BDperiod)) + 30, vBD,
     #           'o', mec='k', mfc='none', ms=10)
     ax_p.add_patch(patches.Rectangle((15, BDperiod.mean() - BDperiod.std()),
@@ -52,16 +53,45 @@ if __name__ == '__main__':
 
     for i in range(len(name)):
         if i == 4:
-            ax_p.text(mass[i] / 2.0, period[i] + 1.2, label[i])
+            ax_p.text(mass[i] / 2.0, period[i] + 1.2, label[i], fontsize=16)
         elif i == 5:
-            ax_p.text(mass[i] / 2.0, period[i] - 1.5, label[i])
+            ax_p.text(mass[i] / 2.0, period[i] - 1.5, label[i], fontsize=16)
         elif i == 6:
-            ax_p.text(mass[i] / 5.0, period[i], label[i])
+            ax_p.text(mass[i] / 6.5, period[i], label[i], fontsize=16)
+        elif i == 0:
+            ax_p.text(mass[i] / 1.5, period[i] + 1.2, label[i], fontsize=16)
         else:
-            ax_p.text(mass[i] * 1.3, period[i], label[i])
-    ax_p.text(0.00017 * 1.2, 26, 'Mercury')
-    ax_p.text(0.00256 * 1.2, 26, 'Venus')
[…]

### 2015-09-25 2M1207ANALYSIS/systematics.py

@@ -68,6 +68,7 @@ if __name__ == '__main__':
     """
     plt.close('all')
     fig = plt.figure(figsize=(12, 9))
+
     gs = mpl.gridspec.GridSpec(3, 2)
     axOut = fig.add_subplot(gs[:, :])
     axOut.set_xlabel('Time (h)', labelpad=24)
@@ -88,7 +89,7 @@ if __name__ == '__main__':
     points125, = ax125B.plot(df125['Time'], f125B0, '+',
                              ms=8, mec='0.8', zorder=0)
 
-    ax125B.set_title('Validation Test: F125W')
+    # ax125B.set_title('Validation Test: F125W')
     # remove the data from the first orbit
     df125 = df125[df125['ORBIT'] > 1]
     f125A0, f125B0 = normFlux(df125, normDither=True)
@@ -102,8 +103,8 @@ if __name__ == '__main__':
                    ms=8, mec='0.8', zorder=0, label='no orbit 1')
 
     ax125_no1.plot(t, normedSin(t, [0.0139, 12.03, 0.7069]), lw=1.8)
-    lg = ax125_no1.legend()
-    lg.draw_frame(False)
+#    lg = ax125_no1.legend()
+#    lg.draw_frame(False)
 
     fn125_AFEM = '2015_Jul_14TinyTimF125Result.csv'  # apply AFEM
     df125_AFEM = pd.read_csv(
@@ -124,8 +125,8 @@ if __name__ == '__main__':
                     ms=8, mec='0.8', zorder=0, label="AFEM")
 
     ax125_AFEM.plot(t, normedSin(t, [0.0139, 10.97, 0.59]), lw=1.8)
-    lg = ax125_AFEM.legend()
-    lg.draw_frame(False)
+    # lg = ax125_AFEM.legend()
+    # lg.draw_frame(False)
 
     """For F160B I used two type fit,
     1. free parameter fit
@@ -146,11 +147,11 @@ if __name__ == '__main__':
     t = np.linspace(df160['Time'].min(), df160['Time'].max(), 500)
     modelFlux1 = 0.0080 * np.sin(2 * np.pi / 10.9765 * t + 0.2525) + 0.9997
     modelFlux2 = 0.0088 * np.sin(2 * np.pi / 9.2692 * t - 0.1180) + 1.0002
-    line160_1, = ax160B.plot(t, modelFlux1, label='P=10.45', linewidth=1.8)
[…]

### 2015-09-25 MarkModelSpectra/calModel.py

@@ -1,0 +1,69 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+from readSpec import readSpec
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+"""calculate model J vs H ratio
+"""
+
+
+def calModel(cloudyFN, clearFN, Jprofile, Hprofile):
+    wlCloudy, fCloudy = readSpec(cloudyFN)
+    wlClear, fClear = readSpec(clearFN)
+
+    # interpolating the data so that their wavelengths match
+    dw = 0.0001  # wavelength inter
+    w = np.linspace(0.8, 3, (3 - 0.8) / dw)
+    funcJ = interp1d(Jprofile[:, 0] / 1e4, Jprofile[:, 1],
+                     kind='linear', bounds_error=False, fill_value=0)
+    Jtrans = funcJ(w)
+    funcH = interp1d(Hprofile[:, 0] / 1e4, Hprofile[:, 1],
+                     kind='linear', bounds_error=False, fill_value=0)
+    Htrans = funcH(w)
+    funcCloudy = interp1d(wlCloudy, fCloudy,
+                          kind='linear', bounds_error=False, fill_value=0)
+    fCloudy = funcCloudy(w)
+    funcClear = interp1d(
+        wlClear, fClear, kind='linear', bounds_error=False, fill_value=0)
+    fClear = funcClear(w)
+    JCloudy = (Jtrans * fCloudy * dw).sum()
+    JClear = (Jtrans * fClear * dw).sum()
+    HCloudy = (Htrans * fCloudy * dw).sum()
+    HClear = (Htrans * fClear * dw).sum()
+    # return JClear, JCloudy, HClear, HCloudy
+    return ((JClear - JCloudy) / (JClear + JCloudy)) /\
+        ((HClear - HCloudy) / (HClear + HCloudy))
+
+
+if __name__ == '__main__':
+    Jprofile = np.loadtxt('F125W_transmission.dat')
+    Hprofile = np.loadtxt('F160W_transmission.dat')
+
+    TList = [900, 950, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700]
+    JHratioHg = np.zeros(len(TList))
+    JHratioLg = np.zeros(len(TList))
+    for i, T in enumerate(TList):
[…]

### 2015-09-25 MarkModelSpectra/getInfo.py

@@ -1,0 +1,28 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+from glob import glob
+import re
+import pandas as pd
+import numpy as np
+"""generate file info
+"""
+
+if __name__ == '__main__':
+    info = pd.DataFrame()
+    fileList = glob('*.flx')
+    fileList.sort()
+    info['file name'] = fileList
+    T = np.zeros(len(fileList), dtype=int)
+    g = np.zeros(len(fileList), dtype=int)
+    fsed = np.zeros(len(fileList), dtype=int)
+    TPattern = re.compile(r't[0-9]{3,4}')
+    gPattern = re.compile(r'g[0-9]{3,4}')
+    fsedPattern = re.compile(r'f[0-9]\.')
+    for i, fn in enumerate(fileList):
+        T[i] = int(TPattern.search(fn).group()[1:])
+        g[i] = int(gPattern.search(fn).group()[1:])
+        fsed[i] = int(fsedPattern.search(fn).group()[1])
+    info['T'] = T
+    info['g'] = g
+    info['fsed'] = fsed
+    info.to_csv('Marley_Model_info.csv', index=False)

### 2015-09-25 MarkModelSpectra/readSpec.py

@@ -1,0 +1,21 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+"""read Mark Marley's model spectra
+"""
+
+
+def readSpec(fn):
+    wl, f = np.loadtxt(fn, unpack=True, usecols=(1, 3))
+    return wl[np.where((wl > 0.8) & (wl < 3.0))],\
+        f[np.where((wl > 0.8) & (wl < 3.0))]
+
+
+if __name__ == '__main__':
+    wl, f = readSpec('t1000g1000f5.flx')
+    plt.plot(wl, f)
+    # xplt.xlim([1, 3])
+    plt.show()

### 2015-11-01 summary/referee_report_reply.md
revision finished

# Referee report reply

## Major comment:

> At the beginning of Sec 4 the authors claim that the photometry 'showed apparently sinusoidal modulations'. They proceed to fit sinusoids to the light curve to determine a period and find periods between 9 and 10 hours. I would argue that this is a dubious approach. The first sensible step is to actually prove that a period is present in the data (in addition to the subjective eye test), before modeling the light curve with a sinusoid.

>As argument in favor of their period detection the authors say that the fitted periods are 'very different from all timescales present in our observations' - that is true, except for ONE timescale, the total duration of the observations, which is around 9 hours. Playing devil's advocate, fitting a sinusoid to a light curve with just a linear trend tends to result in a period around the total length of the dataset. Looking at the light curves, it is not so evident to me that a periodic curve is necessarily the best model - a linear fit would make much sense too, particularly when the first orbit is discarded (as the authors argue, the 1st orbit is often unstable). In that case, 10 hours could be the lower limit of the rotation period.

>What I would like to see is a statistical test that confirms that a periodicity is in fact a better fit to the data than a linear trend. Alternatively, the authors could use some of the well established period search routines to bolster the evidence for their detection. Since the rotational modulation is the key result of this paper, it seems prudent to me to not only rely on the eye test, in particular since there is a wealth of analysis routines available for this kind of problem.

>Parts of introduction, discussion, and abstract may need to be revised after verifying the presumed period.
*****
>Sec 4.2: I do not fully understand why the authors add noise to their light curve and THEN fit sinusoids. Why is the noise increased artificially for this procedure? This seems to be a very unusual period finding algorithm.

The minor comment on the period finding algorithm is directly related to the major comment. Therefore we combine our reply to these comments together.

We agree with the referee that our original fitting method is inappropriate in the way that it artificially adds noise to the light curve. Therefore we did a rigorous MCMC fitting to measure the period and amplitude based on a sinusoidal model. We cannot use normal period search routines (e.g. Fourier analysis, auto-correlation) because the period of the modulation is larger than our observation baseline. We assumed uniform distribution for the period, amplitude and phase of the sinusoid as priors and included period as long as 40 hours as possible solution. We did the fitting for both including and excluding data from the first orbit. Even when the data from the first orbit were excluded, the posterior distributions for the amplitude and period were constraint, though not as well as those for the fitting include the whole dataset. Our measurements for period and amplitude agree within 1-sigma uncertainties with or without using data from the first orbit. Using the posterior distribution of MCMC fitting, we can show the statistical significance of our measurement.

We also added discussion from the perspective of physical viability of the light curve models and explained a sinusoid is the most suitable choice. A complete flat line is a viable physical that would mean no variability is detected. A flat line with non-zero slope is not a physically viable model: we know that 2M1207b is not fainting away or brightening indefinitely. Therefore, a model that is periodic or irregularly variable (but with a constant mean) is a physical model. The simplest of these physically viable non-constant brightness models is a sine wave.

Our fits demonstrate that the constant level (flat line) can be excluded. Of the non-constant physically viable models the sine wave gives a reasonable chi2, but more complex models are not warranted by our data.

We note that, as the referee also pointed out, there is no timescale linked to the observations that would introduce a 9-hour period slope. The fact that the primary’s light curve is constant to a very high accuracy also demonstrates that there is no instrumental sensitivity drift or any similar effect.

The changes of the manuscript include Sec. 4.2 re-writed, substitution of Fig. 4 with MCMC posterior distribution, and expanding the first paragraph of Sec. 6 for above discussion of physical viability.

## Minor comments:

>- Sec 1, end of 2nd paragraph: It might help to say 'comparing to isolated brown dwarfs', to make the sentence clearer.

We added word *isolated* for clarity.

>- Sec 1, end of 3rd paragraph: For the formation scenarios for the 2M1207 system, Lodato et al. (2005) is an important reference.

We added the reference Lodato et. al. (2005)

>- Sec 1, penultimate paragraph: I would like to see some references for the 'discovery of additional planetary-mass companions' (although they are given earlier in this section).

References for AB pic b and HR8799bcde were added as examples of additional PMC that has red color and under-luminosity problems

>- Sec 2: This is the part that might be a little too concise. One basic information I am missing is the exposure time. It would also help to point out that 1.5 minutes is the MAXIMUM cadence (if I understand this correctly). Also, 'we took 8 SPARS10 exposure sequence' might need a bit more information to help the reader.

We added information for Sec. 2. Exposure time information included, SPARS10, NSAMP=10 are explained. Major modification is the following sentence:

**Original**:In each orbit we took 8 SPARS10 exposure sequence with NSAMP=10, alternating between F160W and F125W filters, with 2--3 identical exposures in each exposure sequence.

**Revised** In each orbit, we took 8 SPARS 10 exposure sequences alternating between F125W and F160W filters. Each sequence contained 2--3 identical exposures that had 10 non-destructive read-outs and total exposure time of 88.4 s.

We added word *maximum* before cadence.

>- Sect 3: I like the innovative approach for modeling the PSF, but I would also like to see this demonstrated in a figure, i.e. an extension of Fig. 1 showing the original image, the correction image, and the two PSFs.

We included the examples of Tiny Tim PSFs as well as the correction map and modified the figure caption correspondingly.

>- Fig 2+3: Information about the epoch of the observations in JD needs to be added, either here or in the text.

JD is added at the beginning of Section 2.

>- Sec 6, 2nd paragraph: For disk masses, Scholz et al. (2006) is an important
additional reference.

Reference Scholz et. al. (2006) added for disk masses.

>- The discussion in Sec 6 touches on many interesting points, but unfortunately remains relatively vague. At the end of the 2nd paragraph, the authors write 'may place powerful constraints on the evolution of the internal structures of these contracting objects'. Maybe it is worth saying a little more here? What exactly is expected to change in the internal structures of these fully convective objects?

>- For the discussion of the rotational evolution of brown dwarfs, two relevant references that are missing are the PPVI review by Bouvier et al. (see Sect. 4.3.) and, as an update, the recent paper by Scholz, Kostov, et al.. This second paper is important because it contains a large sample of rotation periods for brown dwarfs at about the same age as 2M1207 (although most of them are more massive than 2M1207). At this age some effect of disk braking is still observed, while for the continuing evolution wind braking does play a role in the substellar regime. If 2M1207b really has a rotation period of 10h, it would be a planetary-mass counterpart of the fastest rotating young brown dwarfs. (It would also rotate at a significant fraction of breakup velocity, which might also be of interest.)

We agree with the referee at this point. We expanded the discussion from the point of view of the evolution of angular momentum mainly based on the two references recommended by the referee. We calculated the break-up rotation period is ~2 hr assuming a mass of 5 M_jup and a radius of 1.4 R_jup. The measured rotation period ~10 hr indicates rotation rate is much smaller than the break-up rotation limit.

Scholz et al. 2015 measures rotation period of 20 young brown dwarfs, and compares the BD rotation period measurements from 3 star formation region with rotation evolution tracks based on conservation of angular momentum. The age of brown dwarf in this sample is similar to 2M1207b (~6-9Myr) and the rotation periods of the brown dwarfs in this sample is closer to 2M1207b comparing to Metchev et al. (2015)

We added one paragraph to discuss the comparison of rotation period with BDs, and the evolution of angular momentum of objects with fully convective interior:

**Rotation period of ∼ 10 hour is significantly larger than field brown dwarfs from the sample of Metchev et al. (2015), but comparable to the me- dian period of the sample of Scholz et al. (2015), of which the age is similar to 2M1207b. The rotation period of 2M1207b is agreed within the range predicted by evolutionary track established from measurements of brown dwarfs assuming conservation of angular momentum (Fig. 4 in Scholz et al. (2015)), and much longer than the break-up limit, i.e. the rotation period where the equatorial centrifugal force exceeded gravitational force. Observed rotation rate for brown dwarfs of different ages show little evidence of angular momentum loss at the age of several Myr as oppose to low mass stars (Bouvier et al. 2014; Scholz et al. 2015), and agree with the model of solid body rotation for the fully convective interior. Rotation periods of planetary mass objects with well established age measurement, can place stronger constrain on the internal structure, since angular momentum loss through disks is even less likely comparing with brown dwarfs.**

We added the measurements from Scholz 2015 to left panel of Figure 5.

>- Sec 7: 'significantly longer than most field BDs with known rotation period'
>- I would advise to be careful with this statement. The available sample of field BD rotation periods is certainly very biased. The vsini data wouldindicate that rotation periods of 10-20 hours may not be that unusual (Reiners& Basri 2008).

Considering the period measurement from sample of Scholz et. al. 2015, We agree with referee at this point.

We modified following sentences in the conclusion.

The period is 10.5 hours, similar to that derived from v sin i measurements for the directly imaged exoplanet β Pic b, significantly longer than most field brown dwarfs with known rotation periods, **but comparable to the brown dwarfs in a sample with similar age to 2M1207b.**

*****

**We include two additional references.**

1. Biller et. al. (2015) (arXiv1510.07625) recently published time resolved observation on PSO J318.5-22, an isolated planetary mass object, and detected variability. We added the reference as an example of time resolved observation and rotational mapping.
2. Karalidi et. al. (2015) published a rotational mapping code that retrieve 2D atmospheric structure from light curves. We added one paragraph at the end of discussion section about the possible application of this tool in the future.

### 2015-11-01 summary/letter/letter_vAG.tex
revision finished

--- 2015-09-25 summary/letter/letter_vAF.tex
@@
 \newcommand{\mjup}{M$_{\mbox{Jup}}$}
+\newcommand{\revise}[1]{\textit{\textbf{{\color{red}{#1}}}}}
+\newcommand{\period}{$10.5^{+1.5}_{-0.8}$}
 \begin{document}
@@
   filters, respectively. We find a consistent period of
-  $10.2^{+0.9}_{-0.8}$ hours and
+\period hours and
   similar phases in both bands. The J- and H-band amplitude ratio of
@@
   \centering
-  \plottwo{original}{subtracted}
+  \plottwo{original}{subtracted}\\
+  \includegraphics[width=0.32\textwidth]{TT_2M1207A}
+  \includegraphics[width=0.32\textwidth]{TT_2M1207b}
+  \includegraphics[width=0.32\textwidth]{TT_residual}
   \caption{Point spread function subtraction allows isolating the
     secondary and accurately measuring its brightness in our WFC3
-    F160W images. {\em Upper}: original image, the position of 2M1207
-    b is indicated by a white circle.  {\em Lower:} residual image --
-    after the subtraction of the hybrid PSF, 2M1207b is detected at a
-    high significance level.}
+    F160W images. {\em Upper row:} original (left) and primary
+    subtracted (right) images. After subtraction of the primary PSF
+    and correction map, 2M1207b is detected at a high significance
+    level. \revise{{\em Lower row:} examples of \tinytim{} PSFs for
+      the primary and the secondary, and the correction map.}
+    % {\em Upper}: original image, the position of 2M1207
+    % b is indicated by a white circle.  {\em Lower:} residual image --
+    % after the subtraction of the hybrid PSF, 2M1207b is detected at a
+    % high significance level.
+  }
   \label{fig:1}
@@
 directly observed and studied via time resolved observation and
-rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
+rotational mapping
+\citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2015,Metchev2015,Heinze2015,
+Biller2015}. These techniques isolate the effect of cloud
 properties and obtained great success in determining the rotation
@@
 challenges for directly imaged exoplanets and planetary-mass
-companions to acquire high-precision light curves comparing to brown
+companions to acquire high-precision light curves comparing to
+\revise{isolated} brown
 dwarfs.
@@
 large separation argue for binary-like gravitational fragmentation
-formation\citep{Mohanty2007}.
+formation \revise{\citep{Lodato2005,Mohanty2007}}.
 
@@
 The discovery of additional planetary-mass companions with similarly
-red colors and apparent under-luminosity have highlighted 2M1207b as a
-template of low gravity ultra-cool atmospheres but as of now
-understanding the composition and structure of clouds and their
-gravity-dependence remained elusive.
+red colors \revise{(e.g. AB pic B, \cite{Chauvin2005b}, HR8799bcde,
+  \cite{Marois2008a,Marois2010})}and apparent under-luminosity have
+highlighted 2M1207b as a template of low gravity ultra-cool
+atmospheres but as of now understanding the composition and structure
+of clouds and their gravity-dependence remained elusive.
 
-In this {\em Letter} we present the first, high-contrast, high-cadence,
+In this {\em Paper} we present the first, high-contrast, high-cadence,
 high-precision, time-resolved {\em Hubble Space Telescope} (HST)
@@
 We obtained direct images of the 2M1207A+b system on UT 2014 April 11
-from 08:07:47 to 16:53:18 using HST and its Wide Field Camera 3
-\citep[WFC3, pixel scale=$0.130$mas/pixel, ][]{Mackenty2008} in the frame of
-the HST Program GO-13418 (PI: D. Apai). We acquired the observations
-in filters F125W ($\lambda_{\mathrm{pivot}}$ = 1245.9 nm, full width
-at half maximum (FWHM) = 301.5 nm) and F160W
-($\lambda_{\mathrm{pivot}}$ 1540.52, FWHM = 287.9 nm), roughly
-corresponding to the J and H bands. We used the $256\times256$ pixels
-sub-array mode to avoid memory dumps during the observations.  In
-order to provide a near-continuous coverage for detecting modulations
-we observed the 2M1207 system in 6 consecutive HST orbits, obtaining
-data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
-40 minutes. The observations were interrupted by 58-minute long Earth
-occultations every 94 minutes.
+from 08:07:47 \revise{(JD 2456758.838738)} to 16:53:18 \revise{JD
+  2456759.203681} using HST and its Wide Field Camera 3 \citep[WFC3,
+pixel scale=$0.130$mas/pixel,
+][]{Mackenty2008} in the frame of the HST Program GO-13418 (PI:
+D. Apai). We acquired the observations in filters F125W
+($\lambda_{\mathrm{pivot}}$
+= 1245.9 nm, full width at half maximum (FWHM) = 301.5 nm) and F160W
+($\lambda_{\mathrm{pivot}}$
+1540.52, FWHM = 287.9 nm), roughly corresponding to the J and H
+bands. We used the $256\times256$
+pixels sub-array mode to avoid memory dumps during the observations.
+In order to provide a near-continuous coverage for detecting
+modulations we observed the 2M1207 system in 6 consecutive HST orbits,
+obtaining data with \revise{maximum} cadence of 1.78 minutes over a
+baseline of 8 hours and 40 minutes. The observations were interrupted
+by 58-minute long Earth occultations every 94 minutes.
 
@@
 difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
-resolution elements in F125W and F160W, respectively. In each orbit we
-took 8 SPARS10 exposure sequence with NSAMP=10, alternating between
-F160W and F125W filters, with 2--3 identical exposures in each
-exposure sequence. To improve sampling and reduce the risk that the
-core of point spread function (PSF) is affected by bad pixels, we
-applied a 4-point dither pattern with differential ``X/Y'' offsets of
-1.375" in the detector frame, providing optimal non-integral (half
-pixel) step of 10.5 and 8.5 pixels in F125W and F160W,
-respectively. In total, we obtained 70 and 64 images with 10 non-destructive
-read-outs in F125W and F160W, respectively.
+resolution elements in F125W and F160W, respectively.
+%In each orbit we took 8 SPARS10 exposure sequence with NSAMP=10,
+%alternating between F160W and F125W filters, with 2--3 identical
+%exposures in each exposure sequence.
+\revise{In each orbit, we took 8 SPARS 10 exposure sequences
+  alternating between F125W and F160W filters. Each sequence contained
+  2--3 identical exposures that had 10 non-destructive read-outs and total
+  exposure time of 88.4 s} To improve sampling and reduce the risk
+that the core of point spread function (PSF) is affected by bad
+pixels, we applied a 4-point dither pattern with differential ``X/Y''
+offsets of 1.375" in the detector frame, providing optimal
+non-integral (half pixel) step of 10.5 and 8.5 pixels in F125W and
+F160W, respectively. In total, we obtained 70 and 64 images with 10 in
+F125W and F160W, respectively.
 
 \section{Data Reduction}
+
+ \begin{figure*}
+  \centering
+  \plotone{systematics}
+  \caption{F125W (left) and F160W (right) light curves under different
+    variability verification tests. Individual measurements are
+    plotted with gray crosses. Photometric measurements of the same exposure
+    sequence are binned, and binned photometry are plotted with points
+    or squares. Best fitted sinusoids are plotted with solid
+    lines. {\em Upper}: binned measurements taken in dithering
+    position 1 and 3 (red points) and that taken in 2 and 4 (blue
+    squares) are plotted with different symbols. They demonstrate same
+    trend of modulation. In upper left panel, the green line a sinusoid
+    fitted with all parameters freely varying, and the purple line is
+    a sinusoid fitted with the period set the same as that of
+    F125W. {\em Middle}: sinusoids fitted without using the
+    data taken in Orbit \#1. These curves are almost identical to the
+    curves plotted in upper panel. {\em Lower}: photometry measured
+    with AFEM-added images and best fitted sinul curves. These
+    points and curves are also almost identical to those plotted
+    in the upper panel.}
+  \label{fig:2}
+
+\end{figure*}
 
@@
 
-\section{Verification of Photometric Modulations and Amplitude
-  Estimate}
+\label{Results}
 
@@
   \centering
-  \plotone{systematics}
-  \caption{F125W (left) and F160W (right) light curves under different
-    variability verification tests. Individual measurements are
-    plotted with gray crosses. Photometric measurements of the same exposure
-    sequence are binned, and binned photometry are plotted with points
-    or squares. Best fitted sinusoids are plotted with solid
-    lines. {\em Upper}: binned measurements taken in dithering
-    position 1 and 3 (red points) and that taken in 2 and 4 (blue
-    squares) are plotted with different symbols. They demonstrate same
-    trend of modulation. In upper left panel, the green line a sinusoid
-    fitted with all parameters freely varying, and the purple line is
-    a sinusoid fitted with the period set the same as that of
-    F125W. {\em Middle}: sinusoids fitted without using the
-    data taken in Orbit \#1. These curves are almost identical to the
-    curves plotted in upper panel. {\em Lower}: photometry measured
-    with AFEM-added images and best fitted sinul curves. These
-    points and curves are also almost identical to those plotted
-    in the upper panel.}
-  \label{fig:2}
+  \plotone{sineCurveFit_binCombined}
+  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
+    with filter F125W (left) and F160W (right). Unbinned
+  measurements are plotted in gray crosses and binned photometry are
+  plotted with red points. Best fitted sinusoids are plotted
+  with blue solid lines.}
+  \label{fig:3}
 \end{figure*}
+
+\section{Verification of Photometric Modulations and Amplitude
+  Estimate}
 
@@
 
-We used a MC method to analyze the light curve, and provided amplitudes
-and periods as well as their uncertainties for both filters. We
-generated series of Gaussian distributed random noise with standard deviation
-same as the photon noise, added the noise to the original light curves, and
-fitted sinusoids to the newly combined light curves. We repeated these
-procedures  for 100,000 times and obtain the distributions of period
-and amplitude (Figure \ref{fig:4}).
-
-\section{Result}
-\label{Results}
+% We used a MC method to analyze the light curve, and provided amplitudes
+% and periods as well as their uncertainties for both filters. We
+% generated series of Gaussian distributed random noise with standard deviation
+% same as the photon noise, added the noise to the original light curves, and
+% fitted sinusoids to the newly combined light curves. We repeated these
+% procedures  for 100,000 times and obtain the distributions of period
+% and amplitude (Figure \ref{fig:4}).
 
@@
   \centering
-  \plotone{sineCurveFit_binCombined}
-  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
-    with filter F125W (left) and F160W (right). Unbinned
-  measurements are plotted in gray crosses and binned photometry are
-  plotted with red points. Best fitted sinusoids are plotted
-  with blue solid lines.}
-  \label{fig:3}
+\plotone{posterior_dist}
+  \caption{\revise{Posterior distribution for amplitude and period for F125W
+    (left) and F160W (right) light curves, with the data from the
+    first orbit included (upper) and excluded (lower). In each panel,
+    the univariate distributions for period and amplitude are plotted
+    along side with the joint distributions. The measurements and
+    uncertainties of period and amplitude are shown on the upper left
+    corner of each panel.}}
+  \label{fig:4}
 \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{periodDistr}
-  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
-  \caption{Distributions for period (left) and amplitude (right) for the light
-    curves of F125W and F160W. The bin sizes for the histograms of
-    period  and amplitude are
-  0.25 hours and 0.5\%, respectively. Histograms are
-  normalized to the maxima. In the right panel, Gaussian profiles are fitted to the
-  histograms and plotted in solid lines.}
-  \label{fig:4}
-\end{figure*}
+\revise{To further constrain the amplitude and period of the light
+  curve, we performed sinusoidal fit using Markov Chain Monte Carlo (MCMC)
+  method.  The priors for the amplitude,
+  the period and the phase of the sinusoid were all assumed to be
+  uniform distributions. The ranges of the prior
+  distributions were 0 to 5\% for the amplitude, 2 to 40 hours for the
+  period, and 0 to $2\pi$ for the phase. The posterior distributions of
+  the period and amplitude were very well constraint
+  for both two filters so that we were able to measure the amplitudes
+  and periods as well as their uncertainties. We also did the
+fitting excluding data from the first orbit. In this case, posterior
+distributions are not as well
+constraint as those for including all the data, especially the
+posterior distributions for period have significant proportion at the
+long period end. However, for both two filters, the positions of the
+peaks  of distributions of period and amplitude agree within 1-$\sigma$ uncertainty with or
+without including data from the first orbit.}
+
+\revise{We note that if the data from the first orbit were excluded, the
+  light curves could be reasonably fitted to a linear trend. When ignoring
+  data from the first orbit, For F125W light
+  curve, the reduced  $\chi^{2}$ for sinusoidal and linear fits are
+  1.138 and 1.143, and for F160W are 0.944 and 0.953. However, We are
+  in favor of the sinusoidal model based on physical viability (See
+  detailed discussion in \S\ref{sec:discussion}). }
+
+\section{Result}
 
@@
 of modulations in directly imaged planetary-mass objects. The best
-fit periods for F125W and F160W are $10.5_{-1.2}^{+1.3}$ and $9.1_{-1.0}^{+1.1}$ hours,
+fit periods for F125W and F160W are $11.1_{-1.2}^{+2.0}$ and $9.3_{-0.8}^{+2.0}$ hours,
 respectively. We also fitted the two band light curves together forcing the
 periods of two sinusoids to be the same, and obtained a period
-of $10.2^{+0.9}_{-0.8}$ hours.
+of $10.5^{+1.5}_{-0.8}$ hours.
 
@@
 \section{Discussion}
-
+\label{sec:discussion}
 \begin{figure*}
@@
       Left}: period vs. mass plot for 2M1207b (red square), solar
-    system planets and \bpic{} b (blue squares), and brown dwarfs
-    (black circles, gray shade). Final rotation rates for 2M1207b and
-    \bpic{} b estimated based on conservation of angular momentum are
-    plotted with faint red and blue squares, respectively. The mass of brown dwarfs are assumed
-    to be 30 \mjup{}. The gray rectangle that has a $\pm$15 \mjup
-    range in $x$, and a $\pm \sigma$ of brown dwarf periods range in
-    $y$, indicates a region where brown dwarfs most likely to appear
-    in this diagram. Rotation period monotonically decreases with the
+    system planets and \bpic{} b (blue squares), field brown dwarfs
+    from the study of \citet[][]{Metchev2015}
+    (black circles, gray shade) and young brown dwarfs from the study
+    of \citet{Scholz2015} (blue
+    triangles). Final rotation rates for 2M1207b and \bpic{} b
+    estimated based on conservation of angular momentum are plotted
+    with faint red and blue squares, respectively. The mass of brown
+    dwarfs are assumed to be $\sim30$ \mjup{}, and the difference mass
+    of field brown dwarfs and young brown dwarfs are added
+    artificially for the sake of clarity . The gray rectangle that has a
+    $\pm$15
+    \mjup range in $x$,
+    and a $\pm \sigma$
+    of field brown dwarf periods range in $y$,
+    indicates a region where field brown dwarfs most likely to appear in
+    this diagram. Rotation period monotonically decreases with the
     increase of mass. {\em Right}: ratio of modulation amplitude in J
     and H band vs. spectral type for 2M1207b and brown dwarfs. The
-    point for 2M1207b is shifted to +$x$ for half spectral type for
-    clarification.  The colors of the points represent J$-$H
+    point for 2M1207b is shifted to +$x$
+    for half spectral type for clarification.  The colors of the
+    points represent J$-$H
     magnitude, and the sizes of the points are proportional to the
     J-band modulation amplitudes. The gray dashed line is the result
-    of a linear fit to these points.  Correlation of J- and
-    H-band modulation amplitude ratio and spectral type is shown.}
+    of a linear fit to these points.  Correlation of J- and H-band
+    modulation amplitude ratio and spectral type is shown.}
  \label{fig:5}
@@
 photometric modulation period of a directly imaged planetary-mass
-object. We infer the rotation period of 2M1207b to be the same as
-the period of photometric variation. Although horizontal winds can cause the
-measured period to differ from true rotation period, it is
-unlikely that the difference is greater than the uncertainty of the
-measurement, since for Jupiter and Saturn, typical wind speeds are
-more than one order of magnitude smaller than the equatorial rotation speeds.
+object. \revise{Although a linear trend can also provide reasonable fit to
+  the light curves when data from the first orbit are excluded, it is
+  not a physical viable model. The light curve of a planetary mass
+  companion is either a complete flat line, or a periodical curve with constant mean. On the contrary,
+  2M1207b is not likely to constantly getting bright or faint. The
+  flatness of the light curves of 2M1207A demonstrate that there is no
+  instrumental sensitivity drift or any similar effect that can
+  introduce a $\sim9$ hour slope. We do include very 
+  long period sinusoid as possible solution for our MC fit, and
+  demonstrate that a sinusoid with period of $\sim10$
+  hour is the most probable solution with or without including data
+  from the first orbit.} We infer the rotation period of
+2M1207b to be the same as the period of photometric
+variation. Although horizontal winds can cause the measured period to
+differ from true rotation period, it is unlikely that the difference
+is greater than the uncertainty of the measurement, since for Jupiter
+and Saturn, typical wind speeds are more than one order of magnitude
+smaller than the equatorial rotation speeds.
 % Our
@@
 % \citep{Reiners2008}.
-In the left panel of Figure~\ref{fig:5} we
-compare the rotation period of 2M1207b to the solar system planets,
-\bpic{} b the only other directly imaged planet with an estimated
-period and measured \vsini, and field brown dwarfs from the study of
-\cite[][]{Metchev2015}. \citet[][]{Snellen2014} measured \vsini{} for
-\bpic{} b and demonstrated that it fits a trend defined by Solar
+In the left panel of Figure~\ref{fig:5} we compare the rotation period
+of 2M1207b to the solar system planets, \bpic{} b the only other
+directly imaged planet with an estimated period and measured \vsini,
+field brown dwarfs from the study of \cite[][]{Metchev2015},
+\revise{and young brown dwarfs (UpSco, age $\sim 11$ Myr) from
+  \cite[][]{Scholz2015}}. \citet[][]{Snellen2014} measured \vsini{}
+for \bpic{} b and demonstrated that it fits a trend defined by Solar
 System planets in which more massive planets have faster rotation
@@
 contribute insufficient evidence for a formation in a disk vs. in a
-cloud core environment. Although rotation rates may have limited value
-for deciphering formation pathways, measurements of mass, age, and
-rotation periods will map the angular momentum evolution of
-planetary-mass objects and may place powerful constraints on the
-evolution of the internal structures of these contracting objects.
+cloud core environment.
+
+\revise{Rotation period of $\sim 10$
+  hour is significantly larger than field brown dwarfs from the sample
+  of \cite{Metchev2015}, but comparable to the median period
+  of the sample of \cite{Scholz2015}, of which the age is similar
+  to 2M1207b. The rotation period of 2M1207b
+  is agreed within the range predicted by evolutionary track
+  established from measurements of brown dwarfs assuming conservation
+  of angular momentum (Fig. 4 in \cite{Scholz2015}), and much longer
+  than the break-up limit, i.e. the rotation period where the
+  equatorial centrifugal force exceeded gravitational force. Observed
+  rotation rate for brown dwarfs of different ages show little
+  evidence of angular momentum loss at the age of several Myr as
+  oppose to low mass stars
+  \citep{Bouvier2014, Scholz2015}, and agree with the model of solid
+  body rotation for the fully convective interior. Rotation periods of
+planetary mass objects with well established age measurement, can
+place stronger constrain on the internal structure, since angular
+momentum loss through disks is even less likely comparing with brown dwarfs.}
+
+% Although rotation
+% rates may have limited value for deciphering formation pathways,
+% measurements of mass, age, and rotation periods will map the angular
+% momentum evolution of planetary-mass objects and may place powerful
+% constraints on the evolution of the internal structures of these
+% contracting objects.
 %{\em Add younger BDs and this may change}
@@
 
+\revise{Recently, \citet{Karalidi2015} published \textit{Aeolus}, an
+atmosphere mapping code that retrieves 2-dimension atmosphere features
+from the light curves. In the future, with higher signal-to-noise
+light curves, we will be able to study more detailed structure of the
+atmospheres of directly imaged exoplanets with this tool. }
+
 % {\color{red}This trend can be qualitatively explained using the toy model proposed
@@
 $10.2^{+0.9}_{-0.8}$ hours, similar to that derived from \vsini{} 
-measurements for the directly imaged exoplanet \bpic{} b and
+measurements for the directly imaged exoplanet \bpic{} b, 
 significantly longer than most field brown dwarfs with known rotation
-periods. The amplitude ratio of J- and H-band is very
+periods, and \revise{comparable to  the brown dwarfs
+in a sample with similar age to 2M1207b.} The amplitude ratio of J- and H-band is very
 similar to that of a field brown dwarf with identical L5 spectral type, although they have

### 2015-11-01 2M1207ANALYSIS/F125Model1.py

@@ -1,0 +1,18 @@
+from pymc import Uniform, deterministic, Normal, MCMC
+import numpy as np
+
+t125, F125B = np.loadtxt('F125_data1.dat', usecols=(0, 2), unpack=True)
+sigma125 = 0.0134
+
+
+amplitude = Uniform('amplitude', lower=0, upper=0.05)
+period = Uniform('period', lower=2, upper=40, doc='period of sinusoid')
+phase = Uniform('phase', lower=0, upper=2 * np.pi)
+
+
+@deterministic(plot=False)
+def count(Amp=amplitude, T=period, Phase=phase):
+    return Amp * np.sin((2 * np.pi / T) * t125 + Phase) + 1
+
+lcModel = Normal('light curve', mu=count, tau=1. / sigma125**2, value=F125B,
+                 observed=True)

### 2015-11-01 2M1207ANALYSIS/F160Model1.py

@@ -1,0 +1,18 @@
+from pymc import Uniform, deterministic, Normal
+import numpy as np
+
+t160, F160B = np.loadtxt('F160_data1.dat', usecols=(0, 2), unpack=True)
+sigma160 = 0.0112
+
+
+amplitude = Uniform('amplitude', lower=0, upper=0.05)
+period = Uniform('period', lower=2, upper=40, doc='period of sinusoid')
+phase = Uniform('phase', lower=0, upper=2 * np.pi)
+
+
+@deterministic(plot=False)
+def count(Amp=amplitude, T=period, Phase=phase):
+    return Amp * np.sin((2 * np.pi / T) * t160 + Phase) + 1
+
+lcModel = Normal('light curve', mu=count, tau=1. / sigma160**2, value=F160B,
+                 observed=True)

### 2015-11-01 2M1207ANALYSIS/MCMCFit.py

@@ -1,0 +1,54 @@
+import F125Model
+from pymc import MCMC
+import visualMCMC
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.optimize import curve_fit
+
+plt.style.use('paper')
+
+
+def gauss(x, a, x0, sigma):
+    return a * np.exp(-(x - x0)**2 / (2 * sigma**2))
+
+M = MCMC(F125Model)
+M.sample(iter=1000000, burn=1000, thin=10)
+
+title = 'F125W: include Orbit 1'
+plt.close('all')
+p = visualMCMC.visualMCMC(M.trace('period')[:],
+                          M.trace('amplitude')[:] * 100,
+                          xlim=[5, 25], ylim=[0, 2.5], color='b')
+p.set_axis_labels('Period [h]', 'Amplitude [%]')
+
+# calculate the 1 sigma error for period and amplitude
+pBins = np.linspace(6, 40, 171)
+midBins = (pBins[:-1] + pBins[1:]) / 2
+dBin = pBins[1] - pBins[0]
+pcount, pBin = np.histogram(M.trace('period')[:], bins=pBins, normed=1)
+p0 = midBins[pcount == pcount.max()][0]
+
+
+p_floor = midBins[(pcount <= 0.60 * pcount[midBins == p0]) &
+                  (midBins < p0)][-1]
+p_ceil = midBins[(pcount <= 0.60 * pcount[midBins == p0]) & (midBins > p0)][0]
+
+aBins = np.linspace(0.00, 0.025, 51) * 100
+midBins = (aBins[:-1] + aBins[1:]) / 2
+aCount, aBin = np.histogram(
+    M.trace('amplitude')[:] * 100, bins=aBins, normed=1)
+gpAmp, cov = curve_fit(gauss, midBins,
+                       aCount, p0=[aCount.max(), 1, 0.5])
+
+
+fig = plt.gcf()
+fig.axes[0].text(0.02, 0.05, title, transform=fig.axes[0].transAxes)
+p_low = '{0:.2f}'.format(p0 - p_floor)
+p_high = '{0:.2f}'.format(p_ceil - p0)
+fig.axes[0].text(0.02, 0.85, r'$p = {0:.2f}^{{+{1:.2f}}}_{{-{2:.2f}}}$'
+                 .format(p0, p_ceil - p0, p0 - p_floor) + '\n' +
[…]

### 2015-11-01 2M1207ANALYSIS/fileInfo.py

@@ -11,6 +11,7 @@ import os
 import pandas as pd
 from math import floor
 
+
 def getTargetNo(file_list):
     """
     get the target number
@@ -30,7 +31,7 @@ if __name__ == '__main__':
     orbitNo = []
     ditherNo = []
     exposureNo = []
-    
+
     for fits_file in sorted(glob.glob(os.path.join(dataDir, target, '*{0}.fits'.format(fileType)))):
         fits_content = fits.open(fits_file)
         file_list.append(fits_file.split('/')[-1])
@@ -41,13 +42,14 @@ if __name__ == '__main__':
         time_list.append(header['time-obs'])
         exposureTime.append(header['exptime'])
         targOff1 = floor(header['postarg1'])
-        targOff2 = floor(header['postarg2']) * 2 # so that dither number could be expressed as targOff1 + tarOff2
+        # so that dither number could be expressed as targOff1 + tarOff2
+        targOff2 = floor(header['postarg2']) * 2
         ditherNo.append(int(targOff1 + targOff2))
         fits_content.close()
 
     orbitNo = getTargetNo(file_list)
     filter0 = filter_list[0]
-    orbit0 =  orbitNo[0]
+    orbit0 = orbitNo[0]
     exposure0 = 0
     for filter_i, orbit_i in zip(filter_list, orbitNo):
         if filter_i == filter0 and orbit_i == orbit0:
@@ -65,6 +67,6 @@ if __name__ == '__main__':
     fileInfo = pd.DataFrame([line for line in zip(file_list,
                                                   filter_list, orbitNo, angle_list,
                                                   ditherNo, exposureNo, date_list,
-                                                  time_list, exposureTime)], columns =
-                            ['file name', 'filter', 'orbit', 'Pos Angle', 'dither', 'exposure set', 'obs date', 'obs time', 'exposure time'])
-    fileInfo.to_csv('{0}_{1}_fileInfo.csv'.format(target, fileType), index = False)
+                                                  time_list, exposureTime)], columns=['file name', 'filter', 'orbit', 'Pos Angle', 'dither', 'exposure set', 'obs date', 'obs time', 'exposure time'])
+    fileInfo.to_csv(
+        '{0}_{1}_fileInfo.csv'.format(target, fileType), index=False)

### 2015-11-01 2M1207ANALYSIS/fitChisq.py

@@ -1,0 +1,184 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import numpy as np
+import pandas as pd
+from plotLightCurve import normFlux
+from linearFit import linearFit
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+"""calculate chisq for two fit
+"""
+
+
+def normedSin(t, p):
+    return p[0] * np.sin((2 * np.pi / p[1]) * t + p[2]) + 1
+
+
+def chisq0(y, ymod, sigma, DoF):
+    """calcualte reduced chisq"""
+    return np.sum((y - ymod)**2 / sigma**2) / DoF
+
+
+def linearChisq(x, y, sigma):
+    if type(sigma) is int or float:
+        sigma = np.array([sigma] * len(x))
+    b, m, sigb, sigm, chisq = linearFit(x, y, sigma)
+    return chisq
+
+
+def allChisq(y, ymod, x, sigma):
+    chisq_1 = chisq0(y, ymod, sigma, len(y) - 4)
+    chisq_2 = chisq0(y, np.array([1] * len(y)),
+                     sigma, len(y) - 1)
+    chisq_3 = linearChisq(x, y, sigma)
+    return chisq_1, chisq_2, chisq_3
+
+
+def plotDistDistr(y, ymod, x, sigma):
+    diff1 = y - ymod
+    b, m, _, _, _ = linearFit(x, y, np.array([sigma] * len(x)))
+    ymod2 = m * x + b
+    diff2 = y - ymod2
+    diffbin = np.linspace(-3, 3, 15)
+    fig = plt.figure(figsize=(12, 6))
+    ax1 = fig.add_subplot(121)
+    sinFunc = interp1d(x, ymod, kind='cubic')
+    t = np.linspace(x.min(), x.max(), 100)
+    lines1 = ax1.plot(t, sinFunc(t))
+    lines2 = ax1.plot(x, ymod2)
+    ax1.plot(x, y, '.', color='k')
+    ax1.set_xlabel('Time (h)')
+    ax1.set_ylabel('Normalized Flux')
+
+    ax2 = fig.add_subplot(122)
+    ax2.hist(diff1 / sigma, diffbin, label='sinusoidal', lw=2,
+             fc=lines1[0].get_color(), ec=lines1[0].get_color(), alpha=0.8)
+    ax2.hist(diff2 / sigma, diffbin, label='linear', lw=2,
[…]

### 2015-11-01 2M1207ANALYSIS/illustrateImage.py

@@ -47,6 +47,51 @@ if __name__ == '__main__':
         ax.set_xlabel('X (pixel)')
         ax.set_ylabel('Y (pixel)')
 
-    plt.show()
+    # plt.show()
     fig1.savefig('original.pdf')
     fig2.savefig('subtracted.pdf')
+
+    PSF1 = fits.getdata('./fitsResult/PSF1.fits', 0)
+    PSF2 = fits.getdata('./fitsResult/PSF2.fits', 0)
+    fig3, ax3 = plt.subplots()
+    cax3 = ax3.imshow(PSF1, cmap='hot', origin='lower',
+                      interpolation='nearest',
+                      norm=BoundaryNorm(bd1, ncolors=255))
+    ax3.set_title('TinyTim PSF for 2M1207A')
+    ax3.set_xlim([0, 26])
+    ax3.set_ylim([0, 26])
+    cbar3 = fig3.colorbar(cax3, ticks=np.logspace(-1, 4, 6))
+    cbar3.formatter = mpl.ticker.LogFormatter()
+    cbar3.update_ticks()
+    ax3.set_xlabel('X (pixel)')
+    ax3.set_ylabel('Y (pixel)')
+    fig3.savefig('TT_2M1207A.pdf')
+
+    fig4, ax4 = plt.subplots()
+    cax4 = ax4.imshow(PSF2, cmap='hot', origin='lower',
+                      interpolation='nearest',
+                      norm=BoundaryNorm(np.logspace(-3, 2, 255), ncolors=255))
+    ax4.set_title('TinyTim PSF for 2M1207b')
+    ax4.set_xlim([0, 26])
+    ax4.set_ylim([0, 26])
+    cbar4 = fig4.colorbar(cax4, ticks=np.logspace(-3, 2, 6))
+    cbar4.formatter = mpl.ticker.LogFormatter()
+    cbar4.update_ticks()
+    ax4.set_xlabel('X (pixel)')
+    ax4.set_ylabel('Y (pixel)')
+    fig4.savefig('TT_2M1207b.pdf')
+
+    residual = fits.getdata('./fitsResult/residual.fits', 0)
+    fig5, ax5 = plt.subplots()
+    cax5 = ax5.imshow(residual, cmap='hot', origin='lower',
+                      interpolation='nearest',
+                      norm=BoundaryNorm(np.linspace(-30, 30, 255), ncolors=255))
[…]

### 2015-11-01 2M1207ANALYSIS/period.py

@@ -51,7 +51,9 @@ if __name__ == '__main__':
         index_col='datetime')
     df160 = df160.sort_index()
     df160['Time'] = np.float32(
-        df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
+        df160.index.values - df125.index.values[0]) / (60 * 60 * 1e9)
+    # print((df125['Time'].values[1:] - df125['Time'].values[:-1]) * 60)
+    # print((df160['Time'].values[1:] - df160['Time'].values[:-1]) * 60)
     f125A0, f125B0 = normFlux(df125, normDither=True)
     f160A0, f160B0 = normFlux(df160, normDither=True)
     # I quit, trying matlab ...
@@ -65,7 +67,7 @@ if __name__ == '__main__':
     fig = plt.figure()
     gs = mpl.gridspec.GridSpec(3, 2)
     axOut = fig.add_subplot(gs[:, :])
-    axOut.set_xlabel('Time (h)', labelpad=30)
+    axOut.set_xlabel('Time - 2014-04-11 08:07:47 [h]', labelpad=30)
     axOut.set_ylabel('Normalized flux', labelpad=56)
     ax125B = fig.add_subplot(gs[0:2, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]

### 2015-11-01 2M1207ANALYSIS/periodFit.m

@@ -1,5 +1,5 @@
 function pFit=periodFit(fn, p0)
-[t, ~, fB] = textread(fn, '%f %f %f');
+[t, fB] = textread(fn, '%f, %f');
 figure();
 F=@(p,xdata)p(1)*sin((2*pi/p(2))*xdata+p(3)) + 1;
 [pFit,~,~,~,~] = lsqcurvefit(F,p0,t,fB);

### 2015-11-01 2M1207ANALYSIS/plotRotation.py

@@ -40,7 +40,7 @@ if __name__ == '__main__':
     vBD = 2 * np.pi * (1 * 69911) / (BDperiod * 3600)
     # suppose BD has period of 1 Mjup
     ax_p.plot(np.zeros(len(BDperiod)) + 30, BDperiod,
-              'o', mec='k', mfc='none', ms=10)
+              'o', mec='k', mfc='none', ms=10, label='Metchev et al. (2015)')
     ax_p.text(45, 10, 'Brown dwarfs', rotation=90)
     # ax_p.plot(np.zeros(len(BDperiod)) + 30, vBD,
     #           'o', mec='k', mfc='none', ms=10)
@@ -93,6 +93,11 @@ if __name__ == '__main__':
                head_width=1.8, head_length=0.8)
     ax_p.set_ylim(0, 29)
 
+    BDperiod2 = np.loadtxt('scholz2015.dat')
+    BDperiod2 = BDperiod2 * 24  # convert day to hour
+    ax_p.plot(np.zeros(BDperiod2.shape) + 45, BDperiod2,
+              '^', mec='b', mfc='none', ms=10, label='Scholz et al. (2015)')
+    ax_p.legend(loc='best')
     plt.show()
     plt.savefig('rotationDiagram.pdf')
     # fig_v, ax_v = plt.subplots()

### 2015-11-01 2M1207ANALYSIS/systematics.py

@@ -55,7 +55,7 @@ if __name__ == '__main__':
         index_col='datetime')
     df160 = df160.sort_index()
     df160['Time'] = np.float32(
-        df160.index.values - df160.index.values[0]) / (60 * 60 * 1e9)
+        df160.index.values - df125.index.values[0]) / (60 * 60 * 1e9)
     f125A0, f125B0 = normFlux(df125, normDither=True)
     f160A0, f160B0 = normFlux(df160, normDither=True)
 
@@ -71,7 +71,7 @@ if __name__ == '__main__':
 
     gs = mpl.gridspec.GridSpec(3, 2)
     axOut = fig.add_subplot(gs[:, :])
-    axOut.set_xlabel('Time (h)', labelpad=24)
+    axOut.set_xlabel('Time - 2014-04-11 08:07:47 [h]', labelpad=24)
     axOut.set_ylabel('Normalized flux', labelpad=42)
     ax125B = fig.add_subplot(gs[0, 0])
     df125_1 = df125[(df125['DITHER'] == 0) | (df125['DITHER'] == 2)]

### 2015-11-01 2M1207ANALYSIS/visualMCMC.py

@@ -1,0 +1,17 @@
+#! /usr/bin/env python
+from __future__ import print_function, division
+import seaborn as sns
+
+"""visualize the MCMC result
+"""
+
+sns.set(style="white", color_codes=False)
+
+
+def visualMCMC(data1, data2, xlim=None, ylim=None, color='b'):
+    dist2d = sns.jointplot(data1, data2, xlim=xlim, ylim=ylim,
+                           stat_func=None, kind='hex', color=color,
+                           marginal_kws=dict(bins=40),
+                           joint_kws=dict(bins=40))
+
+    return dist2d

### 2015-11-01 python_src/linearFit.py

@@ -16,5 +16,5 @@ def linearFit(x, y, dy=None):
     b = b.flat[0]
     m = m.flat[0]
     sigb, sigm = np.sqrt(np.diag(mat1))
-    chisq = 1. / (len(x) - 2) * ((y - m * x - b)**2 / dy**2).sum(axis=-1)
+    chisq = 1. / (len(x) - 2) * np.sum((y - m * x - b)**2 / dy**2)
     return b, m, sigb, sigm, chisq

### 2015-12-11 summary/referee_report_reply.md
duech

@@
 # Referee report reply
+
+We thank the referee for the constructive and prompt report.
+In response to the major comment, we carried out an MCMC fit to the data that convincingly supported our previous results; we followed and addressed each of the minor comments, too.
 
@@
 
-We agree with the referee that our original fitting method is inappropriate in the way that it artificially adds noise to the light curve.
-Therefore we did a rigorous MCMC fitting to measure the period and amplitude based on a sinusoidal model.
-We cannot use normal period search routines (e.g.
-Fourier analysis, auto-correlation) because the period of the modulation is larger than our observation baseline.
-We assumed uniform distribution for the period, amplitude and phase of the sinusoid as priors and included period as long as 40 hours as possible solution.
-We did the fitting for both including and excluding data from the first orbit.
-Even when the data from the first orbit were excluded, the posterior distributions for the amplitude and period were constraint, though not as well as those for the fitting include the whole dataset.
-Our measurements for period and amplitude agree within 1-sigma uncertainties with or without using data from the first orbit.
-Using the posterior distribution of MCMC fitting, we can show the statistical significance of our measurement.
+We agree with the referee that our original fitting method artificially amplified the noise.
+Normal period search routines (e.g.
+Fourier analysis, auto-correlation) are not applicable because the period of the modulation is larger than our observation baseline.
+Therefore we carried out a rigorous MCMC fit to measure the period and amplitude based on a sinusoidal model.
+We assumed uniform distributions for the periods, amplitudes and phases of the sine waves as priors and included period as long as 40 hours as possible solution.
+We fitted the data with and without the data from the first orbit to quantitatively assess the importance of the less stable data.
 
-We also added discussion from the perspective of physical viability of the light curve models and explained a sinusoid is the most suitable choice.
-A complete flat line is a viable physical that would mean no variability is detected.
-A flat line with non-zero slope is not a physically viable model: we know that 2M1207b is not fainting away or brightening indefinitely.
-Therefore, a model that is periodic or irregularly variable (but with a constant mean) is a physical model.
-The simplest of these physically viable non-constant brightness models is a sine wave.
+By allowing very long period sine waves, we in effect allow a nearly linear solution (which directly address the major comment of the referee).
 
-Our fits demonstrate that the constant level (flat line) can be excluded.
-Of the non-constant physically viable models the sine wave gives a reasonable chi2, but more complex models are not warranted by our data.
+A new figure for the posterior distribution of the MCMC fit is shown in Figure 4 in the updated manuscript.
 
-We note that, as the referee also pointed out, there is no timescale linked to the observations that would introduce a 9-hour period slope.
-The fact that the primary’s light curve is constant to a very high accuracy also demonstrates that there is no instrumental sensitivity drift or any similar effect.
+The new analysis leads to two important results:
 
-The changes of the manuscript include Sec.
-4.2 re-writed, substitution of Fig.
-4 with MCMC posterior distribution, and expanding the first paragraph of Sec.
-6 for above discussion of physical viability.
+1. The posterior distributions for the period concentrate on ~10 hour and agree with what we found previously. The probability for very long period (P > 15 hour) is negligible. 
+2. Even only using data from orbits 2-6, the posterior distributions for the amplitude and period are constrained and show result that agree within 1-sigma with the fit using data from orbits 1-6.
+
+The MCMC analysis and above two results directly address and settle the major comments from the referee. Below we explain our response to the minor comments.
 
@@
 
-References for AB pic b and HR8799bcde were added as examples of additional PMC that has red color and under-luminosity problems
+References for AB pic b and HR8799bcde were added as examples of additional PMCs that has red color and under-luminosity problems
 
@@
 
-We added information for Sec. 2. Exposure time information included, SPARS10, NSAMP=10 are explained. Major modification is the following sentence:
+We added information for Sec. 2. Exposure time information are included, SPARS10, NSAMP=10 are explained. Major modification is the following sentence:
 
@@
 
-We agree with the referee at this point.
+We thank the referee for this excellent point.
 We expanded the discussion from the point of view of the evolution of angular momentum mainly based on the two references recommended by the referee.
 We calculated the break-up rotation period is ~2 hr assuming a mass of 5 M_jup and a radius of 1.4 R_jup.
-The measured rotation period ~10 hr indicates rotation rate is much smaller than the break-up rotation limit.
+The measured rotation period ~10 hr indicates rotation rate is much lower than the break-up rotation limit.
 
 Scholz et al.
-2015 measures rotation period of 20 young brown dwarfs, and compares the BD rotation period measurements from 3 star formation region with rotation evolution tracks based on conservation of angular momentum.
-The age of brown dwarf in this sample is similar to 2M1207b (~6-9Myr) and the rotation periods of the brown dwarfs in this sample is closer to 2M1207b comparing to Metchev et al.
+2015 measured rotation periods of 20 young brown dwarfs, and compared the BD rotation periods from 3 star-forming regions with rotational evolution tracks based on the conservation of angular momentum.
+The age of brown dwarfs in this sample is similar to 2M1207b and the rotation periods are closer to that of 2M1207b, in contrast to those of the older brown dwarfs studied in Metchev et al.
+(2015).
+
+We added one paragraph to Sec. 6 to discuss the comparison of rotation period with BDs, and the evolution of angular momentum of objects with fully convective interior.
+
+We added the measurements from Scholz et al.
+(2015) to left panel of Figure 5.
+We also modified the conclusion saying our rotation period measurement is similar to those of brown dwarfs in the sample of Scholz et al.
 (2015)
-
-We added one paragraph to discuss the comparison of rotation period with BDs, and the evolution of angular momentum of objects with fully convective interior:
-
-**Rotation period of ∼ 10 hour is significantly larger than field brown dwarfs from the sample of Metchev et al.
-(2015), but comparable to the me- dian period of the sample of Scholz et al.
-(2015), of which the age is similar to 2M1207b.
-The rotation period of 2M1207b is agreed within the range predicted by evolutionary track established from measurements of brown dwarfs assuming conservation of angular momentum (Fig.
-4 in Scholz et al.
-(2015)), and much longer than the break-up limit, i.e.
-the rotation period where the equatorial centrifugal force exceeded gravitational force.
-Observed rotation rate for brown dwarfs of different ages show little evidence of angular momentum loss at the age of several Myr as oppose to low mass stars (Bouvier et al.
-2014; Scholz et al.
-2015), and agree with the model of solid body rotation for the fully convective interior.
-Rotation periods of planetary mass objects with well established age measurement, can place stronger constrain on the internal structure, since angular momentum loss through disks is even less likely comparing with brown dwarfs.**
-
-We added the measurements from Scholz 2015 to left panel of Figure 5.
 
@@
 The available sample of field BD rotation periods is certainly very biased.
-The vsini data wouldindicate that rotation periods of 10-20 hours may not be that unusual (Reiners& Basri 2008).
+The vsini data would indicate that rotation periods of 10-20 hours may not be that unusual (Reiners& Basri 2008).
 
-Considering the period measurement from sample of Scholz et. al. 2015, We agree with referee at this point.
+We compared our rotation period with the v sin i measurements from Reiners&Basri (2008).
+We found that comparing to L-type brown dwarfs in that sample, equatorial rotation speed of 2M1207b is still lower than most of brown dwarfs.
+We agree with the referee that the available sample can be biased, therefore we emphasize that our comparison is limited to the sample with known rotation periods.
 
-We modified following sentences in the conclusion.
-
-The period is 10.5 hours, similar to that derived from v sin i measurements for the directly imaged exoplanet β Pic b, significantly longer than most field brown dwarfs with known rotation periods, **but comparable to the brown dwarfs in a sample with similar age to 2M1207b.**
+We added the comparison of rotation rate with L-type brown dwarfs in the sample of Reiners&Basri (2008) in the discussion section.
 
@@
 
-**We include two additional references.**
+**We included two additional references.**
 

### 2015-12-11 summary/letter/letter_AH.tex
duech

--- 2015-11-01 summary/letter/letter_vAG.tex
@@
 \usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 \bibliographystyle{apj}
@@
 \newcommand{\mjup}{M$_{\mbox{Jup}}$}
-\newcommand{\revise}[1]{\textit{\textbf{{\color{red}{#1}}}}}
+\newcommand{\revise}[1]{\textbf{{\color{cyan}{#1}}}}
+\renewcommand{\revise}{}
 \newcommand{\period}{$10.5^{+1.5}_{-0.8}$}
+\newcommand{\Jperiod}{$11.1^{+2.0}_{{-1.2}}$}
+\newcommand{\Jamp}{$1.36\pm0.23 \%$}
+\newcommand{\Hperiod}{$9.3^{+2.0}_{{-0.8}}$}
+\newcommand{\Hamp}{$0.78\pm0.22 \%$}
 \begin{document}
@@
 \title{Discovery of Rotational Modulations in the Planetary-mass
-  Companion 2M1207\lowercase{b}: An intermediate Rotation Period and Heterogeneous Clouds in a Low
+  Companion 2M1207\lowercase{b}: Intermediate Rotation Period and Heterogeneous Clouds in a Low
   Gravity Atmosphere}
@@
   combined light curve as well as in different subsets of the data.
-  The amplitudes are 1.45\% in the F125W and 0.92\% in the F160W
+  The amplitudes are 1.36\% in the F125W and 0.78\% in the F160W
   filters, respectively. We find a consistent period of
-\period hours and
+\period{} hours and
   similar phases in both bands. The J- and H-band amplitude ratio of
@@
 Presence of condensate clouds is one the most unique features of the
-ultra-cool atmosphere of directly imaged exoplanet and brown
+ultra-cool atmosphere of directly imaged exoplanets and brown
 dwarfs. Studies of formation and properties of condensate clouds
@@
 properties and obtained great success in determining the rotation
-period and unveiling the structures of the atmosphere of brown dwarfs
-. \citet{Kostov2013}
-demonstrated that these techniques can be applied to directly imaged
+period and unveiling the structures of the atmospheres of brown dwarfs.
+ \citet{Kostov2013} demonstrated that these techniques can be applied to directly imaged
 exoplanets, too, allowing comparative studies of objects with
-different surface gravities. However, high contrast magnifies the
+different surface gravities. However, high contrast amplifies the
 challenges for directly imaged exoplanets and planetary-mass
-companions to acquire high-precision light curves comparing to
+companions to acquire high-precision light curves compared to
 \revise{isolated} brown
@@
 The discovery of additional planetary-mass companions with similarly
-red colors \revise{(e.g. AB pic B, \cite{Chauvin2005b}, HR8799bcde,
-  \cite{Marois2008a,Marois2010})}and apparent under-luminosity have
+red colors \revise{(e.g. AB Pic B, \citealt[][]{Chauvin2005b}, HR8799bcde,
+  \citealt[][]{Marois2008a,Marois2010})} and apparent under-luminosity have
 highlighted 2M1207b as a template of low gravity ultra-cool
@@
 We obtained direct images of the 2M1207A+b system on UT 2014 April 11
-from 08:07:47 \revise{(JD 2456758.838738)} to 16:53:18 \revise{JD
-  2456759.203681} using HST and its Wide Field Camera 3 \citep[WFC3,
+from 08:07:47 \revise{(JD 2456758.838738)} to 16:53:18 \revise{(JD
+  2456759.203681)} using HST and its Wide Field Camera 3 \citep[WFC3,
 pixel scale=$0.130$mas/pixel,
@@
   2--3 identical exposures that had 10 non-destructive read-outs and total
-  exposure time of 88.4 s} To improve sampling and reduce the risk
+  exposure time of 88.4 s.} To improve sampling and reduce the risk
 that the core of point spread function (PSF) is affected by bad
@@
 shapes would argue against a genuine signal.  We found that the periods
-of the best fit sine waves were similar, $10.5^{+1.2}_{-1.3}$h for
-F125W and $9.1^{+1.1}_{-1.0}$h for F160W. These periods are consistent
+of the best fit sine waves were similar, \Jperiod{} h for
+F125W and \Hperiod{} h for F160W. These periods are consistent
 within the uncertainty. Furthermore, these periods are not close to
@@
 \plotone{posterior_dist}
-  \caption{\revise{Posterior distribution for amplitude and period for F125W
-    (left) and F160W (right) light curves, with the data from the
-    first orbit included (upper) and excluded (lower). In each panel,
+  \caption{\revise{Posterior distributions for amplitudes and periods for F125W
+    (left) and F160W (right) light curves, using data from orbits 1-6
+    (upper) and data from orbits 2-6 (lower). In each panel,
     the univariate distributions for period and amplitude are plotted
-    along side with the joint distributions. The measurements and
+    along side with the joint distribution. The values and
     uncertainties of period and amplitude are shown on the upper left
@@
 
-\revise{To further constrain the amplitude and period of the light
-  curve, we performed sinusoidal fit using Markov Chain Monte Carlo (MCMC)
-  method.  The priors for the amplitude,
-  the period and the phase of the sinusoid were all assumed to be
-  uniform distributions. The ranges of the prior
-  distributions were 0 to 5\% for the amplitude, 2 to 40 hours for the
-  period, and 0 to $2\pi$ for the phase. The posterior distributions of
-  the period and amplitude were very well constraint
-  for both two filters so that we were able to measure the amplitudes
-  and periods as well as their uncertainties. We also did the
-fitting excluding data from the first orbit. In this case, posterior
-distributions are not as well
-constraint as those for including all the data, especially the
-posterior distributions for period have significant proportion at the
-long period end. However, for both two filters, the positions of the
-peaks  of distributions of period and amplitude agree within 1-$\sigma$ uncertainty with or
-without including data from the first orbit.}
+\revise{To further constrain the amplitudes and periods of the light
+  curves, we performed sinusoidal fit using Markov Chain Monte Carlo
+  (MCMC) method.  The priors for the amplitudes, the periods and the
+  phases of the sine waves were all assumed to be uniform
+  distributions. The ranges of the prior distributions were 0 to 5\%
+  for the amplitudes, 2 to 40 hours for the periods, and 0 to $2\pi$
+  for the phases. The results of the MCMC fit are shown in Figure
+  \ref{fig:4}. The posterior distributions of the periods and amplitudes
+  are very well constrained for both two filters so that we are able
+  to measure the amplitudes and periods as well as their
+  uncertainties. For F125W, the amplitude and period are \Jamp{} and
+  \Jperiod{}, respectively, and for F160W, they are \Hamp{} and
+  \Hperiod{}, respectively. We also repeated the fitting excluding data from the
+  first orbit in order to quantitatively assess the influence of these
+  less stable data points. Even in the case of limiting
+  our data to Orbits 2-6, the posterior probability distribution peaks
+  at  periods and amplitudes very similar to those found for the entire dataset,
+  demonstrating that a periodic solution is preferred with or without
+  the first orbit data. Nevertheless, unsurprisingly, when shortening
+  the baseline by considering only Orbits 2-6 results in a long-period
+  tail in the probability distribution.}
 
-\revise{We note that if the data from the first orbit were excluded, the
-  light curves could be reasonably fitted to a linear trend. When ignoring
-  data from the first orbit, For F125W light
-  curve, the reduced  $\chi^{2}$ for sinusoidal and linear fits are
-  1.138 and 1.143, and for F160W are 0.944 and 0.953. However, We are
-  in favor of the sinusoidal model based on physical viability (See
-  detailed discussion in \S\ref{sec:discussion}). }
+% \revise{We note that if the data from the first orbit were excluded, the
+%   light curves could be reasonably fitted to a linear trend. When ignoring
+%   data from the first orbit, For F125W light
+%   curve, the reduced  $\chi^{2}$ for sinusoidal and linear fits are
+%   1.138 and 1.143, and for F160W are 0.944 and 0.953. However, We are
+%   in favor of the sinusoidal model based on physical viability (See
+%   detailed discussion in \S\ref{sec:discussion}). }
 
@@
 periods of two sinusoids to be the same, and obtained a period
-of $10.5^{+1.5}_{-0.8}$ hours.
+of \period{} hours.
 
@@
 distributions, we determin that the  amplitude for F125W is
-1.45\% with a standard deviation of 0.22\%, and  the amplitude for F160W is
-0.92\% with a standard deviation of 0.20\%. The amplitudes of two
+1.36\% with a standard deviation of 0.23\%, and  the amplitude for F160W is
+0.78\% with a standard deviation of 0.22\%. The amplitudes of two
 bands are separated by more than 2-$\sigma$. The amplitude
-for F125W is $1.58\pm0.27$ times of that for F160W light curve.
+for F125W is $1.74\pm0.30$ times of that for F160W light curve.
 
@@
 
-An important result of our study is the direct measurement of the
-photometric modulation period of a directly imaged planetary-mass
-object. \revise{Although a linear trend can also provide reasonable fit to
-  the light curves when data from the first orbit are excluded, it is
-  not a physical viable model. The light curve of a planetary mass
-  companion is either a complete flat line, or a periodical curve with constant mean. On the contrary,
+\reviseTwo{Because the period of modulation is longer than the
+  observation time baseline, the most suitable method to constrain
+  period is to fit the light curves with physical viable model. The light curve of a planetary mass
+  companion is either a complete flat line, or a periodical curve with
+  constant mean for which a sine wave is the most simple form. On the contrary,
   2M1207b is not likely to constantly getting bright or faint. The
@@
   hour is the most probable solution with or without including data
-  from the first orbit.} We infer the rotation period of
+  from the first orbit. In the paper, we include the whole photometric
+  data, which can be combined with data available in the future to
+  carry out more rigorous period measurement.}
+
+An important result of our study is the direct measurement of the
+photometric modulation period of a directly imaged planetary-mass
+object.
+
+We infer the rotation period of
 2M1207b to be the same as the period of photometric
@@
 directly imaged planet with an estimated period and measured \vsini,
-field brown dwarfs from the study of \cite[][]{Metchev2015},
+field brown dwarfs from the study of \citet[][]{Metchev2015},
 \revise{and young brown dwarfs (UpSco, age $\sim 11$ Myr) from
-  \cite[][]{Scholz2015}}. \citet[][]{Snellen2014} measured \vsini{}
+  \citet[][]{Scholz2015}}. \citet[][]{Snellen2014} measured \vsini{}
 for \bpic{} b and demonstrated that it fits a trend defined by Solar
@@
 host a circumsubstellar disk \citep{Sterzik2004}, the low mass of
-typical brown dwarf disks \citep[e.g.]{Klein2003, Mohanty2013} and its
+typical brown dwarf disks \citep[e.g.][]{Klein2003, Mohanty2013} and its
 large separation argue against the possibility that 2M1207b has formed
@@
 
-\revise{Rotation period of $\sim 10$
-  hour is significantly larger than field brown dwarfs from the sample
-  of \cite{Metchev2015}, but comparable to the median period
-  of the sample of \cite{Scholz2015}, of which the age is similar
+\revise{ The rotation period of $\sim 10$
+  hour is significantly longer than those of field brown dwarfs from the sample
+  of \cite{Metchev2015}, and the corresponding equatorial rotation
+  speed ($\sim 15\, \mathrm{km\,s^{-1}}$) is lower than most L-type field
+  brown dwarfs \citep[][]{Reiners2008}.
+  In contrast, the rotation period of 2M1207b is similar to the median period
+  of the sample of \cite{Scholz2015}, whose age is similar
   to 2M1207b. The rotation period of 2M1207b
@@
   established from measurements of brown dwarfs assuming conservation
-  of angular momentum (Fig. 4 in \cite{Scholz2015}), and much longer
-  than the break-up limit, i.e. the rotation period where the
-  equatorial centrifugal force exceeded gravitational force. Observed
-  rotation rate for brown dwarfs of different ages show little
-  evidence of angular momentum loss at the age of several Myr as
-  oppose to low mass stars
+  of angular momentum \citep[see Fig. 4 of ][]{Scholz2015}, and much longer
+  than the break-up limit \citep{Marley2011}, i.e. the rotation period where the
+  equatorial centrifugal force exceeds gravitational force. Observed
+  rotation rates for brown dwarfs of different ages show little
+  evidence for angular momentum loss at the age of several Myr in contrast to low-mass stars
   \citep{Bouvier2014, Scholz2015}, and agree with the model of solid
   body rotation for the fully convective interior. Rotation periods of
-planetary mass objects with well established age measurement, can
-place stronger constrain on the internal structure, since angular
-momentum loss through disks is even less likely comparing with brown dwarfs.}
+planetary mass objects with well established age measurements can
+place stronger constrain on their internal structures.}
 
@@
 % momentum evolution of planetary-mass objects and may place powerful
-% constraints on the evolution of the internal structures of these
+% constraineds on the evolution of the internal structures of these
 % contracting objects.
@@
 
-\revise{Recently, \citet{Karalidi2015} published \textit{Aeolus}, an
-atmosphere mapping code that retrieves 2-dimension atmosphere features
-from the light curves. In the future, with higher signal-to-noise
-light curves, we will be able to study more detailed structure of the
-atmospheres of directly imaged exoplanets with this tool. }
+\revise{Recently, \citet{Karalidi2015} showed that an MCMC-optimized
+  light curve modeling tool can correctly retrieve two-dimensional
+  atmospheric features from high quality light curves. In the future,
+  with higher signal-to-noise light curves of planetary mass objects
+  and exoplanets we will be able to map their atmospheres in greater
+  detail.}
 
@@
 in a directly imaged planetary-mass object.  The period is
-$10.2^{+0.9}_{-0.8}$ hours, similar to that derived from \vsini{} 
-measurements for the directly imaged exoplanet \bpic{} b, 
-significantly longer than most field brown dwarfs with known rotation
-periods, and \revise{comparable to  the brown dwarfs
-in a sample with similar age to 2M1207b.} The amplitude ratio of J- and H-band is very
+\period{} hours, similar to that derived from \vsini{} 
+measurements for the directly imaged exoplanet \bpic{} b.
+\revise{The period of 2M1207b is longer than most field brown dwarfs
+  with known rotation period,  but is similar to brown dwarfs
+in a sample with an age similar to that of 2M1207b.} The amplitude ratio of J- and H-band is very
 similar to that of a field brown dwarf with identical L5 spectral type, although they have

### 2015-12-11 summary/letter/letter_vAF.tex
duech

@@
   combined light curve as well as in different subsets of the data.
-  The amplitudes are 1.45\% in the F125W and 0.92\% in the F160W
+  The amplitudes are 1.36\% in the F125W and 0.78\% in the F160W
   filters, respectively. We find a consistent period of
-  $10.2^{+0.9}_{-0.8}$ hours and
+  \period{} hours and
   similar phases in both bands. The J- and H-band amplitude ratio of

### 2015-12-11 summary/letter/letter_vAI.tex
duech

--- 2015-12-11 summary/letter/letter_AH.tex
@@
 \usepackage[dvipsnames]{xcolor}
+\usepackage{multirow}
 \bibliographystyle{apj}
+
 \usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
@@
 \renewcommand{\revise}{}
-\newcommand{\period}{$10.5^{+1.5}_{-0.8}$}
+\newcommand{\reviseTwo}[1]{\textbf{{\color{cyan}{#1}}}}
+\newcommand{\period}{$10.7^{+1.2}_{-0.6}$}
 \newcommand{\Jperiod}{$11.1^{+2.0}_{{-1.2}}$}
+\newcommand{\Jperiodd}{$11.9^{+3.4}_{-1.8}$}
 \newcommand{\Jamp}{$1.36\pm0.23 \%$}
 \newcommand{\Hperiod}{$9.3^{+2.0}_{{-0.8}}$}
+\newcommand{\Hperiodd}{$10.7^{+4.4}_{{-1.4}}$}
 \newcommand{\Hamp}{$0.78\pm0.22 \%$}
@@
   The amplitudes are 1.36\% in the F125W and 0.78\% in the F160W
-  filters, respectively. We find a consistent period of
+  filters, respectively.  \reviseTwo{By fitting sine waves to the
+  light curves,} we find a consistent period of
 \period{} hours and
@@
   measures, for the first time, the rotation period for a directly 
-  imaged planetary-mass companion to another star.
+  imaged \reviseTwo{extra-solar planetary-mass companion.}
 \end{abstract}
@@
 %exposures in each exposure sequence.
-\revise{In each orbit, we took 8 SPARS 10 exposure sequences
-  alternating between F125W and F160W filters. Each sequence contained
-  2--3 identical exposures that had 10 non-destructive read-outs and total
-  exposure time of 88.4 s.} To improve sampling and reduce the risk
+
+\reviseTwo{In each orbit, we used the visibility of 2380s, which allowed us
+  to take eight SPARS10 exposure sequences
+  alternating between the F125W and F160W filter. Each sequence contained
+  2--3 identical exposures of 88.4 s with 10 non-destructive read-outs. The number of exposures were limited by
+  time spent on filter switching and transferring the data from the
+  instrument to the data processing computer.} To improve sampling and reduce the risk
 that the core of point spread function (PSF) is affected by bad
@@
 non-integral (half pixel) step of 10.5 and 8.5 pixels in F125W and
-F160W, respectively. In total, we obtained 70 and 64 images with 10 in
+F160W, respectively. In total, we obtained 70 and 64 images  in
 F125W and F160W, respectively.
@@
     variability verification tests. Individual measurements are
-    plotted with gray crosses. Photometric measurements of the same exposure
-    sequence are binned, and binned photometry are plotted with points
-    or squares. Best fitted sinusoids are plotted with solid
-    lines. {\em Upper}: binned measurements taken in dithering
+    plotted with gray crosses. Photometric measurements of the same
+    exposure sequence are binned, and binned photometry are plotted
+    with points or squares. Best fitted sinusoids are plotted with
+    solid lines. {\em Upper}: binned measurements taken in dithering
     position 1 and 3 (red points) and that taken in 2 and 4 (blue
-    squares) are plotted with different symbols. They demonstrate same
-    trend of modulation. In upper left panel, the green line a sinusoid
-    fitted with all parameters freely varying, and the purple line is
-    a sinusoid fitted with the period set the same as that of
-    F125W. {\em Middle}: sinusoids fitted without using the
-    data taken in Orbit \#1. These curves are almost identical to the
-    curves plotted in upper panel. {\em Lower}: photometry measured
-    with AFEM-added images and best fitted sinul curves. These
-    points and curves are also almost identical to those plotted
-    in the upper panel.}
+    squares) are plotted with different symbols. \reviseTwo{The two halves
+      of data were reduced independently, and show the same modulation
+      trend.} In upper left panel, the green line a sinusoid fitted
+    with all parameters freely varying, and the purple line is a
+    sinusoid fitted with the period set the same as that of
+    F125W. {\em Middle}: sinusoids fitted without using the data taken
+    in Orbit \#1. These curves are almost identical to the curves
+    plotted in upper panel. {\em Lower}: photometry measured with
+    AFEM-added images and best fitted sinul curves. These points and
+    curves are also almost identical to those plotted in the upper
+    panel. \reviseTwo{The slight difference of normalized photometry
+      among panels for the same filters is the result that
+      normalization factors change when omitting the first orbit or when
+      adding artificial noise.}}
   \label{fig:2}
@@
 \begin{equation}
-  \mathrm{residual} = \mathrm{Image} - a\cdot \mathrm{PSF_{A}} - b\cdot
-    \mathrm{PSF_{b}}- c\cdot\mathrm{ Corr}
+  \mathrm{Residual} = \mathrm{Image} - a\times \mathrm{PSF_{A}} - b\times
+    \mathrm{PSF_{b}}- c\times\mathrm{ Corr}
   \end{equation}
@@
 We found that by introducing the correction term,
-the reduced $\chi^{2}$ was decreased from $\sim 10$ to
+the reduced $\chi^{2}$ decreased from $\sim 10$ to
 $\sim 1$. Relative photometry was acquired from the scaling
@@
 Our final step was to correct for a slight apparent trend between the
-position of the targets on the detector and their flux. We attributed
+position of the targets on the detector and their fluxes. We attributed
 this to a combination of slight changes in the PSF profile due to
 pixelation and to the effect of imperfectly corrected pixel-to-pixel
-sensitivity variations. We corrected for these apparent
+sensitivity variations. We corrected for the apparent
 position-dependent flux changes by normalizing each photometric point
@@
 
-\label{Results}
-
   \begin{figure*}
@@
 filters to verify the similarity of the signal in the two bands
-(Figure \ref{fig:2}, top panel). Inconsistent periods or light curve
-shapes would argue against a genuine signal.  We found that the periods
-of the best fit sine waves were similar, \Jperiod{} h for
+(Figure \ref{fig:2}, top panel) \reviseTwo{using an Markov Chain Monte Carlo (MCMC)
+ approach (for detail see \S\ref{sec:MCMC})}. Inconsistent periods or light curve
+shapes would argue against a genuine signal. \reviseTwo{We used
+  sinusoids as examples of the simplest periodic functions.} We found that the periods
+of the best fit sinusoids were similar, \Jperiod{} h for
 F125W and \Hperiod{} h for F160W. These periods are consistent
@@
 very different from all timescales present in our observations
-(dithering timescales, integration times, and orbital timescales).
+(dithering timescales, integration times, and orbital
+timescales). \reviseTwo{We note that the period is close to
+  the total time span of the observation, however, the probability that
+  the period  is equal to or less than the observation time baseline is
+  negligible (see \S\ref{sec:MCMC}).}
 
@@
 significantly fainter in the first orbit (Figure \ref{fig:3}) than in
-the subsequent ones.  Our analysis based on orbits 2--6 found
-essentially identical results to our analysis using the whole 6 orbits, based on
+the subsequent ones.  \reviseTwo{Our analysis based on orbits 2--6 found the
+periods were \Jperiodd{} hours for F125W and \Hperiodd{} hours for F160W, }
+which were almost identical results to our analysis using the whole 6 orbits, based on
 which we conclude that the first less reliable orbit does not affect
@@
 \subsection{Amplitude and Period Measurements}
-
+\label{sec:MCMC}
 % We used a MC method to analyze the light curve, and provided amplitudes
@@
 
-\revise{To further constrain the amplitudes and periods of the light
-  curves, we performed sinusoidal fit using Markov Chain Monte Carlo
-  (MCMC) method.  The priors for the amplitudes, the periods and the
-  phases of the sine waves were all assumed to be uniform
-  distributions. The ranges of the prior distributions were 0 to 5\%
-  for the amplitudes, 2 to 40 hours for the periods, and 0 to $2\pi$
+\revise{To constrain the amplitudes and periods of the light curves,
+  we performed sinusoidal fit using MCMC method.  The priors for the
+  amplitudes, the periods and the phases of the sine waves were all
+  assumed to be uniform distributions. The ranges of the prior
+  distributions were 0 to 5\% for the amplitudes, 2 to 40 hours for
+  the periods, and 0 to $2\pi$
   for the phases. The results of the MCMC fit are shown in Figure
-  \ref{fig:4}. The posterior distributions of the periods and amplitudes
-  are very well constrained for both two filters so that we are able
-  to measure the amplitudes and periods as well as their
+  \ref{fig:4}. The posterior distributions of the periods and
+  amplitudes are very well constrained for both two filters so that we
+  are able to measure the amplitudes and periods as well as their
   uncertainties. For F125W, the amplitude and period are \Jamp{} and
-  \Jperiod{}, respectively, and for F160W, they are \Hamp{} and
-  \Hperiod{}, respectively. We also repeated the fitting excluding data from the
-  first orbit in order to quantitatively assess the influence of these
-  less stable data points. Even in the case of limiting
-  our data to Orbits 2-6, the posterior probability distribution peaks
-  at  periods and amplitudes very similar to those found for the entire dataset,
+  \Jperiod{} \reviseTwo{hours}, respectively, and for F160W, they are
+  \Hamp{} and \Hperiod{} \reviseTwo{hours},
+  respectively. \reviseTwo{Next, to place the strongest constraint on
+    the period of 2M1207b, we jointly fitted the two light curves
+    requiring an identical period for two filters but allowing
+    different phases and amplitudes. The period measured from the
+    posterior distribution of the joint fit is \period{} hours.} We
+  also repeated the fitting excluding data from the first orbit in
+  order to quantitatively assess the influence of these less stable
+  data points. Even in the case of limiting our data to Orbits 2-6,
+  the posterior probability distribution peaks at periods and
+  amplitudes very similar to those found for the entire dataset,
   demonstrating that a periodic solution is preferred with or without
@@
   tail in the probability distribution.}
+
+\reviseTwo{To evaluate the possibility of very long period sinusoids,
+  we integrated the posterior distributions for periods at least
+  2$\sigma$
+  longer than the best fit period, as well as for periods longer than
+  20 hours. For the joint fit, the integrated probabilities are
+  12.68\% longer than and 1.29\% for the period longer than 13.1
+  ($\mathrm{best\, fit + 2}\sigma$)
+  hours and 20 hours, respectively. Given these results we conclude
+  that periods much longer than our baseline are very unlikely.}
 
@@
 \section{Result}
+\label{Results}
 
@@
 fit periods for F125W and F160W are $11.1_{-1.2}^{+2.0}$  and $9.3_{-0.8}^{+2.0}$ hours,
-respectively. We also fitted the two band light curves together forcing the
-periods of two sinusoids to be the same, and obtained a period
-of \period{} hours.
+respectively. Jointly fitting the two light curves gives a period
+measurement of \period{} hours.
 
@@
 and B (Figure \ref{fig:3}). On average, the photometric contrast is
-$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W.
+$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W. We
+provide our photometry result data in Table \ref{tab:F125W}, \ref{tab:F160W}.
 
@@
 We find that the amplitudes in the two bands are
-significantly different. By fitting Gaussians to the MC fit result
+significantly different. By fitting Gaussians to the MCMC fit result
 distributions, we determin that the  amplitude for F125W is
@@
 % system planets and \bpic{} b in the left
-% panel of Figure \ref{fig:5}.  The study by
+% panel of Figure \ref{fig:5}.  The study byf
 % \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
@@
 % formation.
+\reviseTwo{The baseline of our observations is not long enough to
+  cover a complete period of 2M1207b. This should come as no surprise,
+  given the 10-20 hour long periods observed in the Solar System giant
+  planets. Nevertheless, as the observations may cover a large
+  fraction of the complete rotation of 2M1207b, we can derive the
+  probability distribution of the rotation period and the amplitudes
+  (in two bands) based on our data. To do this, we assumed an example
+  of a simplest periodic functions, a sine wave. Approximating
+  periodic or quasi-periodic modulations in light curves with moderate
+  signal-to-noise with sine waves is a common approach \citep[e.g.][]{Buenzli2012}.  We
+  used this approximation and combine it with an MCMC approach in
+  \S\ref{sec:MCMC} to derive posterior probability distributions.}
 
-\reviseTwo{Because the period of modulation is longer than the
-  observation time baseline, the most suitable method to constrain
-  period is to fit the light curves with physical viable model. The light curve of a planetary mass
-  companion is either a complete flat line, or a periodical curve with
-  constant mean for which a sine wave is the most simple form. On the contrary,
-  2M1207b is not likely to constantly getting bright or faint. The
-  flatness of the light curves of 2M1207A demonstrate that there is no
-  instrumental sensitivity drift or any similar effect that can
-  introduce a $\sim9$ hour slope. We do include very 
-  long period sinusoid as possible solution for our MC fit, and
-  demonstrate that a sinusoid with period of $\sim10$
+\reviseTwo{Before discussing our MCMC results for completeness we
+  discuss why other, non-periodic functions cannot be considered
+  adequate fits to our data. We can exclude a flat (zero slope)
+  lightcurve due to its poor fit (reduced $\chi^{2}$=117.3/69,
+  76.9/63 for F125W and F160W, respectively). A constant, but non-zero
+  slope line provides an improved reduced $\chi^{2}$,
+  but is not a physically viable model: 2M1207b's time-averaged
+  brightness cannot rapidly increase or decline. A linear decline or
+  brightening that is not intrinsic but instrumental in nature can be
+  excluded for three reasons: 1) the simultaneously observed 2M1207A
+  shows no such modulation; 2) the signal is consistent between
+  different filters and different
+  parts of the dataset; 3) all known HST thermal responses occur on
+  timescales of 1 orbit or shorter \citep{Lallo2005}, inconsistent
+  with the modulations in our data. Given that the linear models are
+  inconsistent with our data or not physically viable, and the sine
+  waves used in our MCMC fits provide lower reduced $\chi^{2}$ than any of
+  the linear models in both filters, we adopt those as the simplest
+  description of the modulations.  We include sine waves of period as
+  long as 40 hours as possible solutions for our MCMC fit to consider
+  the possibility of very long period variations. We find that a
+  sinusoid with a period of $\sim 11$
   hour is the most probable solution with or without including data
-  from the first orbit. In the paper, we include the whole photometric
-  data, which can be combined with data available in the future to
-  carry out more rigorous period measurement.}
+  from the first orbit. When jointly fitting F125W and F160W light
+  curves with sinusoids with the same period but independent amplitudes and
+  phases, the integrated posterior distributions for periods at least 2-$\sigma$
+  larger than the best fit period is 12.7\%, and that for period
+  longer than 20 hours is only 1.3\%. Therefore, our observations exclude
+  the possibility of a very long period (p$>$20 hours) at a high
+  confidence level. Nevertheless, the period measurement should be further
+  constrained in the future  when light curves with full phase
+  coverage are available.}
 
-An important result of our study is the direct measurement of the
+The direct measurement of the
 photometric modulation period of a directly imaged planetary-mass
-object.
-
+object is an import result of our study.
+% \revise{Although a linear trend can also provide reasonable fit to
+%   the light curves when data from the first orbit are excluded, it is
+%   not a physical viable model. The light curve of a planetary mass
+%   companion is either a complete flat line, or a periodical curve with constant mean. On the contrary,
+%   2M1207b is not likely to constantly getting bright or faint. The
+%   flatness of the light curves of 2M1207A demonstrate that there is no
+%   instrumental sensitivity drift or any similar effect that can
+%   introduce a $\sim9$ hour slope. We do include very 
+%   long period sinusoid as possible solution for our MC fit, and
+%   demonstrate that a sinusoid with period of $\sim10$
+%   hour is the most probable solution with or without including data
+%   from the first orbit.}
 We infer the rotation period of
@@
   to 2M1207b. The rotation period of 2M1207b
-  is agreed within the range predicted by evolutionary track
+  is within the range predicted by evolutionary track
   established from measurements of brown dwarfs assuming conservation
@@
   than the break-up limit \citep{Marley2011}, i.e. the rotation period where the
-  equatorial centrifugal force exceeds gravitational force. Observed
-  rotation rates for brown dwarfs of different ages show little
-  evidence for angular momentum loss at the age of several Myr in contrast to low-mass stars
-  \citep{Bouvier2014, Scholz2015}, and agree with the model of solid
-  body rotation for the fully convective interior. Rotation periods of
+  equatorial centrifugal force exceeds gravitational force. \reviseTwo{Observed
+  rotation rates for brown dwarfs of show little
+  evidence for angular momentum loss 
+  \citep{Bouvier2014, Scholz2015} for the first few Myr of evolution, and agree with the model of solid
+  body rotation. In contrast, young low
+  mass star experience strong angular momentum loss and internal
+  angular momentum redistribution at similar ages.} Rotation periods of
 planetary mass objects with well established age measurements can
-place stronger constrain on their internal structures.}
+\reviseTwo{place  further constraint on the gravitational contraction and
+  angular momentum evolution in the planetary mass regime.}}
 
@@
 object 2M1207b. This is the first detection of rotational modulations
-in a directly imaged planetary-mass object.  The period is
-\period{} hours, similar to that derived from \vsini{} 
+in a directly imaged planetary-mass object.  \reviseTwo{By fitting the
+  sinusoids to the light curves, we find a period of \period{} hours
+  that is 20\% longer than our observation baseline and should be
+  further constrained with full phase coverage in the future.} The
+10.7-hour period is similar to that derived from \vsini{} 
 measurements for the directly imaged exoplanet \bpic{} b.
@@
 support from NSF grant AST1313444.
-\bibliography{ref.bib}
+
+% \bibliography{ref.bib}
+\begin{thebibliography}{52}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{Ackerman \& Marley(2001)}]{Ackerman2001}
+Ackerman, A.~S. \& Marley, M.~S. 2001, ApJ, 556, 872
+
+\bibitem[{{Allard} {et~al.}(2012){Allard}, {Homeier}, \&
+  {Freytag}}]{Allard2012}
+{Allard}, F., {Homeier}, D., \& {Freytag}, B. 2012, Royal Society of London
+  Philosophical Transactions Series A, 370, 2765
+
+\bibitem[{Apai {et~al.}(2013)Apai, Radigan, Buenzli, Burrows, Reid, \&
+  Jayawardhana}]{Apai2013}
+Apai, D., Radigan, J., Buenzli, E., Burrows, A., Reid, I.~N., \& Jayawardhana,
+  R. 2013, ApJ, 768, 121
+
+\bibitem[{{Baraffe} {et~al.}(2003){Baraffe}, {Chabrier}, {Barman}, {Allard}, \&
+  {Hauschildt}}]{Baraffe2003}
+{Baraffe}, I., {Chabrier}, G., {Barman}, T.~S., {Allard}, F., \& {Hauschildt},
+  P.~H. 2003, \aap, 402, 701
+
+\bibitem[{{Barman} {et~al.}(2011){Barman}, {Macintosh}, {Konopacky}, \&
+  {Marois}}]{Barman2011b}
+{Barman}, T.~S., {Macintosh}, B., {Konopacky}, Q.~M., \& {Marois}, C. 2011,
+  \apjl, 735, L39
+
+\bibitem[{Berta {et~al.}(2012)Berta, Charbonneau, D\'{e}sert,
+  {et~al.}}]{Berta2012}
+Berta, Z.~K., Charbonneau, D., D\'{e}sert, J.-M., {et~al.} 2012, ApJ, 747, 35
+
+\bibitem[{{Biller} {et~al.}(2015){Biller}, {Vos}, {Bonavita}, {Buenzli},
+  {Baxter}, {Crossfield}, {Allers}, {Liu}, {Bonnefoy}, {Deacon}, {Brandner},
+  {Schlieder}, {Dupuy}, {Kopytova}, {Manjavacas}, {Allard}, {Homeier}, \&
+  {Henning}}]{Biller2015}
+{Biller}, B.~A., {Vos}, J., {Bonavita}, M., {Buenzli}, E., {Baxter}, C.,
+  {Crossfield}, I.~J.~M., {Allers}, K., {Liu}, M.~C., {Bonnefoy}, M., {Deacon},
+  N., {Brandner}, W., {Schlieder}, J.~E., {Dupuy}, T., {Kopytova}, T.,
+  {Manjavacas}, E., {Allard}, F., {Homeier}, D., \& {Henning}, T. 2015, ArXiv
+  e-prints
+
+\bibitem[{Biretta(2014)}]{Biretta2014}
+Biretta, J. 2014, Space Telescope WFC Instrument Science Report, 1, 10
+
+\bibitem[{Bonnefoy {et~al.}(2014)Bonnefoy, Chauvin, Lagrange, Rojo, Allard,
+  Pinte, Dumas, \& Homeier}]{Bonnefoy2014}
+Bonnefoy, M., Chauvin, G., Lagrange, A.-M., Rojo, P., Allard, F., Pinte, C.,
+  Dumas, C., \& Homeier, D. 2014, A\&A, 562, A127
+
+\bibitem[{Bouvier {et~al.}(2014)Bouvier, Matt, Mohanty, Scholz, Stassun, \&
+  Zanni}]{Bouvier2014}
+Bouvier, J., Matt, S.~P., Mohanty, S., Scholz, A., Stassun, K.~G., \& Zanni, C.
+  2014, Protostars and Planets VI, 1, 433
+
+\bibitem[{Buenzli {et~al.}(2012)Buenzli, Apai, Morley, Flateau, Showman,
+  Burrows, Marley, Lewis, \& Reid}]{Buenzli2012}
+Buenzli, E., Apai, D., Morley, C.~V., Flateau, D., Showman, A.~P., Burrows, A.,
+  Marley, M.~S., Lewis, N.~K., \& Reid, I.~N. 2012, ApJ, 760, L31
+
+\bibitem[{Buenzli {et~al.}(2015)Buenzli, Saumon, Marley, Apai, Radigan, Bedin,
+  Reid, \& Morley}]{Buenzli2015}
+Buenzli, E., Saumon, D., Marley, M.~S., Apai, D., Radigan, J., Bedin, L.~R.,
+  Reid, I.~N., \& Morley, C.~V. 2015, ApJ, 798, 127
+
+\bibitem[{{Burgasser} {et~al.}(2013){Burgasser}, {Sheppard}, \&
+  {Luhman}}]{Burgasser2013}
+{Burgasser}, A.~J., {Sheppard}, S.~S., \& {Luhman}, K.~L. 2013, ApJ, 772, 129
+
+\bibitem[{Burrows {et~al.}(2006)Burrows, Sudarsky, \& Hubeny}]{Burrows2006a}
+Burrows, A., Sudarsky, D., \& Hubeny, I. 2006, ApJ, 640, 1063
+
+\bibitem[{{Chauvin} {et~al.}(2004){Chauvin}, {Lagrange}, {Dumas}, {Zuckerman},
+  {Mouillet}, {Song}, {Beuzit}, \& {Lowrance}}]{Chauvin2004}
+{Chauvin}, G., {Lagrange}, A.-M., {Dumas}, C., {Zuckerman}, B., {Mouillet}, D.,
+  {Song}, I., {Beuzit}, J.-L., \& {Lowrance}, P. 2004, \aap, 425, L29
+
+\bibitem[{{Chauvin} {et~al.}(2005){Chauvin}, {Lagrange}, {Dumas}, {Zuckerman},
+  {Mouillet}, {Song}, {Beuzit}, \& {Lowrance}}]{Chauvin2005}
+---. 2005, \aap, 438, L25
+
+\bibitem[{Chauvin {et~al.}(2005)Chauvin, Lagrange, Zuckerman, Dumas, Mouillet,
+  Song, Beuzit, Lowrance, \& Bessell}]{Chauvin2005b}
+Chauvin, G., Lagrange, A.-M., Zuckerman, B., Dumas, C., Mouillet, D., Song, I.,
+  Beuzit, J.-L., Lowrance, P., \& Bessell, M.~S. 2005, A{\&}A, 438, L29
+
+\bibitem[{{Currie} {et~al.}(2011){Currie}, {Burrows}, {Itoh}, {Matsumura},
+  {Fukagawa}, {Apai}, {Madhusudhan}, {Hinz}, {Rodigas}, {Kasper}, {Pyo}, \&
+  {Ogino}}]{Currie2011}
+{Currie}, T., {Burrows}, A., {Itoh}, Y., {Matsumura}, S., {Fukagawa}, M.,
+  {Apai}, D., {Madhusudhan}, N., {Hinz}, P.~M., {Rodigas}, T.~J., {Kasper}, M.,
+  {Pyo}, T.-S., \& {Ogino}, S. 2011, \apj, 729, 128
+
+\bibitem[{Dressel(2012)}]{dressel2012wide}
+Dressel, L. 2012, Wide Field Camera 3, HST Instrument Handbook, 1
+
+\bibitem[{{Ducourant} {et~al.}(2008){Ducourant}, {Teixeira}, {Chauvin},
+  {Daigne}, {Le Campion}, {Song}, \& {Zuckerman}}]{Ducourant2008}
+{Ducourant}, C., {Teixeira}, R., {Chauvin}, G., {Daigne}, G., {Le Campion},
+  J.-F., {Song}, I., \& {Zuckerman}, B. 2008, \aap, 477, L1
+
+\bibitem[{{Heinze} {et~al.}(2015){Heinze}, {Metchev}, \&
+  {Kellogg}}]{Heinze2015}
+{Heinze}, A.~N., {Metchev}, S., \& {Kellogg}, K. 2015, \apj, 801, 104
+
+\bibitem[{Helling {et~al.}(2008)Helling, Ackerman, Allard, Dehn, Hauschildt,
+  Homeier, Lodders, Marley, Rietmeijer, Tsuji, \& Woitke}]{Helling2008}
+Helling, C., Ackerman, A., Allard, F., Dehn, M., Hauschildt, P., Homeier, D.,
+  Lodders, K., Marley, M., Rietmeijer, F., Tsuji, T., \& Woitke, P. 2008,
+  MNRAS, 391, 1854
+
+\bibitem[{{Karalidi} {et~al.}(2015){Karalidi}, {Apai}, {Schneider}, {Hanson},
+  \& {Pasachoff}}]{Karalidi2015}
+{Karalidi}, T., {Apai}, D., {Schneider}, G., {Hanson}, J.~R., \& {Pasachoff},
+  J.~M. 2015, ArXiv e-prints
+
+\bibitem[{{Klein} {et~al.}(2003){Klein}, {Apai}, {Pascucci}, {Henning}, \&
+  {Waters}}]{Klein2003}
+{Klein}, R., {Apai}, D., {Pascucci}, I., {Henning}, T., \& {Waters},
+  L.~B.~F.~M. 2003, \apjl, 593, L57
+
+\bibitem[{{Kostov} \& {Apai}(2013)}]{Kostov2013}
+{Kostov}, V. \& {Apai}, D. 2013, \apj, 762, 47
+
+\bibitem[{Kreidberg {et~al.}(2014)Kreidberg, Bean, D\'{e}sert,
+  {et~al.}}]{Kreidberg2014}
+Kreidberg, L., Bean, J.~L., D\'{e}sert, J.-M., {et~al.} 2014, Nature, 505, 69
+
+\bibitem[{Krist(1995)}]{Krist1995}
+Krist, J. 1995, in Astronomical Data Analysis Software and Systems IV, Vol.~77,
+  349
+
+\bibitem[{{Lallo} {et~al.}(2005){Lallo}, {Makidon}, {Casertano}, {Gilliland},
+  \& {Stys}}]{Lallo2005}
+{Lallo}, M., {Makidon}, R.~B., {Casertano}, S., {Gilliland}, R., \& {Stys}, J.
+  2005, {HST Temporal Optical Behavior and Current Focus Status}, Tech. rep.
+
+\bibitem[{Lodato {et~al.}(2005)Lodato, Delgado-Donate, \& Clarke}]{Lodato2005}
+Lodato, G., Delgado-Donate, E., \& Clarke, C.~J. 2005, Mon. Not. R. Astron.
+  Soc. Lett., 364, L91
+
+\bibitem[{{MacKenty} {et~al.}(2008){MacKenty}, {Kimble}, {O'Connell}, \&
+  {Townsend}}]{Mackenty2008}
+{MacKenty}, J.~W., {Kimble}, R.~A., {O'Connell}, R.~W., \& {Townsend}, J.~A.
+  2008, in Society of Photo-Optical Instrumentation Engineers (SPIE) Conference
+  Series, Vol. 7010, Society of Photo-Optical Instrumentation Engineers (SPIE)
+  Conference Series, 1
+
+\bibitem[{{Madhusudhan} {et~al.}(2011){Madhusudhan}, {Burrows}, \&
+  {Currie}}]{Madhusudhan2011}
+{Madhusudhan}, N., {Burrows}, A., \& {Currie}, T. 2011, \apj, 737, 34
+
+\bibitem[{Mandell {et~al.}(2013)Mandell, Haynes, Sinukoff,
+  {et~al.}}]{Mandell2013}
+Mandell, A.~M., Haynes, K., Sinukoff, E., {et~al.} 2013, ApJ, 779, 128
+
+\bibitem[{{Marley} {et~al.}(2012){Marley}, {Saumon}, {Cushing}, {Ackerman},
+  {Fortney}, \& {Freedman}}]{Marley2012}
+{Marley}, M.~S., {Saumon}, D., {Cushing}, M., {Ackerman}, A.~S., {Fortney},
+  J.~J., \& {Freedman}, R. 2012, \apj, 754, 135
+
+\bibitem[{{Marley} {et~al.}(2010){Marley}, {Saumon}, \&
+  {Goldblatt}}]{Marley2010}
+{Marley}, M.~S., {Saumon}, D., \& {Goldblatt}, C. 2010, \apjl, 723, L117
+
+\bibitem[{{Marley} \& {Sengupta}(2011)}]{Marley2011}
+{Marley}, M.~S. \& {Sengupta}, S. 2011, \mnras, 417, 2874
+
+\bibitem[{Marois {et~al.}(2008)Marois, Macintosh, Barman, Zuckerman, Song,
+  Patience, Lafreni\`{e}re, \& Doyon}]{Marois2008a}
+Marois, C., Macintosh, B., Barman, T., Zuckerman, B., Song, I., Patience, J.,
+  Lafreni\`{e}re, D., \& Doyon, R. 2008, Science, 322, 1348
+
+\bibitem[{Marois {et~al.}(2010)Marois, Zuckerman, Konopacky, Macintosh, \&
+  Barman}]{Marois2010}
+Marois, C., Zuckerman, B., Konopacky, Q.~M., Macintosh, B., \& Barman, T. 2010,
+  Nature, 468, 1080
+
+\bibitem[{Metchev {et~al.}(2015)Metchev, Heinze, Apai, Flateau, Radigan,
+  Burgasser, Marley, Artigau, Plavchan, \& Goldman}]{Metchev2015}
+Metchev, S.~A., Heinze, A., Apai, D., Flateau, D., Radigan, J., Burgasser, A.,
+  Marley, M.~S., Artigau, E., Plavchan, P., \& Goldman, B. 2015, ApJ, 799, 154
+
+\bibitem[{{Mohanty} {et~al.}(2013){Mohanty}, {Greaves}, {Mortlock}, {Pascucci},
+  {Scholz}, {Thompson}, {Apai}, {Lodato}, \& {Looper}}]{Mohanty2013}
+{Mohanty}, S., {Greaves}, J., {Mortlock}, D., {Pascucci}, I., {Scholz}, A.,
+  {Thompson}, M., {Apai}, D., {Lodato}, G., \& {Looper}, D. 2013, \apj, 773,
+  168
+
+\bibitem[{Mohanty {et~al.}(2007)Mohanty, Jayawardhana, Huelamo, \&
+  Mamajek}]{Mohanty2007}
+Mohanty, S., Jayawardhana, R., Huelamo, N., \& Mamajek, E. 2007, ApJ, 657, 1064
+
+\bibitem[{Patience {et~al.}(2010)Patience, King, {De Rosa}, \&
+  Marois}]{Patience2010}
+Patience, J., King, R.~R., {De Rosa}, R.~J., \& Marois, C. 2010, A\&A, 517, A76
+
+\bibitem[{Radigan {et~al.}(2012)Radigan, Jayawardhana, Lafreni\`{e}re, Artigau,
+  Marley, \& Saumon}]{Radigan2012}
+Radigan, J., Jayawardhana, R., Lafreni\`{e}re, D., Artigau, E., Marley, M., \&
+  Saumon, D. 2012, ApJ, 750, 105
+
+\bibitem[{{Reiners} \& {Basri}(2008)}]{Reiners2008}
+{Reiners}, A. \& {Basri}, G. 2008, \apj, 684, 1390
+
+\bibitem[{Scholz {et~al.}(2015)Scholz, Kostov, Jayawardhana, \&
+  Mu{\v{z}}i{\'{c}}}]{Scholz2015}
+Scholz, A., Kostov, V., Jayawardhana, R., \& Mu{\v{z}}i{\'{c}}, K. 2015, ApJ,
+  809, L29
+
+\bibitem[{{Showman} \& {Kaspi}(2013)}]{Showman2013}
+{Showman}, A.~P. \& {Kaspi}, Y. 2013, \apj, 776, 85
+
+\bibitem[{{Skemer} {et~al.}(2011){Skemer}, {Close}, {Sz{\H u}cs}, {Apai},
+  {Pascucci}, \& {Biller}}]{Skemer2011}
+{Skemer}, A.~J., {Close}, L.~M., {Sz{\H u}cs}, L., {Apai}, D., {Pascucci}, I.,
+  \& {Biller}, B.~A. 2011, \apj, 732, 107
+
+\bibitem[{{Skemer} {et~al.}(2012){Skemer}, {Hinz}, {Esposito}, {Burrows},
+  {et~al.}}]{Skemer2012}
+{Skemer}, A.~J., {Hinz}, P.~M., {Esposito}, S., {Burrows}, A., {et~al.} 2012,
+  \apj, 753, 14
+
+\bibitem[{Snellen {et~al.}(2014)Snellen, Brandl, de~Kok, Brogi, Birkby, \&
+  Schwarz}]{Snellen2014}
+Snellen, I. A.~G., Brandl, B.~R., de~Kok, R.~J., Brogi, M., Birkby, J., \&
+  Schwarz, H. 2014, Nature, 509, 63
+
+\bibitem[{Song {et~al.}(2006)Song, Schneider, Zuckerman, Farihi, Becklin,
+  Bessell, Lowrance, \& Macintosh}]{Song2006}
+Song, I., Schneider, G., Zuckerman, B., Farihi, J., Becklin, E.~E., Bessell,
+  M.~S., Lowrance, P., \& Macintosh, B.~A. 2006, ApJ, 652, 724
+
+\bibitem[{{Sterzik} {et~al.}(2004){Sterzik}, {Pascucci}, {Apai}, {van der
+  Bliek}, \& {Dullemond}}]{Sterzik2004}
+{Sterzik}, M.~F., {Pascucci}, I., {Apai}, D., {van der Bliek}, N., \&
+  {Dullemond}, C.~P. 2004, \aap, 427, 245
+
+\bibitem[{{Yang} {et~al.}(2015){Yang}, {Apai}, {Marley}, {Saumon}, {Morley},
+  {Buenzli}, {Artigau}, {Radigan}, {Metchev}, {Burgasser}, {Mohanty},
+  {Lowrance}, {Showman}, {Karalidi}, {Flateau}, \& {Heinze}}]{Yang2015}
+{Yang}, H., {Apai}, D., {Marley}, M.~S., {Saumon}, D., {Morley}, C.~V.,
+  {Buenzli}, E., {Artigau}, {\'E}., {Radigan}, J., {Metchev}, S., {Burgasser},
+  A.~J., {Mohanty}, S., {Lowrance}, P.~J., {Showman}, A.~P., {Karalidi}, T.,
+  {Flateau}, D., \& {Heinze}, A.~N. 2015, \apjl, 798, L13
+
+\bibitem[{{Zhang} \& {Showman}(2014)}]{Zhang2014}
+{Zhang}, X. \& {Showman}, A.~P. 2014, \apjl, 788, L6
+
+\end{thebibliography}
+
+\clearpage
+\appendix
+\LongTables
+\input{F125W.tex}
+\input{F160W.tex}
+
 \end{document}

### 2015-12-11 summary/letter/ms/ms.tex
duech

--- 2015-12-11 summary/letter/letter_vAI.tex
@@
 \newcommand{\reviseTwo}[1]{\textbf{{\color{cyan}{#1}}}}
+\renewcommand{\reviseTwo}{}
 \newcommand{\period}{$10.7^{+1.2}_{-0.6}$}
@@
   \centering
-  \plottwo{original}{subtracted}\\
-  \includegraphics[width=0.32\textwidth]{TT_2M1207A}
-  \includegraphics[width=0.32\textwidth]{TT_2M1207b}
-  \includegraphics[width=0.32\textwidth]{TT_residual}
+  \plottwo{fig1a}{fig1b}\\
+  \includegraphics[width=0.32\textwidth]{fig1c}
+  \includegraphics[width=0.32\textwidth]{fig1d}
+  \includegraphics[width=0.32\textwidth]{fig1e}
   \caption{Point spread function subtraction allows isolating the
@@
       the primary and the secondary, and the correction map.}
-    % {\em Upper}: original image, the position of 2M1207
-    % b is indicated by a white circle.  {\em Lower:} residual image --
-    % after the subtraction of the hybrid PSF, 2M1207b is detected at a
-    % high significance level.
   }
@@
   \centering
-  \plotone{systematics}
+  \plotone{fig2}
   \caption{F125W (left) and F160W (right) light curves under different
@@
   \centering
-  \plotone{sineCurveFit_binCombined}
+  \plotone{fig3}
   \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
@@
 \label{sec:MCMC}
-% We used a MC method to analyze the light curve, and provided amplitudes
-% and periods as well as their uncertainties for both filters. We
-% generated series of Gaussian distributed random noise with standard deviation
-% same as the photon noise, added the noise to the original light curves, and
-% fitted sinusoids to the newly combined light curves. We repeated these
-% procedures  for 100,000 times and obtain the distributions of period
-% and amplitude (Figure \ref{fig:4}).
 
@@
   \centering
-\plotone{posterior_dist}
+\plotone{fig4}
   \caption{\revise{Posterior distributions for amplitudes and periods for F125W
@@
 
-% \revise{We note that if the data from the first orbit were excluded, the
-%   light curves could be reasonably fitted to a linear trend. When ignoring
-%   data from the first orbit, For F125W light
-%   curve, the reduced  $\chi^{2}$ for sinusoidal and linear fits are
-%   1.138 and 1.143, and for F160W are 0.944 and 0.953. However, We are
-%   in favor of the sinusoidal model based on physical viability (See
-%   detailed discussion in \S\ref{sec:discussion}). }
-
 \section{Result}
@@
 
-%  With 64\% confidence,
-% we estimate the 1-$\sigma$ range for the periods of F125W and F160W
-% to be  and  h,
-% respectively. The period of best fitted sinusoid for F125W light curve
-% is 1.5h longer than that for F160W, which is $\sim 20\%$ larger than
-% 1-$\sigma$. We also jointly fit the two band light curves forcing the
-% periods of two sinusoids to be the same. We derive a modulation period of $10.2^{+0.9}_{-0.8}$ h.
-
 We find that the amplitudes in the two bands are
@@
   \centering
-  \plottwo{rotationDiagram}{JH}
+  \plottwo{fig5a}{fig5b}
   \caption{comparison of 2M1207's rotation period and color change
@@
 
-% Although rotation
-% rates may have limited value for deciphering formation pathways,
-% measurements of mass, age, and rotation periods will map the angular
-% momentum evolution of planetary-mass objects and may place powerful
-% constraineds on the evolution of the internal structures of these
-% contracting objects.
-%{\em Add younger BDs and this may change}
-% Excitingly, our measurement of the rotation period demonstrates that
-% 2M1207b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
-% that fits in the same trend, as well as majority of brown
-% dwarfs. We note that 2M1207b is most likely formed in the same way as brown
-% dwarfs by gravitational fragmentation, which suggests
-% that rotation periods are not good tracers of the formation pathways
-% and may not contribute important evidence for a formation in a disk
-% vs. in a cloud core environment.
-
 Our inferred rotation period is very similar to those of Jupiter and
@@
 
-Support for program number 13418 was provided by NASA through a grant
-from the Space Telescope Science Institute, which is operated by the
-Association of Universities for Research in Astronomy, Inc., under
-NASA contract NAS5-26555. The results reported herein benefited from
-collaborations and/or information exchange within NASA's Nexus for
-Exoplanet System Science (NExSS) research coordination network
-sponsored by NASA's Science Mission Directorate. M.S.M. acknowledges
-support from the NASA Astrophysics Theory Program. A.P.S. acknowledges
-support from NSF grant AST1313444.
+We thank the anonymous referee for the suggestions that are helpful
+for improving the manuscript. Support for program number 13418 was
+provided by NASA through a grant from the Space Telescope Science
+Institute, which is operated by the Association of Universities for
+Research in Astronomy, Inc., under NASA contract NAS5-26555. The
+results reported herein benefited from collaborations and/or
+information exchange within NASA's Nexus for Exoplanet System Science
+(NExSS) research coordination network sponsored by NASA's Science
+Mission Directorate. M.S.M. acknowledges support from the NASA
+Astrophysics Theory Program. A.P.S. acknowledges support from NSF
+grant AST1313444.
 
